### 2020-04-21 2020_EFM_MPM_Eigensoftening.tex
first commit

\documentclass[preprint,12pt,a4paper]{elsarticle}

\usepackage{lineno,hyperref}
\usepackage{float}
\usepackage{subfig}
\usepackage{color}
\usepackage{soul}

\usepackage{algcompatible}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{algpseudocode}

\usepackage{cancel}

\usepackage{amsmath,amsthm,amssymb}

\newcommand{\vec}[1]{
  \ensuremath{\mathbf{{#1}}}
}
\newcommand{\tens}[1]{
  \ensuremath{\mathbf{{#1}}}
}
\newcommand{\Matrix}[1]{
  \ensuremath{\mathbf{{#1}}}
}
\newcommand{\Vector}[1]{
  \ensuremath{\mathbf{{#1}}}
}
% Divergence
\newcommand{\Div}[1]{
  \ensuremath{div({#1})}
}
% Gradient
\newcommand\Grad[1]{grad({#1})}
\newcommand\GradS[1]{grad^s({#1})}
\newcommand\GradT[1]{grad^T({#1})}
% Partial derivative
\newcommand{\Deriv}[3][]{
  \ensuremath{\frac{\partial^{#1}{#2}}{ \partial {#3}^{#1} }}
}
% Integral
\newcommand{\Integral}[2]{
  \IfStrEqCase{#1}{
    {2}{\ensuremath{\int_{\varGamma_d}{#2}\ d\varGamma}}
    {3}{\ensuremath{\int_{\varOmega}{#2}\ d\varOmega}}
  }
}

\modulolinenumbers[5]

\journal{Engineering Fracture Mechanics}

%%%%%%%%%%%%%%%%%%%%%%%
%% Elsevier bibliography styles
%%%%%%%%%%%%%%%%%%%%%%%
%% To change the style, put a % in front of the second line of the current style and
%% remove the % from the second line of the style you would like to use.
%%%%%%%%%%%%%%%%%%%%%%%

%% Numbered
%\bibliographystyle{model1-num-names}

%% Numbered without titles
%\bibliographystyle{model1a-num-names}

%% Harvard
%\bibliographystyle{model2-names.bst}\biboptions{authoryear}

%% Vancouver numbered
%\usepackage{numcompress}\bibliographystyle{model3-num-names}

%% Vancouver name/year
%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}

%% APA style
%\bibliographystyle{model5-names}\biboptions{authoryear}

%% AMA style
%\usepackage{numcompress}\bibliographystyle{model6-num-names}

%% `Elsevier LaTeX' style
\bibliographystyle{elsarticle-num}
%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{frontmatter}

\title{LME-MPM applied to quasi-brittle fracture.}

%% Group authors per affiliation:
\author{
Miguel Molinos$^a$\footnote{Corresponding author: m.molinos@outlook.es},
and Pedro Navas$^a$\footnote{Corresponding author: p.navas@upm.es}
 }
 \address{
 $^a$ ETSI Caminos, Canales y Puertos, Universidad Polit\'ectnica de Madrid.\\ c. Prof. Aranguren 3, 28040 Madrid, Spain
}

\begin{abstract}

  The objective of this work is to introduce an alternative
  technique to address the fracture process of brittle and
  quasi-brittle materials under the material point method (MPM)
  framework. With this purpose the eigensoftening algorithm, developed
  originally for the optimal transportation meshfree (OTM)
  approximation scheme, is extended to the MPM with the aim of present
  a suitable alternative to the existing fracture algorithms developed
  for the MPM. The good fitting in the predictions made by the
  eigensoftening algorithm against both analytical and experimental
  results proofs the well performance of the method under challenging loads.

\end{abstract}

\begin{keyword}
Quasi brittle fracture \sep Local-\textit{max-ent} approximation \sep
Material Point Method \sep Solid Dynamics
\end{keyword}

\end{frontmatter}

\linenumbers

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:1}

The simulation of fracture propagation in a more accurate and
effective way can be considered as one of the original drivers for
developing novel spatial discretization methods such as meshfree
methods like the material point method (MPM). Presence of cracks are a violation of the
continuity requirement of the finite element approach (MPM).

The MPM does not suffer from the above difficulties. Discontinuities
can be described in two ways. One is to abandon the single-valued
velocity field property near the crack by using two or more background
meshes, and the other is to use failed material points to
approximately describe the crack.

In the first approach,

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The meshfree methodology}
\label{sec:2}

The popularity of MPM has increase notoriously during the recent years
due to its ability to deal with large strain problems without mesh
distorsion issues inherent to mesh based methods like FEM, see
Zdzislaw \cite{Wieckowski2004}. However, in the simulations made with
the original MPM, there are numerical noises when particles crossing
the cell boundaries.

\subsection{The Material Point Method}
\label{sec:2.1}

For the spatial discretization, two sets of points are introduced in
the MPM. First, the nodes, this points are considered fixed in the space and are in charge of
computing all the kinematic fields such forces $f_I$, accelerations $a_I$ and
velocities $v_I$. And second the material points or particles. They are in
charge of the discretization of the continuum, and store the local state ($\sigma_p, \varepsilon_p$).

\subsection{Spatial discretization : Local-\textit{max-ent} approximants}
\label{sec:2.2}

Local maximum-entropy (or local \textit{max-ent}) approximation scheme
was introduced by Arroyo \& Ortiz (2006)\cite{Arroyo2006} as a bridge
between finite elements and meshfree methods. The key idea of the 
shape functions is to interpret the nodal of a shape function $N_I$ as
a probability. This allow us to introduce two important limits:
the principle of maximum-entropy (\textit{max-ent}) statistical
inference stated by \cite{Jaynes1957}, and the Delaunay triangulation
which ensures the minimal width of the shape function. To reach to a compromise between two competing objectives, a Pareto set is defined as, 
\begin{align*}
  \label{eq:LME-scheme-pareto-set}
  \text{(LME)}_{\beta} \hspace{0.15cm} &\text{For fixed} \hspace{0.15cm}
  \vec{x} \hspace{0.15cm} \text{minimise} \hspace{0.15cm} f_{\beta}(\vec{x}_p, N_I) = \beta U(\vec{x}_p,N_I) - H(N_I) \\
  &\text{subject to}\
  \begin{cases}
    N_I \ge 0, \hspace{0.15cm} \text{I=1, ..., n} \\[1em]   
    \sum\limits_{I=1}^{N_n}{N_I} = 1 \\[1em]   
    \sum\limits_{I=1}^{N_n}{N_I \vec{x}_I} = \vec{x} \\
  \end{cases}
\end{align*}
where $H(N_I)$ is the entropy of the system of nodes following the
definition given by Shannon (1948) \cite{Shannon1948}, and $U(\vec{x}_p,N_I) =
\sum_I N_I |\vec{x}_p - \vec{x}_I |^2$ a magnitude of the shape
function width. The regularization o \textit{thermalization} parameter
between the two criterion $\beta$ has Pareto optimal values in the range
$(0,\infty)$. The unique solution of the local max-ent problem
(LME)$_\beta$ is:
\begin{equation}
  \label{eq:LME-p}
N_I^*(\vec{x})=\frac{\exp\left[ -\beta \; |\vec{x}-\vec{x}_I|^2 +
    \vec{\lambda}^* \cdot (\vec{x}-\vec{x}_I) \right] } {Z(\vec{x},\vec{\lambda}^*(\vec{x}))}
\end{equation}
where $Z(\vec{x},\vec{\lambda}^*(\vec{x}))$ is the \textit{partition
  function} defined as,
\begin{equation}
  \label{eq:LME-Z}
Z(\vec{x}, {\vec{\lambda}}) = \sum_{I=1}^{N_n}{ \exp \left[ -\beta \; |\vec{x}-\vec{x}_I|^2 + \vec{\lambda} \cdot (\vec{x}-\vec{x}_I)  \right]}
\end{equation}
and evaluated in the unique minimiser $\vec{\lambda}^*(\vec{x})$ for
the function $\log
Z(\vec{x}, \vec{\lambda})$. The traditional way to obtain such a
minimiser is using (\ref{eq:LME-J}) to calculate small increments of $\partial\vec{\lambda}$ in a
Newton-Raphson approach. Where $\tens{J}$ is the Hessian matrix, defined by:
\begin{eqnarray}
  \label{eq:LME-J} 
  \tens{J}(\vec{x}, \vec{\lambda},\beta) &\equiv& \frac{\partial
                                                  \vec{r}}{\partial \vec{\lambda}}\\
  \label{eq:LME-r}
  \vec{r}(\vec{x},\vec{\lambda},\beta) &\equiv& \frac{\partial \log{ Z(   \vec{x},\vec{\lambda}})}{\partial \vec{\lambda}}  = \sum_I^{N_n} p_I(\vec{x},\vec{\lambda},\beta) \, (\vec{x} - \vec{x}_I)
\end{eqnarray}
In order to obtain the first derivatives of the shape function~$\nabla
N^*_I$, can be computed as,
\begin{equation}
  \label{eq:LME-grad-p}
\nabla N^*_I = N^*_I  \, \left(\nabla f^*_I-\sum_J^{N_n} N^*_J \, \nabla f^*_J\right)
\end{equation}
where
\begin{equation}
  \label{eq:LME-f}
f^*_I(\vec{x},  \vec{\lambda},\beta)=-\beta \, |\vec{x}-\vec{x}_I|^2 + \vec{\lambda}^*  \,  (\vec{x}-\vec{x}_I)
\end{equation}
Employing the chain rule over \eqref{eq:LME-grad-p}, rearranging and considering $\beta$ as a
constant, Arroyo and Ortiz~\cite{Arroyo2006} obtained the following
expression for the gradient of the shape function.
\begin{eqnarray}
  \label{eq:LME-gradp} 
\nabla N^*_I &=& -N^*_I \,  (\tens{J}^*)^{-1} \,  (\vec{x} - \vec{x}_I)
\end{eqnarray}

The regularization parameter $\beta$ of LME shape functions may be
controlled by adjusting a dimensionless parameter, $\gamma=\beta h^2$
\cite{Arroyo2006}, where $h$ is defined as a measure of the nodal
spacing. Since  $N_I$ is defined in the entire domain, in practice,
the shape function decay $\exp(-\beta \vec{r} )$ is truncated  by  a
given tolerance, 10$^{-6}$, for example,  would ensure a reasonable range of
neighbours, see \cite{Arroyo2006} for details. This tolerance defines
the limit values of the influence radius and is used thereafter to
find the neighbour nodes of a given integration point.

\subsection{Temporal discretization}
\label{sec:2.3}

This research is devoted to capture the challenging process of
fracture during high velocity impacts. To capture the presence of
elastic shock waves triggered by the fracture process. Here we adopt
a explicit predictor-corrector time integration
scheme. It is based in the Newmark a-form 
$\gamma = 0.5$ and $\beta = 0$ which is the central difference
explicit. In a first stage, the nodal velocity predictor is computed
following \eqref{eq:Predictor-velocity}, 
\begin{equation}
  \label{eq:Predictor-velocity}
  \vec{\tilde{v}}_I^{k+1} = \frac{ N_{Ip}^{k} m_p (\vec{v}_p^k + (1 - \gamma)\ \Delta t\ \vec{a}_p^k)}{m_I}
\end{equation}
This way of computing the nodal predictor is both numerically stable
and minimize the computational effort. Once nodal velocity are
obtained, the essential boundary conditions are imposed. And in the
following, the ``classic'' MPM algorithm continues to reach to the
equilibrium equation \eqref{eq:particle_balance_forces3}. Here we
continue with the \textit{corrector} stage, due to the fact that we
already have nodal velocity, this step is computed in the same way as
in FEM,
\begin{equation}
  \label{eq:Corrector-velocity}
  \vec{v}_{I}^{k+1} = \vec{v}_{I}^{pred} + \gamma\ \Delta t\ \frac{\vec{f}_{I}^{k+1}}{\tens{m}_I^{k+1}}
\end{equation}
Finally updated particle kinetics are computed using nodal values as,
\begin{align}
  \label{eq:Update-lagrangian-pce}
        &\vec{a}_p^{k+1} = \frac{N_{Ip}^k\vec{f}_{I}^{k}}{\tens{m}_I^k}\\
      &\vec{v}_p^{k+1} = \vec{v}_p^n + \Delta t\
        \frac{N_{Ip}^k\
        \vec{f}_{I}^{k}}{\tens{m}_I^k}\\
      &\vec{x}_p^{k+1} = \vec{x}_p^n + \Delta t\
         N_{Ip}^k\ \vec{v}_{I}^{k} +
        \frac{1}{2}\Delta t^2\ \frac{N_{Ip}^k\
        \vec{f}_{I}^{k}}{\tens{m}_I^k} 
\end{align}
The complete pseudo-algorithm it is summarized in \ref{sec:expl-pred-corr}.

\subsection{Fracture modelling approach}
\label{sec:2.4}

Within the context of MPM formulation, fracture can be modelled by
failing particles according to a suitable criterion. When material
points are failed, they are assumed to have a null stress
tensor. Navas {\it et al.} (2017)\cite{Navas_2017_ES} developed a
eigensoftening algorithm as an extension for quasi-brittle materials
of the eigenerosion proposed by Pandolfi \& Ortiz
(2012)\cite{Pandolfi_2012} for fracture of brittle materials. A
comparison between both in \cite{Navas_2017_ES} shows that
the eigenerosion algorithm significantly overestimates the tensile
stress and the strain peaks, while it captures the forces and crack
patterns accurately. On the other hand eigensoftening algorithm agree
very well with experimental results in all the aspects. Furthermore,
this algorithm has also proof its accuracy for complex fracture
patters such the present in fiber reinforces concrete (FRC),
\cite{Navas_2018_ES}.\\

\begin{align}
  \label{eq:energy-release-EE}
&G_p^{k+1} = \frac{C_{\epsilon}}{m_p^{k+1}}  \sum_{x_q^{k+1} \in
  B_{\epsilon}(x_p^{k+1})} m_q W_q^{k+1}\\
&m_p^{k+1} =  \sum_{x_q^{k+1} \in
  B_{\epsilon}(x_p^{k+1})} m_q  
\end{align}
where $B_{\epsilon}(x_p^{k+1})$ is the sphere of radius $\epsilon$
centered at $x_p^{k+1}$ known as the $\epsilon$-neighborhood of the
material point, $m_p^{k+1}$ is the mass of the neighborhood at step
$k+1$, $W_q^{k+1}$ is the current free-energy density per unit mass as
the material point $x_q^{k+1}$ of the neighborhood, finally
$C_{\epsilon}$ is a normalizing constant. This configuration
conveniently is sketched in Figure \ref{fig:Failed-particles}.
%%%%%%%%%%%
\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{Figures/Particle-failed}
  \caption{Scheme of a linear cohesive law, where the shaded area is
    $G_f$, $f_t$ is the tensile strength, and $w_c$ is the critical
    opening displacement.}
  \label{fig:Failed-particles}
\end{figure}
%%%%%%%%%%%
The material point fails when $G_p^{k+1}$ surpasses a critical energy
release rate that measures the material-specific energy, $G_F$. The
convergence of this approach has been analyzed by Schmidt {\it et al.}
(2009)\cite{Schmidt_2009}, who proof that it converges to the Griffith
fracture when discretization size tends to zero. It is necessary to
point out that when a material point overpass the critical energy, its
contribution to the internal forces vector  is set to zero, but its
contribution to the mass matrix is maintained. The mass of a material
point is discarded only when an eroded material point is not connected
to any nodes.\\

As can be noticed, in the eigenerosion algorithm an energetic
criterion is adopted. Due to that fact, unrealistic stress
concentration (higher than tensile strength) in quasi-brittle materials, see
\cite{Navas_2017_ES}. To overcome this limitation, the aforementioned
authors proposed the concept of eigensoftening to take in to account
the gradual failure in quasi-brittle materials. The concept is
inspired in the cohesive fracture widely employed in the context of
FEM \cite{Ortiz_1999}. This gradual failure criterion is plotted in
figure \label{fig:Damage-ft-wc}, where a linear decreasing cohesive
law is presented to illustrate the concept here described. In the
picture, the shaded area represents the static fracture energy per
unit of area, $G_F$. As we can see, a cohesive crack appears when the
maximum tensile strength, $f_t$ is reached. Once the opening
displacement $w$ takes the value of the critical crack displacement
$w_c$, a stress-free crack is attained. For intermediate values 
%%%%%%%%%%%
\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{Figures/Damage}
  \caption{Scheme of a linear cohesive law, where the shaded area is
    $G_f$, $f_t$ is the tensile strength, and $w_c$ is the critical
    opening displacement.}
  \label{fig:Damage-ft-wc}
\end{figure}
%%%%%%%%%%%

\begin{equation}
  \label{eq:variation-averaged-strain-energy-density}
  \delta W_{p,\epsilon} = \frac{\partial G_p}{C_{\epsilon}} =
  \frac{1}{m_p} \sum_{x_q^{k+1} \in
  B_{\epsilon}(x_p^{k+1})} m_q \tens{\sigma}_{q,I} \delta \tens{\epsilon}_q
\end{equation}

\begin{equation}
  \label{eq:variation-averaged-strain-energy-density-simpli}
  \delta W_{p,\epsilon} =
  \frac{\delta \tens{\epsilon}_p}{m_p} \sum_{x_q^{k+1} \in
  B_{\epsilon}(x_p^{k+1})} m_q \tens{\sigma}_{q,I} 
\end{equation}

\begin{equation}
  \label{eq:equivalent-critical-stress}
  \delta \tens{\sigma}_{p,c} =
  \frac{1}{m_p} \sum_{x_q^{k+1} \in
  B_{\epsilon}(x_p^{k+1})} m_q \tens{\sigma}_{q,I} 
\end{equation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Cases of study and discussion}
\label{sec:3}

\subsection{Comparison with analytical solution}
\label{sec:3.1}

\subsection{Brazilian test}
\label{sec:3.2}

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{Figures/Brazilian}
  \caption{Geometry and boundary condition of the Brazilian test.}
  \label{fig:geometry-brazilian-test}
\end{figure}

\subsection{Drop-weight impact test}
\label{sec:3.3}

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{Figures/Drop_weight}
  \caption{Geometry and boundary condition of the drop-weight impact test.}
  \label{fig:geometry-drop-weight-impact-test}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
\label{sec:6}

\section*{Acknowledgements}
The first author acknowledges the fellowship Agustín de Betancourt 262390106114.

\appendix
%\addappheadtotoc
%\appendixpage
%\renewcommand{\theequation}{\Alph{section}.\arabic{equation}}

\clearpage

\section{Explicit Predictor-Corrector algorithm}
\label{sec:expl-pred-corr}

\begin{algorithm}
  \floatname{algorithm}{Algorithm}
  \renewcommand{\thealgorithm}{}
  \caption{Explicit Predictor-Corrector scheme}
  \begin{algorithmic}[1]
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% º
    \STATE \textbf{Update mass matrix}:
    \begin{equation*}
      \tens{m}_{I} = N_{Ip}^{k}\ m_p,
    \end{equation*}
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
    \STATE \textbf{Explicit Newmark Predictor}:\\
    \begin{equation*}
      \vec{v}_I^{pred} = \frac{ N_{Ip}^{k} m_p (\vec{v}_p^k + (1 - \gamma)\ \Delta t\ \vec{a}_p^k)}{m_I}
    \end{equation*}
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
    \STATE \textbf{Impose essential boundary conditions}:\\
    At the fixed boundary, set $\vec{v}_{I}^{pred} = 0$. 
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
    % \STATE \textbf{Discard the previous nodal values}.
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
    \STATE \textbf{Deformation tensor increment calculation}.
    \begin{align*}
      &\dot{\tens{\varepsilon}_{p}}^{k+1} = \left[ \vec{v}_{I}^{pred} \otimes
        \Grad{N_{Ip}^{k+1}} \right]^s \\
      &\Delta \tens{\varepsilon}_{p}^{k+1} = \Delta t\ \dot{\tens{\varepsilon}_{p}}^{k+1}
    \end{align*}
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
    \STATE \textbf{Update the density field}:
    \begin{equation*}
      \rho_p^{k+1} = \frac{\rho_p^k}{1 + \mathit{tra}\left[\Delta\tens{\varepsilon}_{p}^{k+1}\right]}.
    \end{equation*}
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
    \STATE \textbf{Compute damage parameter}:
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
    \STATE \textbf{Balance of forces calculation}:\\
    Calculate the total grid nodal force $\vec{f}_{I}^{k+1} =
    (1-\chi)\vec{f}_{I}^{int,k+1} + \vec{f}_{I}^{ext,k+1}$ evaluating
    \eqref{eq:nodal_internal_forces} and
    \eqref{eq:nodal_external_forces} in the time step $k+1$.
    In the grid node $I$ is fixed in one of the spatial dimensions, set it to
    zero to make the grid nodal acceleration zero in that direction.\\
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
    \STATE \textbf{Explicit Newmark Corrector}:
    \begin{equation*}
      \vec{v}_{I}^{k+1} = \vec{v}_{I}^{pred} + \gamma\ \Delta t\ \frac{\vec{f}_{I}^{k+1}}{\tens{m}_I^{k+1}}  
    \end{equation*}
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \STATE \textbf{Update particles lagrangian quantities}:
    \begin{align*}
      &\vec{a}_p^{k+1} = \frac{N_{Ip}^k\vec{f}_{I}^{k}}{\tens{m}_I^k}\\
      &\vec{v}_p^{k+1} = \vec{v}_p^n + \Delta t\
        \frac{N_{Ip}^k\
        \vec{f}_{I}^{k}}{\tens{m}_I^k}\\
      &\vec{x}_p^{k+1} = \vec{x}_p^n + \Delta t\
         N_{Ip}^k\ \vec{v}_{I}^{k} +
        \frac{1}{2}\Delta t^2\ \frac{N_{Ip}^k\
        \vec{f}_{I}^{k}}{\tens{m}_I^k}
    \end{align*}
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
    \STATE \textbf{Reset nodal values}
  \end{algorithmic}
\end{algorithm}

\section{Eigensoftening Algorithm}
\label{sec:eigens-algor-1}

\begin{algorithm}\caption{Compute damage parameter $\chi_P^{k+1}$}\label{alg-eigens}
  \begin{algorithmic}
    \REQUIRE Particle status\\
    Number of particles: $N_p$\\
    $\epsilon$-neighbourhood of each particle $p$ : $B_{\epsilon,p}$\\
    \REQUIRE Material data\\
    Tensile strength: $f_{t,p}$\\
    Bandwidth of the cohesive fracture: $h_{\epsilon,p}$ \\
    Critical opening displacement: $w_c$\\ 
    \ENSURE Return damage parameter $\chi := \{\chi_p\}$
    \STATE $\chi_p \leftarrow \chi_p^{k}$
    \FOR{$p$ to $N_p$}
    \IF{$\chi_p = 0$ \AND $\epsilon_{f,p} = 0$}
    \FOR{$q \in B_{\epsilon,p}$}
    \IF{$\chi_q < 1$}    
    \STATE $\sum m_p\sigma_{p,I} \leftarrow \sum m_p\sigma_{p,I} + m_q\sigma_{q,I}$
    \ENDIF    
    \STATE $m_p \leftarrow m_p + m_q$
    \ENDFOR
    \STATE $\sigma_{p,\epsilon} \leftarrow \frac{1}{m_p} \sum m_p\sigma_{p,I}$
    \IF{$\sigma_{p,\epsilon} > f_{t,p}$}
    \STATE $\epsilon_{f,p} = \epsilon_{I,p}$   
    \ENDIF        
    \ELSE[$\chi_p \neq 1$ \AND $\epsilon_{f,p} > 0$]
    \STATE $\chi_p^{k+1} \leftarrow \min\Big \{1 , \max \{\chi_p^{k},
    \frac{(\epsilon_{I,p}- \epsilon_{f,p})\ h_{\epsilon,p}}{w_c} \} \Big \}$    
    \ENDIF    
    \ENDFOR
  \end{algorithmic}
\end{algorithm}

% name your BibTeX data base
\bibliography{Biblio/Biblio}

\end{document}

### 2020-04-21 2020_EFM_MPM_Eigensoftening.tex
Version 21-4-2020

@@
 developing novel spatial discretization methods such as meshfree
-methods like the material point method (MPM). Presence of cracks are a violation of the
-continuity requirement of the finite element approach (MPM).
+methods like the material point method (MPM). Presence of cracks are a
+violation of the continuity requirement of the finite element method
+(FEM).
 
-The MPM does not suffer from the above difficulties. Discontinuities
-can be described in two ways. One is to abandon the single-valued
-velocity field property near the crack by using two or more background
-meshes, and the other is to use failed material points to
-approximately describe the crack.
+By contrast, MPM does not suffer from the above difficulty since the
+continuity requirement is less restrictive. Regarding fracture, it can
+be described in two ways. One is to remove the restriction of the single-valued velocity field close to the crack by using two or
+more sets of nodes \cite{Nairn_2006}. This method is based in to
+assign different labels to distinguish if the material points and
+nodes are in the same side of the crack or not. Under this approach
+the crack surface is described with line segments in 2D and triangle
+patches in 3D cases. This method was named as ``CRAcks with Material
+Points (CRAMP)'' \cite{Nairn_2003}. In this method, the criteria for
+crack propagation is based on such parameters as energy release rate
+analyzed by Tan \& Nairn (2002)\cite{Nairn_2002}, and the stress
+intensity factor or the J-integral discussed by Guo \& Nairn
+(2004)\cite{Nairn_2004}.
 
-In the first approach,
+and the other is to use failed material points to
+describe the crack evolution.
+
+The erosion of the material point means that each material point can
+be either intact or be completely failed or eroded and has no load
+bearing capacity, Even thought the method has been successfully
+applied to dynamic fragmentation of metals, quantitative validations,
+such as stress or strain levels near or at the crack set compared to
+experimental measures are still lacking. Having in mind that the
+eigenerosion approach was intended for perfectly brittle fracture, an
+eigensoftening concept is developed for quasi-brittle materials
 
@@
 
-The popularity of MPM has increase notoriously during the recent years
-due to its ability to deal with large strain problems without mesh
-distorsion issues inherent to mesh based methods like FEM, see
-Zdzislaw \cite{Wieckowski2004}. However, in the simulations made with
-the original MPM, there are numerical noises when particles crossing
-the cell boundaries.
+The aim of this section is to provide an overview of the special
+techniques employed to face the fracture problem under the MPM
+framework. In consequence it is structured as follows: first in
+\ref{sec:2.1} we summarize the explicit-predictor algorithm for the
+MPM, next the local \textit{max-ent} approximants are introduced in
+\ref{sec:2.2} as an accurate alternative technique to interpolate data
+between particles and nodes, and finally the fracture algorithms based
+in the eigendeformations are presented in \ref{sec:2.3}.
 
@@
 
-For the spatial discretization, two sets of points are introduced in
-the MPM. First, the nodes, this points are considered fixed in the space and are in charge of
-computing all the kinematic fields such forces $f_I$, accelerations $a_I$ and
-velocities $v_I$. And second the material points or particles. They are in
-charge of the discretization of the continuum, and store the local state ($\sigma_p, \varepsilon_p$).
+The MPM~\cite{Sulsky1994} is a meshfree Lagrangian-Eulerian method
+where particles carries on all the physical information and a set of
+background nodes is employed to compute the equilibrium
+equation. Since the MPM possesses the advantages of both Lagrangian
+and Eulerian descriptions, no element distortion exists in the MPM,
+therefore it is an appropriate and efficient method in solving
+problems involving extremely large deformation and moving
+discontinuities such fracture evolution. For the spatial
+discretization, two sets of points are introduced in 
+the MPM. First, the nodes. This points are considered fixed in the
+space and are in charge of computing all the kinematic fields such
+forces $f_I$, accelerations $a_I$ and velocities $v_I$. And second the
+material points or particles. They are in charge of the discretization
+of the continuum, and store the local state ($\sigma_p,
+\varepsilon_p$). Without loosing generality, the MPM algorithm can be
+described with three main steps: (i) a
+variational recovery process, where particle data is projected to the
+grid nodes, (ii) an Eulerian step, where balance of momentum equation
+is expressed as a nodal equilibrium equation thorough a FEM-like
+procedure, and finally (iii) a Lagrangian advection of the
+particles. In the present research we will adopt a explicit
+predictor-corrector time integration scheme. The purpose of this
+choice is motivated due its proved robustness and stability in
+numerical calculations. In the first stage (i), the nodal velocity
+predictor is computed following \eqref{eq:Predictor-velocity}, 
+\begin{equation}
+  \label{eq:Predictor-velocity}
+  \vec{\tilde{v}}_I^{k+1} = \frac{ N_{Ip}^{k} m_p (\vec{v}_p^k + (1 - \gamma)\ \Delta t\ \vec{a}_p^k)}{m_I}
+\end{equation}
+This way of computing the nodal predictor is both numerically stable
+and minimize the computational effort. Once nodal velocity are
+obtained, the essential boundary conditions are imposed. And in the
+following, a Eulerian phase (ii) is computed in the set of nodes in a
+FEM-like way, where nodal forces $\vec{f}_{I}^{k+1}$ are computed thorough the
+equilibrium equation. Next the nodal velocities are corrected in a
+\textit{corrector} stage,
+\begin{equation}
+  \label{eq:Corrector-velocity}
+  \vec{v}_{I}^{k+1} = \vec{v}_{I}^{pred} + \gamma\ \Delta t\ \frac{\vec{f}_{I}^{k+1}}{\tens{m}_I^{k+1}}
+\end{equation}
+Finally updated the particles are advected in the Lagrangian stage (iii) using nodal values as,
+\begin{align}
+  \label{eq:Update-lagrangian-pce}
+        &\vec{a}_p^{k+1} = \frac{N_{Ip}^k\vec{f}_{I}^{k}}{\tens{m}_I^k}\\
+      &\vec{v}_p^{k+1} = \vec{v}_p^n + \Delta t\
+        \frac{N_{Ip}^k\
+        \vec{f}_{I}^{k}}{\tens{m}_I^k}\\
+      &\vec{x}_p^{k+1} = \vec{x}_p^n + \Delta t\
+         N_{Ip}^k\ \vec{v}_{I}^{k} +
+        \frac{1}{2}\Delta t^2\ \frac{N_{Ip}^k\
+        \vec{f}_{I}^{k}}{\tens{m}_I^k} 
+\end{align}
+The complete pseudo-algorithm it is summarized in \ref{sec:expl-pred-corr}.
 
@@
 
-\subsection{Temporal discretization}
+\subsection{Fracture modelling approach}
 \label{sec:2.3}
-
-This research is devoted to capture the challenging process of
-fracture during high velocity impacts. To capture the presence of
-elastic shock waves triggered by the fracture process. Here we adopt
-a explicit predictor-corrector time integration
-scheme. It is based in the Newmark a-form 
-$\gamma = 0.5$ and $\beta = 0$ which is the central difference
-explicit. In a first stage, the nodal velocity predictor is computed
-following \eqref{eq:Predictor-velocity}, 
-\begin{equation}
-  \label{eq:Predictor-velocity}
-  \vec{\tilde{v}}_I^{k+1} = \frac{ N_{Ip}^{k} m_p (\vec{v}_p^k + (1 - \gamma)\ \Delta t\ \vec{a}_p^k)}{m_I}
-\end{equation}
-This way of computing the nodal predictor is both numerically stable
-and minimize the computational effort. Once nodal velocity are
-obtained, the essential boundary conditions are imposed. And in the
-following, the ``classic'' MPM algorithm continues to reach to the
-equilibrium equation \eqref{eq:particle_balance_forces3}. Here we
-continue with the \textit{corrector} stage, due to the fact that we
-already have nodal velocity, this step is computed in the same way as
-in FEM,
-\begin{equation}
-  \label{eq:Corrector-velocity}
-  \vec{v}_{I}^{k+1} = \vec{v}_{I}^{pred} + \gamma\ \Delta t\ \frac{\vec{f}_{I}^{k+1}}{\tens{m}_I^{k+1}}
-\end{equation}
-Finally updated particle kinetics are computed using nodal values as,
-\begin{align}
-  \label{eq:Update-lagrangian-pce}
-        &\vec{a}_p^{k+1} = \frac{N_{Ip}^k\vec{f}_{I}^{k}}{\tens{m}_I^k}\\
-      &\vec{v}_p^{k+1} = \vec{v}_p^n + \Delta t\
-        \frac{N_{Ip}^k\
-        \vec{f}_{I}^{k}}{\tens{m}_I^k}\\
-      &\vec{x}_p^{k+1} = \vec{x}_p^n + \Delta t\
-         N_{Ip}^k\ \vec{v}_{I}^{k} +
-        \frac{1}{2}\Delta t^2\ \frac{N_{Ip}^k\
-        \vec{f}_{I}^{k}}{\tens{m}_I^k} 
-\end{align}
-The complete pseudo-algorithm it is summarized in \ref{sec:expl-pred-corr}.
-
-\subsection{Fracture modelling approach}
-\label{sec:2.4}
 
@@
 displacement $w$ takes the value of the critical crack displacement
-$w_c$, a stress-free crack is attained. For intermediate values 
+$w_c$, a stress-free crack is attained. For intermediate values,
+$w_n$, a damage value between zero and one represents the extension to
+which the material has failed.
 %%%%%%%%%%%
@@
 %%%%%%%%%%%
+For the eigensoftening algorithm,
+
+a strength criterion for crack initialization was adopted
 

### 2020-04-22 _region_.tex
Versión 22-4-2020

--- 2020-04-21 2020_EFM_MPM_Eigensoftening.tex
@@
-\documentclass[preprint,12pt,a4paper]{elsarticle}
+\message{ !name(2020_EFM_MPM_Eigensoftening.tex)}\documentclass[preprint,12pt,a4paper]{elsarticle}
 
@@
 \usepackage{amsmath,amsthm,amssymb}
+\usepackage{xstring}
 
@@
 
+\journal{Engineering Fracture Mechanics}
+
 \modulolinenumbers[5]
-
-\journal{Engineering Fracture Mechanics}
 
@@
 
+\message{ !name(2020_EFM_MPM_Eigensoftening.tex) !offset(-3) }
+
 \begin{frontmatter}
@@
 \author{
-Miguel Molinos$^a$\footnote{Corresponding author: m.molinos@outlook.es},
+Miguel Molinos$^a$,
 and Pedro Navas$^a$\footnote{Corresponding author: p.navas@upm.es}
@@
 \begin{abstract}
-
   The objective of this work is to introduce an alternative
@@
   results proofs the well performance of the method under challenging loads.
-
 \end{abstract}
@@
 of the continuum, and store the local state ($\sigma_p,
-\varepsilon_p$). Without loosing generality, the MPM algorithm can be
-described with three main steps: (i) a
-variational recovery process, where particle data is projected to the
-grid nodes, (ii) an Eulerian step, where balance of momentum equation
-is expressed as a nodal equilibrium equation thorough a FEM-like
-procedure, and finally (iii) a Lagrangian advection of the
-particles. In the present research we will adopt a explicit
-predictor-corrector time integration scheme. The purpose of this
-choice is motivated due its proved robustness and stability in
-numerical calculations. In the first stage (i), the nodal velocity
-predictor is computed following \eqref{eq:Predictor-velocity}, 
+\varepsilon_p$). Without loosing generality, the MPM algorithm
+can be described with three main steps: (i) a variational recovery
+process, where particle data is projected to the grid nodes, (ii) an
+Eulerian step, where balance of momentum equation is expressed as a
+nodal equilibrium equation thorough a FEM-like procedure, and finally
+(iii) a Lagrangian advection of the particles. In the present research
+we will adopt a explicit predictor-corrector time integration
+scheme. The purpose of this choice is motivated due its proved
+robustness and stability in numerical calculations. In the first stage
+(i), the nodal velocity predictor is computed following
+\eqref{eq:Predictor-velocity}, 
 \begin{equation}
@@
 \label{sec:2.2}
-
 Local maximum-entropy (or local \textit{max-ent}) approximation scheme
@@
 a probability. This allow us to introduce two important limits:
-the principle of maximum-entropy (\textit{max-ent}) statistical
-inference stated by \cite{Jaynes1957}, and the Delaunay triangulation
-which ensures the minimal width of the shape function. To reach to a compromise between two competing objectives, a Pareto set is defined as, 
+maximum-entropy (\textit{max-ent}) limit, and the Delaunay triangulation
+which ensures the minimal width of the shape function. The first
+limit ensures a \textit{unbiased statistical inference} based on the
+nodal data as ensures the Jayne's\cite{Jaynes1957} principle of
+\textit{maximum entropy}, the second limit warrant the \textit{least
+  width} shape function support. To reach to a compromise between two
+competing objectives, a Pareto set is defined as, 
 \begin{align*}
@@
 definition given by Shannon (1948) \cite{Shannon1948}, and $U(\vec{x}_p,N_I) =
-\sum_I N_I |\vec{x}_p - \vec{x}_I |^2$ a magnitude of the shape
-function width. The regularization o \textit{thermalization} parameter
-between the two criterion $\beta$ has Pareto optimal values in the range
-$(0,\infty)$. The unique solution of the local max-ent problem
-(LME)$_\beta$ is:
+\sum_I N_I |\vec{x}_p - \vec{x}_I |^2$ a 
+magnitude of the shape function width. The regularization o
+\textit{thermalization} parameter between the two criterion $\beta$
+has Pareto optimal values in the range $(0,\infty)$. The unique
+solution of the local max-ent problem (LME)$_\beta$ is
  \begin{equation}
@@
 N_I^*(\vec{x})=\frac{\exp\left[ -\beta \; |\vec{x}-\vec{x}_I|^2 +
-    \vec{\lambda}^* \cdot (\vec{x}-\vec{x}_I) \right] } {Z(\vec{x},\vec{\lambda}^*(\vec{x}))}
+    \vec{\lambda}^* \cdot (\vec{x}-\vec{x}_I) \right] } {Z(\vec{x},\vec{\lambda}^*)}
 \end{equation}
-where $Z(\vec{x},\vec{\lambda}^*(\vec{x}))$ is the \textit{partition
-  function} defined as,
+where $Z(\vec{x},\vec{\lambda}^*)$ is the \textit{partition function} defined as,
 \begin{equation}
@@
 \end{equation}
-and evaluated in the unique minimiser $\vec{\lambda}^*(\vec{x})$ for
-the function $\log
-Z(\vec{x}, \vec{\lambda})$. The traditional way to obtain such a
-minimiser is using (\ref{eq:LME-J}) to calculate small increments of $\partial\vec{\lambda}$ in a
-Newton-Raphson approach. Where $\tens{J}$ is the Hessian matrix, defined by:
+and evaluated in the unique minimiser $\vec{\lambda}^*$ for the function $\log
+Z(\vec{x}, \vec{\lambda})$. The traditional way to obtain
+such a minimiser is using (\ref{eq:LME-J}) to calculate small
+increments of $\partial\vec{\lambda}$ in a Newton-Raphson
+approach. Where $\tens{J}$ is the Hessian matrix, defined by:
 \begin{eqnarray}
@@
 \end{eqnarray}
-In order to obtain the first derivatives of the shape function~$\nabla
-N^*_I$, can be computed as,
+The value of $\tens{J}$ can be employed to get the first derivatives of the shape function $\nabla
+N^*_I$,
 \begin{equation}
@@
 \end{eqnarray}
-
 The regularization parameter $\beta$ of LME shape functions may be
@@
 the shape function decay $\exp(-\beta \vec{r} )$ is truncated  by  a
-given tolerance, 10$^{-6}$, for example,  would ensure a reasonable range of
-neighbours, see \cite{Arroyo2006} for details. This tolerance defines
+given tolerance, 10$^{-6}$, for example,  would ensure a reasonable
+range of neighbours, see \cite{Arroyo2006} for details. This tolerance defines
 the limit values of the influence radius and is used thereafter to
@@
 \label{sec:2.3}
-
 Within the context of MPM formulation, fracture can be modelled by
@@
 %%%%%%%%%%%
-For the eigensoftening algorithm,
-
-a strength criterion for crack initialization was adopted
-
+For the eigensoftening algorithm, a strength criterion for crack
+initialization was adopted. Particularly the maximum principal stress
+theory for brittle fracture was considered by authors
+\cite{Navas_2017_ES}. With that purpose, the variation of the averaged strain
+energy density in the $\epsilon$-neighborhood of the material point
+$\vec{x}_p^{k+1}$ can be obtained as,
 \begin{equation}
   \label{eq:variation-averaged-strain-energy-density}
-  \delta W_{p,\epsilon} = \frac{\partial G_p}{C_{\epsilon}} =
+  \delta W_{\epsilon,p} = \frac{\partial G_p}{C_{\epsilon}} =
   \frac{1}{m_p} \sum_{x_q^{k+1} \in
@@
 \end{equation}
-
+where $\tens{\sigma}_{q,I}$ is the maximum principal stress of each
+material point in the $\epsilon$-neighborhood. Here
+\cite{Navas_2017_ES} introduces an effective strain $\varepsilon_q$,
+such the variation of the local strain energy can be obtained as
+$\delta W_q = \sigma_{q,1} \delta\varepsilon_q$. Now with the assumption
+that the effective strain of each material point at every time step
+is constant in the neighborhood of $\vec{x}_p^{k+1}$, the equation
+\eqref{eq:variation-averaged-strain-energy-density} can be simplified
+as follows
 \begin{equation}
   \label{eq:variation-averaged-strain-energy-density-simpli}
-  \delta W_{p,\epsilon} =
+  \delta W_{\epsilon,p} =
   \frac{\delta \tens{\epsilon}_p}{m_p} \sum_{x_q^{k+1} \in
-  B_{\epsilon}(x_p^{k+1})} m_q \tens{\sigma}_{q,I} 
+  B_{\epsilon}(x_p^{k+1})} m_q \tens{\sigma}_{q,I}. 
+\end{equation}
+Consequently we can define an equivalent critical stress at the
+material point $\vec{x}_p^{k+1}$:
+\begin{equation}
+  \label{eq:equivalent-critical-stress}
+  \tens{\sigma}_{\epsilon,p} =
+  \frac{1}{m_p} \sum_{x_q^{k+1} \in
+  B_{\epsilon}(x_p^{k+1})} m_q \tens{\sigma}_{q,I}, 
+\end{equation}
+where $m_p$ can be computed as:
+\begin{equation}
+  \label{eq:averaged-mass}
+  m_p = \sum_{x_q^{k+1} \in B_{\epsilon}(x_p^{k+1})} m_q.
+\end{equation}
+This definition of the equivalent critical stress allow us to
+link it with the averaged strain energy as $\delta W_{\epsilon,p} =
+ \tens{\sigma}_{\epsilon,p}\ \delta\varepsilon_p$. The fracture
+criterion is defined as once $\tens{\sigma}_{\epsilon,p}^{k+1}$
+surpasses the tensile strength, $f_t$, the softening behaviour is
+activated, which in turn causes a reduction of the initial forces as,
+ \begin{equation}
+   \label{eq:f-int-damaged}
+   f^{int}_I = \sum_p (1 - \chi_p)\ \tens{\sigma}_{p}^{k+1} \cdot \Grad{N_{Ip}}
+ \end{equation}
+where $\chi_p$ is the damage variable of each material point $p$,
+ranges between zero (an intact material) and one (completely failed
+material points). For the case of a linear softening such the sketched
+in the Figure \ref{fig:Damage-ft-wc}, it is calculated as,
+ \begin{equation}
+   \label{eq:damaged-variable-chi}
+   1 - \chi = \frac{f_n}{f_t} = 1 - \frac{w_n}{w_c}\ \rightarrow\ \chi
+   = \frac{w_n}{w_c}.
  \end{equation}
 
+Following Bazant~\cite{Bazant83} crack-model, \cite{Navas_2017_ES}
+introduced a band width $h_{\epsilon}$. The effective fracture strain
+$\varepsilon_{\epsilon,f}$ is defined as the difference between the
+strain at crack initialization, $\varepsilon_1(\vec{x}_p^{0})$, and
+the current strain, $\varepsilon_1(\vec{x}_p^{k+1})$, for material
+point $p$. Also, $\varepsilon_{\epsilon,f}$ can be represented as the
+current crack opening $w_n$ within the band width,
+$h_{\epsilon}$. Therefore,
 \begin{equation}
-  \label{eq:equivalent-critical-stress}
-  \delta \tens{\sigma}_{p,c} =
-  \frac{1}{m_p} \sum_{x_q^{k+1} \in
-  B_{\epsilon}(x_p^{k+1})} m_q \tens{\sigma}_{q,I} 
+  \label{eq:effective-fracture-strain}
+  \varepsilon_{\epsilon,f} = \varepsilon_1(\vec{x}_p^{k+1}) -
+  \varepsilon_1(\vec{x}_p^{0}) = \frac{w_n}{h_{\epsilon}}
 \end{equation}
-
+Introducing \eqref{eq:effective-fracture-strain} in
+\eqref{eq:damaged-variable-chi}, the damage variable can be computed
+as,
+\begin{equation}
+  \label{eq:damage-variable-chi-II}
+\chi = \frac{\varepsilon_{\epsilon,f}\ h^{\epsilon}}{w_c}  
+\end{equation}
+for the case of a linear softening behaviour. In a more general case,
+the damage variable can be expressed in terms of the following
+variables,
+\begin{equation}
+  \label{eq:damage-variable-chi-III}
+  \chi = \chi(\varepsilon_{\epsilon,f}, h^{\epsilon}, f_t, w_c, G_f)
+\end{equation}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
   \centering
-  \includegraphics[width=0.5\textwidth]{Figures/Brazilian}
+  \includegraphics[width=0.3\textwidth]{Figures/Brazilian}
   \caption{Geometry and boundary condition of the Brazilian test.}
@@
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-    % \STATE \textbf{Discard the previous nodal values}.
-    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
     \STATE \textbf{Deformation tensor increment calculation}.
-    \begin{align*}
-      &\dot{\tens{\varepsilon}_{p}}^{k+1} = \left[ \vec{v}_{I}^{pred} \otimes
-        \Grad{N_{Ip}^{k+1}} \right]^s \\
-      &\Delta \tens{\varepsilon}_{p}^{k+1} = \Delta t\ \dot{\tens{\varepsilon}_{p}}^{k+1}
-    \end{align*}
+    \begin{equation*}
+      \Delta \tens{\varepsilon}_{p}^{k+1} = \Delta t\
+        \dot{\tens{\varepsilon}_{p}}^{k+1} = \Delta \left[ \vec{v}_{I}^{pred} \otimes
+        \Grad{N_{Ip}^{k+1}} \right]^s
+    \end{equation*}
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
@@
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-    \STATE \textbf{Compute damage parameter}:
+    \STATE \textbf{Compute stress field and update damage parameter}:\\
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
@@
     Calculate the total grid nodal force $\vec{f}_{I}^{k+1} =
-    (1-\chi)\vec{f}_{I}^{int,k+1} + \vec{f}_{I}^{ext,k+1}$ evaluating
-    \eqref{eq:nodal_internal_forces} and
-    \eqref{eq:nodal_external_forces} in the time step $k+1$.
-    In the grid node $I$ is fixed in one of the spatial dimensions, set it to
-    zero to make the grid nodal acceleration zero in that direction.\\
+    \vec{f}_{I}^{int,k+1} + \vec{f}_{I}^{ext,k+1}$.
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-    \STATE \textbf{Explicit Newmark Corrector}:
+    \STATE \textbf{Explicit Newmark Corrector}:\\
     \begin{equation*}
@@
 
-\begin{algorithm}\caption{Compute damage parameter $\chi_P^{k+1}$}\label{alg-eigens}
-  \begin{algorithmic}
-    \REQUIRE Particle status\\
+\begin{algorithm}
+  \caption{Compute damage parameter $\chi_P^{k+1}$}
+  \label{alg-eigens}
+  \begin{algorithmic}[1]
+    \Require Particle status\\
     Number of particles: $N_p$\\
     $\epsilon$-neighbourhood of each particle $p$ : $B_{\epsilon,p}$\\
-    \REQUIRE Material data\\
+    \Require Material data\\
     Tensile strength: $f_{t,p}$\\
@@
     Critical opening displacement: $w_c$\\ 
-    \ENSURE Return damage parameter $\chi := \{\chi_p\}$
-    \STATE $\chi_p \leftarrow \chi_p^{k}$
-    \FOR{$p$ to $N_p$}
-    \IF{$\chi_p = 0$ \AND $\epsilon_{f,p} = 0$}
-    \FOR{$q \in B_{\epsilon,p}$}
-    \IF{$\chi_q < 1$}    
-    \STATE $\sum m_p\sigma_{p,I} \leftarrow \sum m_p\sigma_{p,I} + m_q\sigma_{q,I}$
-    \ENDIF    
-    \STATE $m_p \leftarrow m_p + m_q$
-    \ENDFOR
-    \STATE $\sigma_{p,\epsilon} \leftarrow \frac{1}{m_p} \sum m_p\sigma_{p,I}$
-    \IF{$\sigma_{p,\epsilon} > f_{t,p}$}
-    \STATE $\epsilon_{f,p} = \epsilon_{I,p}$   
-    \ENDIF        
-    \ELSE[$\chi_p \neq 1$ \AND $\epsilon_{f,p} > 0$]
-    \STATE $\chi_p^{k+1} \leftarrow \min\Big \{1 , \max \{\chi_p^{k},
+    \Ensure Return damage parameter $\chi := \{\chi_p\}$
+    \State $\chi_p \leftarrow \chi_p^{k}$
+    \For{$p$ to $N_p$}
+    \If{$\chi_p = 0$ \AND $\epsilon_{f,p} = 0$}
+    \For{$q \in B_{\epsilon,p}$}
+    \If{$\chi_q < 1$}    
+    \State $\sum m_p\sigma_{p,I} \leftarrow \sum m_p\sigma_{p,I} + m_q\sigma_{q,I}$
+    \EndIf    
+    \State $m_p \leftarrow m_p + m_q$
+    \EndFor
+    \State $\sigma_{p,\epsilon} \leftarrow \frac{1}{m_p} \sum m_p\sigma_{p,I}$
+    \If{$\sigma_{p,\epsilon} > f_{t,p}$}
+    \State $\epsilon_{f,p} = \epsilon_{I,p}$   
+    \EndIf        
+    \Else[$\chi_p \neq 1$ \AND $\epsilon_{f,p} > 0$]
+    \State $\chi_p^{k+1} \leftarrow \min\Big \{1 , \max \{\chi_p^{k},
     \frac{(\epsilon_{I,p}- \epsilon_{f,p})\ h_{\epsilon,p}}{w_c} \} \Big \}$    
-    \ENDIF    
-    \ENDFOR
+    \EndIf    
+    \EndFor
   \end{algorithmic}
@@
 \end{document}
+\message{ !name(2020_EFM_MPM_Eigensoftening.tex) !offset(-630) }

### 2020-04-23 2020_EFM_MPM_Eigensoftening.tex
Version 22-4-2020
Version 23-4-2020

@@
  \address{
- $^a$ ETSI Caminos, Canales y Puertos, Universidad Polit\'ectnica de Madrid.\\ c. Prof. Aranguren 3, 28040 Madrid, Spain
+ $^a$ ETSI Caminos, Canales y Puertos, Universidad Polit\'ectnica de Madrid.\\
+ c. Prof. Aranguren 3, 28040 Madrid, Spain
 }
@@
 violation of the continuity requirement of the finite element method
-(FEM).
+(FEM). To overcome it, numerous of numerical artifacts has been
+proposed with the aim of reproduce such a complex behaviour. This
+techniques vary from employing cohesive approaches
+\cite{Barenblatt,Hilleborg_1976}, by adaptively inserting cohesive
+elements \cite{Ortiz_1999,Pandolfi_2002,Ruiz_2000} at solid elements
+boundaries, or handling arbitrary cracks paths by level set
+representation of the fracture surface \cite{Belytschko_03}.
+
+The severe
+limitations of the mesh-dependent methods to simulate fracture
+process, have motivated the development of mesh-free technique to
+reproduce crack propagation such the element-free Galerkin method
+(EFGM) \cite{BELYTSCHKO_1995,BELYTSCHKO_2000,Zhuang_2012,Muthu_2013},
+the smoothed particle hydrodynamics (SPH) \cite{Wang_2020,Wang_2019},
+the optimal transportation meshfree method (OTM)
+\cite{Li2010,Li_2012,Pandolfi_2013,Li_2015} or peridynamics
+\cite{HA_2011,RABCZUK_2017}.
 
 By contrast, MPM does not suffer from the above difficulty since the
-continuity requirement is less restrictive. Regarding fracture, it can
-be described in two ways. One is to remove the restriction of the single-valued velocity field close to the crack by using two or
-more sets of nodes \cite{Nairn_2006}. This method is based in to
-assign different labels to distinguish if the material points and
-nodes are in the same side of the crack or not. Under this approach
-the crack surface is described with line segments in 2D and triangle
-patches in 3D cases. This method was named as ``CRAcks with Material
-Points (CRAMP)'' \cite{Nairn_2003}. In this method, the criteria for
-crack propagation is based on such parameters as energy release rate
+continuity requirement is less restrictive. Fracture can be described
+in two ways. One is to remove the restriction of the single-valued
+velocity field close to the crack by using two or more sets of nodes
+\cite{Nairn_2006}. This method is based in to assign different labels
+to distinguish if the material points and nodes are in the same side
+of the crack or not. Under this approach the crack surface is
+described with line segments in 2D and triangle patches in 3D
+cases. This method was named as ``CRAcks with Material Points
+(CRAMP)'' \cite{Nairn_2003}. In this method, the criteria for crack
+propagation is based on such parameters as energy release rate
 analyzed by Tan \& Nairn (2002)\cite{Nairn_2002}, and the stress
 intensity factor or the J-integral discussed by Guo \& Nairn
-(2004)\cite{Nairn_2004}.
+(2004)\cite{Nairn_2004}. The other approach is to use failed material
+points to describe the crack evolution. In this method, the formation
+of failed points describes the nucleation of cracks, and thereafter its propagation and
+branching. Consequently, the position of the crack does not need to be
+explicitly stated. This represents a significant advantage over the
+``CRAMP''. Under this approach, the prediction the failure evolution
+employing a decohesion model has been discussed by Chen {\it et al.}\cite{Zhenmao_2005} or
+Schreyer {\it et al.}\cite{Schreyer_2002}. And has been successfully
+employed to simulate the fracture of brittle materials by Chen {\it et
+  al.} \cite{Chen_2002,Chen_2003} and Sulsky \& Schreyer
+(2004)\nocite{Sulsky_2004}.
 
-and the other is to use failed material points to
-describe the crack evolution.
+\cite{Belytschko_04,Schmidt_2009,Pandolfi_2012}
 
@@
 framework. In consequence it is structured as follows: first in
-\ref{sec:2.1} we summarize the explicit-predictor algorithm for the
-MPM, next the local \textit{max-ent} approximants are introduced in
+\ref{sec:2.1} the explicit-predictor algorithm for the
+MPM will be exposed, next the local \textit{max-ent} approximants are introduced in
 \ref{sec:2.2} as an accurate alternative technique to interpolate data
@@
 of the continuum, and store the local state ($\sigma_p,
-\varepsilon_p$). Without loosing generality, the MPM algorithm can be
-described with three main steps: (i) a
-variational recovery process, where particle data is projected to the
-grid nodes, (ii) an Eulerian step, where balance of momentum equation
-is expressed as a nodal equilibrium equation thorough a FEM-like
-procedure, and finally (iii) a Lagrangian advection of the
-particles. In the present research we will adopt a explicit
-predictor-corrector time integration scheme. The purpose of this
-choice is motivated due its proved robustness and stability in
-numerical calculations. In the first stage (i), the nodal velocity
-predictor is computed following \eqref{eq:Predictor-velocity}, 
+\varepsilon_p$). Without loosing generality, the MPM algorithm
+can be described with three main steps: (i) a variational recovery
+process, where particle data is projected to the grid nodes, (ii) an
+Eulerian step, where balance of momentum equation is expressed as a
+nodal equilibrium equation thorough a FEM-like procedure, and finally
+(iii) a Lagrangian advection of the particles. In the present research
+a explicit predictor-corrector time integration
+scheme is adopted. The purpose of this choice is motivated due its proved
+robustness and stability in numerical calculations. In the first stage
+(i), the nodal velocity predictor is computed following
+\eqref{eq:Predictor-velocity}, 
 \begin{equation}
@@
 picture, the shaded area represents the static fracture energy per
-unit of area, $G_F$. As we can see, a cohesive crack appears when the
+unit of area, $G_F$. Notice how a cohesive crack appears when the
 maximum tensile strength, $f_t$ is reached. Once the opening
@@
 \end{equation}
-
+where $\tens{\sigma}_{q,I}$ is the maximum principal stress of each
+material point in the $\epsilon$-neighborhood. Here
+\cite{Navas_2017_ES} introduces an effective strain $\varepsilon_q$,
+such the variation of the local strain energy can be obtained as
+$\delta W_q = \sigma_{q,1} \delta\varepsilon_q$. Now with the assumption
+that the effective strain of each material point at every time step
+is constant in the neighborhood of $\vec{x}_p^{k+1}$, the equation
+\eqref{eq:variation-averaged-strain-energy-density} can be simplified
+as follows
 \begin{equation}
   \label{eq:variation-averaged-strain-energy-density-simpli}
-  \delta W_{p,\epsilon} =
+  \delta W_{\epsilon,p} =
   \frac{\delta \tens{\epsilon}_p}{m_p} \sum_{x_q^{k+1} \in
-  B_{\epsilon}(x_p^{k+1})} m_q \tens{\sigma}_{q,I} 
+  B_{\epsilon}(x_p^{k+1})} m_q \tens{\sigma}_{q,I}. 
+\end{equation}
+Consequently it is possible to define an equivalent critical stress at the
+material point $\vec{x}_p^{k+1}$:
+\begin{equation}
+  \label{eq:equivalent-critical-stress}
+  \tens{\sigma}_{\epsilon,p} =
+  \frac{1}{m_p} \sum_{x_q^{k+1} \in
+  B_{\epsilon}(x_p^{k+1})} m_q \tens{\sigma}_{q,I}, 
+\end{equation}
+where $m_p$ can be computed as:
+\begin{equation}
+  \label{eq:averaged-mass}
+  m_p = \sum_{x_q^{k+1} \in B_{\epsilon}(x_p^{k+1})} m_q.
+\end{equation}
+This definition of the equivalent critical stress allow us to
+link it with the averaged strain energy as $\delta W_{\epsilon,p} =
+ \tens{\sigma}_{\epsilon,p}\ \delta\varepsilon_p$. The fracture
+criterion is defined as once $\tens{\sigma}_{\epsilon,p}^{k+1}$
+surpasses the tensile strength, $f_t$, the softening behaviour is
+activated, which in turn causes a reduction of the initial forces as,
+ \begin{equation}
+   \label{eq:f-int-damaged}
+   f^{int}_I = \sum_p (1 - \chi_p)\ \tens{\sigma}_{p}^{k+1} \cdot \Grad{N_{Ip}}
+ \end{equation}
+where $\chi_p$ is the damage variable of each material point $p$,
+ranges between zero (an intact material) and one (completely failed
+material points). For the case of a linear softening such the sketched
+in the Figure \ref{fig:Damage-ft-wc}, it is calculated as,
+ \begin{equation}
+   \label{eq:damaged-variable-chi}
+   1 - \chi = \frac{f_n}{f_t} = 1 - \frac{w_n}{w_c}\ \rightarrow\ \chi
+   = \frac{w_n}{w_c}.
  \end{equation}
 
+Following Bazant~\cite{Bazant83} crack-model, \cite{Navas_2017_ES}
+introduced a band width $h_{\epsilon}$, which has values between two
+and four times the maximum size of the aggregates for the
+concrete. The effective fracture strain $\varepsilon_{\epsilon,f}$ is
+defined as the difference between the strain at crack initialization,
+$\varepsilon_1(\vec{x}_p^{0})$, and the current strain, $\varepsilon_1(\vec{x}_p^{k+1})$, for material
+point $p$. Also, $\varepsilon_{\epsilon,f}$ can be represented as the
+current crack opening $w_n$ within the band width,
+$h_{\epsilon}$. Therefore,
 \begin{equation}
-  \label{eq:equivalent-critical-stress}
-  \delta \tens{\sigma}_{p,c} =
-  \frac{1}{m_p} \sum_{x_q^{k+1} \in
-  B_{\epsilon}(x_p^{k+1})} m_q \tens{\sigma}_{q,I} 
+  \label{eq:effective-fracture-strain}
+  \varepsilon_{\epsilon,f} = \varepsilon_1(\vec{x}_p^{k+1}) -
+  \varepsilon_1(\vec{x}_p^{0}) = \frac{w_n}{h_{\epsilon}}
 \end{equation}
-
+Introducing \eqref{eq:effective-fracture-strain} in
+\eqref{eq:damaged-variable-chi}, the damage variable can be computed
+as,
+\begin{equation}
+  \label{eq:damage-variable-chi-II}
+\chi = \frac{\varepsilon_{\epsilon,f}\ h^{\epsilon}}{w_c}  
+\end{equation}
+for the case of a linear softening behaviour. In a more general case,
+the damage variable can be expressed in terms of the following
+variables,
+\begin{equation}
+  \label{eq:damage-variable-chi-III}
+  \chi = \chi(\varepsilon_{\epsilon,f}, h^{\epsilon}, f_t, w_c, G_f)
+\end{equation}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\begin{algorithm}\caption{Compute damage parameter $\chi_P^{k+1}$}\label{alg-eigens}
+\begin{algorithm}
+  \caption{Compute damage parameter $\chi_p^{k+1}$}
+  \label{alg-eigens}
   \begin{algorithmic}
-    \REQUIRE Particle status\\
+    \Require Particle status\\
     Number of particles: $N_p$\\
     $\epsilon$-neighbourhood of each particle $p$ : $B_{\epsilon,p}$\\
-    \REQUIRE Material data\\
+    \Require Material data\\
     Tensile strength: $f_{t,p}$\\

### 2020-04-23 _region_.tex
Version 23-4-2020

@@
 (iii) a Lagrangian advection of the particles. In the present research
-we will adopt a explicit predictor-corrector time integration
-scheme. The purpose of this choice is motivated due its proved
+a explicit predictor-corrector time integration
+scheme is adopted. The purpose of this choice is motivated due its proved
 robustness and stability in numerical calculations. In the first stage
@@
 \end{equation}
-Consequently we can define an equivalent critical stress at the
+Consequently it is possible to define an equivalent critical stress at the
 material point $\vec{x}_p^{k+1}$:
@@
 Following Bazant~\cite{Bazant83} crack-model, \cite{Navas_2017_ES}
-introduced a band width $h_{\epsilon}$. The effective fracture strain
-$\varepsilon_{\epsilon,f}$ is defined as the difference between the
-strain at crack initialization, $\varepsilon_1(\vec{x}_p^{0})$, and
-the current strain, $\varepsilon_1(\vec{x}_p^{k+1})$, for material
+introduced a band width $h_{\epsilon}$, which has values between two
+and four times the maximum size of the aggregates for the
+concrete. The effective fracture strain $\varepsilon_{\epsilon,f}$ is
+defined as the difference between the strain at crack initialization,
+$\varepsilon_1(\vec{x}_p^{0})$, and the current strain, $\varepsilon_1(\vec{x}_p^{k+1})$, for material
 point $p$. Also, $\varepsilon_{\epsilon,f}$ can be represented as the
@@
 \begin{algorithm}
-  \caption{Compute damage parameter $\chi_P^{k+1}$}
+  \caption{Compute damage parameter $\chi_p^{k+1}$}
   \label{alg-eigens}
-  \begin{algorithmic}[1]
+  \begin{algorithmic}
     \Require Particle status\\
@@
 \end{document}
-\message{ !name(2020_EFM_MPM_Eigensoftening.tex) !offset(-630) }
+\message{ !name(2020_EFM_MPM_Eigensoftening.tex) !offset(-660) }

### 2020-04-25 2020_EFM_MPM_Eigensoftening.tex
Cambios 24-4-2020

@@
 \label{sec:1}
+Presence of cracks are a violation of the continuity requirement of
+the finite element method (FEM). To overcome it, numerous of numerical
+artifacts has been proposed with the aim of reproducing  such a
+complex behaviour. This techniques vary from employing cohesive
+approaches \cite{Barenblatt,Hilleborg_1976}, by adaptively inserting
+cohesive elements \cite{Ortiz_1999,Pandolfi_2002,Ruiz_2000} at solid
+elements boundaries, or handling arbitrary cracks paths by level set
+representation of the fracture surface \cite{Belytschko_03}.
 
@@
 developing novel spatial discretization methods such as meshfree
-methods like the material point method (MPM). Presence of cracks are a
-violation of the continuity requirement of the finite element method
-(FEM). To overcome it, numerous of numerical artifacts has been
-proposed with the aim of reproduce such a complex behaviour. This
-techniques vary from employing cohesive approaches
-\cite{Barenblatt,Hilleborg_1976}, by adaptively inserting cohesive
-elements \cite{Ortiz_1999,Pandolfi_2002,Ruiz_2000} at solid elements
-boundaries, or handling arbitrary cracks paths by level set
-representation of the fracture surface \cite{Belytschko_03}.
-
-The severe
-limitations of the mesh-dependent methods to simulate fracture
-process, have motivated the development of mesh-free technique to
-reproduce crack propagation such the element-free Galerkin method
-(EFGM) \cite{BELYTSCHKO_1995,BELYTSCHKO_2000,Zhuang_2012,Muthu_2013},
+techniques. Some examples of it are the material
+point method (MPM) \cite{Schreyer_2002,Chen_2002,Nairn_2003,Zhenmao_2005}, the
+element-free Galerkin method (EFGM) \cite{BELYTSCHKO_1995,BELYTSCHKO_2000,Zhuang_2012,Muthu_2013},
 the smoothed particle hydrodynamics (SPH) \cite{Wang_2020,Wang_2019},
@@
 \cite{Li2010,Li_2012,Pandolfi_2013,Li_2015} or peridynamics
-\cite{HA_2011,RABCZUK_2017}.
+\cite{HA_2011,RABCZUK_2017} among others.
 
-By contrast, MPM does not suffer from the above difficulty since the
-continuity requirement is less restrictive. Fracture can be described
-in two ways. One is to remove the restriction of the single-valued
-velocity field close to the crack by using two or more sets of nodes
-\cite{Nairn_2006}. This method is based in to assign different labels
-to distinguish if the material points and nodes are in the same side
-of the crack or not. Under this approach the crack surface is
-described with line segments in 2D and triangle patches in 3D
-cases. This method was named as ``CRAcks with Material Points
-(CRAMP)'' \cite{Nairn_2003}. In this method, the criteria for crack
-propagation is based on such parameters as energy release rate
-analyzed by Tan \& Nairn (2002)\cite{Nairn_2002}, and the stress
-intensity factor or the J-integral discussed by Guo \& Nairn
+Fracture can be described in two ways. One is to remove the
+restriction of the single-valued velocity field close to the crack by
+using two or more sets of nodes \cite{Nairn_2006}. This method is
+based in to assign different labels to distinguish if the material
+points and nodes are in the same side of the crack or not. Under this
+approach the crack surface is described with line segments in 2D and
+triangle patches in 3D cases. This method was named as ``CRAcks with
+Material Points (CRAMP)'' \cite{Nairn_2003}. In this method, the
+criteria for crack propagation is based on such parameters as energy
+release rate analyzed by Tan \& Nairn (2002)\cite{Nairn_2002}, and the
+stress intensity factor or the J-integral discussed by Guo \& Nairn 
 (2004)\cite{Nairn_2004}. The other approach is to use failed material
 points to describe the crack evolution. In this method, the formation
-of failed points describes the nucleation of cracks, and thereafter its propagation and
-branching. Consequently, the position of the crack does not need to be
-explicitly stated. This represents a significant advantage over the
-``CRAMP''. Under this approach, the prediction the failure evolution
-employing a decohesion model has been discussed by Chen {\it et al.}\cite{Zhenmao_2005} or
-Schreyer {\it et al.}\cite{Schreyer_2002}. And has been successfully
-employed to simulate the fracture of brittle materials by Chen {\it et
-  al.} \cite{Chen_2002,Chen_2003} and Sulsky \& Schreyer
-(2004)\nocite{Sulsky_2004}.
+of failed points describes the nucleation of cracks, and thereafter
+its propagation and branching. Consequently, the position of the crack
+does not need to be explicitly stated. This represents a significant
+advantage over the ``CRAMP''. Under this approach, the prediction the
+failure evolution employing a decohesion model has been discussed by
+Chen {\it et al.}\cite{Zhenmao_2005} or Schreyer {\it et
+  al.}\cite{Schreyer_2002}. And has been successfully employed to
+simulate the fracture of brittle materials by Chen {\it et al.}
+\cite{Chen_2002,Chen_2003} and Sulsky \& Schreyer
+\cite{Sulsky_2004}. Similar to this approach, Schmidt {\it et al.}
+\cite{Schmidt_2009} introduced the concept of eigenfracture, where
+they approximate the crack set by means of eigen-deformations, wich
+enable the material to develop displacement jumps at no cost of local
+elastic energy. Later, the eigenerosion approach to brittle facture
+was developed by Pandolfi {\it et al.}
+\cite{Pandolfi_2012,Pandolfi_2013}. In this technique the erosion of
+the material point means that each material point can be either intact
+or be completely failed or eroded and has no load bearing
+capacity. This method has been successfully applied to simulate high
+complex phenomena such dynamic fragmentation of metals \cite{Li_2015},
+nonetheless in quasi-brittle materials, simulations performed with
+this approach exhibit an overestimation of tensile stress and the
+strain peaks. To overcome this limitation, Navas {\it et al.}
+\cite{Navas_2017_ES,Navas2018a} introduced the concept of
+eigensoftening. Engineered for quasi-brittle materials, this approach
+is devoted to capture the gradual rather than abrupt dissipation of
+the fracture energy. It is inspired in the concept of the crack band
+model \cite{Bazant83}, since energy dissipation is thorough the
+softened (or failed) volume. Due to the similarities between the OTM, 
+where this procedure was developed, and the MPM, we propose
 
-\cite{Belytschko_04,Schmidt_2009,Pandolfi_2012}
+The eigensoftening algorithm together with a explicit predictor
+corrector and the local \textit{max-ent} approximation technique
+offers a new perspective in the MPM fracture simulation.
 
-The erosion of the material point means that each material point can
-be either intact or be completely failed or eroded and has no load
-bearing capacity, Even thought the method has been successfully
-applied to dynamic fragmentation of metals, quantitative validations,
-such as stress or strain levels near or at the crack set compared to
-experimental measures are still lacking. Having in mind that the
-eigenerosion approach was intended for perfectly brittle fracture, an
-eigensoftening concept is developed for quasi-brittle materials
+To overcome the difficulties of the e
+
+In the present research we will introduce the
+
+In the current work we attempt to model the fracture propagation
+employing the MPM and introducing both eigenerosion and eigensoftening
+\cite{Navas_2017_ES,Navas_2018_ES} and the concept of the
+eigenfracture under this framework.
+
+Even thought the method has been successfully applied to dynamic
+fragmentation of metals, quantitative validations, such as stress or 
+strain levels near or at the crack set compared to experimental
+measures are still lacking. Having in mind that the eigenerosion
+approach was intended for perfectly brittle fracture, an
+eigensoftening concept is developed for quasi-brittle materials.
+
+This document is structured as follows
 
@@
 \label{sec:2}
-
 The aim of this section is to provide an overview of the special
@@
 \label{sec:2.1}
-
 The MPM~\cite{Sulsky1994} is a meshfree Lagrangian-Eulerian method
@@
 definition given by Shannon (1948) \cite{Shannon1948}, and $U(\vec{x}_p,N_I) =
-\sum_I N_I |\vec{x}_p - \vec{x}_I |^2$ a 
-magnitude of the shape function width. The regularization o
-\textit{thermalization} parameter between the two criterion $\beta$
-has Pareto optimal values in the range $(0,\infty)$. The unique
-solution of the local max-ent problem (LME)$_\beta$ is
+\sum_I N_I |\vec{x}_p - \vec{x}_I |^2$ a magnitude of the shape
+function width. The regularization o \textit{thermalization} parameter
+between the two criterion $\beta$ has Pareto optimal values in the
+range $(0,\infty)$. The unique solution of the local \textit{max-ent} problem
+(LME)$_\beta$ is,
  \begin{equation}
@@
 range of neighbours, see \cite{Arroyo2006} for details. This tolerance defines
-the limit values of the influence radius and is used thereafter to
+a limit values of the influence radius and is used thereafter to
 find the neighbour nodes of a given integration point.

### 2020-04-25 _region_.tex
Cambios 24-4-2020

@@
 \cite{Li2010,Li_2012,Pandolfi_2013,Li_2015} or peridynamics
-\cite{HA_2011,RABCZUK_2017}.
+\cite{HA_2011,RABCZUK_2017} among others.
 
-By contrast, MPM does not suffer from the above difficulty since the
-continuity requirement is less restrictive. Fracture can be described
-in two ways. One is to remove the restriction of the single-valued
-velocity field close to the crack by using two or more sets of nodes
-\cite{Nairn_2006}. This method is based in to assign different labels
-to distinguish if the material points and nodes are in the same side
-of the crack or not. Under this approach the crack surface is
-described with line segments in 2D and triangle patches in 3D
-cases. This method was named as ``CRAcks with Material Points
-(CRAMP)'' \cite{Nairn_2003}. In this method, the criteria for crack
-propagation is based on such parameters as energy release rate
-analyzed by Tan \& Nairn (2002)\cite{Nairn_2002}, and the stress
-intensity factor or the J-integral discussed by Guo \& Nairn
+Fracture can be described in two ways. One is to remove the
+restriction of the single-valued velocity field close to the crack by
+using two or more sets of nodes \cite{Nairn_2006}. This method is
+based in to assign different labels to distinguish if the material
+points and nodes are in the same side of the crack or not. Under this
+approach the crack surface is described with line segments in 2D and
+triangle patches in 3D cases. This method was named as ``CRAcks with
+Material Points (CRAMP)'' \cite{Nairn_2003}. In this method, the
+criteria for crack propagation is based on such parameters as energy
+release rate analyzed by Tan \& Nairn (2002)\cite{Nairn_2002}, and the
+stress intensity factor or the J-integral discussed by Guo \& Nairn 
 (2004)\cite{Nairn_2004}. The other approach is to use failed material
 points to describe the crack evolution. In this method, the formation
-of failed points describes the nucleation of cracks, and thereafter its propagation and
-branching. Consequently, the position of the crack does not need to be
-explicitly stated. This represents a significant advantage over the
-``CRAMP''. Under this approach, the prediction the failure evolution
-employing a decohesion model has been discussed by Chen {\it et al.}\cite{Zhenmao_2005} or
-Schreyer {\it et al.}\cite{Schreyer_2002}. And has been successfully
-employed to simulate the fracture of brittle materials by Chen {\it et
-  al.} \cite{Chen_2002,Chen_2003} and Sulsky \& Schreyer
-(2004)\nocite{Sulsky_2004}.
+of failed points describes the nucleation of cracks, and thereafter
+its propagation and branching. Consequently, the position of the crack
+does not need to be explicitly stated. This represents a significant
+advantage over the ``CRAMP''. Under this approach, the prediction the
+failure evolution employing a decohesion model has been discussed by
+Chen {\it et al.}\cite{Zhenmao_2005} or Schreyer {\it et
+  al.}\cite{Schreyer_2002}. And has been successfully employed to
+simulate the fracture of brittle materials by Chen {\it et al.}
+\cite{Chen_2002,Chen_2003} and Sulsky \& Schreyer
+\cite{Sulsky_2004}. Similar to this approach, Schmidt {\it et al.}
+\cite{Schmidt_2009} introduced the concept of eigenfracture, where
+they approximate the crack set by means of eigen-deformations, wich
+enable the material to develop displacement jumps at no cost of local
+elastic energy. Later, the eigenerosion approach to brittle facture
+was developed by Pandolfi {\it et al.}
+\cite{Pandolfi_2012,Pandolfi_2013}. In this technique the erosion of
+the material point means that each material point can be either intact
+or be completely failed or eroded and has no load bearing
+capacity. This method has been successfully applied to simulate high
+complex phenomena such dynamic fragmentation of metals \cite{Li_2015},
+nonetheless in quasi-brittle materials, simulations performed with
+this approach exhibit an overestimation of tensile stress and the
+strain peaks. To overcome this limitation, Navas {\it et al.}
+\cite{Navas_2017_ES,Navas2018a} introduced the concept of
+eigensoftening. Engineered for quasi-brittle materials, this approach
+is devoted to capture the gradual rather than abrupt dissipation of
+the fracture energy. It is inspired in the concept of the crack band
+model \cite{Bazant83}, since energy dissipation is thorough the
+softened (or failed) volume. Due to the similarities between the OTM, 
+where this procedure was developed, and the MPM, we propose
 
-\cite{Belytschko_04,Schmidt_2009,Pandolfi_2012}
+To overcome the difficulties of the e
 
-The erosion of the material point means that each material point can
-be either intact or be completely failed or eroded and has no load
-bearing capacity, Even thought the method has been successfully
-applied to dynamic fragmentation of metals, quantitative validations,
-such as stress or strain levels near or at the crack set compared to
-experimental measures are still lacking. Having in mind that the
-eigenerosion approach was intended for perfectly brittle fracture, an
+In the present research we will introduce the
+
+In the current work we attempt to model the fracture propagation
+employing the MPM and introducing both eigenerosion
+ and eigensoftening \cite{Navas_2017_ES,Navas_2018_ES} and the concept of the
+eigenfracture under this framework.
+
+Even thought the method has been successfully applied to dynamic
+fragmentation of metals, quantitative validations, such as stress or 
+strain levels near or at the crack set compared to experimental
+measures are still lacking. Having in mind that the eigenerosion
+approach was intended for perfectly brittle fracture, an
 eigensoftening concept is developed for quasi-brittle materials
@@
 \end{document}
-\message{ !name(2020_EFM_MPM_Eigensoftening.tex) !offset(-660) }
+\message{ !name(2020_EFM_MPM_Eigensoftening.tex) !offset(-676) }

### 2020-05-18 2020_EFM_MPM_Eigensoftening.tex
Cambios 18-5-2020

@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Init macros math
+
 \usepackage{amsmath,amsthm,amssymb}
@@
 
-\newcommand{\vec}[1]{
+\newcommand{\vect}[1]{
   \ensuremath{\mathbf{{#1}}}
@@
 }
+% End macros math
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Init glossaries
+\usepackage[acronym]{glossaries}
+
+\makeglossaries
+
+\newglossaryentry{domain}
+{
+  name=$\varOmega$,
+  description={Continuum domain}
+}
+
+\newglossaryentry{contour}
+{
+  name=$\partial\varOmega$,
+  description={Boundary of the continuum domain $\varOmega$. Also
+    defined as $\Gamma$}
+}
+
+\newglossaryentry{dirichlet-boundary}
+{
+  name=$ \Gamma_d$,
+  description={Essential or Dirichlet boundary conditions over $\partial\varOmega$}
+}
+
+\newglossaryentry{neumann-boundary}
+{
+  name=$ \Gamma_n$,
+  description={Natural or Nemann boundary conditions over $\partial\varOmega$}
+}
+
+\newglossaryentry{rho}
+{
+  name=$\rho$,
+  description={Describes the scalar density field}
+}
+
+\newglossaryentry{a}
+{
+  name=$\vect{a}$,
+  description={First order tensor which describes the acceleration field}
+}
+
+\newglossaryentry{v}
+{
+  name=$\vect{v}$,
+  description={First order tensor which describes the velocity field}
+}
+
+\newglossaryentry{u}
+{
+  name=$\vect{u}$,
+  description={First order tensor which describes the displacement field}
+}
+
+\newglossaryentry{x}
+{
+  name=$\vect{x}$,
+  description={First order tensor which describes the global coordinates field}
+}
+
+\newglossaryentry{xi}
+{
+  name=$\vect{\xi}$,
+  description={First order tensor which describes the local coordinates field}
+}
+
+\newglossaryentry{stress}
+{
+  name=$\tens{\sigma}$,
+  description={Second order tensor which means the Cauchy stress tensor}
+}
+
+\newglossaryentry{strain}
+{
+  name=$\tens{\varepsilon}$,
+  description={Second order tensor which means the Cauchy strain tensor}
+}
+
+\newglossaryentry{Constitutive}
+{
+  name=$\tens{D}$,
+  description={Four order tensor which means the constitutive response
+    of the material}
+}
+
+\newglossaryentry{LME-beta}
+{
+  name=$\beta$,
+  description={Regularization or thermalization parameter of the
+    LME$_{\beta}$ Pareto set}
+}
+
+\newacronym{mpm}{MPM}{Material Point Method}
+\newacronym{otm}{OTM}{Optimal Transportation Meshfree}
+\newacronym{sph}{SPH}{Smoothed Particle Hydrodynamics}
+\newacronym{fem}{FEM}{Finite Element Method}
+\newacronym{efgm}{EFGM}{Element-Free Galerkin Method}
+\newacronym{lme}{LME}{Local Maximum-Entropy}
+\newacronym{flip}{FLIP}{Fluid Implicit Particle}
+\newacronym{gimp}{GIMP}{Generalized Interpolation Material Point}
+\newacronym{igimp}{iGIMP}{Implicit GIMP}
+\newacronym{ugimp}{uGIMP}{Uniform GIMP}
+\newacronym{ddmp}{DDMP}{Dual Domain Material Point}
+\newacronym{ctls}{CTLS}{Conservative Taylor Least Squares}
+\newacronym{npc}{NPC}{Newmark Predictor-Corrector}
+\newacronym{fe}{FE}{Forward Euler}
+
+% End glossaries
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
   technique to address the fracture process of brittle and
-  quasi-brittle materials under the material point method (MPM)
+  quasi-brittle materials under the \acrfull{mpm} 
   framework. With this purpose the eigensoftening algorithm, developed
-  originally for the optimal transportation meshfree (OTM)
-  approximation scheme, is extended to the MPM with the aim of present
-  a suitable alternative to the existing fracture algorithms developed
-  for the MPM. The good fitting in the predictions made by the
-  eigensoftening algorithm against both analytical and experimental
-  results proofs the well performance of the method under challenging loads.
+  originally for the \acrfull{otm} approximation scheme, is extended
+  to the \acrshort{mpm} with the aim of present a suitable alternative to the
+  existing fracture algorithms developed for the \acrshort{mpm}. The good fitting
+  in the predictions made by the eigensoftening algorithm against both
+  analytical and experimental results proofs the well performance of
+  the method under challenging loads.
 \end{abstract}
@@
 \label{sec:1}
-Presence of cracks are a violation of the continuity requirement of
-the finite element method (FEM). To overcome it, numerous of numerical
+Presence of cracks are a violation of the continuity requirement in
+\acrfull{fem}. To overcome it, numerous of numerical
 artifacts has been proposed with the aim of reproducing  such a
@@
 developing novel spatial discretization methods such as meshfree
-techniques. Some examples of it are the material
-point method (MPM) \cite{Schreyer_2002,Chen_2002,Nairn_2003,Zhenmao_2005}, the
-element-free Galerkin method (EFGM) \cite{BELYTSCHKO_1995,BELYTSCHKO_2000,Zhuang_2012,Muthu_2013},
-the smoothed particle hydrodynamics (SPH) \cite{Wang_2020,Wang_2019},
-the optimal transportation meshfree method (OTM)
-\cite{Li2010,Li_2012,Pandolfi_2013,Li_2015} or peridynamics
+techniques. Some examples of it are the \acrfull{mpm}
+\cite{Schreyer_2002,Chen_2002,Nairn_2003,Zhenmao_2005}, the \acrfull{efgm}  \cite{BELYTSCHKO_1995,BELYTSCHKO_2000,Zhuang_2012,Muthu_2013},
+the \acrfull{sph} \cite{Wang_2020,Wang_2019},
+the \acrfull{otm} \cite{Li2010,Li_2012,Pandolfi_2013,Li_2015} or Peridynamics
 \cite{HA_2011,RABCZUK_2017} among others.
@@
 model \cite{Bazant83}, since energy dissipation is thorough the
-softened (or failed) volume. Due to the similarities between the OTM, 
-where this procedure was developed, and the MPM, we propose
+softened (or failed) volume. Due to the similarities between the \acrshort{otm}, 
+where this procedure was developed, and the \acrshort{mpm}, we propose
 
@@
 corrector and the local \textit{max-ent} approximation technique
-offers a new perspective in the MPM fracture simulation.
+offers a new perspective in the \acrshort{mpm} fracture simulation.
 
@@
 In the current work we attempt to model the fracture propagation
-employing the MPM and introducing both eigenerosion and eigensoftening
+employing the \acrshort{mpm} and introducing both eigenerosion and eigensoftening
 \cite{Navas_2017_ES,Navas_2018_ES} and the concept of the
@@
 The aim of this section is to provide an overview of the special
-techniques employed to face the fracture problem under the MPM
+techniques employed to face the fracture problem under the \acrshort{mpm}
 framework. In consequence it is structured as follows: first in
-\ref{sec:2.1} the explicit-predictor algorithm for the
-MPM will be exposed, next the local \textit{max-ent} approximants are introduced in
+\ref{sec:2.1} the explicit-predictor algorithm for the \acrshort{mpm} will be exposed, next the local \textit{max-ent} approximants are introduced in
 \ref{sec:2.2} as an accurate alternative technique to interpolate data
@@
 \label{sec:2.1}
-The MPM~\cite{Sulsky1994} is a meshfree Lagrangian-Eulerian method
+The \acrshort{mpm}~\cite{Sulsky1994} is a meshfree Lagrangian-Eulerian method
 where particles carries on all the physical information and a set of
 background nodes is employed to compute the equilibrium
-equation. Since the MPM possesses the advantages of both Lagrangian
-and Eulerian descriptions, no element distortion exists in the MPM,
+equation. Since the \acrshort{mpm} possesses the advantages of both Lagrangian
+and Eulerian descriptions, no element distortion exists in the \acrshort{mpm},
 therefore it is an appropriate and efficient method in solving
@@
 discretization, two sets of points are introduced in 
-the MPM. First, the nodes. This points are considered fixed in the
+the \acrshort{mpm}. First, the nodes. This points are considered fixed in the
 space and are in charge of computing all the kinematic fields such
@@
 of the continuum, and store the local state ($\sigma_p,
-\varepsilon_p$). Without loosing generality, the MPM algorithm
+\varepsilon_p$). Without loosing generality, the \acrshort{mpm} algorithm
 can be described with three main steps: (i) a variational recovery
@@
 range $(0,\infty)$. The unique solution of the local \textit{max-ent} problem
-(LME)$_\beta$ is,
+ \acrshort{lme}$_\beta$ is,
  \begin{equation}
@@
 \end{eqnarray}
-The regularization parameter $\beta$ of LME shape functions may be
+The regularization parameter $\beta$ of \acrshort{lme} shape functions may be
 controlled by adjusting a dimensionless parameter, $\gamma=\beta h^2$
@@
 \label{sec:2.3}
-Within the context of MPM formulation, fracture can be modelled by
+Within the context of \acrshort{mpm} formulation, fracture can be modelled by
 failing particles according to a suitable criterion. When material
@@
 
-\subsection{Comparison with analytical solution}
-\label{sec:3.1}
+\subsection{Edge-cracked square panel in mode I}
+\label{sec:edge-cracked-square-I}
 
-\subsection{Brazilian test}
-\label{sec:3.2}
+This problem is devoted to compare the develop of both linear shape
+functions and the \acrshort{lme}
 
@@
   \centering
-  \includegraphics[width=0.3\textwidth]{Figures/Brazilian}
-  \caption{Geometry and boundary condition of the Brazilian test.}
-  \label{fig:geometry-brazilian-test}
+  \includegraphics[width=0.8\textwidth]{Figures/Mode_I}
+  \caption{Geometry and boundary condition of the drop-weight impact test.}
+  \label{fig:geometry-cracked-panel-mode-I}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.8\textwidth]{Figures/Reactions_displacements_square_panel_mode_I}
+  \caption{Geometry and boundary condition of the drop-weight impact test.}
+  \label{fig:geometry-cracked-panel-mode-I}
 \end{figure}
@@
 \section*{Acknowledgements}
-The first author acknowledges the fellowship Agustín de Betancourt 262390106114.
+The financial support to develop this research from the Ministerio de
+Ciencia e Innovaci\'on, under Grant No. BIA-2016-76253 is greatly
+appreciated. The first and the second authors also acknowledge the
+fellowship Fundaci\'on Agust\'in de Betancourt and Juan de la Cierva
+(FJCI-2017–31544) respectively.
 

### 2020-05-18 _region_.tex
Cambios 18-5-2020

@@
 model \cite{Bazant83}, since energy dissipation is thorough the
-softened (or failed) volume. Due to the similarities between the OTM, 
-where this procedure was developed, and the MPM, we propose
+softened (or failed) volume. Due to the similarities between the \acrshort{otm}, 
+where this procedure was developed, and the \acrshort{mpm}, we propose
+
+The eigensoftening algorithm together with a explicit predictor
+corrector and the local \textit{max-ent} approximation technique
+offers a new perspective in the \acrshort{mpm} fracture simulation.
 
@@
 In the current work we attempt to model the fracture propagation
-employing the MPM and introducing both eigenerosion
- and eigensoftening \cite{Navas_2017_ES,Navas_2018_ES} and the concept of the
+employing the \acrshort{mpm} and introducing both eigenerosion and eigensoftening
+\cite{Navas_2017_ES,Navas_2018_ES} and the concept of the
 eigenfracture under this framework.
@@
 approach was intended for perfectly brittle fracture, an
-eigensoftening concept is developed for quasi-brittle materials
+eigensoftening concept is developed for quasi-brittle materials.
+
+This document is structured as follows
 
@@
 \end{document}
-\message{ !name(2020_EFM_MPM_Eigensoftening.tex) !offset(-676) }
+\message{ !name(2020_EFM_MPM_Eigensoftening.tex) !offset(-813) }

### 2020-05-18 Documentacion/2_Material.py

@@ -1,0 +1,466 @@
+import glob,os
+import numpy as np
+import matplotlib.pyplot as plt
+from mpl_toolkits.mplot3d import Axes3D
+from matplotlib import cm
+from matplotlib.ticker import LinearLocator
+from matplotlib.ticker import FixedLocator
+from matplotlib.ticker import FormatStrFormatter
+
+def find_nearest(array, value):
+    array = np.asarray(array)
+    idx = (np.abs(array - value)).argmin()
+    return idx
+
+def Get_Riemann_I(Stress_I,Velocity_I,nu):
+    R_I = (0.5/nu)*(- Stress_I + Velocity_I*nu)
+    return R_I
+
+def Get_Riemann_II(Stress_II,Velocity_II,nu):
+    R_II = (0.5/nu)*(Stress_II + Velocity_II*nu)
+    return R_II
+
+def Dyka_Riemann(CFL,T_END,i_RES):
+                     
+    # Material properties
+    L = 380
+    x_a = 0
+    x_b = L*0.1
+    x_c = L
+    
+    E_ab = 210*10**3 # MPa
+    rho_ab = 7.8*10**(-9) # Tn/mm³
+    CEL_ab = np.sqrt(E_ab/rho_ab)
+    E_bc = 210*10**3 # MPa
+    rho_bc = 1.2*10**(-7) # Tn/mm³
+    CEL_bc = np.sqrt(E_bc/rho_bc)
+
+    CEL = max(CEL_ab,CEL_bc)
+
+    # Discretize domain
+    DeltaX = 1
+    N_nodes = int(L/DeltaX)
+    X = np.linspace(x_a,x_c,N_nodes)
+    I_a = find_nearest(X,x_a)
+    I_b = find_nearest(X,x_b)
+    I_c = find_nearest(X,x_c)    
+
+    # Discretize time
+    N_steps = int(T_END/(1*CFL/CEL))
+    DeltaT = CFL*DeltaX/CEL
+    T = np.linspace(0.0,T_END,int(N_steps/i_RES))
+
+    # Initial conditions
+    v0 = -500
+    Stress = np.zeros([int(N_steps/i_RES),N_nodes])
+    Velocity = np.zeros([int(N_steps/i_RES),N_nodes])
+    for x in range(0,N_nodes):
+        if X[x] <= 10 :
+            Velocity[0,x] = v0
+        else :
+            Velocity[0,x] = 0
+        
[…]

### 2020-05-18 Documentacion/Geometria_martillo.py

@@ -1,0 +1,25 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+Mass_hummer = 120E-3 # Tons
+L_1 = 38 # mm
+rho_1 = 7.85E-9 # Tons/mm^3
+E = 210E3 # N/mm^2
+R = 14
+B = 28
+H = 100
+T_end = 550E-6 # sg
+
+rho_2 = np.linspace(1E-8,3E-7,100)
+
+# Restriction 1 (Celerity)
+L_R1 = (2*L_1*(np.sqrt(rho_2) - np.sqrt(rho_1)) + T_end*np.sqrt(E))/(2*np.sqrt(rho_2))
+
+# Restriction 2 (Mass)
+L_R2 = (Mass_hummer - B*H*rho_1*(L_1-R) - 0.5*np.pi*R*R*H*rho_1 + B*H*L_1*rho_2)/(B*H*rho_2)
+
+
+plt.plot(rho_2,L_R1,label='Celerity restriction')
+plt.plot(rho_2,L_R2,label='Mass restriction')
+plt.legend()
+plt.show()

### 2020-05-18 Documentacion/Hummer_gap.py

@@ -1,0 +1,23 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+E = 210E3 # N/mm^2
+rho1 = 7.85E-9 # Tons/mm^3
+rho2 = 1.2E-7 # Tons/mm^3
+L = 390 # mm
+L1 = 38 # mm
+L2 = L-L1 # mm
+V_hummer = [881,1760,2640] # mm/s 
+CFL = 0.1
+Cel1 = np.sqrt(E/rho1) # mm/s
+Cel2 = np.sqrt(E/rho2) # mm/s
+DeltaX = np.linspace(0.1,1.0,100)
+# DeltaX = np.array([0.1,0.5,1.0])
+DeltaT = (CFL/Cel1)*DeltaX
+
+for i in range(0,3):
+    Tend = DeltaX/V_hummer[i] + 2*L1/Cel1 + 2*L2/Cel2
+    Nsteps = Tend/DeltaT
+    plt.plot(Tend,Nsteps, label="Hummer vel : %f"%V_hummer[i])
+plt.legend()
+plt.show()

### 2020-05-19 2020_EFM_MPM_Eigensoftening.tex
Cambios 19-5-2020

@@
-\documentclass[preprint,12pt,a4paper]{elsarticle}
-
-\usepackage{lineno,hyperref}
+% \documentclass[preprint,12pt,a4paper]{elsarticle}
+\documentclass[12pt,a4paper]{elsarticle}
+\usepackage{lineno}
+\usepackage{hyperref}
 \usepackage{float}
-\usepackage{subfig}
+\usepackage{graphicx} % figuras
+% \usepackage{subfig}
+\usepackage{subfigure} % subfiguras
 \usepackage{color}
 \usepackage{soul}
-
-\usepackage{algcompatible}
-\usepackage{algorithm}
-\usepackage{algorithmic}
-\usepackage{algpseudocode}
-
 \usepackage{cancel}
@@
 
-\usepackage{amsmath,amsthm,amssymb}
+\usepackage[fleqn,tbtags]{amsmath}
+\usepackage{mathtools}
+\usepackage{amsthm,amssymb}
 \usepackage{xstring}
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%\usepackage{algorithm,algcompatible}
+\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
+\algnewcommand\INPUT{\item[\textbf{Input:}]}%
+\algnewcommand\OUTPUT{\item[\textbf{Output:}]}%
 
@@
 
+% \title{An enhanced EigenMPM }
+
 %% Group authors per affiliation:
 \author{
-Miguel Molinos$^a$,
-and Pedro Navas$^a$\footnote{Corresponding author: p.navas@upm.es}
+Miguel Molinos$^a$\footnote{Corresponding author: m.molinos@alumnos.upm.es},
+Pedro Navas$^a$\footnote{Corresponding author: p.navas@upm.es},
+Diego Manzanal$^a$,
+and Manuel Pastor$^a$
  }
@@
   originally for the \acrfull{otm} approximation scheme, is extended
-  to the \acrshort{mpm} with the aim of present a suitable alternative to the
-  existing fracture algorithms developed for the \acrshort{mpm}. The good fitting
-  in the predictions made by the eigensoftening algorithm against both
-  analytical and experimental results proofs the well performance of
-  the method under challenging loads.
+  to the \acrshort{mpm} with the aim of present a suitable alternative
+  to the existing fracture algorithms developed for the
+  \acrshort{mpm}. The good fitting in the predictions made by the
+  eigensoftening algorithm against both analytical and experimental
+  results proofs the well performance of the method under challenging
+  loads.
 \end{abstract}
@@
 artifacts has been proposed with the aim of reproducing such a
-complex behaviour. This techniques vary from employing cohesive
+complex behaviour. These techniques vary from employing cohesive
 approaches \cite{Barenblatt,Hilleborg_1976}, by adaptively inserting
@@
 elements boundaries, or handling arbitrary cracks paths by level set
-representation of the fracture surface \cite{Belytschko_03}.
+representation of the fracture surface \cite{Belytschko_03}. The
+simulation of fracture propagation in a more accurate and effective
+way can be considered as one of the original drivers for developing
+novel spatial discretization methods like meshfree techniques. Some
+examples of it are the \acrfull{mpm}
+\cite{Schreyer_2002,Chen_2002,Nairn_2003,Zhenmao_2005}, the
+\acrfull{efgm} \cite{BELYTSCHKO_1995,BELYTSCHKO_2000,Zhuang_2012,Muthu_2013}, the
+\acrfull{sph} \cite{Wang_2020,Wang_2019}, the \acrfull{otm} \cite{Li2010,Li_2012,Pandolfi_2013,Li_2015} or Peridynamics
+\cite{HA_2011,RABCZUK_2017} among others. \\
 
-The simulation of fracture propagation in a more accurate and
-effective way can be considered as one of the original drivers for
-developing novel spatial discretization methods such as meshfree
-techniques. Some examples of it are the \acrfull{mpm}
-\cite{Schreyer_2002,Chen_2002,Nairn_2003,Zhenmao_2005}, the \acrfull{efgm}  \cite{BELYTSCHKO_1995,BELYTSCHKO_2000,Zhuang_2012,Muthu_2013},
-the \acrfull{sph} \cite{Wang_2020,Wang_2019},
-the \acrfull{otm} \cite{Li2010,Li_2012,Pandolfi_2013,Li_2015} or Peridynamics
-\cite{HA_2011,RABCZUK_2017} among others.
+Regarding \acrshort{mpm}, fracture can be described numerically in
+two ways. One is the ``CRAcks with Material Points (CRAMP)''
+\cite{Nairn_2003,Nairn_2006} and consist in to remove the restriction
+of the single-valued velocity field close to the crack thorough two or
+more sets of nodes. In this method, different labels are assigned to the material points
+and nodes to distinguish if they are in the same side of the crack or
+not. Under this approach crack surface is described with line segments
+in 2D and triangle patches in 3D cases. The chosen criteria for crack
+propagation is based on such parameters as energy release rate
+analyzed by Tan \& Nairn (2002)\cite{Nairn_2002}, and the stress
+intensity factor or the J-integral discussed by Guo \& Nairn
+(2004)\cite{Nairn_2004}. The other approach is to introduce failed
+material points to describe the crack evolution. In this method, the
+formation of failed points describes the nucleation of cracks, and
+thereafter its propagation and branching. Consequently, the position
+of the crack does not need to be explicitly stated. These represents
+significant advantages over the ``CRAMP''. Under this approach, the
+prediction of failure evolution is computed with a decohesion model,
+which has been discussed by Chen {\it et al.}\cite{Zhenmao_2005} and
+Schreyer {\it et al.}\cite{Schreyer_2002}. And has been successfully
+employed to simulate the fracture of brittle materials by Chen {\it et
+  al.} \cite{Chen_2002,Chen_2003} and Sulsky \& Schreyer
+\cite{Sulsky_2004}.\\
 
-Fracture can be described in two ways. One is to remove the
-restriction of the single-valued velocity field close to the crack by
-using two or more sets of nodes \cite{Nairn_2006}. This method is
-based in to assign different labels to distinguish if the material
-points and nodes are in the same side of the crack or not. Under this
-approach the crack surface is described with line segments in 2D and
-triangle patches in 3D cases. This method was named as ``CRAcks with
-Material Points (CRAMP)'' \cite{Nairn_2003}. In this method, the
-criteria for crack propagation is based on such parameters as energy
-release rate analyzed by Tan \& Nairn (2002)\cite{Nairn_2002}, and the
-stress intensity factor or the J-integral discussed by Guo \& Nairn 
-(2004)\cite{Nairn_2004}. The other approach is to use failed material
-points to describe the crack evolution. In this method, the formation
-of failed points describes the nucleation of cracks, and thereafter
-its propagation and branching. Consequently, the position of the crack
-does not need to be explicitly stated. This represents a significant
-advantage over the ``CRAMP''. Under this approach, the prediction the
-failure evolution employing a decohesion model has been discussed by
-Chen {\it et al.}\cite{Zhenmao_2005} or Schreyer {\it et
-  al.}\cite{Schreyer_2002}. And has been successfully employed to
-simulate the fracture of brittle materials by Chen {\it et al.}
-\cite{Chen_2002,Chen_2003} and Sulsky \& Schreyer
-\cite{Sulsky_2004}. Similar to this approach, Schmidt {\it et al.}
+Similar to this approach, Schmidt {\it et al.}
 \cite{Schmidt_2009} introduced the concept of eigenfracture, where
@@
 \cite{Pandolfi_2012,Pandolfi_2013}. In this technique the erosion of
-the material point means that each material point can be either intact
-or be completely failed or eroded and has no load bearing
+the material point means that each material point can be either intact or be completely failed or eroded and has no load bearing
 capacity. This method has been successfully applied to simulate high
-complex phenomena such dynamic fragmentation of metals \cite{Li_2015},
-nonetheless in quasi-brittle materials, simulations performed with
-this approach exhibit an overestimation of tensile stress and the
-strain peaks. To overcome this limitation, Navas {\it et al.}
-\cite{Navas_2017_ES,Navas2018a} introduced the concept of
-eigensoftening. Engineered for quasi-brittle materials, this approach
-is devoted to capture the gradual rather than abrupt dissipation of
-the fracture energy. It is inspired in the concept of the crack band
-model \cite{Bazant83}, since energy dissipation is thorough the
-softened (or failed) volume. Due to the similarities between the \acrshort{otm}, 
-where this procedure was developed, and the \acrshort{mpm}, we propose
+complex phenomena such dynamic fragmentation of metals
+\cite{Li_2015}. Recently, Zhang {\it et al.}
+\cite{Zhang_EE_2020} adopted the eigenerosion to resolve the dynamic
+fracture of brittle materials in the \acrshort{mpm}
+framework. Nonetheless, in quasi-brittle materials simulations
+performed with this approach exhibit an overestimation of tensile
+stress and the strain peaks. And conventional \acrshort{mpm}/\acrshort{gimp} always
+faces stress oscillations.\\
 
-The eigensoftening algorithm together with a explicit predictor
-corrector and the local \textit{max-ent} approximation technique
-offers a new perspective in the \acrshort{mpm} fracture simulation.
+To overcome the limitations observed in the EigenMPM
+\cite{Zhang_EE_2020}. The present research propose the eigensoftening
+algorithm developed by Navas {\it et al.}
+\cite{Navas_2017_ES,Navas2018a} for the \acrshort{otm} framework and
+engineered for quasi-brittle materials. Inspired in the concept of the
+crack band model \cite{Bazant83}, since energy dissipation is thorough
+the softened (or failed) volume, it is able to capture the gradual rather than abrupt
+dissipation of the fracture energy. Second, to mitigate stress
+oscillations the \acrfull{lme} approximation technique
+\cite{Arroyo2006} to deal with tensile instabilities, such those that
+occurs when particles crosses an element boundary.\\
 
-To overcome the difficulties of the e
-
-In the present research we will introduce the
-
-In the current work we attempt to model the fracture propagation
-employing the \acrshort{mpm} and introducing both eigenerosion and eigensoftening
-\cite{Navas_2017_ES,Navas_2018_ES} and the concept of the
-eigenfracture under this framework.
-
-Even thought the method has been successfully applied to dynamic
-fragmentation of metals, quantitative validations, such as stress or 
-strain levels near or at the crack set compared to experimental
-measures are still lacking. Having in mind that the eigenerosion
-approach was intended for perfectly brittle fracture, an
-eigensoftening concept is developed for quasi-brittle materials.
-
-This document is structured as follows
+The paper is structured as follows. First meshfree methodology,
+eigenerosion and eigensoftening algorithms are presented in Section
+\ref{sec:2}. Then, both approaches are compared and verified by means of
+comparisons with analytical and experimental results in Section
+\ref{sec:3}. Finally, relevant conclusions are exposed in Section \ref{sec:4}.
 
@@
 \label{sec:2}
+
 The aim of this section is to provide an overview of the special
@@
 framework. In consequence it is structured as follows: first in
-\ref{sec:2.1} the explicit-predictor algorithm for the \acrshort{mpm} will be exposed, next the local \textit{max-ent} approximants are introduced in
-\ref{sec:2.2} as an accurate alternative technique to interpolate data
-between particles and nodes, and finally the fracture algorithms based
-in the eigendeformations are presented in \ref{sec:2.3}.
+\ref{sec:2.1} the \acrfull{npc} algorithm for the \acrshort{mpm}
+will be exposed, next the \acrshort{lme} approximants are
+introduced in \ref{sec:2.2} as an accurate alternative technique to
+interpolate data between particles and nodes, and finally fracture
+algorithms based in the eigendeformation concept are presented in \ref{sec:2.3}.
 
-\subsection{The Material Point Method}
+\subsection{The \acrshort{mpm} time integration : A \acrlong{npc}  scheme}
 \label{sec:2.1}
-The \acrshort{mpm}~\cite{Sulsky1994} is a meshfree Lagrangian-Eulerian method
-where particles carries on all the physical information and a set of
-background nodes is employed to compute the equilibrium
-equation. Since the \acrshort{mpm} possesses the advantages of both Lagrangian
-and Eulerian descriptions, no element distortion exists in the \acrshort{mpm},
-therefore it is an appropriate and efficient method in solving
-problems involving extremely large deformation and moving
-discontinuities such fracture evolution. For the spatial
-discretization, two sets of points are introduced in 
-the \acrshort{mpm}. First, the nodes. This points are considered fixed in the
-space and are in charge of computing all the kinematic fields such
-forces $f_I$, accelerations $a_I$ and velocities $v_I$. And second the
-material points or particles. They are in charge of the discretization
-of the continuum, and store the local state ($\sigma_p,
-\varepsilon_p$). Without loosing generality, the \acrshort{mpm} algorithm
+The \acrshort{mpm}~\cite{Sulsky1994} is a meshfree Lagrangian-Eulerian
+method where moving material points, henceforth particles, carries on
+all the physical information of the local state ($\sigma_p,
+\varepsilon_p$) and a set of fixed background nodes is employed to
+compute the balance of momentum equation. Since the \acrshort{mpm}
+possesses the advantages of both Lagrangian and Eulerian descriptions,
+no element distortion takes place in the \acrshort{mpm}. Therefore it
+is an appropriate and efficient method to solve problems with moving
+discontinuities such as fracture evolution.\\
+Without loosing generality, the \acrshort{mpm} algorithm
 can be described with three main steps: (i) a variational recovery
@@
 Eulerian step, where balance of momentum equation is expressed as a
-nodal equilibrium equation thorough a FEM-like procedure, and finally
+nodal equilibrium equation in a FEM-like procedure, and finally
 (iii) a Lagrangian advection of the particles. In the present research
-a explicit predictor-corrector time integration
-scheme is adopted. The purpose of this choice is motivated due its proved
-robustness and stability in numerical calculations. In the first stage
-(i), the nodal velocity predictor is computed following
-\eqref{eq:Predictor-velocity}, 
+a explicit predictor-corrector time integration scheme is adopted. The
+purposes of this choice is motivated due its proved robustness and
+stability for dynamic computations. In the first stage, the nodal
+velocity predictor is computed following \eqref{eq:Predictor-velocity}, 
 \begin{equation}
   \label{eq:Predictor-velocity}
-  \vec{\tilde{v}}_I^{k+1} = \frac{ N_{Ip}^{k} m_p (\vec{v}_p^k + (1 - \gamma)\ \Delta t\ \vec{a}_p^k)}{m_I}
+  \vec{\tilde{v}}_I^{k+1} = \frac{ N_{Ip}^{k} m_p (\vec{v}_p^k + (1 - \gamma)\ \Delta t\ \vec{a}_p^k)}{\tens{m}_I^{k+1}}\ .
 \end{equation}
 This way of computing the nodal predictor is both numerically stable
-and minimize the computational effort. Once nodal velocity are
-obtained, the essential boundary conditions are imposed. And in the
-following, a Eulerian phase (ii) is computed in the set of nodes in a
-FEM-like way, where nodal forces $\vec{f}_{I}^{k+1}$ are computed thorough the
-equilibrium equation. Next the nodal velocities are corrected in a
-\textit{corrector} stage,
+and minimise the computational effort. Once nodal velocities are
+obtained, the essential boundary conditions are imposed. After that, a
+Eulerian phase is computed in the set of nodes in a
+\acrshort{fem}-like way, where nodal forces $\vec{f}_{I}^{k+1}$ are
+computed thorough the equilibrium equation. Next the nodal velocities
+are corrected in a \textit{corrector} stage,
 \begin{equation}
   \label{eq:Corrector-velocity}
-  \vec{v}_{I}^{k+1} = \vec{v}_{I}^{pred} + \gamma\ \Delta t\ \frac{\vec{f}_{I}^{k+1}}{\tens{m}_I^{k+1}}
+  \vec{v}_{I}^{k+1} = \vec{v}_{I}^{pred} + \gamma\ \Delta t\
+  \frac{\vec{f}_{I}^{k+1}}{\tens{m}_I^{k+1}}\ .
 \end{equation}
-Finally updated the particles are advected in the Lagrangian stage (iii) using nodal values as,
+Finally updated the particles are advected in the Lagrangian stage as
 \begin{align}
   \label{eq:Update-lagrangian-pce}
-        &\vec{a}_p^{k+1} = \frac{N_{Ip}^k\vec{f}_{I}^{k}}{\tens{m}_I^k}\\
+        &\vec{a}_p^{k+1} =
+          \frac{N_{Ip}^k\vec{f}_{I}^{k}}{\tens{m}_I^k}\ ,\\
       &\vec{v}_p^{k+1} = \vec{v}_p^n + \Delta t\
         \frac{N_{Ip}^k\
-        \vec{f}_{I}^{k}}{\tens{m}_I^k}\\
+        \vec{f}_{I}^{k}}{\tens{m}_I^k}\ ,\\
       &\vec{x}_p^{k+1} = \vec{x}_p^n + \Delta t\
@@
         \frac{1}{2}\Delta t^2\ \frac{N_{Ip}^k\
-        \vec{f}_{I}^{k}}{\tens{m}_I^k} 
+        \vec{f}_{I}^{k}}{\tens{m}_I^k}\ .
 \end{align}
-The complete pseudo-algorithm it is summarized in \ref{sec:expl-pred-corr}.
+The complete pseudo-algorithm it is summarised in \ref{sec:expl-pred-corr}.
 
-\subsection{Spatial discretization : Local-\textit{max-ent} approximants}
+\subsection{Spatial interpolation technique : \acrlong{lme} approximants}
 \label{sec:2.2}
-Local maximum-entropy (or local \textit{max-ent}) approximation scheme
-was introduced by Arroyo \& Ortiz (2006)\cite{Arroyo2006} as a bridge
-between finite elements and meshfree methods. The key idea of the
-shape functions is to interpret the nodal of a shape function $N_I$ as
-a probability. This allow us to introduce two important limits:
-maximum-entropy (\textit{max-ent}) limit, and the Delaunay triangulation
-which ensures the minimal width of the shape function. The first
-limit ensures a \textit{unbiased statistical inference} based on the
-nodal data as ensures the Jayne's\cite{Jaynes1957} principle of
-\textit{maximum entropy}, the second limit warrant the \textit{least
-  width} shape function support. To reach to a compromise between two
-competing objectives, a Pareto set is defined as, 
+\acrfull{lme} approximation scheme was introduced by Arroyo \& Ortiz
+(2006)\cite{Arroyo2006} as a bridge between finite elements and
+meshfree methods. The key idea under this interpolation technique is
+the interpretation of each nodal value $N_I$ as a
+probability. Related with this definition, two important limits are
+introduced. First the maximum-entropy (\textit{max-ent}) limit, which
+ensures a \textit{unbiased statistical inference} based on the nodal
+data as states the Jayne's\cite{Jaynes1957} principle of
+\textit{maximum entropy}. And second the Delaunay triangulation that
+warranties the \textit{least width} shape function support. To reach
+to a compromise between two competing objectives, a Pareto set is
+defined as,
 \begin{align*}
@@
   \text{(LME)}_{\beta} \hspace{0.15cm} &\text{For fixed} \hspace{0.15cm}
-  \vec{x} \hspace{0.15cm} \text{minimise} \hspace{0.15cm} f_{\beta}(\vec{x}_p, N_I) = \beta U(\vec{x}_p,N_I) - H(N_I) \\
+                                         \vec{x} \hspace{0.15cm} \text{minimise} \hspace{0.15cm} f_{\beta}(\vec{x}_p, N_I) \coloneqq \beta U(\vec{x}_p,N_I) - H(N_I) \\
                                        &\text{subject to}\
@@
 where $H(N_I)$ is the entropy of the system of nodes following the
-definition given by Shannon (1948) \cite{Shannon1948}, and $U(\vec{x}_p,N_I) =
-\sum_I N_I |\vec{x}_p - \vec{x}_I |^2$ a magnitude of the shape
-function width. The regularization o \textit{thermalization} parameter
-between the two criterion $\beta$ has Pareto optimal values in the
-range $(0,\infty)$. The unique solution of the local \textit{max-ent} problem
- \acrshort{lme}$_\beta$ is,
+definition given by Shannon (1948) \cite{Shannon1948}, the shape
+function width is defined as $U(\vec{x}_p,N_I) \coloneqq
+\sum_I N_I |\vec{x}_p - \vec{x}_I |^2$, and $\beta$ is a
+regularization o \textit{thermalization} parameter such that for
+Pareto optimal solutions $\beta \in
+(0,\infty)$. Notice that $\beta$ has units of $[L]^{-2}$,
+therefore it can be controlled by adjusting a dimensionless parameter,
+$\gamma=\beta h^2$ \cite{Arroyo2006}, where $h$ is defined as a
+suitable measure of the nodal spacing. With the restrictions exposed in
+\eqref{eq:LME-scheme-pareto-set}, the unique solution of the local
+\textit{max-ent} problem \acrshort{lme}$_\beta$ is,
  \begin{equation}
@@
 N_I^*(\vec{x})=\frac{\exp\left[ -\beta \; |\vec{x}-\vec{x}_I|^2 +
-    \vec{\lambda}^* \cdot (\vec{x}-\vec{x}_I) \right] } {Z(\vec{x},\vec{\lambda}^*)}
+    \vec{\lambda}^* \cdot (\vec{x}-\vec{x}_I) \right] } {Z(\vec{x},\vec{\lambda}^*)},
 \end{equation}
@@
   \label{eq:LME-Z}
-Z(\vec{x}, {\vec{\lambda}}) = \sum_{I=1}^{N_n}{ \exp \left[ -\beta \; |\vec{x}-\vec{x}_I|^2 + \vec{\lambda} \cdot (\vec{x}-\vec{x}_I)  \right]}
+Z(\vec{x}, {\vec{\lambda}}) = \sum_{I=1}^{N_n}{ \exp \left[ -\beta \; |\vec{x}-\vec{x}_I|^2 + \vec{\lambda} \cdot (\vec{x}-\vec{x}_I)  \right]},
 \end{equation}
-and evaluated in the unique minimiser $\vec{\lambda}^*$ for the function $\log
-Z(\vec{x}, \vec{\lambda})$. The traditional way to obtain
-such a minimiser is using (\ref{eq:LME-J}) to calculate small
-increments of $\partial\vec{\lambda}$ in a Newton-Raphson
-approach. Where $\tens{J}$ is the Hessian matrix, defined by:
-\begin{eqnarray}
-  \label{eq:LME-J} 
-  \tens{J}(\vec{x}, \vec{\lambda},\beta) &\equiv& \frac{\partial
-                                                  \vec{r}}{\partial \vec{\lambda}}\\
-  \label{eq:LME-r}
-  \vec{r}(\vec{x},\vec{\lambda},\beta) &\equiv& \frac{\partial \log{ Z(   \vec{x},\vec{\lambda}})}{\partial \vec{\lambda}}  = \sum_I^{N_n} p_I(\vec{x},\vec{\lambda},\beta) \, (\vec{x} - \vec{x}_I)
-\end{eqnarray}
-The value of $\tens{J}$ can be employed to get the first derivatives of the shape function $\nabla
-N^*_I$,
-\begin{equation}
-  \label{eq:LME-grad-p}
-\nabla N^*_I = N^*_I  \, \left(\nabla f^*_I-\sum_J^{N_n} N^*_J \, \nabla f^*_J\right)
-\end{equation}
-where
-\begin{equation}
-  \label{eq:LME-f}
-f^*_I(\vec{x},  \vec{\lambda},\beta)=-\beta \, |\vec{x}-\vec{x}_I|^2 + \vec{\lambda}^*  \,  (\vec{x}-\vec{x}_I)
-\end{equation}
-Employing the chain rule over \eqref{eq:LME-grad-p}, rearranging and considering $\beta$ as a
-constant, Arroyo and Ortiz~\cite{Arroyo2006} obtained the following
-expression for the gradient of the shape function.
+and a Lagrange multiplier $\vec{\lambda}^*$ such minimise the function $\log
+Z(\vec{x}, \vec{\lambda})$.
+The traditional way to compute the optimal value of $\vec{\lambda}^*$
+is thorough a Newton-Raphson procedure, or in more challenging
+scenarios by a combination of the Newton-Raphson and the Nelder-Mead
+Simplex algorithms \cite{Navas2018a}. Nonetheless, since finite
+strains are not involved in the present research, Newton-Raphson is an
+enough efficient method. For an uniform nodal spacing, $\beta$ can be
+considered constant, thus first derivatives of the interpolation technique $\nabla
+N^*_I$ can be obtained 
+by evaluating the following expression
 \begin{eqnarray}
@@
 \end{eqnarray}
-The regularization parameter $\beta$ of \acrshort{lme} shape functions may be
-controlled by adjusting a dimensionless parameter, $\gamma=\beta h^2$
-\cite{Arroyo2006}, where $h$ is defined as a measure of the nodal
-spacing. Since $N_I$ is defined in the entire domain, in practice,
-the shape function decay $\exp(-\beta \vec{r} )$ is truncated  by  a
-given tolerance, 10$^{-6}$, for example, would ensure a reasonable
-range of neighbours, see \cite{Arroyo2006} for details. This tolerance defines
-a limit values of the influence radius and is used thereafter to
-find the neighbour nodes of a given integration point.
+where $\tens{J}$ is the Hessian matrix, defined by
+\begin{eqnarray}
+  \label{eq:LME-J} 
+  \tens{J}(\vec{x}, \vec{\lambda},\beta) &\equiv& \frac{\partial
+                                                  \vec{r}}{\partial \vec{\lambda}},\\
+  \label{eq:LME-r}
+  \vec{r}(\vec{x},\vec{\lambda},\beta) &\equiv& \frac{\partial \log{ Z(   \vec{x},\vec{\lambda}})}{\partial \vec{\lambda}}  = \sum_I^{N_n} p_I(\vec{x},\vec{\lambda},\beta) \, (\vec{x} - \vec{x}_I).
+\end{eqnarray}
+An additional remark concerning the support of the interpolation
+function is that in practice the value of $N_I$ decay exponentially following $\exp(-\beta \vec{r}
+)$. In this sense
+a good practice is to truncate it under a tolerance, 10$^{-6}$ would ensure a reasonable
+range of neighbours, see \cite{Arroyo2006} for details. This tolerance
+defines a limit value of the influence radius to find the neighbour
+nodes of a given integration point.
 
@@
 \label{sec:2.3}
-Within the context of \acrshort{mpm} formulation, fracture can be modelled by
-failing particles according to a suitable criterion. When material
-points are failed, they are assumed to have a null stress
-tensor. Navas {\it et al.} (2017)\cite{Navas_2017_ES} developed a
-eigensoftening algorithm as an extension for quasi-brittle materials
+Within the context of \acrshort{mpm} formulation, fracture can be
+modelled by failing particles according to a suitable failure
+criterion. When material points are failed, they are assumed to have
+null stress tensor. To reproduce this behaviour in the present
+research, the eigensoftening algorithm is introduced in the 
+\acrshort{mpm} framework as an alternative approach to the decohesion
+model \cite{Zhenmao_2005,Schreyer_2002}. The eigensoftening concept
+was originally developed by Navas {\it et al.}
+(2017)\cite{Navas_2017_ES} as an extension for quasi-brittle materials
 of the eigenerosion proposed by Pandolfi \& Ortiz
 (2012)\cite{Pandolfi_2012} for fracture of brittle materials. A
-comparison between both in \cite{Navas_2017_ES} shows that
-the eigenerosion algorithm significantly overestimates the tensile
+comparison between both in \cite{Navas_2017_ES} shows that the
+eigenerosion algorithm significantly overestimates the tensile  
 stress and the strain peaks, while it captures the forces and crack
@@
 very well with experimental results in all the aspects. Furthermore,
-this algorithm has also proof its accuracy for complex fracture
+this algorithm has proof its accuracy for complex fracture
 patters such the present in fiber reinforces concrete (FRC),
@@
 
+The key idea behind the eigenerosion algorithm is the computation of the
+energy-release rate attendant to the failure of material point $p$,
 \begin{align}
@@
 \end{align}
-where $B_{\epsilon}(x_p^{k+1})$ is the sphere of radius $\epsilon$
-centered at $x_p^{k+1}$ known as the $\epsilon$-neighborhood of the
-material point, $m_p^{k+1}$ is the mass of the neighborhood at step
-$k+1$, $W_q^{k+1}$ is the current free-energy density per unit mass as
-the material point $x_q^{k+1}$ of the neighborhood, finally
-$C_{\epsilon}$ is a normalizing constant. This configuration
-conveniently is sketched in Figure \ref{fig:Failed-particles}.
+where $B_{\epsilon}(x_p^{k+1})$ is a $^n$dimensional sphere of radius $\epsilon$
+centered at $x_p^{k+1}$. The particles which lies under this sphere are
+known as the $\epsilon$-neighborhood of the material point, see
+\cite{Pandolfi_2012}, this concept is conveniently is sketched in
+Figure \ref{fig:Failed-particles}.
 %%%%%%%%%%%
@@
 %%%%%%%%%%%
-The material point fails when $G_p^{k+1}$ surpasses a critical energy
-release rate that measures the material-specific energy, $G_F$. The
-convergence of this approach has been analyzed by Schmidt {\it et al.}
-(2009)\cite{Schmidt_2009}, who proof that it converges to the Griffith
+Other parameters are, the mass of the neighborhood $m_p^{k+1}$, the
+current free-energy density per unit mass  $W_q^{k+1}$ and finally a
+normalizing constant $C_{\epsilon}$. 
+The failure criterion consist in to consider the material point fails
+when $G_p^{k+1}$ surpasses a critical energy release rate that
+measures the material-specific energy, $G_F$. The convergence of this
+approach has been analyzed by Schmidt {\it et al.}
+(2009)\cite{Schmidt_2009}, who proofed that it converges to the Griffith
 fracture when discretization size tends to zero. It is necessary to
@@
 contribution to the internal forces vector is set to zero, but its
-contribution to the mass matrix is maintained. The mass of a material
-point is discarded only when an eroded material point is not connected
-to any nodes.\\
+contribution to the mass matrix is preserved.\\
 
-As can be noticed, in the eigenerosion algorithm an energetic
-criterion is adopted. Due to that fact, unrealistic stress
-concentration (higher than tensile strength) in quasi-brittle materials, see
-\cite{Navas_2017_ES}. To overcome this limitation, the aforementioned
-authors proposed the concept of eigensoftening to take in to account
-the gradual failure in quasi-brittle materials. The concept is
-inspired in the cohesive fracture widely employed in the context of
-FEM \cite{Ortiz_1999}. This gradual failure criterion is plotted in
-figure \label{fig:Damage-ft-wc}, where a linear decreasing cohesive
-law is presented to illustrate the concept here described. In the
-picture, the shaded area represents the static fracture energy per
-unit of area, $G_F$. Notice how a cohesive crack appears when the
-maximum tensile strength, $f_t$ is reached. Once the opening
-displacement $w$ takes the value of the critical crack displacement
-$w_c$, a stress-free crack is attained. For intermediate values,
-$w_n$, a damage value between zero and one represents the extension to
-which the material has failed.
+As can be noticed, the eigenerosion algorithm relies over an energetic
+failure criterion. Because of this, unrealistic stress
+concentration (higher than tensile strength) appears in quasi-brittle
+materials \cite{Navas_2017_ES}. To overcome this limitation, the
+aforementioned authors proposed the concept of eigensoftening to take
+in to account the gradual failure in quasi-brittle materials. The idea
+behind this concept is inspired in the cohesive fracture. This gradual
+failure criterion is plotted in figure \label{fig:Damage-ft-wc}, where
+a linear decreasing cohesive law is presented to illustrate the
+concept earlier described. In the picture, the shaded region represents
+the static fracture energy per unit of area, $G_F$. Notice how a
+cohesive crack appears when the maximum tensile strength, $f_t$ is
+reached. Once the opening displacement $w$ reach the value of the
+critical crack displacement $w_c$, a stress-free crack is
+attained. For intermediate values, $w_n$, a damage value between zero
+and one represents the extension to which the material has failed.
 %%%%%%%%%%%
@@
 theory for brittle fracture was considered by authors
-\cite{Navas_2017_ES}. With that purpose, the variation of the averaged strain
-energy density in the $\epsilon$-neighborhood of the material point
-$\vec{x}_p^{k+1}$ can be obtained as,
+\cite{Navas_2017_ES}. With that purpose, the variation of the averaged
+strain energy density in the $\epsilon$-neighborhood of the material point
+$\vec{x}_p^{k+1}$ can be obtained as
 \begin{equation}
@@
   \frac{1}{m_p} \sum_{x_q^{k+1} \in
-  B_{\epsilon}(x_p^{k+1})} m_q \tens{\sigma}_{q,I} \delta \tens{\epsilon}_q
+  B_{\epsilon}(x_p^{k+1})} m_q \tens{\sigma}_{q,I} \delta \tens{\epsilon}_q,
 \end{equation}
 where $\tens{\sigma}_{q,I}$ is the maximum principal stress of each
-material point in the $\epsilon$-neighborhood. Here
-\cite{Navas_2017_ES} introduces an effective strain $\varepsilon_q$,
-such the variation of the local strain energy can be obtained as
-$\delta W_q = \sigma_{q,1} \delta\varepsilon_q$. Now with the assumption
-that the effective strain of each material point at every time step
-is constant in the neighborhood of $\vec{x}_p^{k+1}$, the equation
+material point in the $\epsilon$-neighborhood. In this point in
+introduced an effective strain $\varepsilon_q$, such the variation of
+the local strain energy can be obtained as $\delta W_q = \sigma_{q,1}
+\delta\varepsilon_q$. Now with the assumption that the effective
+strain of each material point at every time step is constant in the
+neighborhood of $\vec{x}_p^{k+1}$, the equation 
 \eqref{eq:variation-averaged-strain-energy-density} can be simplified
-as follows
+ to
 \begin{equation}
@@
 Consequently it is possible to define an equivalent critical stress at the
-material point $\vec{x}_p^{k+1}$:
+material point $\vec{x}_p^{k+1}$as
 \begin{equation}
@@
 \end{equation}
-where $m_p$ can be computed as:
+where $m_p$ is the total mass of the $\epsilon$-neighborhood
 \begin{equation}
@@
 \end{equation}
-This definition of the equivalent critical stress allow us to
-link it with the averaged strain energy as $\delta W_{\epsilon,p} =
- \tens{\sigma}_{\epsilon,p}\ \delta\varepsilon_p$. The fracture
-criterion is defined as once $\tens{\sigma}_{\epsilon,p}^{k+1}$
-surpasses the tensile strength, $f_t$, the softening behaviour is
-activated, which in turn causes a reduction of the initial forces as,
+This definition of the equivalent critical stress leads to a
+definition of the averaged strain energy in terms of the averaged
+strain as $\delta W_{\epsilon,p} =
+ \tens{\sigma}_{\epsilon,p}\ \delta\varepsilon_p$. The softening behaviour is
+activated once $\tens{\sigma}_{\epsilon,p}^{k+1}$ surpasses the
+tensile strength, $f_t$. This consists in a reduction of the internal
+forces as,
  \begin{equation}
    \label{eq:f-int-damaged}
-   f^{int}_I = \sum_p (1 - \chi_p)\ \tens{\sigma}_{p}^{k+1} \cdot \Grad{N_{Ip}}
+   f^{int}_I = \sum_p (1 - \chi_p)\ \tens{\sigma}_{p}^{k+1} \cdot
+   \Grad{N_{Ip}}\ \Omega_p
  \end{equation}
-where $\chi_p$ is the damage variable of each material point $p$,
-ranges between zero (an intact material) and one (completely failed
-material points). For the case of a linear softening such the sketched
-in the Figure \ref{fig:Damage-ft-wc}, it is calculated as,
+where $\chi_p$ and $\Omega_p$ are respectively the damage or softening
+variable and the volume for each material point $p$. $\chi_p$ takes
+values between zero (an intact material) and one (completely failed
+material points). For the case of a linear softening such the sketched in the Figure \ref{fig:Damage-ft-wc}, $\chi_p$ is computed as,
  \begin{equation}
@@
  \end{equation}
-
-Following Bazant~\cite{Bazant83} crack-model, \cite{Navas_2017_ES}
-introduced a band width $h_{\epsilon}$, which has values between two
-and four times the maximum size of the aggregates for the
-concrete. The effective fracture strain $\varepsilon_{\epsilon,f}$ is
-defined as the difference between the strain at crack initialization,
-$\varepsilon_1(\vec{x}_p^{0})$, and the current strain, $\varepsilon_1(\vec{x}_p^{k+1})$, for material
-point $p$. Also, $\varepsilon_{\epsilon,f}$ can be represented as the
-current crack opening $w_n$ within the band width,
-$h_{\epsilon}$. Therefore,
+In analogy to the band crack model presented by
+Bazant~\cite{Bazant83}, Navas {\it et al.} \cite{Navas_2018_ES}
+\cite{Navas_2017_ES} introduced a band width parameter $h_{\epsilon}$.
+Concerning this parameter, a typical value of it is between two and
+four times the maximum size of the aggregates, in the case of
+concrete as brittle material. The effective fracture strain
+$\varepsilon_{\epsilon,f}$ is defined as the difference between the strain at crack initialization,
+$\varepsilon_1(\vec{x}_p^{0})$, and the current strain, $\varepsilon_1(\vec{x}_p^{k+1})$, for material point $p$. Also,
+$\varepsilon_{\epsilon,f}$ can be represented as the current crack
+opening $w_n$ within the band width, $h_{\epsilon}$. Therefore, 
 \begin{equation}
@@
   \label{eq:damage-variable-chi-II}
-\chi = \frac{\varepsilon_{\epsilon,f}\ h^{\epsilon}}{w_c}  
+\chi = \frac{\varepsilon_{\epsilon,f}\ h^{\epsilon}}{w_c}.  
 \end{equation}
-for the case of a linear softening behaviour. In a more general case,
-the damage variable can be expressed in terms of the following
-variables,
+The function of $\chi$ presented in \eqref{eq:damage-variable-chi-III}
+represents a linear softening behaviour. For a general case, the
+damage variable can be expressed in terms of the following variables,
 \begin{equation}
@@
 
+As noticed in \cite{Zhang_EE_2020}, the EigenMPM have two important
+shortcomings. The first is the presence of stress instabilities even
+with \acrshort{gimp} shape functions. To overcome it, \acrshort{lme}
+approximants are introduced as an
+alternative to the existing interpolation techniques. Its
+impressive performance mitigating spurious stress oscillations
+\cite{Wobbes2020} under the \acrshort{mpm} framework help to enhance
+notoriously the quality of the results as we can see in Section
+\ref{sec:edge-cracked-square-I}. Where both interpolation techniques
+are compared by carry out an eigenerosion simulation. The second
+limitation is concerning its inability to simulate properly quasi-brittle
+fracture \cite{Navas_2018_ES}. It can be solved thorough the
+eigensoftening algorithm described in Section \ref{sec:2.3}. A proof
+of it is exposed in Section \ref{sec:3.3}, where experimental results
+of a drop-weight impact test are compared with those produced by
+eigensoftening computations.
+
 \subsection{Edge-cracked square panel in mode I}
@@
 
-This problem is devoted to compare the develop of both linear shape
-functions and the \acrshort{lme}
+This problem here presented is devoted to compare how much \acrshort{lme}
+approximants are able to improve the result \textit{versus} standard
+linear interpolation. It consists in a square plate of size $H = 1$ containing
+an initial edge crack of length $0.25 \cdot H$ loaded in a pure mode I
+by displacement control on the outer flanks of the plate, Figure
+\ref{fig:geometry-cracked-panel-mode-I}.
+%%%%%%%%%%%
+\begin{figure}
+  \centering
+  \includegraphics[width=0.4\textwidth]{Figures/Mode_I}
+  \caption{Geometry and boundary condition of the drop-weight impact test.}
+  \label{fig:geometry-cracked-panel-mode-I}
+\end{figure}
+%%%%%%%%%%%
+The constitutive model consider for numerical experiment is a
+linear-elastic Hookean material, where Young's modulus $E = 1.06$, the Poisson's ratio
+$\mu = 0.333$, and critical energy-release rate $G_c = 0.0001$.
+
+Figure \ref{fig:Reactions-cracked-panel-mode-I} clearly shows the
+presence of wiggles in the loading and also in the unloading regions
+of the curve when a linear interpolation technique is employed. In
+contrast with it \acrshort{lme} simulation does not exhibit this
+accuracy and remains rectilinear during loading and unloading. An
+important consideration regarding the presence of oscillations once
+both parts of the panel are separated. Is that they should not be
+attributed to the eigenerosion algorithm since the fracture process is
+over. They are due to the dynamic nature of the simulation.
 
@@
   \centering
-  \includegraphics[width=0.8\textwidth]{Figures/Mode_I}
-  \caption{Geometry and boundary condition of the drop-weight impact test.}
-  \label{fig:geometry-cracked-panel-mode-I}
+  \includegraphics[width=0.8\textwidth]{Figures/Reactions_displacements_square_panel_mode_I}
+  \caption{Evolution of the reaction forces plotted \textit{versus}
+    the imposed displacement for linear interpolation technique and
+    the \acrshort{lme} approximants.}
+  \label{fig:Reactions-cracked-panel-mode-I}
 \end{figure}
@@
 \centering
-  \includegraphics[width=0.8\textwidth]{Figures/Reactions_displacements_square_panel_mode_I}
-  \caption{Geometry and boundary condition of the drop-weight impact test.}
-  \label{fig:geometry-cracked-panel-mode-I}
+\subfigure[t1]{\includegraphics[width=0.7\textwidth]{./Figures/Edge_cracked_square_panel_in_mode_I_Stress_0100.png}}
+\subfigure[t2]{\includegraphics[width=0.7\textwidth]{./Figures/Edge_cracked_square_panel_in_mode_I_Stress_0250.png}}
+\subfigure[t3]{\includegraphics[width=0.7\textwidth]{./Figures/Edge_cracked_square_panel_in_mode_I_Stress_0398.png}}
+\caption{Evolution of the stress tensor magnitude for linear
+  interpolation (pictures in the left side), and \acrshort{lme}
+  (pictures in the right side). Both simulations performed with an
+  eigenerosion algorithm.}
+\label{fig:Stress-cracked-panel-mode-I}
 \end{figure}
@@
 \section{Conclusions}
-\label{sec:6}
+\label{sec:4}
 
@@
 \begin{algorithm}
+  \DontPrintSemicolon
+  \KwInput{For each $p$, $\epsilon$-neighbourhood, $f_{t,p}$, $h_{\epsilon,p}$, $w_c$}
+  \KwOutput{Return damage parameter $\chi := \{\chi_p\}$}
+  % \KwData{Testing set $x$}
+  $\chi_p \leftarrow \chi_p^{k}$ \;
+  \For{$p$ to $N_p$}
+  {
+    \If{$\chi_p = 0$ \AND $\epsilon_{f,p} = 0$}
+    {
+      \For{$q \in B_{\epsilon,p}$}
+      {
+        $\sigma_{q,I} \leftarrow \text{getEigenvaluesOf}(\sigma_{q})$ \;
+        \If{$\chi_q < 1$}
+        {
+          $\sum m_p\sigma_{p,I} \leftarrow \sum m_p\sigma_{p,I} + m_q\sigma_{q,I}$ \;
+        }
+        $m_p \leftarrow m_p + m_q$ \;
+      }
+      $\sigma_{p,\epsilon} \leftarrow \frac{1}{m_p} \sum m_p\sigma_{p,I}$\;
+      \If{$\sigma_{p,\epsilon} > f_{t,p}$}
+      {
+        $\epsilon_{f,p} = \epsilon_{I,p}$ \;  
+      }
+      \ElseIf{$\chi_p \neq 1$ \AND $\epsilon_{f,p} > 0$}
+      {
+        $\chi_p^{k+1} \leftarrow \min\Big \{1 , \max \{\chi_p^{k},
+        \frac{(\epsilon_{I,p}- \epsilon_{f,p})\ h_{\epsilon,p}}{w_c}
+        \} \Big \}$ \;
+      }
+    }
+  }
   \caption{Compute damage parameter $\chi_p^{k+1}$}
   \label{alg-eigens}
-  \begin{algorithmic}
-    \Require Particle status\\
-    Number of particles: $N_p$\\
-    $\epsilon$-neighbourhood of each particle $p$ : $B_{\epsilon,p}$\\
-    \Require Material data\\
-    Tensile strength: $f_{t,p}$\\
-    Bandwidth of the cohesive fracture: $h_{\epsilon,p}$ \\
-    Critical opening displacement: $w_c$\\ 
-    \Ensure Return damage parameter $\chi := \{\chi_p\}$
-    \State $\chi_p \leftarrow \chi_p^{k}$
-    \For{$p$ to $N_p$}
-    \If{$\chi_p = 0$ \AND $\epsilon_{f,p} = 0$}
-    \For{$q \in B_{\epsilon,p}$}
-    \If{$\chi_q < 1$}    
-    \State $\sum m_p\sigma_{p,I} \leftarrow \sum m_p\sigma_{p,I} + m_q\sigma_{q,I}$
-    \EndIf    
-    \State $m_p \leftarrow m_p + m_q$
-    \EndFor
-    \State $\sigma_{p,\epsilon} \leftarrow \frac{1}{m_p} \sum m_p\sigma_{p,I}$
-    \If{$\sigma_{p,\epsilon} > f_{t,p}$}
-    \State $\epsilon_{f,p} = \epsilon_{I,p}$   
-    \EndIf        
-    \Else[$\chi_p \neq 1$ \AND $\epsilon_{f,p} > 0$]
-    \State $\chi_p^{k+1} \leftarrow \min\Big \{1 , \max \{\chi_p^{k},
-    \frac{(\epsilon_{I,p}- \epsilon_{f,p})\ h_{\epsilon,p}}{w_c} \} \Big \}$    
-    \EndIf    
-    \EndFor
-  \end{algorithmic}
 \end{algorithm}

### 2020-05-19 _region_.tex
Cambios 19-5-2020

@@
-\message{ !name(2020_EFM_MPM_Eigensoftening.tex)}\documentclass[preprint,12pt,a4paper]{elsarticle}
-
-\usepackage{lineno,hyperref}
+\message{ !name(2020_EFM_MPM_Eigensoftening.tex)}% \documentclass[preprint,12pt,a4paper]{elsarticle}
+\documentclass[12pt,a4paper]{elsarticle}
+\usepackage{lineno}
+\usepackage{hyperref}
 \usepackage{float}
 \usepackage{subfig}
+\usepackage{subfigure} % subfiguras
 \usepackage{color}
 \usepackage{soul}
-
-\usepackage{algcompatible}
-\usepackage{algorithm}
-\usepackage{algorithmic}
-\usepackage{algpseudocode}
-
 \usepackage{cancel}
@@
 \centering
-  \includegraphics[width=0.8\textwidth]{Figures/Reactions_displacements_square_panel_mode_I}
-  \caption{Geometry and boundary condition of the drop-weight impact test.}
-  \label{fig:geometry-cracked-panel-mode-I}
+\subfigure[t1]{\includegraphics[width=0.7\textwidth]{./Figures/Edge_cracked_square_panel_in_mode_I_Stress_0100.png}}
+\subfigure[t2]{\includegraphics[width=0.7\textwidth]{./Figures/Edge_cracked_square_panel_in_mode_I_Stress_0250.png}}
+\subfigure[t3]{\includegraphics[width=0.7\textwidth]{./Figures/Edge_cracked_square_panel_in_mode_I_Stress_0398.png}}
+\caption{Legos.}
+\label{fig:Stress-cracked-panel-mode-I}
 \end{figure}
+
+Edge_cracked_square_panel_in_mode_I_Stress_0250.png
+Edge_cracked_square_panel_in_mode_I_Stress_0398.png
 
@@
 \end{document}
-\message{ !name(2020_EFM_MPM_Eigensoftening.tex) !offset(-813) }
+\message{ !name(2020_EFM_MPM_Eigensoftening.tex) !offset(-867) }

### 2020-05-19 2020_EFM_MPM_Eigensoftening.tex
Carpetas y gitignore

@@
-% \documentclass[preprint,12pt,a4paper]{elsarticle}
-\documentclass[12pt,a4paper]{elsarticle}
+\documentclass[preprint,12pt,a4paper]{elsarticle}
 \usepackage{lineno}
@@
   \centering
-  \includegraphics[width=0.5\textwidth]{Figures/Particle-failed}
+  \includegraphics[width=0.5\textwidth]{Figure-Particle-failed}
   \caption{Scheme of a linear cohesive law, where the shaded area is
@@
   \centering
-  \includegraphics[width=0.5\textwidth]{Figures/Damage}
+  \includegraphics[width=0.5\textwidth]{Figure-Damage}
   \caption{Scheme of a linear cohesive law, where the shaded area is
@@
   \centering
-  \includegraphics[width=0.4\textwidth]{Figures/Mode_I}
+  \includegraphics[width=0.4\textwidth]{Figure-Mode_I}
   \caption{Geometry and boundary condition of the drop-weight impact test.}
@@
   \centering
-  \includegraphics[width=0.8\textwidth]{Figures/Reactions_displacements_square_panel_mode_I}
+  \includegraphics[width=0.8\textwidth]{Figure-Reactions-mode-I}
   \caption{Evolution of the reaction forces plotted \textit{versus}
@@
 \centering
-\subfigure[t1]{\includegraphics[width=0.7\textwidth]{./Figures/Edge_cracked_square_panel_in_mode_I_Stress_0100.png}}
-\subfigure[t2]{\includegraphics[width=0.7\textwidth]{./Figures/Edge_cracked_square_panel_in_mode_I_Stress_0250.png}}
-\subfigure[t3]{\includegraphics[width=0.7\textwidth]{./Figures/Edge_cracked_square_panel_in_mode_I_Stress_0398.png}}
+\subfigure[t1]{\includegraphics[width=0.7\textwidth]{./Figure-Stress-0100-mode-I.png}}
+\subfigure[t2]{\includegraphics[width=0.7\textwidth]{./Figure-Stress-0250-mode-I.png}}
+\subfigure[t3]{\includegraphics[width=0.7\textwidth]{./Figure-Stress-0398-mode-I.png}}
 \caption{Evolution of the stress tensor magnitude for linear
@@
   \centering
-  \includegraphics[width=0.8\textwidth]{Figures/Drop_weight}
+  \includegraphics[width=0.8\textwidth]{./Figure-Drop-weight}
   \caption{Geometry and boundary condition of the drop-weight impact test.}
@@
 % name your BibTeX data base
-\bibliography{Biblio/Biblio}
+\bibliography{Biblio}
 

### 2020-05-19 _region_.tex
Carpetas y gitignore

@@
-\message{ !name(2020_EFM_MPM_Eigensoftening.tex)}% \documentclass[preprint,12pt,a4paper]{elsarticle}
-\documentclass[12pt,a4paper]{elsarticle}
+\message{ !name(2020_EFM_MPM_Eigensoftening.tex)}\documentclass[preprint,12pt,a4paper]{elsarticle}
 \usepackage{lineno}
@@
 \usepackage{float}
-\usepackage{subfig}
+\usepackage{graphicx} % figuras
+% \usepackage{subfig}
 \usepackage{subfigure} % subfiguras
@@
   \centering
-  \includegraphics[width=0.5\textwidth]{Figures/Particle-failed}
+  \includegraphics[width=0.5\textwidth]{Particle-failed}
   \caption{Scheme of a linear cohesive law, where the shaded area is
@@
   \centering
-  \includegraphics[width=0.5\textwidth]{Figures/Damage}
+  \includegraphics[width=0.5\textwidth]{Damage}
   \caption{Scheme of a linear cohesive law, where the shaded area is
@@
   \centering
-  \includegraphics[width=0.4\textwidth]{Figures/Mode_I}
+  \includegraphics[width=0.4\textwidth]{Mode_I}
   \caption{Geometry and boundary condition of the drop-weight impact test.}
@@
   \centering
-  \includegraphics[width=0.8\textwidth]{Figures/Reactions_displacements_square_panel_mode_I}
+  \includegraphics[width=0.8\textwidth]{Reactions_displacements_square_panel_mode_I}
   \caption{Evolution of the reaction forces plotted \textit{versus}
@@
 \centering
-\subfigure[t1]{\includegraphics[width=0.7\textwidth]{./Figures/Edge_cracked_square_panel_in_mode_I_Stress_0100.png}}
-\subfigure[t2]{\includegraphics[width=0.7\textwidth]{./Figures/Edge_cracked_square_panel_in_mode_I_Stress_0250.png}}
-\subfigure[t3]{\includegraphics[width=0.7\textwidth]{./Figures/Edge_cracked_square_panel_in_mode_I_Stress_0398.png}}
-\caption{Legos.}
+\subfigure[t1]{\includegraphics[width=0.7\textwidth]{./Edge_cracked_square_panel_in_mode_I_Stress_0100.png}}
+\subfigure[t2]{\includegraphics[width=0.7\textwidth]{./Edge_cracked_square_panel_in_mode_I_Stress_0250.png}}
+\subfigure[t3]{\includegraphics[width=0.7\textwidth]{./Edge_cracked_square_panel_in_mode_I_Stress_0398.png}}
+\caption{Evolution of the stress tensor magnitude for linear
+  interpolation (pictures in the left side), and \acrshort{lme}
+  (pictures in the right side). Both simulations performed with an
+  eigenerosion algorithm.}
 \label{fig:Stress-cracked-panel-mode-I}
 \end{figure}
-
-Edge_cracked_square_panel_in_mode_I_Stress_0250.png
-Edge_cracked_square_panel_in_mode_I_Stress_0398.png
 
@@
   \centering
-  \includegraphics[width=0.8\textwidth]{Figures/Drop_weight}
+  \includegraphics[width=0.8\textwidth]{./Drop_weight}
   \caption{Geometry and boundary condition of the drop-weight impact test.}
@@
 % name your BibTeX data base
-\bibliography{Biblio/Biblio}
+\bibliography{Biblio}
 
 \end{document}
-\message{ !name(2020_EFM_MPM_Eigensoftening.tex) !offset(-867) }
+\message{ !name(2020_EFM_MPM_Eigensoftening.tex) !offset(-868) }

### 2020-05-19 Documentacion/2_Material.py
Fuera carpetas

@@ -1,466 +1,0 @@
-import glob,os
-import numpy as np
-import matplotlib.pyplot as plt
-from mpl_toolkits.mplot3d import Axes3D
-from matplotlib import cm
-from matplotlib.ticker import LinearLocator
-from matplotlib.ticker import FixedLocator
-from matplotlib.ticker import FormatStrFormatter
-
-def find_nearest(array, value):
-    array = np.asarray(array)
-    idx = (np.abs(array - value)).argmin()
-    return idx
-
-def Get_Riemann_I(Stress_I,Velocity_I,nu):
-    R_I = (0.5/nu)*(- Stress_I + Velocity_I*nu)
-    return R_I
-
-def Get_Riemann_II(Stress_II,Velocity_II,nu):
-    R_II = (0.5/nu)*(Stress_II + Velocity_II*nu)
-    return R_II
-
-def Dyka_Riemann(CFL,T_END,i_RES):
-                     
-    # Material properties
-    L = 380
-    x_a = 0
-    x_b = L*0.1
-    x_c = L
-    
-    E_ab = 210*10**3 # MPa
-    rho_ab = 7.8*10**(-9) # Tn/mm³
-    CEL_ab = np.sqrt(E_ab/rho_ab)
-    E_bc = 210*10**3 # MPa
-    rho_bc = 1.2*10**(-7) # Tn/mm³
-    CEL_bc = np.sqrt(E_bc/rho_bc)
-
-    CEL = max(CEL_ab,CEL_bc)
-
-    # Discretize domain
-    DeltaX = 1
-    N_nodes = int(L/DeltaX)
-    X = np.linspace(x_a,x_c,N_nodes)
-    I_a = find_nearest(X,x_a)
-    I_b = find_nearest(X,x_b)
-    I_c = find_nearest(X,x_c)    
-
-    # Discretize time
-    N_steps = int(T_END/(1*CFL/CEL))
-    DeltaT = CFL*DeltaX/CEL
-    T = np.linspace(0.0,T_END,int(N_steps/i_RES))
-
-    # Initial conditions
-    v0 = -500
-    Stress = np.zeros([int(N_steps/i_RES),N_nodes])
-    Velocity = np.zeros([int(N_steps/i_RES),N_nodes])
-    for x in range(0,N_nodes):
-        if X[x] <= 10 :
-            Velocity[0,x] = v0
-        else :
-            Velocity[0,x] = 0
-        
[…]

### 2020-05-19 Documentacion/Hummer_gap.py

@@ -1,23 +1,0 @@
-import numpy as np
-import matplotlib.pyplot as plt
-
-E = 210E3 # N/mm^2
-rho1 = 7.85E-9 # Tons/mm^3
-rho2 = 1.2E-7 # Tons/mm^3
-L = 390 # mm
-L1 = 38 # mm
-L2 = L-L1 # mm
-V_hummer = [881,1760,2640] # mm/s 
-CFL = 0.1
-Cel1 = np.sqrt(E/rho1) # mm/s
-Cel2 = np.sqrt(E/rho2) # mm/s
-DeltaX = np.linspace(0.1,1.0,100)
-# DeltaX = np.array([0.1,0.5,1.0])
-DeltaT = (CFL/Cel1)*DeltaX
-
-for i in range(0,3):
-    Tend = DeltaX/V_hummer[i] + 2*L1/Cel1 + 2*L2/Cel2
-    Nsteps = Tend/DeltaT
-    plt.plot(Tend,Nsteps, label="Hummer vel : %f"%V_hummer[i])
-plt.legend()
-plt.show()

### 2020-05-20 2020_EFM_MPM_Eigensoftening.tex
Cambios 20-5-2020 (I) : Hasta 3.1

@@
 
-%\usepackage{algorithm,algcompatible}
-\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
-\algnewcommand\INPUT{\item[\textbf{Input:}]}%
-\algnewcommand\OUTPUT{\item[\textbf{Output:}]}%
+% \usepackage{algorithm,algcompatible}
+
+\usepackage{blindtext}
+\usepackage[linesnumbered,boxed]{algorithm2e}
+
+\SetAlCapSkip{1em}
+
+\SetKwInput{KwInput}{Input}
+\SetKwInput{KwOutput}{Output}
+
+% \usepackage[linesnumbered,ruled,vlined]{algorithm2e}
+% \algnewcommand\INPUT{\item[\textbf{Input:}]}%
+% \algnewcommand\OUTPUT{\item[\textbf{Output:}]}%
 
@@
 notoriously the quality of the results as we can see in Section
-\ref{sec:edge-cracked-square-I}. Where both interpolation techniques
+\ref{sec:3.1}. Where both interpolation techniques
 are compared by carry out an eigenerosion simulation. The second
@@
 \subsection{Edge-cracked square panel in mode I}
-\label{sec:edge-cracked-square-I}
+\label{sec:3.1}
 
@@
 \ref{fig:geometry-cracked-panel-mode-I}.
-%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}
@@
 \end{figure}
-%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 The constitutive model consider for numerical experiment is a
-linear-elastic Hookean material, where Young's modulus $E = 1.06$, the Poisson's ratio
-$\mu = 0.333$, and critical energy-release rate $G_c = 0.0001$.
+linear-elastic Hookean material, where Young's modulus $E = 1.06$, the
+Poisson's ratio $\mu = 0.333$, and critical energy-release rate $G_c =
+0.0001$.
+This set of parameters was taken from \cite{Pandolfi_2012}. In
+\acrshort{mpm}, two different discretization are required. In one hand
+a cartesian grid of nodes is consider with a nodal spacing value of
+0.025. On the other hand, the plate will be modeled with a initial
+layout of four particles per element and occupying the Gauss quadrature
+positions.
 
 Figure \ref{fig:Reactions-cracked-panel-mode-I} clearly shows the
-presence of wiggles in the loading and also in the unloading regions
-of the curve when a linear interpolation technique is employed. In
-contrast with it \acrshort{lme} simulation does not exhibit this
-accuracy and remains rectilinear during loading and unloading. An
-important consideration regarding the presence of oscillations once
-both parts of the panel are separated. Is that they should not be
-attributed to the eigenerosion algorithm since the fracture process is
-over. They are due to the dynamic nature of the simulation.
-
+presence of wiggles in both loading and fracture stages
+in the reaction-displacements curve when linear interpolation technique is employed. In
+contrast, \acrshort{lme} simulation does not exhibit these spurious
+oscillations and remains linear. Besides that, linear interpolation
+produces stiffer results than \acrshort{lme}. This can be attributed
+to imprecision in the stress field due to grid-crossing phenomena.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}
   \centering
-  \includegraphics[width=0.8\textwidth]{Figure-Reactions-mode-I}
+  \includegraphics[width=0.8\textwidth]{Figure-Reactions-Mode-I}
   \caption{Evolution of the reaction forces plotted \textit{versus}
@@
 \end{figure}
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+On the other hand, Figure \ref{fig:Stress-cracked-panel-mode-I}
+exhibits more clearly the difference between linear interpolation and
+\acrshort{lme}, since numerical instability becomes rather significant
+when particles crosses the boundary of the element in the linear
+case. Although this behavior does not affect significantly to the peak
+stress value in a hookean material \cite{Zhang_EE_2020}, if
+hyperelastic materials are consider for future simulations,
+inaccuracies in the stress field could affect dramatically to the
+final result. On the other hand \acrshort{lme} produces soft stress
+field evolution even after breaking    
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}
 \centering
-\subfigure[t1]{\includegraphics[width=0.7\textwidth]{./Figure-Stress-0100-mode-I.png}}
-\subfigure[t2]{\includegraphics[width=0.7\textwidth]{./Figure-Stress-0250-mode-I.png}}
-\subfigure[t3]{\includegraphics[width=0.7\textwidth]{./Figure-Stress-0398-mode-I.png}}
+\subfigure[t = 25]{\includegraphics[width=0.7\textwidth]{./Figure-Stress-0100-mode-I.png}}
+\subfigure[t = 60]{\includegraphics[width=0.7\textwidth]{./Figure-Stress-0250-mode-I.png}}
+\subfigure[t = 100]{\includegraphics[width=0.7\textwidth]{./Figure-Stress-0398-mode-I.png}}
 \caption{Evolution of the stress tensor magnitude for linear
@@
 \end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+An important consideration regarding the presence of oscillations once
+both parts of the panel are separated, Figure
+\ref{fig:Reactions-cracked-panel-mode-I}. These phenomena should not be
+attributed to the eigenerosion algorithm since the fracture process is
+over. They are due to the dynamic nature of the solver.
 
 \subsection{Drop-weight impact test}
-\label{sec:3.3}
+\label{sec:3.2}
+
+Once the accuracy of the \acrshort{lme} approximants have been proven
+in Section \ref{sec:3.1}, henceforth will be adopted without comparing
+with linear interpolation. Therefore this section is devoted
 
@@
 \begin{algorithm}
-  \floatname{algorithm}{Algorithm}
-  \renewcommand{\thealgorithm}{}
-  \caption{Explicit Predictor-Corrector scheme}
-  \begin{algorithmic}[1]
+  \DontPrintSemicolon
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% º
-    \STATE \textbf{Update mass matrix}:
-    \begin{equation*}
-      \tens{m}_{I} = N_{Ip}^{k}\ m_p,
-    \end{equation*}
+    \textbf{Update mass matrix :} $ \tens{m}_{I} = N_{Ip}^{k}\ m_p$ \;
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-    \STATE \textbf{Explicit Newmark Predictor}:\\
+    \textbf{Explicit Newmark Predictor :}
     \begin{equation*}
       \vec{v}_I^{pred} = \frac{ N_{Ip}^{k} m_p (\vec{v}_p^k + (1 - \gamma)\ \Delta t\ \vec{a}_p^k)}{m_I}
-    \end{equation*}
+    \end{equation*}\;
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-    \STATE \textbf{Impose essential boundary conditions}:\\
-    At the fixed boundary, set $\vec{v}_{I}^{pred} = 0$. 
+    \textbf{Impose essential boundary conditions :} At the fixed
+    boundary, set $\vec{v}_{I}^{pred} = 0$.\; 
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-    \STATE \textbf{Deformation tensor increment calculation}.
+    \textbf{Deformation tensor increment calculation :}
     \begin{equation*}
       \Delta \tens{\varepsilon}_{p}^{k+1} = \Delta t\
-        \dot{\tens{\varepsilon}_{p}}^{k+1} = \Delta \left[ \vec{v}_{I}^{pred} \otimes
+        \dot{\tens{\varepsilon}_{p}}^{k+1} = \Delta t\ \left[ \vec{v}_{I}^{pred} \otimes
         \Grad{N_{Ip}^{k+1}} \right]^s
-    \end{equation*}
+    \end{equation*} \;
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-    \STATE \textbf{Update the density field}:
-    \begin{equation*}
-      \rho_p^{k+1} = \frac{\rho_p^k}{1 + \mathit{tra}\left[\Delta\tens{\varepsilon}_{p}^{k+1}\right]}.
-    \end{equation*}
+    \textbf{Update the density field :} $\rho_p^{k+1} =
+    \frac{\rho_p^k}{1 + \mathit{tra}\left[\Delta\tens{\varepsilon}_{p}^{k+1}\right]}.$\;
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-    \STATE \textbf{Compute stress field and update damage parameter}:\\
+    \textbf{Compute stress field and update damage parameter}\;
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-    \STATE \textbf{Balance of forces calculation}:\\
-    Calculate the total grid nodal force $\vec{f}_{I}^{k+1} =
-    \vec{f}_{I}^{int,k+1} + \vec{f}_{I}^{ext,k+1}$.
+    \textbf{Balance of forces calculation :} Calculate the total grid
+    nodal force $\vec{f}_{I}^{k+1} = \vec{f}_{I}^{int,k+1} + \vec{f}_{I}^{ext,k+1}$.\;
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-    \STATE \textbf{Explicit Newmark Corrector}:\\
+    \textbf{Explicit Newmark Corrector :}
     \begin{equation*}
       \vec{v}_{I}^{k+1} = \vec{v}_{I}^{pred} + \gamma\ \Delta t\ \frac{\vec{f}_{I}^{k+1}}{\tens{m}_I^{k+1}}  
-    \end{equation*}
+    \end{equation*}\;
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-    \STATE \textbf{Update particles lagrangian quantities}:
+    \textbf{Update particles lagrangian quantities :}
     \begin{align*}
@@
         \vec{f}_{I}^{k}}{\tens{m}_I^k}
-    \end{align*}
+    \end{align*}\;
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-    \STATE \textbf{Reset nodal values}
-  \end{algorithmic}
+    \textbf{Reset nodal values}\;
+    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+    \label{alg-epc}
+    \caption{Explicit Predictor-Corrector scheme}
 \end{algorithm}

### 2020-05-20 _region_.tex
Cambios 20-5-2020 (I) : Hasta 3.1

@@
   \centering
-  \includegraphics[width=0.5\textwidth]{Particle-failed}
+  \includegraphics[width=0.5\textwidth]{Figure-Particle-failed}
   \caption{Scheme of a linear cohesive law, where the shaded area is
@@
   \centering
-  \includegraphics[width=0.5\textwidth]{Damage}
+  \includegraphics[width=0.5\textwidth]{Figure-Damage}
   \caption{Scheme of a linear cohesive law, where the shaded area is
@@
 \ref{fig:geometry-cracked-panel-mode-I}.
-%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}
   \centering
-  \includegraphics[width=0.4\textwidth]{Mode_I}
+  \includegraphics[width=0.4\textwidth]{Figure-Mode_I}
   \caption{Geometry and boundary condition of the drop-weight impact test.}
@@
 \end{figure}
-%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 The constitutive model consider for numerical experiment is a
-linear-elastic Hookean material, where Young's modulus $E = 1.06$, the Poisson's ratio
-$\mu = 0.333$, and critical energy-release rate $G_c = 0.0001$.
+linear-elastic Hookean material, where Young's modulus $E = 1.06$, the
+Poisson's ratio $\mu = 0.333$, and critical energy-release rate $G_c =
+0.0001$.
+This set of parameters was taken from \cite{Pandolfi_2012}. In
+\acrshort{mpm}, two different discretization are required. In one hand
+a cartesian grid of nodes is consider with a nodal spacing value of
+0.025. On the other hand, the plate will be modeled with a initial
+layout of four particles per element and occupying the Gauss quadrature
+positions.
 
 Figure \ref{fig:Reactions-cracked-panel-mode-I} clearly shows the
-presence of wiggles in the loading and also in the unloading regions
-of the curve when a linear interpolation technique is employed. In
-contrast with it \acrshort{lme} simulation does not exhibit this
-accuracy and remains rectilinear during loading and unloading. An
-important consideration regarding the presence of oscillations once
-both parts of the panel are separated. Is that they should not be
-attributed to the eigenerosion algorithm since the fracture process is
-over. They are due to the dynamic nature of the simulation.
-
+presence of wiggles in both loading and fracture stages
+in the reaction-displacements curve when linear interpolation technique is employed. In
+contrast, \acrshort{lme} simulation does not exhibit these spurious
+oscillations and remains linear. Besides that, linear interpolation
+produces stiffer results than \acrshort{lme}. This can be attributed
+to imprecision in the stress field due to grid-crossing phenomena.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}
   \centering
-  \includegraphics[width=0.8\textwidth]{Reactions_displacements_square_panel_mode_I}
+  \includegraphics[width=0.8\textwidth]{Figure-Reactions-Mode-I}
   \caption{Evolution of the reaction forces plotted \textit{versus}
@@
 \end{figure}
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+On the other hand, Figure \ref{fig:Stress-cracked-panel-mode-I}
+exhibits more clearly the difference between linear interpolation and
+\acrshort{lme}, since numerical instability becomes rather significant
+when particles crosses the boundary of the element in the linear
+case. Although this behavior does not affect significantly to the peak
+stress value in a hookean material \cite{Zhang_EE_2020}, if
+hyperelastic materials are consider for future simulations,
+inaccuracies in the stress field could affect dramatically to the
+final result. On the other hand \acrshort{lme} produces soft stress
+field evolution even after breaking    
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}
 \centering
-\subfigure[t1]{\includegraphics[width=0.7\textwidth]{./Edge_cracked_square_panel_in_mode_I_Stress_0100.png}}
-\subfigure[t2]{\includegraphics[width=0.7\textwidth]{./Edge_cracked_square_panel_in_mode_I_Stress_0250.png}}
-\subfigure[t3]{\includegraphics[width=0.7\textwidth]{./Edge_cracked_square_panel_in_mode_I_Stress_0398.png}}
+\subfigure[t = 25]{\includegraphics[width=0.7\textwidth]{./Figure-Stress-0100-mode-I.png}}
+\subfigure[t = 60]{\includegraphics[width=0.7\textwidth]{./Figure-Stress-0250-mode-I.png}}
+\subfigure[t = 100]{\includegraphics[width=0.7\textwidth]{./Figure-Stress-0398-mode-I.png}}
 \caption{Evolution of the stress tensor magnitude for linear
@@
   \centering
-  \includegraphics[width=0.8\textwidth]{./Drop_weight}
+  \includegraphics[width=0.8\textwidth]{./Figure-Drop-weight}
   \caption{Geometry and boundary condition of the drop-weight impact test.}
@@
 \end{document}
-\message{ !name(2020_EFM_MPM_Eigensoftening.tex) !offset(-868) }
+\message{ !name(2020_EFM_MPM_Eigensoftening.tex) !offset(-902) }

### 2020-05-21 2020_EFM_MPM_Eigensoftening.tex
Cambios 20-5-2020 (I) : Hasta 3.2
Faltan las conclusiones

@@
 \usepackage{subfigure} % subfiguras
+\usepackage{multirow} 
 \usepackage{color}
@@
 
-\newglossaryentry{rho}
-{
-  name=$\rho$,
-  description={Describes the scalar density field}
-}
-
 \newglossaryentry{a}
@@
     LME$_{\beta}$ Pareto set}
+}
+
+\newglossaryentry{rho}
+{
+  name=$\rho$,
+  description={Describes the scalar density field}
+}
+
+\newglossaryentry{fc}
+{
+  name=f$_c$,
+  description={Compressive strenght}
+}
+
+\newglossaryentry{ft}
+{
+  name=f$_t$,
+  description={Tensile strenght}
+}
+
+\newglossaryentry{Gf}
+{
+  name=G$_F$,
+  description={Specific fracture energy}
+}
+
+\newglossaryentry{E}
+{
+  name=E,
+  description={Elastic modulus}
+}
+
+\newglossaryentry{nu}
+{
+  name=$\nu$,
+  description={Poisson ratio}
 }
@@
 \end{equation}
+Implementation details can be consulted in \ref{sec:eigens-algor-1}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 The constitutive model consider for numerical experiment is a
-linear-elastic Hookean material, where Young's modulus $E = 1.06$, the
-Poisson's ratio $\mu = 0.333$, and critical energy-release rate $G_c =
-0.0001$.
-This set of parameters was taken from \cite{Pandolfi_2012}. In
+linear-elastic Hookean material, where Young's modulus \gls{E} = 1.06, the
+Poisson's ratio \gls{nu} = 0.333, and critical energy-release rate
+\gls{Gf} = 0.0001. This set of parameters was taken from \cite{Pandolfi_2012}. In
 \acrshort{mpm}, two different discretization are required. In one hand
@@
 layout of four particles per element and occupying the Gauss quadrature
-positions.
+positions.\\
 
@@
 produces stiffer results than \acrshort{lme}. This can be attributed
-to imprecision in the stress field due to grid-crossing phenomena.
+to imprecision in the stress field due to grid-crossing phenomena.\\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 final result. On the other hand \acrshort{lme} produces soft stress
-field evolution even after breaking    
+field evolution even after breaking.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \centering
-\subfigure[t = 25]{\includegraphics[width=0.7\textwidth]{./Figure-Stress-0100-mode-I.png}}
-\subfigure[t = 60]{\includegraphics[width=0.7\textwidth]{./Figure-Stress-0250-mode-I.png}}
-\subfigure[t = 100]{\includegraphics[width=0.7\textwidth]{./Figure-Stress-0398-mode-I.png}}
+\subfigure[t = 25]{\includegraphics[width=0.73\textwidth]{./Figure-Stress-0100-mode-I.png}}
+\subfigure[t = 60]{\includegraphics[width=0.73\textwidth]{./Figure-Stress-0250-mode-I.png}}
+\subfigure[t = 100]{\includegraphics[width=0.73\textwidth]{./Figure-Stress-0398-mode-I.png}}
 \caption{Evolution of the stress tensor magnitude for linear
@@
 in Section \ref{sec:3.1}, henceforth will be adopted without comparing
-with linear interpolation. Therefore this section is devoted
+with linear interpolation. Therefore this section is devoted to proof
+the accuracy of the eigensoftening algorithm to simulate the behavior
+of quasi-brittle materials under dynamic loading. An example of this
+load case is the three-point bending test on a notched beam is
+conducted under impact loading. This kinds of experiments are
+challenging to reproduce numerically with an explicit solver since
+fracture occurs in a period of milliseconds and high strength
+materials are involved. Accordingly, really small time steps are
+required to achieve a simulation numerically stable. Additionally,
+this kind of simulations traditionally require the implementation of
+contact algorithm to reproduce the hammer impact in the beam. In the
+\acrshort{mpm}, the implementation of this feature can be bypassed to
+obtain preliminary results. Nevertheless, this kind of algorithm could
+be implemented to get ever more accurate solutions. Although this is
+out of the scope of this document, future research of authors will overcome this
+limitation.\\
 
+As in the study of Zhang {\it et al.} \cite{Zhang_2009,Zhang_2010a},
+an impact hammer of 120.6 kg was employed to drop it at an impact
+speed of 881 mm/s. The beam dimensions where 100 mm x 100 mm (B x D)
+in cross section, and 420 mm in total lenght (L). The initial
+notch-depth ratio was approximately 0.5, and the span, S, was fixed at
+300 mm during the tests, see Figure
+\ref{fig:geometry-drop-weight-impact-test}.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}
   \centering
-  \includegraphics[width=0.8\textwidth]{./Figure-Drop-weight}
+  \includegraphics[width=0.8\textwidth]{./Figure-impact-test}
   \caption{Geometry and boundary condition of the drop-weight impact test.}
@@
 \end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The material adopted for the simulation was characterised by Navas
+{\it et al.}~\cite{Navas_2017_ES}, and the material properties, such
+as the material density, \gls{rho}, the compressive strenght, \gls{fc},
+the tensile strenght \gls{ft}, the specific fracture energy, \gls{Gf},
+and the elastic modulus \gls{E} are given in table \ref{tab:concrete-properties}.\\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{table}
+  \centering
+  \begin{tabular}[]{c c c c c c c}
+    \hline
+      &   $\rho$   & $\text{f}_c$ & $\text{f}_t$ & $G_F$ &   E   & $\text{d}_{max}$ \\
+      & (kg/m$^3$) &     (MPa)    &     (MPa)    & (N/m) & (GPa) & (mm) \\
+    \hline
+Value &    2368    &     102.7    &      5.4     &  141  &   31  &  12 \\
+    \hline
+  \end{tabular}
+  \caption[Mechanical properties of thje concrete]{Mechanical
+    properties of the high strenght concrete.}
+  \label{tab:concrete-properties}
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+For the present research, a 2D setting of the experiment has been
+adopted. Both the hammer and the concrete beam are explicitly
+represented. Several levels of discretization are employed to assess
+the objectiveness of the obtained results. The results here exposed
+are from a discretization of 30616 material points and 6297 nodes. To
+achieve better results, an unestructured grid layout has been adopted
+focusing the minimum nodal spacing, 0.47 mm, in the middle of the beam and in
+the impact surface of the hammer. For this simulation, $\gamma$ was
+fixed to 6.\\
+
+First the reaction and impact forces are validated against their
+experimental counterparts. Since the impact forces applied by the
+hammer and the reaction forces at the two supports were experimentally
+measured, they are compared with numerical ones in Figure
+\ref{fig:Reactions-Forces-impact-test}. 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+\begin{figure}
+  \centering
+  \includegraphics[width=0.8\textwidth]{Figure-impact-test-Forces-Time}
+  \caption{Evolution of the reaction forces plotted \textit{versus}
+    the imposed displacement for linear interpolation technique and
+    the \acrshort{lme} approximants.}
+  \label{fig:Reactions-Forces-impact-test}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Note that the general trend of both forces are correctly
+captured. Observe that in experimental solution the delay between
+impact peak and reactions peak does not agree with the numerical
+ones. On the other hand, if the delay is computed analytically through
+concrete wave speed is much closer to the numerical results. A
+feasible explanation to this unexpected result can due the composite
+nature of the concrete. Another discrepancy is in the much higher
+values of maximum impact and reaction forces in numerical than in
+experimental. In this case, this is a consequence of over-rigidity
+supports. Therefore, this results can be improved in future research
+by a suitable contact algorithm.\\
+
+And finally horizontal stress distributions and crack propagation are
+extracted, see Figure \ref{fig:Stress-vs-damage-impact-test}. Compared
+with results obtained by \cite{Navas_2017_ES}, stress evolution
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering
+\subfigure[t = 0.27 ms]{\includegraphics[width=0.83\textwidth]{./Figure-impact-test-Damage-vs-Stress-0060}}
+\subfigure[t = 0.36 ms]{\includegraphics[width=0.83\textwidth]{./Figure-impact-test-Damage-vs-Stress-0080}}
+\subfigure[t = 0.45 ms]{\includegraphics[width=0.83\textwidth]{./Figure-impact-test-Damage-vs-Stress-0100}}
+\caption{Evolution of the stress tensor magnitude for linear
+  interpolation (pictures in the left side), and \acrshort{lme}
+  (pictures in the right side). Both simulations performed with an
+  eigenerosion algorithm.}
+\label{fig:Stress-vs-damage-impact-test}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\clearpage
-
-\section{Explicit Predictor-Corrector algorithm}
+\section{Explicit Newmark Predictor-Corrector algorithm}
 \label{sec:expl-pred-corr}
-
-\begin{algorithm}
+\begin{algorithm}[H]
   \DontPrintSemicolon
@@
     \label{alg-epc}
-    \caption{Explicit Predictor-Corrector scheme}
+    \caption{Explicit Newmark Predictor-Corrector scheme}
 \end{algorithm}
@@
 
-\begin{algorithm}
+\begin{algorithm}[H]
   \DontPrintSemicolon

### 2020-05-21 _region_.tex
Cambios 20-5-2020 (I) : Hasta 3.2
Faltan las conclusiones

@@
 The constitutive model consider for numerical experiment is a
-linear-elastic Hookean material, where Young's modulus $E = 1.06$, the
-Poisson's ratio $\mu = 0.333$, and critical energy-release rate $G_c =
-0.0001$.
+linear-elastic Hookean material, where Young's modulus \gls{E} = 1.06, the
+Poisson's ratio \gls{nu} = 0.333, and critical energy-release rate
+\gls{Gf} = 0.0001.
 This set of parameters was taken from \cite{Pandolfi_2012}. In
@@
 in Section \ref{sec:3.1}, henceforth will be adopted without comparing
-with linear interpolation. Therefore this section is devoted
+with linear interpolation. Therefore this section is devoted to proof
+the accuracy of the eigensoftening algorithm to simulate the behavior
+of quasi-brittle materials under dynamic loading. An example of this
+load case is the three-point bending test on a notched beam is
+conducted under impact loading. This kinds of experiments are
+challenging to reproduce numerically with an explicit solver since
+fracture occurs in a period of milliseconds and high strength
+materials are involved. Accordingly, really small time steps are
+required to achieve a simulation numerically stable.
 
+As in the study of Zhang {\it et al.} \cite{Zhang_2009,Zhang_2010a},
+an impact hammer of 120.6 kg was employed to drop it at an impact
+speed of 881 mm/s. The beam dimensions where 100 mm x 100 mm (B x D)
+in cross section, and 420 mm in total lenght (L). The initial
+notch-depth ratio was approximately 0.5, and the span, S, was fixed at
+300 mm during the tests, see Figure
+\ref{fig:geometry-drop-weight-impact-test}.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}
   \centering
-  \includegraphics[width=0.8\textwidth]{./Figure-Drop-weight}
+  \includegraphics[width=0.8\textwidth]{./Figure-impact-test}
   \caption{Geometry and boundary condition of the drop-weight impact test.}
@@
 \end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The material adopted for the simulation was characterised by Navas
+{\it et al.}~\cite{Navas_2017_ES}, and the material properties, such
+as the material density, \gls{rho}, the compressive strenght, \gls{fc},
+the tensile strenght \gls{ft}, the specific fracture energy, \gls{Gf},
+and the elastic modulus \gls{E} are given in table \ref{tab:concrete-properties}.\\
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{table}
+  \centering
+  \begin{tabular}[]{c c c c c c c}
+    \hline
+      &   $\rho$   & $\text{f}_c$ & $\text{f}_t$ & $G_F$ &   E   & $\text{d}_{max}$ \\
+      & (kg/m$^3$) &     (MPa)    &     (MPa)    & (N/m) & (GPa) & (mm) \\
+    \hline
+Value &    2368    &     102.7    &      5.4     &  141  &   31  &  12 \\
+    \hline
+  \end{tabular}
+  \caption[Mechanical properties of thje concrete]{Mechanical
+    properties of the high strenght concrete.}
+  \label{tab:concrete-properties}
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+For the present research, a 2D setting of the experiment has been
+adopted. Both the hammer and the concrete beam are explicitly
+represented. Several levels of discretization are employed to assess
+the objectiveness of the obtained results. The results here exposed
+are from a discretization of 30616 material points and 6297 nodes. To
+achieve better results, an unestructured grid layout has been adopted
+focusing the minimum nodal spacing, 0.47 mm, in the middle of the beam and in
+the impact surface of the hammer. For this simulation, $\gamma$ was
+fixed to 6.\\
+
+First the reaction and impact forces are validated against their
+experimental counterparts. Since the impact forces applied by the
+hammer and the reaction forces at the two supports were experimentally
+measured, they are compared with numerical ones in Figure
+\ref{fig:Reactions-Forces-impact-test}. 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+\begin{figure}
+  \centering
+  \includegraphics[width=0.8\textwidth]{Figure-impact-test-Forces-Time}
+  \caption{Evolution of the reaction forces plotted \textit{versus}
+    the imposed displacement for linear interpolation technique and
+    the \acrshort{lme} approximants.}
+  \label{fig:Reactions-Forces-impact-test}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Note that the general trend of both forces are correctly
+captured. Observe that in experimental solution the delay between
+impact peak and reactions peak does not agree with the numerical
+ones. On the other hand, if the delay is computed analytically through
+concrete wave speed is much closer to the numerical results. A
+feasible explanation to this unexpected result can due the composite
+nature of the concrete. Another discrepancy is in the much higher
+values of maximum impact and reaction forces in numerical than in
+experimental. In this case, this is a consequence of over-rigidity
+supports. Therefore, this results can be improved in future research
+by a suitable contact algorithm.\\
+
+And finally horizontal stress distributions and crack propagation are
+extracted, see Figure \ref{fig:Stress-vs-damage-impact-test}. 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering
+\subfigure[t = 0.27 ms]{\includegraphics[width=0.83\textwidth]{./Figure-impact-test-Damage-vs-Stress-0060}}
+\subfigure[t = 0.36 ms]{\includegraphics[width=0.83\textwidth]{./Figure-impact-test-Damage-vs-Stress-0080}}
+\subfigure[t = 0.45 ms]{\includegraphics[width=0.83\textwidth]{./Figure-impact-test-Damage-vs-Stress-0100}}
+\caption{Evolution of the stress tensor magnitude for linear
+  interpolation (pictures in the left side), and \acrshort{lme}
+  (pictures in the right side). Both simulations performed with an
+  eigenerosion algorithm.}
+\label{fig:Stress-vs-damage-impact-test}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\clearpage
-
-\section{Explicit Predictor-Corrector algorithm}
+\section{Explicit Newmark Predictor-Corrector algorithm}
 \label{sec:expl-pred-corr}
-
-\begin{algorithm}
-  \floatname{algorithm}{Algorithm}
-  \renewcommand{\thealgorithm}{}
-  \caption{Explicit Predictor-Corrector scheme}
-  \begin{algorithmic}[1]
+\begin{algorithm}[H]
+  \DontPrintSemicolon
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% º
-    \STATE \textbf{Update mass matrix}:
-    \begin{equation*}
-      \tens{m}_{I} = N_{Ip}^{k}\ m_p,
-    \end{equation*}
+    \textbf{Update mass matrix :} $ \tens{m}_{I} = N_{Ip}^{k}\ m_p$ \;
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-    \STATE \textbf{Explicit Newmark Predictor}:\\
+    \textbf{Explicit Newmark Predictor :}
     \begin{equation*}
       \vec{v}_I^{pred} = \frac{ N_{Ip}^{k} m_p (\vec{v}_p^k + (1 - \gamma)\ \Delta t\ \vec{a}_p^k)}{m_I}
-    \end{equation*}
+    \end{equation*}\;
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-    \STATE \textbf{Impose essential boundary conditions}:\\
-    At the fixed boundary, set $\vec{v}_{I}^{pred} = 0$. 
+    \textbf{Impose essential boundary conditions :} At the fixed
+    boundary, set $\vec{v}_{I}^{pred} = 0$.\; 
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-    \STATE \textbf{Deformation tensor increment calculation}.
+    \textbf{Deformation tensor increment calculation :}
     \begin{equation*}
       \Delta \tens{\varepsilon}_{p}^{k+1} = \Delta t\
-        \dot{\tens{\varepsilon}_{p}}^{k+1} = \Delta \left[ \vec{v}_{I}^{pred} \otimes
+        \dot{\tens{\varepsilon}_{p}}^{k+1} = \Delta t\ \left[ \vec{v}_{I}^{pred} \otimes
         \Grad{N_{Ip}^{k+1}} \right]^s
-    \end{equation*}
+    \end{equation*} \;
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-    \STATE \textbf{Update the density field}:
-    \begin{equation*}
-      \rho_p^{k+1} = \frac{\rho_p^k}{1 + \mathit{tra}\left[\Delta\tens{\varepsilon}_{p}^{k+1}\right]}.
-    \end{equation*}
+    \textbf{Update the density field :} $\rho_p^{k+1} =
+    \frac{\rho_p^k}{1 + \mathit{tra}\left[\Delta\tens{\varepsilon}_{p}^{k+1}\right]}.$\;
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-    \STATE \textbf{Compute stress field and update damage parameter}:\\
+    \textbf{Compute stress field and update damage parameter}\;
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-    \STATE \textbf{Balance of forces calculation}:\\
-    Calculate the total grid nodal force $\vec{f}_{I}^{k+1} =
-    \vec{f}_{I}^{int,k+1} + \vec{f}_{I}^{ext,k+1}$.
+    \textbf{Balance of forces calculation :} Calculate the total grid
+    nodal force $\vec{f}_{I}^{k+1} = \vec{f}_{I}^{int,k+1} + \vec{f}_{I}^{ext,k+1}$.\;
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-    \STATE \textbf{Explicit Newmark Corrector}:\\
+    \textbf{Explicit Newmark Corrector :}
     \begin{equation*}
       \vec{v}_{I}^{k+1} = \vec{v}_{I}^{pred} + \gamma\ \Delta t\ \frac{\vec{f}_{I}^{k+1}}{\tens{m}_I^{k+1}}  
-    \end{equation*}
+    \end{equation*}\;
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-    \STATE \textbf{Update particles lagrangian quantities}:
+    \textbf{Update particles lagrangian quantities :}
     \begin{align*}
@@
         \vec{f}_{I}^{k}}{\tens{m}_I^k}
-    \end{align*}
+    \end{align*}\;
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-    \STATE \textbf{Reset nodal values}
-  \end{algorithmic}
+    \textbf{Reset nodal values}\;
+    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+    \label{alg-epc}
+    \caption{Explicit Newmark Predictor-Corrector scheme}
 \end{algorithm}
@@
 \end{document}
-\message{ !name(2020_EFM_MPM_Eigensoftening.tex) !offset(-902) }
+\message{ !name(2020_EFM_MPM_Eigensoftening.tex) !offset(-1010) }

### 2020-05-21 2020_EFM_MPM_Eigensoftening.tex
Cambios 20-5-2020 (II) : Borrador terminado

@@
 
-\journal{Engineering Fracture Mechanics}
+\newcommand{\PNA}[1]{
+  \textcolor{red}{{#1}}
+}
+
+\newcommand{\MMP}[1]{
+  \textcolor{blue}{{#1}}
+}
+
+\newcommand{\DM}[1]{
+  \textcolor{gree}{{#1}}
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% \journal{Engineering Fracture Mechanics}
+\journal{Computers and Structures}
 
@@
 
-The aim of this section is to provide an overview of the special
-techniques employed to face the fracture problem under the \acrshort{mpm}
+The aim of this section is to describe and introduce some special
+techniques required to face the fracture problem under the \acrshort{mpm}
 framework. In consequence it is structured as follows: first in
@@
 all the physical information of the local state ($\sigma_p,
-\varepsilon_p$) and a set of fixed background nodes is employed to
-compute the balance of momentum equation. Since the \acrshort{mpm}
+\varepsilon_p$) and a set of fixed background nodes are introduced to compute the balance of momentum equation. Since the \acrshort{mpm} 
 possesses the advantages of both Lagrangian and Eulerian descriptions,
@@
 presence of wiggles in both loading and fracture stages
-in the reaction-displacements curve when linear interpolation technique is employed. In
-contrast, \acrshort{lme} simulation does not exhibit these spurious
-oscillations and remains linear. Besides that, linear interpolation
-produces stiffer results than \acrshort{lme}. This can be attributed
-to imprecision in the stress field due to grid-crossing phenomena.\\
+in the reaction-displacements curve when linear interpolation
+technique is used. In contrast, \acrshort{lme} simulation does not
+exhibit these spurious oscillations and remains linear. Besides that,
+linear interpolation produces stiffer results than
+\acrshort{lme}. This can be attributed to imprecision in the stress
+field due to grid-crossing phenomena.\\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 adopted. Both the hammer and the concrete beam are explicitly
-represented. Several levels of discretization are employed to assess
+represented. Several levels of discretization were required to assess
 the objectiveness of the obtained results. The results here exposed
@@
 experimental. In this case, this is a consequence of over-rigidity
-supports. Therefore, this results can be improved in future research
+in the supports. Therefore, this results can be improved in future research
 by a suitable contact algorithm.\\
@@
 And finally horizontal stress distributions and crack propagation are
-extracted, see Figure \ref{fig:Stress-vs-damage-impact-test}. Compared
-with results obtained by \cite{Navas_2017_ES}, stress evolution
-
+extracted, see Figure \ref{fig:Stress-vs-damage-impact-test}. Stress
+evolution agrees with the results obtained by \cite{Navas_2017_ES}
+under the \acrshort{otm} framework. Two additional considerations about
+this results are concerning the interpolation technique. In one hand,
+in the opposite to the \acrshort{ugimp} shape function, \acrshort{lme}
+allows unstructured grids. This is a remarkable benefit for this kind
+of simulations since the majority of the computational effort is
+clearly localised in a tiny region of the domain. And in the other
+hand there is the possibility to reduce the shape function support to avoid
+a material point in one side of the crack is affected by those in the
+other side of the crack. 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Conclusions}
 \label{sec:4}
+Based on the EigenMPM approach to fracture proposed by Zhang {\it et al.}
+\cite{Zhang_EE_2020}, we have proposed two addition improvements which
+solves the shortcomings presented in the original concept. First by
+bring to the \acrshort{mpm} framework the concept of eigensoftening,
+which allow to consider gradual failure process of each material
+point. This concept can be compared with cohesive law in the context
+of cohesive fracture. Furthermore, more elaborated damage curves can
+be designed to describe the failure process in sophisticated
+materials. In this direction, an interesting future improvement of the
+algorithm would be the ability to simulate of crack patterns in
+composite material such carbon fiber. This leads a challenging
+research topic. Secondly, \acrshort{lme} is employed to remove from
+the solution those wiggles due to inaccuracies in the stress
+integration. This interpolation technique could help to improve the
+results in fracture propagation by adapting it thorough the
+deformation gradient. \textit{A priori} this will enhance the already
+impressive localisation properties of eigensoftening and eigenerosion
+algorithms.
 
@@
   \DontPrintSemicolon
-    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% º
+    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
     \textbf{Update mass matrix :} $ \tens{m}_{I} = N_{Ip}^{k}\ m_p$ \;

### 2020-05-21 _region_.tex
Cambios 20-5-2020 (II) : Borrador terminado

@@
 Poisson's ratio \gls{nu} = 0.333, and critical energy-release rate
-\gls{Gf} = 0.0001.
-This set of parameters was taken from \cite{Pandolfi_2012}. In
+\gls{Gf} = 0.0001. This set of parameters was taken from \cite{Pandolfi_2012}. In
 \acrshort{mpm}, two different discretization are required. In one hand
@@
 materials are involved. Accordingly, really small time steps are
-required to achieve a simulation numerically stable.
+required to achieve a simulation numerically stable. Additionally,
+this kind of simulations traditionally require the implementation of
+contact algorithm to reproduce the hammer impact in the beam. In the
+\acrshort{mpm}, the implementation of this feature can be bypassed to
+obtain preliminary results. Nevertheless, this kind of algorithm could
+be implemented to get ever more accurate solutions. Although this is
+out of the scope of this document, future research of authors will overcome this
+limitation.\\
 
@@
 And finally horizontal stress distributions and crack propagation are
-extracted, see Figure \ref{fig:Stress-vs-damage-impact-test}. 
+extracted, see Figure \ref{fig:Stress-vs-damage-impact-test}. Compared
+with results obtained by \cite{Navas_2017_ES}, stress evolution
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \end{document}
-\message{ !name(2020_EFM_MPM_Eigensoftening.tex) !offset(-1010) }
+\message{ !name(2020_EFM_MPM_Eigensoftening.tex) !offset(-1019) }

### 2020-05-21 2020_EFM_MPM_Eigensoftening.tex
Pequeños cambios

@@
 which allow to consider gradual failure process of each material
-point. This concept can be compared with cohesive law in the context
+point. This concept can be compared with a cohesive law in the context
 of cohesive fracture. Furthermore, more elaborated damage curves can
-be designed to describe the failure process in sophisticated
+be designed to describe the failure process in more sophisticated
 materials. In this direction, an interesting future improvement of the
@@
 the solution those wiggles due to inaccuracies in the stress
-integration. This interpolation technique could help to improve the
+integration. This interpolation technique could help to improve
 results in fracture propagation by adapting it thorough the

### 2020-05-24 2020_EFM_MPM_Eigensoftening.tex
20200524

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newcommand{\etal}{
+  \textit{et al.}
+}
 
@@
   originally for the \acrfull{otm} approximation scheme, is extended
-  to the \acrshort{mpm} with the aim of present a suitable alternative
+  to the \acrshort{mpm} with the aim of presenting a suitable alternative
   to the existing fracture algorithms developed for the
@@
   eigensoftening algorithm against both analytical and experimental
-  results proofs the well performance of the method under challenging
-  loads.
+  results proofs the well performance of the method when challenging
+  applications are to modeled.
 \end{abstract}
@@
 \begin{keyword}
-Quasi brittle fracture \sep Local-\textit{max-ent} approximation \sep
+Quasi brittle fracture \sep Local-\textit{Max-Ent} approximation \sep
 Material Point Method \sep Solid Dynamics
@@
 \label{sec:1}
-Presence of cracks are a violation of the continuity requirement in
-\acrfull{fem}. To overcome it, numerous of numerical
-artifacts has been proposed with the aim of reproducing such a
-complex behaviour. These techniques vary from employing cohesive
-approaches \cite{Barenblatt,Hilleborg_1976}, by adaptively inserting
+The presence of cracks is a violation of the continuity requirement of the
+\acrfull{fem}. To overcome this issue, numerous numerical
+artifacts have been proposed with the aim of reproducing such a
+complex behaviour. These techniques vary from the employment of cohesive
+approaches~\cite{Barenblatt,Hilleborg_1976}, \PNA{to the gradual insertion of}
 cohesive elements \cite{Ortiz_1999,Pandolfi_2002,Ruiz_2000} at solid
-elements boundaries, or handling arbitrary cracks paths by level set
-representation of the fracture surface \cite{Belytschko_03}. The
+elements boundaries, or handling arbitrary crack paths by level set
+representation of the fracture surface~\cite{Belytschko_03}. The
 simulation of fracture propagation in a more accurate and effective
-way can be considered as one of the original drivers for developing
-novel spatial discretization methods like meshfree techniques. Some
+way can be considered as one of the \PNA{ongoing goals} of the development of novel spatial discretization methods like meshfree techniques. Some
 examples of it are the \acrfull{mpm}
@@
 
-Regarding \acrshort{mpm}, fracture can be described numerically in
-two ways. One is the ``CRAcks with Material Points (CRAMP)''
-\cite{Nairn_2003,Nairn_2006} and consist in to remove the restriction
-of the single-valued velocity field close to the crack thorough two or
-more sets of nodes. In this method, different labels are assigned to the material points
+Regarding \acrshort{mpm}, fracture \PNA{has been treated numerically through two different ways}.
+On the one hand, the ``CRAcks with Material Points (CRAMP)'' is proposed~\cite{Nairn_2003,Nairn_2006}.
+\PNA{The basis of this methodology consist of the removal of} the restriction
+of the single-valued velocity field close to the crack through, at least, two sets of nodes. In this method, different labels are assigned to the material points
 and nodes to distinguish if they are in the same side of the crack or
-not. Under this approach crack surface is described with line segments
+not. Under this approach, crack surface is described with line segments
 in 2D and triangle patches in 3D cases. The chosen criteria for crack
@@
 intensity factor or the J-integral discussed by Guo \& Nairn
-(2004)\cite{Nairn_2004}. The other approach is to introduce failed
-material points to describe the crack evolution. In this method, the
+(2004)\cite{Nairn_2004}. 
+On the other hand, the \PNA{foundation} of the second approach is the introduction of failed
+material points to describe the crack evolution. In these methods, the
 formation of failed points describes the nucleation of cracks, and
 thereafter its propagation and branching. Consequently, the position
-of the crack does not need to be explicitly stated. These represents
+of the crack does not need to be explicitly stated. This fact represents
 significant advantages over the ``CRAMP''. Under this approach, the
@@
 which has been discussed by Chen {\it et al.}\cite{Zhenmao_2005} and
-Schreyer {\it et al.}\cite{Schreyer_2002}. And has been successfully
-employed to simulate the fracture of brittle materials by Chen {\it et
+Schreyer {\it et al.}\cite{Schreyer_2002}. Successful simulations are provided within the framework of the fracture of brittle materials by Chen {\it et
   al.} \cite{Chen_2002,Chen_2003} and Sulsky \& Schreyer
@@
 \cite{Schmidt_2009} introduced the concept of eigenfracture, where
-they approximate the crack set by means of eigen-deformations, wich
+crack sets are approximated by means of eigen-deformations, which
 enable the material to develop displacement jumps at no cost of local
 elastic energy. Later, the eigenerosion approach to brittle facture
-was developed by Pandolfi {\it et al.}
-\cite{Pandolfi_2012,Pandolfi_2013}. In this technique the erosion of
-the material point means that each material point can be either intact or be completely failed or eroded and has no load bearing
-capacity. This method has been successfully applied to simulate high
-complex phenomena such dynamic fragmentation of metals
+was carried out by Pandolfi {\it et al.}
+\cite{Pandolfi_2012,Pandolfi_2013}. \PNA{In this technique, the concept of ``erosion'' of
+the material point is depicted, being the material point able to remain intact or become completely failed or eroded, when no loading
+capacity is bore}. This method has been successfully applied to simulate high
+complex phenomena such as dynamic fragmentation of metals
 \cite{Li_2015}. Recently, Zhang {\it et al.}
@@
 fracture of brittle materials in the \acrshort{mpm}
-framework. Nonetheless, in quasi-brittle materials simulations
-performed with this approach exhibit an overestimation of tensile
-stress and the strain peaks. And conventional \acrshort{mpm}/\acrshort{gimp} always
-faces stress oscillations.\\
+framework. Nonetheless, when quasi-brittle materials are simulated
+though this approach, the results exhibit an overestimation of tensile
+stress and strain peaks. Furthermore, since the work of Zhang {\it et al.}
+\cite{Zhang_EE_2020} is made with conventional \acrshort{mpm}/\acrshort{gimp}, stress oscillations are to be faced.\\
 
 To overcome the limitations observed in the EigenMPM
-\cite{Zhang_EE_2020}. The present research propose the eigensoftening
+\cite{Zhang_EE_2020}, the present research proposes the eigensoftening
 algorithm developed by Navas {\it et al.}
@@
 engineered for quasi-brittle materials. Inspired in the concept of the
-crack band model \cite{Bazant83}, since energy dissipation is thorough
-the softened (or failed) volume, it is able to capture the gradual rather than abrupt
-dissipation of the fracture energy. Second, to mitigate stress
-oscillations the \acrfull{lme} approximation technique
-\cite{Arroyo2006} to deal with tensile instabilities, such those that
-occurs when particles crosses an element boundary.\\
+crack band model \cite{Bazant83}, since energy dissipation is performed through the softened (or failed) volume, this methodology is able to capture the gradual rather than abrupt
+dissipation of the fracture energy. \PNA{Moreover, in order to mitigate stress
+oscillations as well as to deal with tensile instabilities, such those that
+occurs when particles crosses an element boundary, the work of Molinos~\etal~\cite{Molinos2020} is followed.
+The traditional \acrshort{mpm} technique is enhanced through the \acrfull{lme} approximation technique
+\cite{Arroyo2006} for the spatial discretization as well as a explicitly \acrshort{mpm} \acrfull{npc} scheme is derived for the time discretization.}\\
 
@@
 techniques required to face the fracture problem under the \acrshort{mpm}
-framework. In consequence it is structured as follows: first in
-\ref{sec:2.1} the \acrfull{npc} algorithm for the \acrshort{mpm}
-will be exposed, next the \acrshort{lme} approximants are
+framework. In consequence, this section is structured as follows: first, in
+\ref{sec:2.1}, the \acrfull{npc} algorithm for the \acrshort{mpm}
+will be exposed; next the \acrshort{lme} approximants are
 introduced in \ref{sec:2.2} as an accurate alternative technique to
 interpolate data between particles and nodes, and finally fracture
-algorithms based in the eigendeformation concept are presented in \ref{sec:2.3}.
+algorithms based on the eigendeformation concept are presented in \ref{sec:2.3}.
 
@@
 The \acrshort{mpm}~\cite{Sulsky1994} is a meshfree Lagrangian-Eulerian
-method where moving material points, henceforth particles, carries on
+method where moving material points, henceforth in this research, particles will carry on
 all the physical information of the local state ($\sigma_p,
-\varepsilon_p$) and a set of fixed background nodes are introduced to compute the balance of momentum equation. Since the \acrshort{mpm} 
+\varepsilon_p$) and a set of fixed background nodes will be introduced to compute the balance of momentum equation. Since the \acrshort{mpm} 
 possesses the advantages of both Lagrangian and Eulerian descriptions,
-no element distortion takes place in the \acrshort{mpm}. Therefore it
+no element distortion takes place in the \acrshort{mpm}. Therefore, it
 is an appropriate and efficient method to solve problems with moving
@@
 nodal equilibrium equation in a FEM-like procedure, and finally
-(iii) a Lagrangian advection of the particles. In the present research
-a explicit predictor-corrector time integration scheme is adopted. The
-purposes of this choice is motivated due its proved robustness and
+(iii) a Lagrangian advection of the particles. In the present research,
+an explicit predictor-corrector time integration scheme is adopted. The
+purposes of this choice is motivated due to its proved robustness and
 stability for dynamic computations. In the first stage, the nodal
-velocity predictor is computed following \eqref{eq:Predictor-velocity}, 
+velocity predictor is computed following \eqref{eq:Predictor-velocity}: 
 \begin{equation}
@@
 \end{equation}
-This way of computing the nodal predictor is both numerically stable
-and minimise the computational effort. Once nodal velocities are
-obtained, the essential boundary conditions are imposed. After that, a
+\PNA{EXPLICAR NOTACION, CUIDADO CON EL GAMMA} This way of computing the nodal predictor is numerically stable
+as well as minimises the computational effort. Once nodal velocities are
+obtained, the essential boundary conditions are imposed. After that, an
 Eulerian phase is computed in the set of nodes in a
 \acrshort{fem}-like way, where nodal forces $\vec{f}_{I}^{k+1}$ are
-computed thorough the equilibrium equation. Next the nodal velocities
-are corrected in a \textit{corrector} stage,
+computed through the equilibrium equation. Next the nodal velocities
+are corrected in a \textit{corrector} stage:
 \begin{equation}
@@
 \end{equation}
-Finally updated the particles are advected in the Lagrangian stage as
+Finally, in order to update the particles, those are advected in the Lagrangian stage as
 \begin{align}
@@
 The traditional way to compute the optimal value of $\vec{\lambda}^*$
-is thorough a Newton-Raphson procedure, or in more challenging
+is through a Newton-Raphson procedure, or in more challenging
 scenarios by a combination of the Newton-Raphson and the Nelder-Mead
@@
 limitation is concerning its inability to simulate properly quasi-brittle
-fracture \cite{Navas_2018_ES}. It can be solved thorough the
+fracture \cite{Navas_2018_ES}. It can be solved through the
 eigensoftening algorithm described in Section \ref{sec:2.3}. A proof
@@
 integration. This interpolation technique could help to improve
-results in fracture propagation by adapting it thorough the
+results in fracture propagation by adapting it through the
 deformation gradient. \textit{A priori} this will enhance the already

### 2020-05-25 2020_EFM_MPM_Eigensoftening.tex
Cambios 25-5-2020
Nueva sección describiendo el algoritmo de reconstrucción de la vecindad. 
Aclaraciones sobre la notación

@@
 \makeglossaries
-
-\newglossaryentry{domain}
-{
-  name=$\varOmega$,
-  description={Continuum domain}
-}
-
-\newglossaryentry{contour}
-{
-  name=$\partial\varOmega$,
-  description={Boundary of the continuum domain $\varOmega$. Also
-    defined as $\Gamma$}
-}
-
-\newglossaryentry{dirichlet-boundary}
-{
-  name=$ \Gamma_d$,
-  description={Essential or Dirichlet boundary conditions over $\partial\varOmega$}
-}
-
-\newglossaryentry{neumann-boundary}
-{
-  name=$ \Gamma_n$,
-  description={Natural or Nemann boundary conditions over $\partial\varOmega$}
-}
-
-\newglossaryentry{a}
-{
-  name=$\vect{a}$,
-  description={First order tensor which describes the acceleration field}
-}
-
-\newglossaryentry{v}
-{
-  name=$\vect{v}$,
-  description={First order tensor which describes the velocity field}
-}
-
-\newglossaryentry{u}
-{
-  name=$\vect{u}$,
-  description={First order tensor which describes the displacement field}
-}
-
-\newglossaryentry{x}
-{
-  name=$\vect{x}$,
-  description={First order tensor which describes the global coordinates field}
-}
-
-\newglossaryentry{xi}
-{
-  name=$\vect{\xi}$,
-  description={First order tensor which describes the local coordinates field}
-}
-
-\newglossaryentry{stress}
-{
-  name=$\tens{\sigma}$,
-  description={Second order tensor which means the Cauchy stress tensor}
-}
-
-\newglossaryentry{strain}
-{
-  name=$\tens{\varepsilon}$,
-  description={Second order tensor which means the Cauchy strain tensor}
-}
-
-\newglossaryentry{Constitutive}
-{
-  name=$\tens{D}$,
-  description={Four order tensor which means the constitutive response
-    of the material}
-}
-
-\newglossaryentry{LME-beta}
-{
-  name=$\beta$,
-  description={Regularization or thermalization parameter of the
-    LME$_{\beta}$ Pareto set}
-}
-
-\newglossaryentry{rho}
-{
-  name=$\rho$,
-  description={Describes the scalar density field}
-}
-
-\newglossaryentry{fc}
-{
-  name=f$_c$,
-  description={Compressive strenght}
-}
-
-\newglossaryentry{ft}
-{
-  name=f$_t$,
-  description={Tensile strenght}
-}
-
-\newglossaryentry{Gf}
-{
-  name=G$_F$,
-  description={Specific fracture energy}
-}
-
-\newglossaryentry{E}
-{
-  name=E,
-  description={Elastic modulus}
-}
-
-\newglossaryentry{nu}
-{
-  name=$\nu$,
-  description={Poisson ratio}
-}
 
@@
 \newacronym{fe}{FE}{Forward Euler}
+
+\newglossaryentry{domain}
+{
+  name=$\varOmega$,
+  description={Continuum domain}
+}
+
+\newglossaryentry{contour}
+{
+  name=$\partial\varOmega$,
+  description={Boundary of the continuum domain $\varOmega$. Also
+    defined as $\Gamma$}
+}
+
+\newglossaryentry{dirichlet-boundary}
+{
+  name=$ \Gamma_d$,
+  description={Essential or Dirichlet boundary conditions over $\partial\varOmega$}
+}
+
+\newglossaryentry{neumann-boundary}
+{
+  name=$ \Gamma_n$,
+  description={Natural or Nemann boundary conditions over $\partial\varOmega$}
+}
+
+\newglossaryentry{a}
+{
+  name=$\vect{a}$,
+  description={First order tensor which describes the acceleration field}
+}
+
+\newglossaryentry{v}
+{
+  name=$\vect{v}$,
+  description={First order tensor which describes the velocity field}
+}
+
+\newglossaryentry{u}
+{
+  name=$\vect{u}$,
+  description={First order tensor which describes the displacement field}
+}
+
+\newglossaryentry{x}
+{
+  name=$\vect{x}$,
+  description={First order tensor which describes the global coordinates field}
+}
+
+\newglossaryentry{xi}
+{
+  name=$\vect{\xi}$,
+  description={First order tensor which describes the local coordinates field}
+}
+
+\newglossaryentry{stress}
+{
+  name=$\tens{\sigma}$,
+  description={Second order tensor which means the Cauchy stress tensor}
+}
+
+\newglossaryentry{strain}
+{
+  name=$\tens{\varepsilon}$,
+  description={Second order tensor which means the Cauchy strain tensor}
+}
+
+\newglossaryentry{Constitutive}
+{
+  name=$\tens{D}$,
+  description={Four order tensor which means the constitutive response
+    of the material}
+}
+
+\newglossaryentry{LME-beta}
+{
+  name=$\beta$,
+  description={Regularization or thermalization parameter of the
+    LME$_{\beta}$ Pareto set}
+}
+
+\newglossaryentry{rho}
+{
+  name=$\rho$,
+  description={Describes the scalar density field}
+}
+
+\newglossaryentry{fc}
+{
+  name=f$_c$,
+  description={Compressive strenght}
+}
+
+\newglossaryentry{ft}
+{
+  name=f$_t$,
+  description={Tensile strenght}
+}
+
+\newglossaryentry{Gf}
+{
+  name=G$_F$,
+  description={Specific fracture energy}
+}
+
+\newglossaryentry{E}
+{
+  name=E,
+  description={Elastic modulus}
+}
+
+\newglossaryentry{nu}
+{
+  name=$\nu$,
+  description={Poisson ratio}
+}
+
+\newglossaryentry{gamma-npc}
+{
+  name=$\gamma$,
+  description={Time integration parameter for the \acrshort{npc} algorithm}
+}
+
+\newglossaryentry{gamma-lme}
+{
+  name=$\widehat{\gamma}$,
+  description={Dimensionless parameter to control the value of the
+    thermalization parameter $\beta$ of the \acrshort{lme} shape functions.}
+}
 
@@
 interpolate data between particles and nodes, and finally fracture
-algorithms based on the eigendeformation concept are presented in \ref{sec:2.3}.
+algorithms based on the eigendeformation concept are presented in
+\ref{sec:2.3}.
 
@@
 The \acrshort{mpm}~\cite{Sulsky1994} is a meshfree Lagrangian-Eulerian
-method where moving material points, henceforth in this research, particles will carry on
-all the physical information of the local state ($\sigma_p,
-\varepsilon_p$) and a set of fixed background nodes will be introduced to compute the balance of momentum equation. Since the \acrshort{mpm} 
-possesses the advantages of both Lagrangian and Eulerian descriptions,
-no element distortion takes place in the \acrshort{mpm}. Therefore, it
-is an appropriate and efficient method to solve problems with moving
-discontinuities such as fracture evolution.\\
+method where moving material points, henceforth in this research,
+particles \MMP{($\square_p$)} will carry on all the physical information of the local state ($\sigma_p,
+\varepsilon_p$) and a set of fixed background nodes \MMP{($\square_I$)} will
+be introduced to compute the balance of momentum equation. Since the
+\acrshort{mpm} possesses the advantages of both Lagrangian and
+Eulerian descriptions, no element distortion takes place in the
+\acrshort{mpm}. Therefore, it is an appropriate and efficient method
+to solve problems with moving discontinuities such as fracture evolution.\\
 Without loosing generality, the \acrshort{mpm} algorithm
@@
 purposes of this choice is motivated due to its proved robustness and
-stability for dynamic computations. In the first stage, the nodal
-velocity predictor is computed following \eqref{eq:Predictor-velocity}: 
+stability for dynamic computations. \MMP{In the first stage, the nodal
+velocity predictor $ \vec{\tilde{v}}_I^{k+1}$ is computed thorough
+nodal velocities $\vec{v}_I$ and accelerations $\vec{a}_I$ evaluated
+in the $k$ time step},
 \begin{equation}
   \label{eq:Predictor-velocity}
-  \vec{\tilde{v}}_I^{k+1} = \frac{ N_{Ip}^{k} m_p (\vec{v}_p^k + (1 - \gamma)\ \Delta t\ \vec{a}_p^k)}{\tens{m}_I^{k+1}}\ .
-\end{equation}
-\PNA{EXPLICAR NOTACION, CUIDADO CON EL GAMMA} This way of computing the nodal predictor is numerically stable
+  \vec{\tilde{v}}_I^{k+1} = \frac{N_{Ip}^{k} m_p (\vec{v}_p^k + (1 - \gamma)\ \Delta t\ \vec{a}_p^k)}{\tens{m}_I^{k+1}}\ .
+\end{equation}
+\MMP{Where \gls{gamma-npc} is an user-defined parameter (typically adopted as
+0.5), $\tens{m}_I$ represents the lumped mass matrix, and $N_{Ip}^{k}$ is
+the nodal contribution of the shape function evaluated in the particle
+coordinates $\vec{x}_p^k$.} This way of computing the nodal predictor is numerically stable
 as well as minimises the computational effort. Once nodal velocities are
@@
 Pareto optimal solutions $\beta \in
-(0,\infty)$. Notice that $\beta$ has units of $[L]^{-2}$,
-therefore it can be controlled by adjusting a dimensionless parameter,
-$\gamma=\beta h^2$ \cite{Arroyo2006}, where $h$ is defined as a
-suitable measure of the nodal spacing. With the restrictions exposed in
-\eqref{eq:LME-scheme-pareto-set}, the unique solution of the local
+(0,\infty)$.\MMP{Notice that $\beta$ has units of $[L]^{-2}$,
+therefore it can be controlled by adjusting a dimensionless
+parameter\footnote{To avoid confusion with the \gls{gamma-npc} parameter of
+  the \acrshort{npc}, the dimensionless parameter defined in Arroyo \&
+  Ortiz \cite{Arroyo2006} as $\gamma$ will be represent by
+  \gls{gamma-lme} to preserve as much as possible the original notation.},
+$\widehat{\gamma}=\beta h^2$}, where $h$ is defined as a
+suitable measure of the nodal spacing. With the restrictions of the
+Pareto set, the unique solution of the local
 \textit{max-ent} problem \acrshort{lme}$_\beta$ is,
@@
 \end{equation}
-Implementation details can be consulted in \ref{sec:eigens-algor-1}
+Implementation details can be consulted in \ref{sec:eigens-algor-1}.
+
+\MMP{
+\subsection{$\epsilon$-neighborhood reconstruction : A node-linked method}
+\label{sec:epsil-neighb-reconst}
+Since this operation could be extremely demanding, optimal
+numerical implementation should be employed. In opposite with the Cell-linked
+method proposed by Allen \& Tildesley \cite{Allen_et_al_1989} where
+the definition of a numerical tolerance is required for auxiliar
+algorithms like Crossing Number \cite{Shimrat_1962} or Correct
+Even-Odd \cite{Galetzka_et_al_2017}. To avoid these error prone
+techniques, the method here proposed exploits the meshfree benefits of
+the \acrshort{lme} approximants to introduce a node-linked method. Due
+to the global definition of this interpolation technique, the classical
+interpretation of the \acrshort{fem} element typically adopted in
+\acrshort{mpm} simulations is not required anymore, instead a linked
+list of tributary nodes is reconstructed with the closest node as
+starting point at each time step. Therefore, each node is assigned an
+unique linked-list of those particles which are closest to it. This
+approach allows to reconstruct easily a search list with the support
+of the initial connectivity of the mesh and offers a suitable basis
+for an easy implementation of other interpolation techniques with
+minimum coding effort. A detailed explanation of the proposed
+algorithm can be found in \ref{sec:node-linked-method-1}.
+}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 focusing the minimum nodal spacing, 0.47 mm, in the middle of the beam and in
-the impact surface of the hammer. For this simulation, $\gamma$ was
+the impact surface of the hammer. For this simulation, \gls{gamma-lme} was
 fixed to 6.\\
@@
   \label{alg-eigens}
+  \caption{Eigensoftening algorithm}
+\end{algorithm}
+
+\section{Node-linked method for $\epsilon$-neighborhood reconstruction}
+\label{sec:node-linked-method-1}
+\begin{algorithm}[H]
+  \DontPrintSemicolon
+  \KwInput{$I_0$ : Closest node for each particle}
+  \KwInput{$I_{Nodes}$ : List of nodes close to each node}
+  \KwInput{$Particles_I$ : List of particles close to each node}
+  \KwOutput{$\text{neighborhood}_{\epsilon}$ : $\epsilon$-neighborhood for each particle}
+  \For{$p$ to $N_p$}
+  {
+    For each $p$ get $I_0$\;
+    Eval $I_{Nodes}(I_0)$ \;
+    \For{$k \in I_{Nodes}(I_0)$}
+    {
+      $\text{neighborhood}_{\epsilon}^{k+1}$ = $\text{neighborhood}_{\epsilon}^{k} \cup Particles_I(k)$
+    }
+    \For{$p_{\epsilon} \in \text{neighborhood}_{\epsilon}$}
+    {
+      \If{$distance(p_{\epsilon},p) > \epsilon $}
+      {
+        pop $p_{\epsilon}$ from neighborhood$_{\epsilon}$\;
+      }      
+    }
+
+  }  
+  \caption{$\epsilon$-neighborhood reconstruction algorithm}
 \end{algorithm}

### 2020-05-25 _region_.tex
Cambios 25-5-2020
Nueva sección describiendo el algoritmo de reconstrucción de la vecindad. 
Aclaraciones sobre la notación

@@
 
+\newglossaryentry{domain}
+{
+  name=$\varOmega$,
+  description={Continuum domain}
+}
+
+\newglossaryentry{contour}
+{
+  name=$\partial\varOmega$,
+  description={Boundary of the continuum domain $\varOmega$. Also
+    defined as $\Gamma$}
+}
+
+\newglossaryentry{dirichlet-boundary}
+{
+  name=$ \Gamma_d$,
+  description={Essential or Dirichlet boundary conditions over $\partial\varOmega$}
+}
+
+\newglossaryentry{neumann-boundary}
+{
+  name=$ \Gamma_n$,
+  description={Natural or Nemann boundary conditions over $\partial\varOmega$}
+}
+
+\newglossaryentry{a}
+{
+  name=$\vect{a}$,
+  description={First order tensor which describes the acceleration field}
+}
+
+\newglossaryentry{v}
+{
+  name=$\vect{v}$,
+  description={First order tensor which describes the velocity field}
+}
+
+\newglossaryentry{u}
+{
+  name=$\vect{u}$,
+  description={First order tensor which describes the displacement field}
+}
+
+\newglossaryentry{x}
+{
+  name=$\vect{x}$,
+  description={First order tensor which describes the global coordinates field}
+}
+
+\newglossaryentry{xi}
+{
+  name=$\vect{\xi}$,
+  description={First order tensor which describes the local coordinates field}
+}
+
+\newglossaryentry{stress}
+{
+  name=$\tens{\sigma}$,
+  description={Second order tensor which means the Cauchy stress tensor}
+}
+
+\newglossaryentry{strain}
+{
+  name=$\tens{\varepsilon}$,
+  description={Second order tensor which means the Cauchy strain tensor}
+}
+
+\newglossaryentry{Constitutive}
+{
+  name=$\tens{D}$,
+  description={Four order tensor which means the constitutive response
+    of the material}
+}
+
+\newglossaryentry{LME-beta}
+{
+  name=$\beta$,
+  description={Regularization or thermalization parameter of the
+    LME$_{\beta}$ Pareto set}
+}
+
+\newglossaryentry{rho}
+{
+  name=$\rho$,
+  description={Describes the scalar density field}
+}
+
+\newglossaryentry{fc}
+{
+  name=f$_c$,
+  description={Compressive strenght}
+}
+
+\newglossaryentry{ft}
+{
+  name=f$_t$,
+  description={Tensile strenght}
+}
+
+\newglossaryentry{Gf}
+{
+  name=G$_F$,
+  description={Specific fracture energy}
+}
+
+\newglossaryentry{E}
+{
+  name=E,
+  description={Elastic modulus}
+}
+
+\newglossaryentry{nu}
+{
+  name=$\nu$,
+  description={Poisson ratio}
+}
+
+\newglossaryentry{gamma-npc}
+{
+  name=$\gamma$,
+  description={Time integration parameter for the \acrshort{npc} algorithm}
+}
+
+\newglossaryentry{gamma-lme}
+{
+  name=$\widehat{\gamma}$,
+  description={Dimensionless parameter to control the value of the
+    thermalization parameter $\beta$ of the \acrshort{lme} shape functions.}
+}
+
 % End glossaries
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\journal{Engineering Fracture Mechanics}
+\newcommand{\etal}{
+  \textit{et al.}
+}
+
+\newcommand{\PNA}[1]{
+  \textcolor{red}{{#1}}
+}
+
+\newcommand{\MMP}[1]{
+  \textcolor{blue}{{#1}}
+}
+
+\newcommand{\DM}[1]{
+  \textcolor{gree}{{#1}}
+}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% \journal{Engineering Fracture Mechanics}
+\journal{Computers and Structures}
 
@@
 
-The aim of this section is to provide an overview of the special
-techniques employed to face the fracture problem under the \acrshort{mpm}
-framework. In consequence it is structured as follows: first in
-\ref{sec:2.1} the \acrfull{npc} algorithm for the \acrshort{mpm}
-will be exposed, next the \acrshort{lme} approximants are
+The aim of this section is to describe and introduce some special
+techniques required to face the fracture problem under the \acrshort{mpm}
+framework. In consequence, this section is structured as follows: first, in
+\ref{sec:2.1}, the \acrfull{npc} algorithm for the \acrshort{mpm}
+will be exposed; next the \acrshort{lme} approximants are
 introduced in \ref{sec:2.2} as an accurate alternative technique to
 interpolate data between particles and nodes, and finally fracture
-algorithms based in the eigendeformation concept are presented in \ref{sec:2.3}.
+algorithms based on the eigendeformation concept are presented in
+\ref{sec:2.3}.
 
@@
 The \acrshort{mpm}~\cite{Sulsky1994} is a meshfree Lagrangian-Eulerian
-method where moving material points, henceforth particles, carries on
-all the physical information of the local state ($\sigma_p,
-\varepsilon_p$) and a set of fixed background nodes is employed to
-compute the balance of momentum equation. Since the \acrshort{mpm}
-possesses the advantages of both Lagrangian and Eulerian descriptions,
-no element distortion takes place in the \acrshort{mpm}. Therefore it
-is an appropriate and efficient method to solve problems with moving
-discontinuities such as fracture evolution.\\
+method where moving material points, henceforth in this research,
+particles \MMP{($\square_p$)} will carry on all the physical information of the local state ($\sigma_p,
+\varepsilon_p$) and a set of fixed background nodes \MMP{($\square_I$)} will
+be introduced to compute the balance of momentum equation. Since the
+\acrshort{mpm} possesses the advantages of both Lagrangian and
+Eulerian descriptions, no element distortion takes place in the
+\acrshort{mpm}. Therefore, it is an appropriate and efficient method
+to solve problems with moving discontinuities such as fracture evolution.\\
 Without loosing generality, the \acrshort{mpm} algorithm
@@
 nodal equilibrium equation in a FEM-like procedure, and finally
-(iii) a Lagrangian advection of the particles. In the present research
-a explicit predictor-corrector time integration scheme is adopted. The
-purposes of this choice is motivated due its proved robustness and
-stability for dynamic computations. In the first stage, the nodal
-velocity predictor is computed following \eqref{eq:Predictor-velocity}, 
+(iii) a Lagrangian advection of the particles. In the present research,
+an explicit predictor-corrector time integration scheme is adopted. The
+purposes of this choice is motivated due to its proved robustness and
+stability for dynamic computations. \MMP{In the first stage, the nodal
+velocity predictor $ \vec{\tilde{v}}_I^{k+1}$ is computed thorough
+nodal velocities $\vec{v}_I$ and accelerations $\vec{a}_I$ evaluated
+in the $k$ time step},
 \begin{equation}
   \label{eq:Predictor-velocity}
-  \vec{\tilde{v}}_I^{k+1} = \frac{ N_{Ip}^{k} m_p (\vec{v}_p^k + (1 - \gamma)\ \Delta t\ \vec{a}_p^k)}{\tens{m}_I^{k+1}}\ .
-\end{equation}
-This way of computing the nodal predictor is both numerically stable
-and minimise the computational effort. Once nodal velocities are
-obtained, the essential boundary conditions are imposed. After that, a
+  \vec{\tilde{v}}_I^{k+1} = \frac{N_{Ip}^{k} m_p (\vec{v}_p^k + (1 - \gamma)\ \Delta t\ \vec{a}_p^k)}{\tens{m}_I^{k+1}}\ .
+\end{equation}
+\MMP{Where \gls{gamma-npc} is an user-defined parameter (typically adopted as
+0.5), $\tens{m}_I$ represents the lumped mass matrix, and $N_{Ip}^{k}$ is
+the nodal contribution of the shape function evaluated in the particle
+coordinates $\vec{x}_p^k$.} This way of computing the nodal predictor is numerically stable
+as well as minimises the computational effort. Once nodal velocities are
+obtained, the essential boundary conditions are imposed. After that, an
 Eulerian phase is computed in the set of nodes in a
 \acrshort{fem}-like way, where nodal forces $\vec{f}_{I}^{k+1}$ are
-computed thorough the equilibrium equation. Next the nodal velocities
-are corrected in a \textit{corrector} stage,
+computed through the equilibrium equation. Next the nodal velocities
+are corrected in a \textit{corrector} stage:
 \begin{equation}
@@
 Pareto optimal solutions $\beta \in
-(0,\infty)$. Notice that $\beta$ has units of $[L]^{-2}$,
-therefore it can be controlled by adjusting a dimensionless parameter,
-$\gamma=\beta h^2$ \cite{Arroyo2006}, where $h$ is defined as a
-suitable measure of the nodal spacing. With the restrictions exposed in
-\eqref{eq:LME-scheme-pareto-set}, the unique solution of the local
+(0,\infty)$.\MMP{Notice that $\beta$ has units of $[L]^{-2}$,
+therefore it can be controlled by adjusting a dimensionless
+parameter\footnote{To avoid confusion with the $\gamma$ parameter of
+  the \acrshort{npc}, the dimensionless parameter defined in Arroyo \&
+  Ortiz \cite{Arroyo2006} as $\gamma$ will be represent by
+  $\widehat{\gamma}$ to preserve as much as possible the original notation.},
+$\widehat{\gamma}=\beta h^2$}, where $h$ is defined as a
+suitable measure of the nodal spacing. With the restrictions of the
+Pareto set, the unique solution of the local
 \textit{max-ent} problem \acrshort{lme}$_\beta$ is,
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Conclusions}
 \label{sec:4}
+Based on the EigenMPM approach to fracture proposed by Zhang {\it et al.}
+\cite{Zhang_EE_2020}, we have proposed two addition improvements which
+solves the shortcomings presented in the original concept. First by
+bring to the \acrshort{mpm} framework the concept of eigensoftening,
+which allow to consider gradual failure process of each material
+point. This concept can be compared with a cohesive law in the context
+of cohesive fracture. Furthermore, more elaborated damage curves can
+be designed to describe the failure process in more sophisticated
+materials. In this direction, an interesting future improvement of the
+algorithm would be the ability to simulate of crack patterns in
+composite material such carbon fiber. This leads a challenging
+research topic. Secondly, \acrshort{lme} is employed to remove from
+the solution those wiggles due to inaccuracies in the stress
+integration. This interpolation technique could help to improve
+results in fracture propagation by adapting it through the
+deformation gradient. \textit{A priori} this will enhance the already
+impressive localisation properties of eigensoftening and eigenerosion
+algorithms.
 
@@
 \end{document}
-\message{ !name(2020_EFM_MPM_Eigensoftening.tex) !offset(-1019) }
+\message{ !name(2020_EFM_MPM_Eigensoftening.tex) !offset(-1131) }

### 2020-05-26 2020_EFM_MPM_Eigensoftening.tex

@@
 }
+\begin{itemize}
+\item 
+\end{itemize}
 
@@
 method where moving material points, henceforth in this research,
-particles \MMP{($\square_p$)} will carry on all the physical information of the local state ($\sigma_p,
-\varepsilon_p$) and a set of fixed background nodes \MMP{($\square_I$)} will
+particles ($\square_p$) will carry on all the physical information of the local state ($\sigma_p,
+\varepsilon_p$) and a set of fixed background nodes ($\square_I$) will
 be introduced to compute the balance of momentum equation. Since the
@@
 an explicit predictor-corrector time integration scheme is adopted. The
-purposes of this choice is motivated due to its proved robustness and
-stability for dynamic computations. \MMP{In the first stage, the nodal
-velocity predictor $ \vec{\tilde{v}}_I^{k+1}$ is computed thorough
-nodal velocities $\vec{v}_I$ and accelerations $\vec{a}_I$ evaluated
-in the $k$ time step},
+purpose of this choice is motivated due to its proved robustness and
+stability for dynamic computations. In the first stage, the nodal
+velocity predictor $ \vec{\tilde{v}}_I^{k+1}$ is computed through
+nodal velocities $\vec{v}_I$ and accelerations $\vec{a}_I$ and evaluated
+in the $k$ time step,
 \begin{equation}
@@
 \end{equation}
-\MMP{Where \gls{gamma-npc} is an user-defined parameter (typically adopted as
+Where \gls{gamma-npc} is an user-defined parameter (typically adopted as
 0.5), $\tens{m}_I$ represents the lumped mass matrix, and $N_{Ip}^{k}$ is
 the nodal contribution of the shape function evaluated in the particle
-coordinates $\vec{x}_p^k$.} This way of computing the nodal predictor is numerically stable
+coordinates $\vec{x}_p^k$. This way of computing the nodal predictor is numerically stable
 as well as minimises the computational effort. Once nodal velocities are
@@
 Pareto optimal solutions $\beta \in
-(0,\infty)$.\MMP{Notice that $\beta$ has units of $[L]^{-2}$,
+(0,\infty)$. Notice that $\beta$ has units of $[L]^{-2}$,
 therefore it can be controlled by adjusting a dimensionless
@@
   \gls{gamma-lme} to preserve as much as possible the original notation.},
-$\widehat{\gamma}=\beta h^2$}, where $h$ is defined as a
+$\widehat{\gamma}=\beta h^2$, where $h$ is defined as a
 suitable measure of the nodal spacing. With the restrictions of the
@@
 An additional remark concerning the support of the interpolation
-function is that in practice the value of $N_I$ decay exponentially following $\exp(-\beta \vec{r}
-)$. In this sense
-a good practice is to truncate it under a tolerance, 10$^{-6}$ would ensure a reasonable
+function is that, in practice, the value of $N_I$ decay exponentially following $\exp(-\beta \vec{r}
+)$. In this sense,
+a good practice is to truncate it under a tolerance  (typically around 10$^{-6}$) that would ensure a reasonable
 range of neighbours, see \cite{Arroyo2006} for details. This tolerance
@@
 eigenerosion algorithm significantly overestimates the tensile  
-stress and the strain peaks, while it captures the forces and crack
-patterns accurately. On the other hand eigensoftening algorithm agree
+stress and the strain peaks, meanwhile eigensoftening captures the forces and crack
+patterns accurately. On the other hand, eigensoftening algorithm agrees
 very well with experimental results in all the aspects. Furthermore,
-this algorithm has proof its accuracy for complex fracture
-patters such the present in fiber reinforces concrete (FRC),
+the accuracy of this algorithm has been proven for complex fracture
+patterns such as the ones obtained with fiber reinforces concrete (FRC),
 \cite{Navas_2018_ES}.\\
@@
   B_{\epsilon}(x_p^{k+1})} m_q W_q^{k+1}\\
+  \label{eq:mass-EE}
 &m_p^{k+1} =  \sum_{x_q^{k+1} \in
@@
 where $B_{\epsilon}(x_p^{k+1})$ is a $^n$dimensional sphere of radius $\epsilon$
-centered at $x_p^{k+1}$. The particles which lies under this sphere are
-known as the $\epsilon$-neighborhood of the material point, see
-\cite{Pandolfi_2012}, this concept is conveniently is sketched in
+centered at $x_p^{k+1}$. The particles which lie under this sphere are
+known as the $\epsilon$-neighborhood of the material point (see
+\cite{Pandolfi_2012}). This concept is conveniently sketched in
 Figure \ref{fig:Failed-particles}.
@@
 %%%%%%%%%%%
-Other parameters are, the mass of the neighborhood $m_p^{k+1}$, the
-current free-energy density per unit mass  $W_q^{k+1}$ and finally a
-normalizing constant $C_{\epsilon}$. 
-The failure criterion consist in to consider the material point fails
-when $G_p^{k+1}$ surpasses a critical energy release rate that
+Other parameters are the mass of the neighborhood $m_p^{k+1}$, the
+current free-energy density per unit mass  $W_q^{k+1}$ and the
+normalizing constant $C_{\epsilon}$, \PNA{which also defines the $\epsilon$-neighborhood size, being $\epsilon = C_\epsilon h$.}
+
+The failure criterion consist of considering that a material point is failed
+when $G_p^{k+1}$ surpasses the critical energy release rate that
 measures the material-specific energy, $G_F$. The convergence of this
 approach has been analyzed by Schmidt {\it et al.}
-(2009)\cite{Schmidt_2009}, who proofed that it converges to the Griffith
-fracture when discretization size tends to zero. It is necessary to
-point out that when a material point overpass the critical energy, its
+(2009)\cite{Schmidt_2009}, who proved that $G_F$ converges to the Griffith
+fracture when the discretization size tends to zero. It is necessary to
+point out that, when a material point overpass the critical energy, its
 contribution to the internal forces vector is set to zero, but its
@@
 aforementioned authors proposed the concept of eigensoftening to take
-in to account the gradual failure in quasi-brittle materials. The idea
+into account the gradual failure in quasi-brittle materials. The idea
 behind this concept is inspired in the cohesive fracture. This gradual
@@
 the static fracture energy per unit of area, $G_F$. Notice how a
-cohesive crack appears when the maximum tensile strength, $f_t$ is
-reached. Once the opening displacement $w$ reach the value of the
-critical crack displacement $w_c$, a stress-free crack is
-attained. For intermediate values, $w_n$, a damage value between zero
+cohesive crack appears when the maximum tensile strength, $f_t$, is
+reached. Once the crack, $w_n$, reaches the value of the
+critical crack opening, $w_c$, a stress-free crack is
+attained. For intermediate values a damage value between zero
 and one represents the extension to which the material has failed.
@@
   \frac{1}{m_p} \sum_{x_q^{k+1} \in
-  B_{\epsilon}(x_p^{k+1})} m_q \tens{\sigma}_{q,I} \delta \tens{\epsilon}_q,
+  B_{\epsilon}(x_p^{k+1})} m_q \tens{\sigma}_{q,I} \delta \tens{\varepsilon}_q,
 \end{equation}
 where $\tens{\sigma}_{q,I}$ is the maximum principal stress of each
-material point in the $\epsilon$-neighborhood. In this point in
-introduced an effective strain $\varepsilon_q$, such the variation of
-the local strain energy can be obtained as $\delta W_q = \sigma_{q,1}
-\delta\varepsilon_q$. Now with the assumption that the effective
+material point in the $\epsilon$-neighborhood. At this point, an \textit{effective} strain $\varepsilon_q$ is introduced in order to obtain the variation of
+the local strain energy as $\delta W_q = \sigma_{q,1}
+\delta\varepsilon_q$. Now, with the assumption that the effective
 strain of each material point at every time step is constant in the
@@
 \end{equation}
-Consequently it is possible to define an equivalent critical stress at the
-material point $\vec{x}_p^{k+1}$as
+Consequently, it is possible to define an equivalent critical stress at the
+material point $\vec{x}_p^{k+1}$ as
 \begin{equation}
@@
 \end{equation}
-where $m_p$ is the total mass of the $\epsilon$-neighborhood
-\begin{equation}
-  \label{eq:averaged-mass}
-  m_p = \sum_{x_q^{k+1} \in B_{\epsilon}(x_p^{k+1})} m_q.
-\end{equation}
+where $m_p$ is the total mass of the $\epsilon$-neighborhood, defined similarly than in the eigenerosion methodology (Eq.~\eqref{eq:mass-EE}).
+%\begin{equation}
+%  \label{eq:averaged-mass}
+%  m_p = \sum_{x_q^{k+1} \in B_{\epsilon}(x_p^{k+1})} m_q.
+%\end{equation}
 This definition of the equivalent critical stress leads to a
@@
 activated once $\tens{\sigma}_{\epsilon,p}^{k+1}$ surpasses the
-tensile strength, $f_t$. This consists in a reduction of the internal
+tensile strength, $f_t$. This consists of a reduction of the internal
 forces as,
@@
 where $\chi_p$ and $\Omega_p$ are respectively the damage or softening
-variable and the volume for each material point $p$. $\chi_p$ takes
+variable and the volume for each material point $p$. \PNA{$\chi_p$ is any function, taking
 values between zero (an intact material) and one (completely failed
-material points). For the case of a linear softening such the sketched in the Figure \ref{fig:Damage-ft-wc}, $\chi_p$ is computed as,
+material points), that relates the crack opening and the residual strength.
+To calculate it, typical shapes of cohesive laws such as linear, bilinear or exponential, may be employed.} For the case of a linear softening such the sketched one in the Figure \ref{fig:Damage-ft-wc}, $\chi_p$ is computed as,
  \begin{equation}
@@
  \end{equation}
-In analogy to the band crack model presented by
+Analogous to the crack band model presented by
 Bazant~\cite{Bazant83}, Navas {\it et al.} \cite{Navas_2018_ES}
-\cite{Navas_2017_ES} introduced a band width parameter $h_{\epsilon}$.
-Concerning this parameter, a typical value of it is between two and
-four times the maximum size of the aggregates, in the case of
+\cite{Navas_2017_ES} introduced a band width parameter $h_{\epsilon}$ in order to relate the crack opening with the strain.
+Concerning this parameter, a typical value between two and
+four times the maximum size of the aggregates is adopted in the case of
 concrete as brittle material. The effective fracture strain
 $\varepsilon_{\epsilon,f}$ is defined as the difference between the strain at crack initialization,
-$\varepsilon_1(\vec{x}_p^{0})$, and the current strain, $\varepsilon_1(\vec{x}_p^{k+1})$, for material point $p$. Also,
+$\varepsilon_1(\vec{x}_p^{0})$, and the current strain, $\varepsilon_1(\vec{x}_p^{k+1})$, for a material point $p$. Also,
 $\varepsilon_{\epsilon,f}$ can be represented as the current crack
@@
 \end{equation}
-The function of $\chi$ presented in \eqref{eq:damage-variable-chi-III}
+The function of $\chi$ presented in \eqref{eq:damage-variable-chi-II}
 represents a linear softening behaviour. For a general case, the
@@
 
-\MMP{
 \subsection{$\epsilon$-neighborhood reconstruction : A node-linked method}
 \label{sec:epsil-neighb-reconst}
-Since this operation could be extremely demanding, optimal
+\PNA{The construction of the $\epsilon$-neighborhood is a major issue of the proposed methodology.} Since this operation could be extremely demanding, optimal
 numerical implementation should be employed. In opposite with the Cell-linked
@@
 algorithms like Crossing Number \cite{Shimrat_1962} or Correct
-Even-Odd \cite{Galetzka_et_al_2017}. To avoid these error prone
-techniques, the method here proposed exploits the meshfree benefits of
+Even-Odd \cite{Galetzka_et_al_2017}, \PNA{the proposed methodology adopted herein is linked to the shape function neighbourhood. In order to avoid the aforementioned error} prone
+techniques, we endeavour to exploit the meshfree benefits of
 the \acrshort{lme} approximants to introduce a node-linked method. Due
@@
 interpretation of the \acrshort{fem} element typically adopted in
-\acrshort{mpm} simulations is not required anymore, instead a linked
+\acrshort{mpm} simulations is not required anymore. A linked
 list of tributary nodes is reconstructed with the closest node as
-starting point at each time step. Therefore, each node is assigned an
+starting point at each time step instead. Therefore, each node is assigned to an
 unique linked-list of those particles which are closest to it. This
@@
 algorithm can be found in \ref{sec:node-linked-method-1}.
-}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2020-05-26 _region_.tex
Cambios figuras y algoritmos

@@
 therefore it can be controlled by adjusting a dimensionless
-parameter\footnote{To avoid confusion with the $\gamma$ parameter of
+parameter\footnote{To avoid confusion with the \gls{gamma-npc} parameter of
   the \acrshort{npc}, the dimensionless parameter defined in Arroyo \&
   Ortiz \cite{Arroyo2006} as $\gamma$ will be represent by
-  $\widehat{\gamma}$ to preserve as much as possible the original notation.},
+  \gls{gamma-lme} to preserve as much as possible the original notation.},
 $\widehat{\gamma}=\beta h^2$}, where $h$ is defined as a

### 2020-05-26 _region_.tex
Se me olvidó cambiar una figura...

@@
   \label{alg-eigens}
-  \caption{Eigensoftening algorithm}
 \end{algorithm}
@@
   }
+  \label{alg-node-link}
   \caption{$\epsilon$-neighborhood reconstruction algorithm}
@@
 \end{document}
-\message{ !name(2020_EFM_MPM_Eigensoftening.tex) !offset(-1131) }
+\message{ !name(2020_EFM_MPM_Eigensoftening.tex) !offset(-1135) }

### 2020-05-27 2020_EFM_MPM_Eigensoftening.tex
Cambios figuras y algoritmos
PNA+DM_20_05_27

@@
 \newcommand{\DM}[1]{
-  \textcolor{gree}{{#1}}
+  \textcolor{green}{{#1}}
 }
@@
 warranties the \textit{least width} shape function support. To reach
-to a compromise between two competing objectives, a Pareto set is
+\DM{delete to} a compromise between two competing objectives, a Pareto set is
 defined as,
@@
 of the eigenerosion proposed by Pandolfi \& Ortiz
-(2012)\cite{Pandolfi_2012} for fracture of brittle materials. A
+(2012)\cite{Pandolfi_2012} for fracture of brittle materials. \DM{ XXXX I would modify the following  sentence as "The evaluation of both approaches \cite{Navas_2017_ES} show that the
+eigenerosion algorithm significantly overestimates the tensile  
+stress and the strain peaks, meanwhile eigensoftening captures the forces and crack
+patterns accurately XXXXX}. A
 comparison between both in \cite{Navas_2017_ES} shows that the
@@
 patterns accurately. On the other hand, eigensoftening algorithm agrees
-very well with experimental results in all the aspects. Furthermore,
+very well with experimental results in all the aspects \DM{which aspect?} . Furthermore,
 the accuracy of this algorithm has been proven for complex fracture
@@
 critical crack opening, $w_c$, a stress-free crack is
-attained. For intermediate values a damage value between zero
-and one represents the extension to which the material has failed.
+attained.
+\DM{ see the following sentence: comma missing?
+Clarified--->} For intermediate values a damage value between zero and one represents the extension to which the material has failed.
+\DM{ hasta acá }
 %%%%%%%%%%%
@@
 initialization was adopted. Particularly the maximum principal stress
-theory for brittle fracture was considered by authors
-\cite{Navas_2017_ES}. With that purpose, the variation of the averaged
+theory for brittle fracture was considered  \DM{ delete by the authors}  by authors
+\cite{Navas_2017_ES}. With that purpose \DM{ which purpose?}, the variation of the averaged
 strain energy density in the $\epsilon$-neighborhood of the material point
@@
 \end{equation}
-where $m_p$ is the total mass of the $\epsilon$-neighborhood, defined similarly than in the eigenerosion methodology (Eq.~\eqref{eq:mass-EE}).
+where $m_p$ is the total mass of the $\epsilon$-neighborhood, defined similarly  \DM{ Pondría:  defined similarly TO  the eigenerosion method} than in the eigenerosion methodology (Eq.~\eqref{eq:mass-EE}).
 %\begin{equation}
@@
 %\end{equation}
-This definition of the equivalent critical stress leads to a
+This definition \DM{ dos veces definition en la misma oración, podes poner directamente: The equivalent critical stress leads to a definition of the averaged strain energy ...
+} of the equivalent critical stress leads to a
 definition of the averaged strain energy in terms of the averaged
@@
 $\varepsilon_{\epsilon,f}$ can be represented as the current crack
-opening $w_n$ within the band width, $h_{\epsilon}$. Therefore, 
+opening $w_n$ within the band width, $h_{\epsilon}$. \DM{Check band width $h_{\epsilon}$ subindex or superindex? or both. See eq. 18,19 and 20} Therefore, 
 \begin{equation}
@@
 interpretation of the \acrshort{fem} element typically adopted in
-\acrshort{mpm} simulations is not required anymore. A linked
+\acrshort{mpm} simulations is not required anymore. \DM{Intead, a} linked
 list of tributary nodes is reconstructed with the closest node as
-starting point at each time step instead. Therefore, each node is assigned to an
+starting point at each time step \DM{deleted instead}. Therefore, each node is assigned to an
 unique linked-list of those particles which are closest to it. This
@@
 
-As noticed in \cite{Zhang_EE_2020}, the EigenMPM have two important
-shortcomings. The first is the presence of stress instabilities even
-with \acrshort{gimp} shape functions. To overcome it, \acrshort{lme}
+\DM{The proposed approach to overcome the two main shortcomings of EighenMPM \cite{Zhang_EE_2020} has been evaluated with "two benchmark tests"¿?.
+} \DM{DELETE: As noticed in \cite{Zhang_EE_2020}, the EigenMPM have two important
+shortcomings}. The first one deals with the presence of stress instabilities provoked by the spatial discretization, appearing even
+when the \acrshort{gimp} shape functions are employed. To overcome it, \acrshort{lme}
 approximants are introduced as an
 alternative to the existing interpolation techniques. Its
-impressive performance mitigating spurious stress oscillations
-\cite{Wobbes2020} under the \acrshort{mpm} framework help to enhance
-notoriously the quality of the results as we can see in Section
-\ref{sec:3.1}. Where both interpolation techniques
-are compared by carry out an eigenerosion simulation. The second
-limitation is concerning its inability to simulate properly quasi-brittle
+performance in mitigating spurious stress oscillations under the \acrshort{mpm}~\cite{Wobbes2020,Molinos2020} framework helps to enhance
+notoriously the quality of the results as it is observed in Section
+\ref{sec:3.1}, where both interpolation techniques
+are compared by carrying out an eigenerosion simulation. The second
+limitation is concerned to its inability to simulate properly quasi-brittle
 fracture \cite{Navas_2018_ES}. It can be solved through the
@@
 of it is exposed in Section \ref{sec:3.3}, where experimental results
-of a drop-weight impact test are compared with those produced by
-eigensoftening computations.
+of a drop-weight impact test are compared with experimental ones as well as eigensoftening computations. \PNA{FALTA LO DE BUI}.
 
@@
 
-This problem here presented is devoted to compare how much \acrshort{lme}
-approximants are able to improve the result \textit{versus} standard
-linear interpolation. It consists in a square plate of size $H = 1$ containing
+The aim of the problem presented hereinafter is to assess the capability of the \acrshort{lme}
+approximants to improve the result \textit{versus} the standard linear interpolation. The application consists of a square plate of size $H = 1$ containing
 an initial edge crack of length $0.25 \cdot H$ loaded in a pure mode I
-by displacement control on the outer flanks of the plate, Figure
-\ref{fig:geometry-cracked-panel-mode-I}.
+by displacement control on the outer flanks of the plate (See Figure
+\ref{fig:geometry-cracked-panel-mode-I} for details).
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The constitutive model consider for numerical experiment is a
-linear-elastic Hookean material, where Young's modulus \gls{E} = 1.06, the
+
+\PNA{UNIDADES}
+
+\PNA{NOMBRAR ALGO A LOS CASOS ANALITICOS O DE MICHAEL ORTIZ}
+
+The constitutive model considered in the numerical experiment is a
+linear-elastic Hookean material, whose Young's modulus \gls{E} = 1.06, the
 Poisson's ratio \gls{nu} = 0.333, and critical energy-release rate
-\gls{Gf} = 0.0001. This set of parameters was taken from \cite{Pandolfi_2012}. In
-\acrshort{mpm}, two different discretization are required. In one hand
-a cartesian grid of nodes is consider with a nodal spacing value of
+\gls{Gf} = 0.0001. This set of parameters has been previously employed by Pandolfi~\textit{et al.}~\cite{Pandolfi_2012}. In
+\acrshort{mpm}, two different discretization are required. On the one hand,
+a cartesian grid of nodes is considered with a nodal spacing value of
 0.025. On the other hand, the plate will be modeled with a initial
@@
 Figure \ref{fig:Reactions-cracked-panel-mode-I} clearly shows the
-presence of wiggles in both loading and fracture stages
-in the reaction-displacements curve when linear interpolation
-technique is used. In contrast, \acrshort{lme} simulation does not
-exhibit these spurious oscillations and remains linear. Besides that,
+presence of wiggles in the reaction-displacements curve, in both loading and post-failure stages,
+when linear interpolation technique is used. In contrast, \acrshort{lme} simulation does not
+exhibit these spurious oscillations and remains linear until the failure. About the strength,
 linear interpolation produces stiffer results than
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-On the other hand, Figure \ref{fig:Stress-cracked-panel-mode-I}
+
+Additionally, Figure \ref{fig:Stress-cracked-panel-mode-I}
 exhibits more clearly the difference between linear interpolation and
@@
 when particles crosses the boundary of the element in the linear
-case. Although this behavior does not affect significantly to the peak
-stress value in a hookean material \cite{Zhang_EE_2020}, if
-hyperelastic materials are consider for future simulations,
-inaccuracies in the stress field could affect dramatically to the
-final result. On the other hand \acrshort{lme} produces soft stress
-field evolution even after breaking.
+case, which is observed at 60 seconds.
+\PNA{Although, apparently, the differences in the obtained peaks are not extremely significant, it can be owing to the aforementioned hookean material employed~\cite{Zhang_EE_2020}.
+When more sophisticated constitutive models will be employed, severe
+%if hyperelastic materials are consider for future simulations,
+inaccuracies may appear in the stress field that could affect dramatically to the
+final result. Focusing on the post failure behavior, it can be seen how \acrshort{lme} produces soft stress
+field evolution even after breaking.}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 An important consideration regarding the presence of oscillations once
-both parts of the panel are separated, Figure
+both parts of the panel are separated is observed in Figure
 \ref{fig:Reactions-cracked-panel-mode-I}. These phenomena should not be
 attributed to the eigenerosion algorithm since the fracture process is
-over. They are due to the dynamic nature of the solver.
+over. They are due to the dynamic nature of the solver: \PNA{once the energy is release dinamically by the crack, the waves propagate along the domain.}
 
@@
 \label{sec:3.2}
-
-Once the accuracy of the \acrshort{lme} approximants have been proven
-in Section \ref{sec:3.1}, henceforth will be adopted without comparing
-with linear interpolation. Therefore this section is devoted to proof
-the accuracy of the eigensoftening algorithm to simulate the behavior
-of quasi-brittle materials under dynamic loading. An example of this
-load case is the three-point bending test on a notched beam is
-conducted under impact loading. This kinds of experiments are
-challenging to reproduce numerically with an explicit solver since
-fracture occurs in a period of milliseconds and high strength
-materials are involved. Accordingly, really small time steps are
-required to achieve a simulation numerically stable. Additionally,
-this kind of simulations traditionally require the implementation of
-contact algorithm to reproduce the hammer impact in the beam. In the
-\acrshort{mpm}, the implementation of this feature can be bypassed to
-obtain preliminary results. Nevertheless, this kind of algorithm could
-be implemented to get ever more accurate solutions. Although this is
-out of the scope of this document, future research of authors will overcome this
-limitation.\\
-
-As in the study of Zhang {\it et al.} \cite{Zhang_2009,Zhang_2010a},
-an impact hammer of 120.6 kg was employed to drop it at an impact
-speed of 881 mm/s. The beam dimensions where 100 mm x 100 mm (B x D)
+\PNA{This section is devoted to proof
+the accuracy of the eigensoftening algorithm within the \acrshort{mpm} framework when the behavior
+of quasi-brittle materials under dynamic loading is simulated. One of the most interesting examples of this
+loading case is the three-point bending test on a concrete notched beam when it is conducted under impact loading.
+Indeed, this experimental test is appropriate to be reproduced numerically with the explicit solver proposed in this paper since
+fracture occurs in a period of milliseconds and waves propagate fast along the high strength
+materials involved in the aforementioned test.} Accordingly, small time steps are
+required to achieve a numerically stable simulation.\\
+
+An interesting case of this experimental test was reported by Zhang {\it et al.} \cite{Zhang_2009,Zhang_2010a}. As in the aforementioned study,
+an impact hammer of 120.6 kg has been employed in the proposed simulations to drop it at an impact
+speed of 881 mm/s. The beam dimensions were 100 mm x 100 mm (B x D)
 in cross section, and 420 mm in total lenght (L). The initial
 notch-depth ratio was approximately 0.5, and the span, S, was fixed at
-300 mm during the tests, see Figure
-\ref{fig:geometry-drop-weight-impact-test}.
+300 mm during the tests (see Figure
+\ref{fig:geometry-drop-weight-impact-test}).
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 The material adopted for the simulation was characterised by Navas
-{\it et al.}~\cite{Navas_2017_ES}, and the material properties, such
+{\it et al.}~\cite{Navas_2017_ES}, being the material properties, such
 as the material density, \gls{rho}, the compressive strenght, \gls{fc},
 the tensile strenght \gls{ft}, the specific fracture energy, \gls{Gf},
-and the elastic modulus \gls{E} are given in table \ref{tab:concrete-properties}.\\
+and the elastic modulus \gls{E}, provided in table \ref{tab:concrete-properties}.\\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 For the present research, a 2D setting of the experiment has been
 adopted. Both the hammer and the concrete beam are explicitly
-represented. Several levels of discretization were required to assess
+represented in order to properly capture the impact. Several levels of discretization were required to assess
 the objectiveness of the obtained results. The results here exposed
@@
 the impact surface of the hammer. For this simulation, \gls{gamma-lme} was
-fixed to 6.\\
-
-First the reaction and impact forces are validated against their
+fixed to 6. Once the accuracy of the \acrshort{lme} approximants have been proven
+in Section \ref{sec:3.1}, this discretization has been adopted.
+%without comparing
+%with linear interpolation. Therefore \\
+
+First, the reaction and impact forces are validated against their
 experimental counterparts. Since the impact forces applied by the
@@
 experimental. In this case, this is a consequence of over-rigidity
-in the supports. Therefore, this results can be improved in future research
-by a suitable contact algorithm.\\
-
-And finally horizontal stress distributions and crack propagation are
-extracted, see Figure \ref{fig:Stress-vs-damage-impact-test}. Stress
+in the supports.
+\PNA{Although the traditional \acrshort{mpm} implementation allows collision of two bodies, inaccurate energy conservation is obtained without the implementation of a conservative contact algorithm to reproduce the hammer impact in the beam.
+%In the
+%%\acrshort{mpm}, the implementation of this feature can be bypassed to obtain preliminary results. Nevertheless, this kind of algorithm could
+%be implemented to get ever more accurate solutions. 
+Despite the observed discrepancies, this is
+out of the scope of this document, although future research of authors will overcome this
+limitation. Similarly, results of support forces will be more realistic when modelled by a suitable contact algorithm instead of avoiding any vertical displacement}.\\
+
+Finally, longitudinal stress distribution and crack propagation are
+depicted in Figure \ref{fig:Stress-vs-damage-impact-test}. Stress
 evolution agrees with the results obtained by \cite{Navas_2017_ES}
 under the \acrshort{otm} framework. Two additional considerations about
-this results are concerning the interpolation technique. In one hand,
+this results are concerning the interpolation technique. On the one hand,
 in the opposite to the \acrshort{ugimp} shape function, \acrshort{lme}
@@
 of simulations since the majority of the computational effort is
-clearly localised in a tiny region of the domain. And in the other
-hand there is the possibility to reduce the shape function support to avoid
+clearly localised in a tiny region of the domain. On the other
+hand, there is the possibility to reduce the shape function support to avoid
 a material point in one side of the crack is affected by those in the
@@
 \label{sec:4}
-Based on the EigenMPM approach to fracture proposed by Zhang {\it et al.}
-\cite{Zhang_EE_2020}, we have proposed two addition improvements which
-solves the shortcomings presented in the original concept. First by
-bring to the \acrshort{mpm} framework the concept of eigensoftening,
-which allow to consider gradual failure process of each material
-point. This concept can be compared with a cohesive law in the context
-of cohesive fracture. Furthermore, more elaborated damage curves can
-be designed to describe the failure process in more sophisticated
+\PNA{Based on the EigenMPM approach to fracture proposed by Zhang {\it et al.}
+\cite{Zhang_EE_2020}, two additional improvements have been proposed in the present research in order to 
+solve the shortcomings of the original concept that Zhang {\it et al.} pointed out in the aforementioned paper \cite{Zhang_EE_2020}.
+
+Firstly, by
+introducing the concept of eigensoftening to the \acrshort{mpm} framework,
+which allows to consider gradual failure process of each material point. This concept is analogous the softening law which is traditionally employed in the context
+of cohesive fracture in \acrfull{fem}.
+Furthermore, this failure criterion admits the design of more elaborated damage curves, which can be employed in order to describe the failure process in more sophisticated
 materials. In this direction, an interesting future improvement of the
 algorithm would be the ability to simulate of crack patterns in
-composite material such carbon fiber. This leads a challenging
-research topic. Secondly, \acrshort{lme} is employed to remove from
-the solution those wiggles due to inaccuracies in the stress
-integration. This interpolation technique could help to improve
-results in fracture propagation by adapting it through the
-deformation gradient. \textit{A priori} this will enhance the already
-impressive localisation properties of eigensoftening and eigenerosion
-algorithms.
+composite material such as steel or carbon fiber reinforced concretes\cite{Ruiz2019}.
+Interesting researches have been done on this field~\cite{Navas_2018_ES}.
+In addition, the eigensoftening approach can be extrapolated to rock fracture in the same manner the eigenerosion was~\cite{Wang2017}, taking into account that the volumetric stiffness remains in order to support bulk loads.
+
+Secondly, \acrshort{lme} is employed to remove from
+the solution those wiggles provoked by inaccuracies in the stress integration.
+This spatial discretization was previously employed within the \acrshort{mpm} framework with excellent results under the elastic regime~\cite{Wobbes2020,Molinos2020}.
+The traditional time scheme of the \acrshort{mpm} has been improved with a Newmark Predictor Corrector scheme as well.
+In this research, the aforementioned techniques have helped to improve the
+results in fracture propagation through the eigensoftening and eigenerosion algorithms. Further improvement may be reached by adapting \acrshort{lme} through the
+deformation gradient\MMP{CITA AQUI LOS QUE LO HACEN}. \textit{A priori} this would enhance the localisation properties of the proposed algorithms in more sophisticated domains.
+
+Finally, for better capturing the measurement of forces made in the laboratory, more realistic contact tools have to be developed.
+Navas~\textif{et al.} demonstrate the importance of the stiffness of the support in order to obtain accurate results of the reaction forces.
+Interesting contact algorithms within the \acrshort{mpm} methodology are available in the literature \MMP{CITA ALGUNO Y SI SON CONSERVATIVOS EN ENERGIAS, MEJOR}.
+}
 

### 2020-05-27 2020_EFM_MPM_Eigensoftening.tex
Correcciones sobre PNA+DM 20-5-2020
Faltan cosas por modificar sobre lo corregido

@@
 of the eigenerosion proposed by Pandolfi \& Ortiz
-(2012)\cite{Pandolfi_2012} for fracture of brittle materials. \DM{ XXXX I would modify the following  sentence as "The evaluation of both approaches \cite{Navas_2017_ES} show that the
-eigenerosion algorithm significantly overestimates the tensile  
-stress and the strain peaks, meanwhile eigensoftening captures the forces and crack
-patterns accurately XXXXX}. A
-comparison between both in \cite{Navas_2017_ES} shows that the
-eigenerosion algorithm significantly overestimates the tensile  
-stress and the strain peaks, meanwhile eigensoftening captures the forces and crack
-patterns accurately. On the other hand, eigensoftening algorithm agrees
-very well with experimental results in all the aspects \DM{which aspect?} . Furthermore,
+(2012)\cite{Pandolfi_2012} for fracture of brittle materials.\DM{The evaluation of both approaches \cite{Navas_2017_ES} show that the eigenerosion algorithm significantly overestimates the tensile stress and the strain peaks, meanwhile eigensoftening captures the forces and crack
+patterns accurately}. On the other hand, eigensoftening algorithm agrees
+very well with experimental results in all the aspects \DM{which aspect?}. Furthermore,
 the accuracy of this algorithm has been proven for complex fracture
@@
 $\varepsilon_{\epsilon,f}$ can be represented as the current crack
-opening $w_n$ within the band width, $h_{\epsilon}$. \DM{Check band width $h_{\epsilon}$ subindex or superindex? or both. See eq. 18,19 and 20} Therefore, 
+opening $w_n$ within the band width $h_{\epsilon}$. Therefore, 
 \begin{equation}
@@
   \label{eq:damage-variable-chi-II}
-\chi = \frac{\varepsilon_{\epsilon,f}\ h^{\epsilon}}{w_c}.  
+\chi = \frac{\varepsilon_{\epsilon,f}\ h_{\epsilon}}{w_c}.  
 \end{equation}
@@
   \label{eq:damage-variable-chi-III}
-  \chi = \chi(\varepsilon_{\epsilon,f}, h^{\epsilon}, f_t, w_c, G_f)
+  \chi = \chi(\varepsilon_{\epsilon,f}, h_{\epsilon}, f_t, w_c, G_f)
 \end{equation}
@@
 interpretation of the \acrshort{fem} element typically adopted in
-\acrshort{mpm} simulations is not required anymore. \DM{Intead, a} linked
+\acrshort{mpm} simulations is not required anymore.\DM{Intead, a}linked
 list of tributary nodes is reconstructed with the closest node as
-starting point at each time step \DM{deleted instead}. Therefore, each node is assigned to an
+starting point at each time step. Therefore, each node is assigned to an
 unique linked-list of those particles which are closest to it. This
@@
 
-\DM{The proposed approach to overcome the two main shortcomings of EighenMPM \cite{Zhang_EE_2020} has been evaluated with "two benchmark tests"¿?.
-} \DM{DELETE: As noticed in \cite{Zhang_EE_2020}, the EigenMPM have two important
-shortcomings}. The first one deals with the presence of stress instabilities provoked by the spatial discretization, appearing even
+\DM{The proposed approach to overcome the two main shortcomings of EighenMPM \cite{Zhang_EE_2020} has been evaluated with ``two benchmark tests''.}The first one deals with the presence of stress instabilities provoked by the spatial discretization, appearing even
 when the \acrshort{gimp} shape functions are employed. To overcome it, \acrshort{lme}
@@
 fracture \cite{Navas_2018_ES}. It can be solved through the
-eigensoftening algorithm described in Section \ref{sec:2.3}. A proof
-of it is exposed in Section \ref{sec:3.3}, where experimental results
-of a drop-weight impact test are compared with experimental ones as well as eigensoftening computations. \PNA{FALTA LO DE BUI}.
+eigensoftening algorithm described in Section \ref{sec:2.3}.\MMP{A proof
+of it is exposed in Sections \ref{sec:3.2} \ref{sec:3.3}, where experimental results
+are compared with experimental ones as well as eigensoftening
+computations. In the first case comparing with a semicircular bending
+test and in the second case with a drop-weight impact test.}
 
@@
 \label{sec:3.1}
-
-The aim of the problem presented hereinafter is to assess the capability of the \acrshort{lme}
-approximants to improve the result \textit{versus} the standard linear interpolation. The application consists of a square plate of size $H = 1$ containing
-an initial edge crack of length $0.25 \cdot H$ loaded in a pure mode I
-by displacement control on the outer flanks of the plate (See Figure
+The aim of the problem presented hereinafter is to assess the
+capability of the \acrshort{lme} approximants to improve the result
+\textit{versus} the standard linear interpolation. The application
+consists of a square plate of size $H = 1$ containing an initial edge
+crack of length $0.25 \cdot H$ loaded in a pure mode I by displacement
+control on the outer flanks of the plate (See Figure
 \ref{fig:geometry-cracked-panel-mode-I} for details). 
@@
 attributed to the eigenerosion algorithm since the fracture process is
-over. They are due to the dynamic nature of the solver: \PNA{once the energy is release dinamically by the crack, the waves propagate along the domain.}
+over. They are due to the dynamic nature of the solver: \PNA{once the
+  energy is release dinamically by the crack, the waves propagate
+  along the domain.}
+
+\subsection{Semicircular bending test}
+\label{sec:3.2}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{table}
+  \centering
+  \begin{tabular}[]{c c c c c c c}
+    \hline
+      &   $\rho$   & $\text{f}_c$ & $\text{f}_t$ & $G_F$ &   E   & $\text{d}_{max}$ \\
+      & (kg/m$^3$) &     (MPa)    &     (MPa)    & (N/m) & (GPa) & (mm) \\
+    \hline
+Value &    1540    &     102.7    &      5.4     &  141  &   31  &  12 \\
+    \hline
+  \end{tabular}
+  \caption[Mechanical properties of thje concrete]{Material properties of Johnstone.}
+  \label{tab:Johnstone-properties}
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+  \centering
+  \includegraphics[width=0.6\textwidth]{./Figure-Semicircular-bending-test}
+  \caption{Geometry and boundary condition of the semicircular bending
+    test.}
+  \label{fig:geometry-Semicircular-bending-test}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\cite{Wang_2020}
 
 \subsection{Drop-weight impact test}
-\label{sec:3.2}
+\label{sec:3.3}
 \PNA{This section is devoted to proof
@@
 results in fracture propagation through the eigensoftening and eigenerosion algorithms. Further improvement may be reached by adapting \acrshort{lme} through the
-deformation gradient\MMP{CITA AQUI LOS QUE LO HACEN}. \textit{A priori} this would enhance the localisation properties of the proposed algorithms in more sophisticated domains.
-
-Finally, for better capturing the measurement of forces made in the laboratory, more realistic contact tools have to be developed.
-Navas~\textif{et al.} demonstrate the importance of the stiffness of the support in order to obtain accurate results of the reaction forces.
-Interesting contact algorithms within the \acrshort{mpm} methodology are available in the literature \MMP{CITA ALGUNO Y SI SON CONSERVATIVOS EN ENERGIAS, MEJOR}.
-}
+deformation gradient \cite{Kochmann2019}. \textit{A priori} this would enhance the localisation properties of the proposed algorithms in more sophisticated domains.
+
+Finally, for better capturing the measurement of forces made in the
+laboratory, more realistic contact tools have to be
+developed. Navas~\textif{et al.} demonstrate the importance of the
+stiffness of the support in order to obtain accurate results of the
+reaction forces. Interesting contact algorithms within the
+\acrshort{mpm} methodology are available in the literature
+\cite{Bardenhagen_Contact_2001,XZhang_Contact_2011}}
 
@@
 \end{document}
+
+% The second application to be considered is a series of semicircular
+% bending tests on Johnstone, which have been carried out by Lim et al.95 The aim of this example is to examine its predictive capability of the SPH model under a wide range
+% of mixed-mode loading conditions. The geometry and boundary conditions of the test in the experiment are shown in
+% Figure 9A. Similar with 3-point bending test, the semicircular specimens with a radius of 47.5 mm and a thickness of
+% 20 mm are supported by two rollers at a span of 47.5 mm and loaded by another roller on its mid-span. Notches with a
+% length of 16.6 mm are created with different notch angles varying from 0 to 60 with respect to the vertical axis to
+% investigate the influences of the notch angles on the peak load (P) and the fracture toughness (KI,KII), which are calcu-
+% lated as follows:
+
+% where KI and KII are respectively mode I and mode II fracture toughness; r is the specimen radius; t is the specimen
+% thickness; a is the notch length; YI and YII are mode I and mode II normalised stress intensity factor. As the values of YI
+% and YII can be obtained from the data by Lim at al.6 KI and KII can be calculated based on the above equation once the
+% peak load (P) is known. The material properties of Johnstone are listed in Table 1. The friction angle and dilation angle
+% are respectively taken as 33 and 4  for average quality rock masses in Hoek and Brown96 for the following examples.
+% Figure 9 shows the corresponding SPH configuration of the semicircular bending test with a notch angle of 30 . In
+% the tests, a particle discretisation of 0.95 mm is used, resulting in a total number of 3995 SPH particles for generating
+% the specimen. To create accurate notch angles using reasonable particle numbers, the initial SPH arrangement in this
+% test is different from the traditional one such as the 3-point bending test in Section 5.1. The initial location of each SPH
+% particle in semicircular bending tests is related to the notch angle as shown in Figure 9B. Similar to the 3-point bending
+% tests, three layers of boundary particles are generated for simulating the point loading in the experiments. The velocities
+% of the top boundary particles are vx = 0,vy = − 2 mm/s, whereas the velocities of the bottom boundary particles are
+% as vy = 0. As Johnstone rocks are classified as soft rocks with a relatively small elastic Young's modulus, both artificial
+% viscosity and artificial stress are used in this test to stabilise the numerical solutions. The ramp loading is also applied
+% to alleviate the dynamic effect due to the sudden loading. The stresses of boundary particles are updated in the same
+% way as that in the 3-point bending test. The stresses of real particles near the loading particles are recorded during the
+% simulation process, from which the peak load and fracture toughness can be obtained for the comparison with the
+% experimental data.
+% Figure 10 illustrates the progressive development of fracture and the horizontal velocity profile at the failure stage
+% for the semicircular specimen with the rotational angle of 30 . As seen in Figure 10A, some particles near the tip of the
+% notch are first damaged, showing that the fracture is initiated at the location of the notch tip. Then, the fracture propa-
+% gates towards the loading point (Figure 10B–D), and eventually, a vertical curvilinear fracture pattern is formed in the
+% middle of the sample (Figure 10E). The horizontal velocity profile corresponding to Figure 10E is also plotted in
+% Figure 10F. It can be seen that the particles on the left side of the fracture move to the left whereas the particles on the
+% other side move to the right direction; thus, the sample is split into two halves at the end. In this approach, SPH particle
+% itself could not be cracked visually; however, each damaged SPH particle possesses a FPZ, and the material behaviour
+% within the FPZ will contribute to the decrease in the overall stress state of the SPH particle, thereby resulting in the sep-
+% aration between two damaged SPH particles. The same test without using the artificial stress is also plotted in
+% Figure 11. The result remains stable when the fracture is initiated (Figure 11A) but becomes unstable during the post-
+% failure process (Figure 11B,C). Unrealistic fracture and particles clustering are observed in Figure 11B,C, which indi-
+% cates the tensile instability problem is occurred in SPH. By comparing those two results, it can be concluded that the
+
+% tensile instability problem can be completely removed and good numerical stability can be achieved by just adopting
+% this artificial stress term.
+% Figure 12 depicts the comparison of mixed-mode fracture envelope between experiments and SPH simulations for
+% different notch inclination angles α = 0 , 15  , 30  , 45 , 50 and 60 . It shows that the simulation fracture patterns
+% marked as red lines match well with the experimental results shown as black lines. The final fracture pattern is a verti-
+% cal straight line when α = 0 (pure mode I). When α > 0 , the sample is subjected to mixed-mode or pure mode II load-
+% ing, resulting in a curvilinear fracture paths. For all simulation cases, the fractures initiate from the notch tip and then
+% propagate towards upper loading point, while the experiments show that a few fractures tend to initiate behind the
+% notch tip when the notch angle is beyond α =50 . Nevertheless, the simulation results still could successfully predict
+% the overall fracture envelope in experiments and demonstrate the
+% capability of the traditional SPH model for capturing
+
+% the fracture development under various complex loading conditions. In the meanwhile, the comparison of peak load
+% between experiments and simulations for the notch inclination angles varying from 0 to 60 with an internal incre-
+% ment of 5 is plotted in Figure 13A. It is noted here that a notch angle of 54 (instead of 55) is used in the current test
+% as the sample is subjected to pure mode II loading condition when α = 54 .95 The SPH simulation can well capture the
+% increasing trend of the peak load with the increasing notch angles in the experiment. Additionally, Figure 13B com-
+% pares the predictions of fracture toughness in SPH simulation against the experimental results and Lim's theory.95 The
+% simulation results perfectly fall within the experimental data ranges even though the fracture toughness data in the
+% experiments are quite scattered. Nevertheless, the numerical results agree closely with the empirical fracture toughness
+% envelope, which was proposed by Lim et al.95 and represented as a black line Figure 13B. It further confirms that our
+% model could accurately predict the mixed-mode fracture behaviour of rocks in semicircular bending test.

### 2020-05-27 _region_.tex
Correcciones sobre PNA+DM 20-5-2020
Faltan cosas por modificar sobre lo corregido

@@
 
-As noticed in \cite{Zhang_EE_2020}, the EigenMPM have two important
-shortcomings. The first is the presence of stress instabilities even
-with \acrshort{gimp} shape functions. To overcome it, \acrshort{lme}
+\DM{The proposed approach to overcome the two main shortcomings of EighenMPM \cite{Zhang_EE_2020} has been evaluated with "two benchmark tests"¿?.
+} \DM{DELETE: As noticed in \cite{Zhang_EE_2020}, the EigenMPM have two important
+shortcomings}. The first one deals with the presence of stress instabilities provoked by the spatial discretization, appearing even
+when the \acrshort{gimp} shape functions are employed. To overcome it, \acrshort{lme}
 approximants are introduced as an
 alternative to the existing interpolation techniques. Its
-impressive performance mitigating spurious stress oscillations
-\cite{Wobbes2020} under the \acrshort{mpm} framework help to enhance
-notoriously the quality of the results as we can see in Section
-\ref{sec:3.1}. Where both interpolation techniques
-are compared by carry out an eigenerosion simulation. The second
-limitation is concerning its inability to simulate properly quasi-brittle
+performance in mitigating spurious stress oscillations under the \acrshort{mpm}~\cite{Wobbes2020,Molinos2020} framework helps to enhance
+notoriously the quality of the results as it is observed in Section
+\ref{sec:3.1}, where both interpolation techniques
+are compared by carrying out an eigenerosion simulation. The second
+limitation is concerned to its inability to simulate properly quasi-brittle
 fracture \cite{Navas_2018_ES}. It can be solved through the
-eigensoftening algorithm described in Section \ref{sec:2.3}. A proof
-of it is exposed in Section \ref{sec:3.3}, where experimental results
-of a drop-weight impact test are compared with those produced by
-eigensoftening computations.
+eigensoftening algorithm described in Section \ref{sec:2.3}.\MMP{A proof
+of it is exposed in Sections \ref{sec:3.2} \ref{sec:3.3}, where experimental results
+are compared with experimental ones as well as eigensoftening
+computations. In the first case comparing with a semicircular bending
+test and in the second case with a drop-weight impact test.}
 
@@
 \label{sec:3.1}
-
-This problem here presented is devoted to compare how much \acrshort{lme}
-approximants are able to improve the result \textit{versus} standard
-linear interpolation. It consists in a square plate of size $H = 1$ containing
-an initial edge crack of length $0.25 \cdot H$ loaded in a pure mode I
-by displacement control on the outer flanks of the plate, Figure
-\ref{fig:geometry-cracked-panel-mode-I}.
+The aim of the problem presented hereinafter is to assess the
+capability of the \acrshort{lme} approximants to improve the result
+\textit{versus} the standard linear interpolation. The application
+consists of a square plate of size $H = 1$ containing an initial edge
+crack of length $0.25 \cdot H$ loaded in a pure mode I by displacement
+control on the outer flanks of the plate (See Figure
+\ref{fig:geometry-cracked-panel-mode-I} for details). 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 An important consideration regarding the presence of oscillations once
-both parts of the panel are separated, Figure
+both parts of the panel are separated is observed in Figure
 \ref{fig:Reactions-cracked-panel-mode-I}. These phenomena should not be
 attributed to the eigenerosion algorithm since the fracture process is
-over. They are due to the dynamic nature of the solver.
+over. They are due to the dynamic nature of the solver: \PNA{once the
+  energy is release dinamically by the crack, the waves propagate
+  along the domain.}
+
+\subsection{Semicircular bending test}
+\label{sec:3.2}
+
+% The second application to be considered is a series of semicircular
+% bending tests on Johnstone, which have been carried out by Lim et al.95 The aim of this example is to examine its predictive capability of the SPH model under a wide range
+% of mixed-mode loading conditions. The geometry and boundary conditions of the test in the experiment are shown in
+% Figure 9A. Similar with 3-point bending test, the semicircular specimens with a radius of 47.5 mm and a thickness of
+% 20 mm are supported by two rollers at a span of 47.5 mm and loaded by another roller on its mid-span. Notches with a
+% length of 16.6 mm are created with different notch angles varying from 0 to 60 with respect to the vertical axis to
+% investigate the influences of the notch angles on the peak load (P) and the fracture toughness (KI,KII), which are calcu-
+% lated as follows:
+
+% where KI and KII are respectively mode I and mode II fracture toughness; r is the specimen radius; t is the specimen
+% thickness; a is the notch length; YI and YII are mode I and mode II normalised stress intensity factor. As the values of YI
+% and YII can be obtained from the data by Lim at al.6 KI and KII can be calculated based on the above equation once the
+% peak load (P) is known. The material properties of Johnstone are listed in Table 1. The friction angle and dilation angle
+% are respectively taken as 33 and 4  for average quality rock masses in Hoek and Brown96 for the following examples.
+% Figure 9 shows the corresponding SPH configuration of the semicircular bending test with a notch angle of 30 . In
+% the tests, a particle discretisation of 0.95 mm is used, resulting in a total number of 3995 SPH particles for generating
+% the specimen. To create accurate notch angles using reasonable particle numbers, the initial SPH arrangement in this
+% test is different from the traditional one such as the 3-point bending test in Section 5.1. The initial location of each SPH
+% particle in semicircular bending tests is related to the notch angle as shown in Figure 9B. Similar to the 3-point bending
+% tests, three layers of boundary particles are generated for simulating the point loading in the experiments. The velocities
+% of the top boundary particles are vx = 0,vy = − 2 mm/s, whereas the velocities of the bottom boundary particles are
+% as vy = 0. As Johnstone rocks are classified as soft rocks with a relatively small elastic Young's modulus, both artificial
+% viscosity and artificial stress are used in this test to stabilise the numerical solutions. The ramp loading is also applied
+% to alleviate the dynamic effect due to the sudden loading. The stresses of boundary particles are updated in the same
+% way as that in the 3-point bending test. The stresses of real particles near the loading particles are recorded during the
+% simulation process, from which the peak load and fracture toughness can be obtained for the comparison with the
+% experimental data.
+% Figure 10 illustrates the progressive development of fracture and the horizontal velocity profile at the failure stage
+% for the semicircular specimen with the rotational angle of 30 . As seen in Figure 10A, some particles near the tip of the
+% notch are first damaged, showing that the fracture is initiated at the location of the notch tip. Then, the fracture propa-
+% gates towards the loading point (Figure 10B–D), and eventually, a vertical curvilinear fracture pattern is formed in the
+% middle of the sample (Figure 10E). The horizontal velocity profile corresponding to Figure 10E is also plotted in
+% Figure 10F. It can be seen that the particles on the left side of the fracture move to the left whereas the particles on the
+% other side move to the right direction; thus, the sample is split into two halves at the end. In this approach, SPH particle
+% itself could not be cracked visually; however, each damaged SPH particle possesses a FPZ, and the material behaviour
+% within the FPZ will contribute to the decrease in the overall stress state of the SPH particle, thereby resulting in the sep-
+% aration between two damaged SPH particles. The same test without using the artificial stress is also plotted in
+% Figure 11. The result remains stable when the fracture is initiated (Figure 11A) but becomes unstable during the post-
+% failure process (Figure 11B,C). Unrealistic fracture and particles clustering are observed in Figure 11B,C, which indi-
+% cates the tensile instability problem is occurred in SPH. By comparing those two results, it can be concluded that the
+
+% tensile instability problem can be completely removed and good numerical stability can be achieved by just adopting
+% this artificial stress term.
+% Figure 12 depicts the comparison of mixed-mode fracture envelope between experiments and SPH simulations for
+% different notch inclination angles α = 0 , 15  , 30  , 45 , 50 and 60 . It shows that the simulation fracture patterns
+% marked as red lines match well with the experimental results shown as black lines. The final fracture pattern is a verti-
+% cal straight line when α = 0 (pure mode I). When α > 0 , the sample is subjected to mixed-mode or pure mode II load-
+% ing, resulting in a curvilinear fracture paths. For all simulation cases, the fractures initiate from the notch tip and then
+% propagate towards upper loading point, while the experiments show that a few fractures tend to initiate behind the
+% notch tip when the notch angle is beyond α =50 . Nevertheless, the simulation results still could successfully predict
+% the overall fracture envelope in experiments and demonstrate the
+% capability of the traditional SPH model for capturing
+
+% the fracture development under various complex loading conditions. In the meanwhile, the comparison of peak load
+% between experiments and simulations for the notch inclination angles varying from 0 to 60 with an internal incre-
+% ment of 5 is plotted in Figure 13A. It is noted here that a notch angle of 54 (instead of 55) is used in the current test
+% as the sample is subjected to pure mode II loading condition when α = 54 .95 The SPH simulation can well capture the
+% increasing trend of the peak load with the increasing notch angles in the experiment. Additionally, Figure 13B com-
+% pares the predictions of fracture toughness in SPH simulation against the experimental results and Lim's theory.95 The
+% simulation results perfectly fall within the experimental data ranges even though the fracture toughness data in the
+% experiments are quite scattered. Nevertheless, the numerical results agree closely with the empirical fracture toughness
+% envelope, which was proposed by Lim et al.95 and represented as a black line Figure 13B. It further confirms that our
+% model could accurately predict the mixed-mode fracture behaviour of rocks in semicircular bending test.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\begin{table}
+  \centering
+  \begin{tabular}[]{c c c c c c c}
+    \hline
+      &   $\rho$   & $\text{f}_c$ & $\text{f}_t$ & $G_F$ &   E   & $\text{d}_{max}$ \\
+      & (kg/m$^3$) &     (MPa)    &     (MPa)    & (N/m) & (GPa) & (mm) \\
+    \hline
+Value &    1540    &     102.7    &      5.4     &  141  &   31  &  12 \\
+    \hline
+  \end{tabular}
+  \caption[Mechanical properties of thje concrete]{Material properties of Johnstone.}
+  \label{tab:Johnstone-properties}
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+  \centering
+  \includegraphics[width=0.6\textwidth]{./Figure-Semicircular-bending-test}
+  \caption{Geometry and boundary condition of the semicircular bending
+    test.}
+  \label{fig:geometry-Semicircular-bending-test}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\cite{Wang_2020}
 
 \subsection{Drop-weight impact test}
-\label{sec:3.2}
-
-Once the accuracy of the \acrshort{lme} approximants have been proven
-in Section \ref{sec:3.1}, henceforth will be adopted without comparing
-with linear interpolation. Therefore this section is devoted to proof
-the accuracy of the eigensoftening algorithm to simulate the behavior
-of quasi-brittle materials under dynamic loading. An example of this
-load case is the three-point bending test on a notched beam is
-conducted under impact loading. This kinds of experiments are
-challenging to reproduce numerically with an explicit solver since
-fracture occurs in a period of milliseconds and high strength
-materials are involved. Accordingly, really small time steps are
-required to achieve a simulation numerically stable. Additionally,
-this kind of simulations traditionally require the implementation of
-contact algorithm to reproduce the hammer impact in the beam. In the
-\acrshort{mpm}, the implementation of this feature can be bypassed to
-obtain preliminary results. Nevertheless, this kind of algorithm could
-be implemented to get ever more accurate solutions. Although this is
-out of the scope of this document, future research of authors will overcome this
-limitation.\\
-
-As in the study of Zhang {\it et al.} \cite{Zhang_2009,Zhang_2010a},
-an impact hammer of 120.6 kg was employed to drop it at an impact
-speed of 881 mm/s. The beam dimensions where 100 mm x 100 mm (B x D)
+\label{sec:3.3}
+\PNA{This section is devoted to proof
+the accuracy of the eigensoftening algorithm within the \acrshort{mpm} framework when the behavior
+of quasi-brittle materials under dynamic loading is simulated. One of the most interesting examples of this
+loading case is the three-point bending test on a concrete notched beam when it is conducted under impact loading.
+Indeed, this experimental test is appropriate to be reproduced numerically with the explicit solver proposed in this paper since
+fracture occurs in a period of milliseconds and waves propagate fast along the high strength
+materials involved in the aforementioned test.} Accordingly, small time steps are
+required to achieve a numerically stable simulation.\\
+
+An interesting case of this experimental test was reported by Zhang {\it et al.} \cite{Zhang_2009,Zhang_2010a}. As in the aforementioned study,
+an impact hammer of 120.6 kg has been employed in the proposed simulations to drop it at an impact
+speed of 881 mm/s. The beam dimensions were 100 mm x 100 mm (B x D)
 in cross section, and 420 mm in total lenght (L). The initial
 notch-depth ratio was approximately 0.5, and the span, S, was fixed at
-300 mm during the tests, see Figure
-\ref{fig:geometry-drop-weight-impact-test}.
+300 mm during the tests (see Figure
+\ref{fig:geometry-drop-weight-impact-test}).
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \label{sec:4}
-Based on the EigenMPM approach to fracture proposed by Zhang {\it et al.}
-\cite{Zhang_EE_2020}, we have proposed two addition improvements which
-solves the shortcomings presented in the original concept. First by
-bring to the \acrshort{mpm} framework the concept of eigensoftening,
-which allow to consider gradual failure process of each material
-point. This concept can be compared with a cohesive law in the context
-of cohesive fracture. Furthermore, more elaborated damage curves can
-be designed to describe the failure process in more sophisticated
+\PNA{Based on the EigenMPM approach to fracture proposed by Zhang {\it et al.}
+\cite{Zhang_EE_2020}, two additional improvements have been proposed in the present research in order to 
+solve the shortcomings of the original concept that Zhang {\it et al.} pointed out in the aforementioned paper \cite{Zhang_EE_2020}.
+
+Firstly, by
+introducing the concept of eigensoftening to the \acrshort{mpm} framework,
+which allows to consider gradual failure process of each material point. This concept is analogous the softening law which is traditionally employed in the context
+of cohesive fracture in \acrfull{fem}.
+Furthermore, this failure criterion admits the design of more elaborated damage curves, which can be employed in order to describe the failure process in more sophisticated
 materials. In this direction, an interesting future improvement of the
 algorithm would be the ability to simulate of crack patterns in
-composite material such carbon fiber. This leads a challenging
-research topic. Secondly, \acrshort{lme} is employed to remove from
-the solution those wiggles due to inaccuracies in the stress
-integration. This interpolation technique could help to improve
-results in fracture propagation by adapting it through the
-deformation gradient. \textit{A priori} this will enhance the already
-impressive localisation properties of eigensoftening and eigenerosion
-algorithms.
+composite material such as steel or carbon fiber reinforced concretes\cite{Ruiz2019}.
+Interesting researches have been done on this field~\cite{Navas_2018_ES}.
+In addition, the eigensoftening approach can be extrapolated to rock fracture in the same manner the eigenerosion was~\cite{Wang2017}, taking into account that the volumetric stiffness remains in order to support bulk loads.
+
+Secondly, \acrshort{lme} is employed to remove from
+the solution those wiggles provoked by inaccuracies in the stress integration.
+This spatial discretization was previously employed within the \acrshort{mpm} framework with excellent results under the elastic regime~\cite{Wobbes2020,Molinos2020}.
+The traditional time scheme of the \acrshort{mpm} has been improved with a Newmark Predictor Corrector scheme as well.
+In this research, the aforementioned techniques have helped to improve the
+results in fracture propagation through the eigensoftening and eigenerosion algorithms. Further improvement may be reached by adapting \acrshort{lme} through the
+deformation gradient \cite{Kochmann2019}. \textit{A priori} this would enhance the localisation properties of the proposed algorithms in more sophisticated domains.
+
+Finally, for better capturing the measurement of forces made in the
+laboratory, more realistic contact tools have to be
+developed. Navas~\textif{et al.} demonstrate the importance of the
+stiffness of the support in order to obtain accurate results of the
+reaction forces. Interesting contact algorithms within the
+\acrshort{mpm} methodology are available in the literature
+\cite{Bardenhagen_Contact_2001,XZhang_Contact_2011}}
 
@@
 \end{document}
-\message{ !name(2020_EFM_MPM_Eigensoftening.tex) !offset(-1135) }
+\message{ !name(2020_EFM_MPM_Eigensoftening.tex) !offset(-1244) }

### 2020-05-29 2020_EFM_MPM_Eigensoftening.tex
Cambios 29-5-2020

--- 2020-05-27 2020_EFM_MPM_Eigensoftening.tex
@@
 }
-\begin{itemize}
-\item 
-\end{itemize}
+
+\newglossaryentry{Ceps}
+{
+  name=$C_{\epsilon}$,
+  description={Normalizing constant}
+}
+
+\newglossaryentry{heps}
+{
+  name=$h_{\epsilon}$,
+  description={Band width}
+}
+
+\newglossaryentry{Wc}
+{
+  name=$w_{c}$,
+  description={Critical opening displacement}
+}
 
@@
 of the eigenerosion proposed by Pandolfi \& Ortiz
-(2012)\cite{Pandolfi_2012} for fracture of brittle materials. \DM{ XXXX I would modify the following  sentence as "The evaluation of both approaches \cite{Navas_2017_ES} show that the
-eigenerosion algorithm significantly overestimates the tensile  
-stress and the strain peaks, meanwhile eigensoftening captures the forces and crack
-patterns accurately XXXXX}. A
-comparison between both in \cite{Navas_2017_ES} shows that the
-eigenerosion algorithm significantly overestimates the tensile  
-stress and the strain peaks, meanwhile eigensoftening captures the forces and crack
-patterns accurately. On the other hand, eigensoftening algorithm agrees
-very well with experimental results in all the aspects \DM{which aspect?} . Furthermore,
+(2012)\cite{Pandolfi_2012} for fracture of brittle materials.\DM{The
+  evaluation of both approaches \cite{Navas_2017_ES}}\MMP{against
+  experimental measures}\DM{show that the eigenerosion algorithm significantly overestimates the tensile stress and the strain peaks, meanwhile eigensoftening captures the forces and crack
+patterns accurately}. Furthermore,
 the accuracy of this algorithm has been proven for complex fracture
@@
 current free-energy density per unit mass  $W_q^{k+1}$ and the
-normalizing constant $C_{\epsilon}$, \PNA{which also defines the $\epsilon$-neighborhood size, being $\epsilon = C_\epsilon h$.}
+normalizing constant $C_{\epsilon}$, \PNA{which also defines the
+  $\epsilon$-neighborhood size, being $\epsilon = C_\epsilon h$}, \MMP{ and
+  $h$ is a measure of the distance between nodes.}
 
@@
 cohesive crack appears when the maximum tensile strength, $f_t$, is
-reached. Once the crack, $w_n$, reaches the value of the
-critical crack opening, $w_c$, a stress-free crack is
-attained.
-\DM{ see the following sentence: comma missing?
-Clarified--->} For intermediate values a damage value between zero and one represents the extension to which the material has failed.
-\DM{ hasta acá }
+reached. Once the crack, $w_n$, reaches the value of the critical
+crack opening, $w_c$, a stress-free crack is attained.
 %%%%%%%%%%%
@@
 For the eigensoftening algorithm, a strength criterion for crack
-initialization was adopted. Particularly the maximum principal stress
-theory for brittle fracture was considered  \DM{ delete by the authors}  by authors
-\cite{Navas_2017_ES}. With that purpose \DM{ which purpose?}, the variation of the averaged
-strain energy density in the $\epsilon$-neighborhood of the material point
-$\vec{x}_p^{k+1}$ can be obtained as
+initialization was adopted. \MMP{Particularly the maximum principal stress
+theory for brittle fracture was considered in \cite{Navas_2017_ES},
+this allows to quantify the variation of the averaged strain energy density in the
+$\epsilon$-neighborhood of the material point $\vec{x}_p^{k+1}$ as}
 \begin{equation}
@@
 \end{equation}
-where $m_p$ is the total mass of the $\epsilon$-neighborhood, defined similarly  \DM{ Pondría:  defined similarly TO  the eigenerosion method} than in the eigenerosion methodology (Eq.~\eqref{eq:mass-EE}).
-%\begin{equation}
-%  \label{eq:averaged-mass}
-%  m_p = \sum_{x_q^{k+1} \in B_{\epsilon}(x_p^{k+1})} m_q.
-%\end{equation}
-This definition \DM{ dos veces definition en la misma oración, podes poner directamente: The equivalent critical stress leads to a definition of the averaged strain energy ...
-} of the equivalent critical stress leads to a
-definition of the averaged strain energy in terms of the averaged
+where $m_p$ is the total mass of the
+$\epsilon$-neighborhood,\DM{defined similarly to the eigenerosion
+  method (Eq.~\eqref{eq:mass-EE}). The equivalent critical stress
+  leads to a definition of the   averaged strain energy} in terms of the averaged
 strain as $\delta W_{\epsilon,p} =
@@
 
-\subsection{$\epsilon$-neighborhood reconstruction : A node-linked method}
+\subsection{$\epsilon$-neighbourhood reconstruction : A node-linked method}
 \label{sec:epsil-neighb-reconst}
-\PNA{The construction of the $\epsilon$-neighborhood is a major issue of the proposed methodology.} Since this operation could be extremely demanding, optimal
+\PNA{The construction of the $\epsilon$-neighbourhood is a major issue of the proposed methodology.} Since this operation could be extremely demanding, optimal
 numerical implementation should be employed. In opposite with the Cell-linked
@@
 the \acrshort{lme} approximants to introduce a node-linked method. Due
-to the global definition of this interpolation technique, the classical
+to the global support of this interpolation technique, the classical
 interpretation of the \acrshort{fem} element typically adopted in
-\acrshort{mpm} simulations is not required anymore. \DM{Intead, a} linked
-list of tributary nodes is reconstructed with the closest node as
-starting point at each time step \DM{deleted instead}. Therefore, each node is assigned to an
-unique linked-list of those particles which are closest to it. This
-approach allows to reconstruct easily a search list with the support
-of the initial connectivity of the mesh and offers a suitable basis
-for an easy implementation of other interpolation techniques with
-minimum coding effort. A detailed explanation of the proposed
-algorithm can be found in \ref{sec:node-linked-method-1}.
-
+\acrshort{mpm} simulations is not required anymore. Instead, a linked
+list with the surrounding nodes for each node is defined at the initial
+time. Also, each particle has to be associated with the
+closest node instead with the belonging element as heretofore has been
+done.
+\MMP{Now lets define the concept of a particle \textit{tributary nodes} as the
+list of nodes close to it among which the information transfers
+occurs. Once the closest node are defined, the particle
+posses automatically a list of \textit{tributary nodes}. This has two
+immediate benefits, the first is that shape functions with global
+support as \acrshort{lme} are easier to implement,
+and the second is the increase of the efficiency of the $\epsilon$-neighbourhood
+reconstruction. Regarding this last benefit, since the current
+particle has a \textit{tributary nodes} list assigned to it, and
+consequently each node has a linked list with a set of
+\textit{tributary particles}\footnote{Notice that the list of the
+  particles close to each node is unique for each node and is updated
+  in each time step.} close to it, is possible to define efficiently a
+search list with those particles close to the current particle.
+In the end, particles out of the area of influence, Figure
+\ref{fig:Failed-particles}, are pop out of the final
+$\epsilon$-neighbourhood. A final remark about this new approach is
+its ability to reconstruct easily a search list with the support of
+the initial connectivity of the mesh. It provides a suitable basis for
+an easy implementation of other interpolation techniques with minimum
+coding effort. A detailed explanation of the proposed algorithm can be
+found in \ref{sec:node-linked-method-1}.}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Cases of study and discussion}
@@
 
-\DM{The proposed approach to overcome the two main shortcomings of EighenMPM \cite{Zhang_EE_2020} has been evaluated with "two benchmark tests"¿?.
-} \DM{DELETE: As noticed in \cite{Zhang_EE_2020}, the EigenMPM have two important
-shortcomings}. The first one deals with the presence of stress instabilities provoked by the spatial discretization, appearing even
-when the \acrshort{gimp} shape functions are employed. To overcome it, \acrshort{lme}
-approximants are introduced as an
-alternative to the existing interpolation techniques. Its
+\DM{The proposed approach to overcome the two main shortcomings of
+  EighenMPM \cite{Zhang_EE_2020} has been evaluated with ``three
+  benchmark tests''}.
+The first one deals with the presence of stress
+instabilities provoked by the spatial discretization, appearing even when the \acrshort{gimp} shape functions are employed. To overcome it, \acrshort{lme}
+approximants are introduced as an alternative to the existing interpolation techniques. Its
 performance in mitigating spurious stress oscillations under the \acrshort{mpm}~\cite{Wobbes2020,Molinos2020} framework helps to enhance
@@
 \label{sec:3.1}
-
-The aim of the problem presented hereinafter is to assess the capability of the \acrshort{lme}
-approximants to improve the result \textit{versus} the standard linear interpolation. The application consists of a square plate of size $H = 1$ containing
-an initial edge crack of length $0.25 \cdot H$ loaded in a pure mode I
-by displacement control on the outer flanks of the plate (See Figure
+The aim of the problem presented hereinafter is to assess the
+capability of the \acrshort{lme} approximants to improve the result
+\textit{versus} the standard linear interpolation. The application
+consists of a square plate of size\MMP{$H = 1\ [L] $} containing an initial edge
+crack of length $0.25 \cdot H$ loaded in a pure mode I by displacement
+control on the outer flanks of the plate (See Figure
 \ref{fig:geometry-cracked-panel-mode-I} for details). 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\PNA{UNIDADES}
+The constitutive model considered in the numerical experiment is a
+linear-elastic Hookean material, whose Young's modulus \MMP{\gls{E} = 1.06
+$[M] / ([L] \cdot [T]^2)$, the Poisson's ratio \gls{nu} = 0.333, and
+critical energy-release rate \gls{Gf} = 0.0001 $[M] / \cdot
+[T]^2$. The absence of units is due to the current simulation will not be validated against experimental results, where
+scale factor is relevant, but will be against an analytical
+solution provided by Pandolfi \& Ortiz \cite{Pandolfi_2012}.} In
+\acrshort{mpm}, two different discretization are required. On the one hand, a cartesian grid of
+nodes is considered with a nodal spacing value of 0.025. On the other
+hand, the plate will be modeled with a initial layout of four
+particles per element and occupying the Gauss quadrature positions.\\
 
@@
 
-The constitutive model considered in the numerical experiment is a
-linear-elastic Hookean material, whose Young's modulus \gls{E} = 1.06, the
-Poisson's ratio \gls{nu} = 0.333, and critical energy-release rate
-\gls{Gf} = 0.0001. This set of parameters has been previously employed by Pandolfi~\textit{et al.}~\cite{Pandolfi_2012}. In
-\acrshort{mpm}, two different discretization are required. On the one hand,
-a cartesian grid of nodes is considered with a nodal spacing value of
-0.025. On the other hand, the plate will be modeled with a initial
-layout of four particles per element and occupying the Gauss quadrature
-positions.\\
-
 Figure \ref{fig:Reactions-cracked-panel-mode-I} clearly shows the
-presence of wiggles in the reaction-displacements curve, in both loading and post-failure stages,
-when linear interpolation technique is used. In contrast, \acrshort{lme} simulation does not
-exhibit these spurious oscillations and remains linear until the failure. About the strength,
-linear interpolation produces stiffer results than
+presence of wiggles in the reaction-displacements curve, in both
+loading and post-failure stages, when linear interpolation technique
+is used. In contrast, \acrshort{lme} simulation does not exhibit these
+spurious oscillations and remains linear until the failure. About the
+strength, linear interpolation produces stiffer results than
 \acrshort{lme}. This can be attributed to imprecision in the stress
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 Additionally, Figure \ref{fig:Stress-cracked-panel-mode-I}
@@
 when particles crosses the boundary of the element in the linear
-case, which is observed at 60 seconds.
-\PNA{Although, apparently, the differences in the obtained peaks are not extremely significant, it can be owing to the aforementioned hookean material employed~\cite{Zhang_EE_2020}.
-When more sophisticated constitutive models will be employed, severe
-%if hyperelastic materials are consider for future simulations,
-inaccuracies may appear in the stress field that could affect dramatically to the
-final result. Focusing on the post failure behavior, it can be seen how \acrshort{lme} produces soft stress
-field evolution even after breaking.}
+case, which is observed at 60 seconds. \PNA{Although, apparently, the
+  differences in the obtained peaks are not extremely significant, it
+  can be owing to the aforementioned hookean material
+  employed~\cite{Zhang_EE_2020}. When more sophisticated constitutive
+  models will be employed, severe inaccuracies may appear in the
+  stress field that could affect dramatically to the final 
+  result. Focusing on the post failure behavior, it can be seen how
+  \acrshort{lme} produces soft stress field evolution even after
+  breaking.} 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 attributed to the eigenerosion algorithm since the fracture process is
-over. They are due to the dynamic nature of the solver: \PNA{once the energy is release dinamically by the crack, the waves propagate along the domain.}
+over. They are due to the dynamic nature of the solver: \PNA{once the
+  energy is release dinamically by the crack, the waves propagate
+  along the domain.}
+
+\subsection{Semicircular bending test}
+\label{sec:3.2}
+
+The second application to be considered is two semicircular
+bending tests on Johnstone, which have been carried out by Lim {\it et
+  al.} \cite{LIM_1993} and numerically reproduced by Wang {\it et
+  al.}\cite{Wang_2020} under \acrshort{sph} framework within an
+implicit algorithm. The aim of the test is to examine the predictive
+capability of the eigensoftening algorithm under different kind of
+mixed-mode loading conditions. This capability was previously within a
+\acrshort{otm} implementation \cite{Navas_2018_ES}.
+
+The geometry and boundary conditions are sketched in Figure 
+\ref{fig:geometry-Semicircular-bending-test}. The experiment consist in two
+semicircular specimens with a radius of 47.5 mm and a thickness of
+20 mm are supported by two rollers at a span of 47.5 mm and loaded by
+another roller on its mid-span. Notches with a length of 16.6 mm are
+created with different notch angles of 0$^º$ and 60$^º$ with respect
+to the vertical axis to investigate the influences of the
+notch angles on the peak load.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+  \centering
+  \includegraphics[width=0.6\textwidth]{./Figure-Semicircular-bending-test}
+  \caption{Geometry and boundary condition of the semicircular bending
+    test.}
+  \label{fig:geometry-Semicircular-bending-test}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The material properties of Johnstone are listed in Table \ref{tab:Johnstone-properties}.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{table}
+  \centering
+  \begin{tabular}[]{l l}
+    \hline
+    Young's modulus (\gls{E})   & 0.4\ $GPa$       \\
+    Poisson ratio (\gls{nu})    & 0.25           \\
+    Density (\gls{rho})         & 1.54\ $g/cm^3$ \\
+    Tensile strength (\gls{ft}) & 0.6\ $MPa$       \\
+    Critical opening displacement (\gls{Wc}) & 0.015\ $mm$ \\
+    \hline
+  \end{tabular}
+  \caption[Mechanical properties of Johnstone. ]{Material properties of Johnstone.}
+  \label{tab:Johnstone-properties}
+\end{table}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+In the tests, particles were uniformly distributed with an almost
+constant separation of 1 mm between them, resulting in a total number of 4672
+\acrshort{mpm} particles for generating the specimen. Additionally a
+regular cartesian background grid of 1917 nodes with 1.5 mm of nodal distance
+ was generated.
+
+% The velocities of the top boundary particles are vx =
+% 0,vy = − 2 mm/s, whereas the velocities of the bottom boundary
+% particles are as vy = 0.
+
+%     \gls{heps}
+%     \gls{Ceps}
+
+% As Johnstone rocks are classified as soft rocks with a relatively
+% small elastic Young's modulus. Ramp loading is applied to alleviate the dynamic
+% effect due to the sudden loading.
 
 \subsection{Drop-weight impact test}
-\label{sec:3.2}
+\label{sec:3.3}
 \PNA{This section is devoted to proof
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 For the present research, a 2D setting of the experiment has been
 adopted. Both the hammer and the concrete beam are explicitly
-represented in order to properly capture the impact. Several levels of discretization were required to assess
-the objectiveness of the obtained results. The results here exposed
-are from a discretization of 30616 material points and 6297 nodes. To
-achieve better results, an unestructured grid layout has been adopted
-focusing the minimum nodal spacing, 0.47 mm, in the middle of the beam and in
-the impact surface of the hammer. For this simulation, \gls{gamma-lme} was
-fixed to 6. Once the accuracy of the \acrshort{lme} approximants have been proven
-in Section \ref{sec:3.1}, this discretization has been adopted.
+represented in order to properly capture the impact. Several levels of
+discretization were required to assess the objectiveness of the
+obtained results. The results here exposed are from a discretization
+of 30616 material points and 6297 nodes. To achieve better results, an
+unestructured grid layout has been adopted focusing the minimum nodal
+spacing, 0.47 mm, in the middle of the beam and in the impact surface
+of the hammer. For this simulation, \gls{gamma-lme} was fixed to
+6. Once the accuracy of the \acrshort{lme} approximants have been
+proven in Section \ref{sec:3.1}, this discretization has been adopted.
 %without comparing
@@
 
-\section{Node-linked method for $\epsilon$-neighborhood reconstruction}
+\section{Node-linked method for $\epsilon$-neighbourhood reconstruction}
 \label{sec:node-linked-method-1}
@@
   \KwInput{$Particles_I$ : List of particles close to each node}
-  \KwOutput{$\text{neighborhood}_{\epsilon}$ : $\epsilon$-neighborhood for each particle}
+  \KwOutput{$\text{neighbourhood}_{\epsilon}$ : $\epsilon$-neighbourhood for each particle}
   \For{$p$ to $N_p$}
@@
     {
-      $\text{neighborhood}_{\epsilon}^{k+1}$ = $\text{neighborhood}_{\epsilon}^{k} \cup Particles_I(k)$
-    }
-    \For{$p_{\epsilon} \in \text{neighborhood}_{\epsilon}$}
+      $\text{neighbourhood}_{\epsilon}^{k+1}$ = $\text{neighbourhood}_{\epsilon}^{k} \cup Particles_I(k)$
+    }
+    \For{$p_{\epsilon} \in \text{neighbourhood}_{\epsilon}$}
     {

### 2020-05-29 _region_.tex
Cambios 29-5-2020

@@
 $\varepsilon_{\epsilon,f}$ can be represented as the current crack
-opening $w_n$ within the band width, $h_{\epsilon}$. Therefore, 
+opening $w_n$ within the band width $h_{\epsilon}$. Therefore, 
 \begin{equation}
@@
 \textit{versus} the standard linear interpolation. The application
-consists of a square plate of size $H = 1$ containing an initial edge
+consists of a square plate of size\MMP{$H = 1\ [L] $} containing an initial edge
 crack of length $0.25 \cdot H$ loaded in a pure mode I by displacement
@@
 
-% The second application to be considered is a series of semicircular
-% bending tests on Johnstone, which have been carried out by Lim et al.95 The aim of this example is to examine its predictive capability of the SPH model under a wide range
-% of mixed-mode loading conditions. The geometry and boundary conditions of the test in the experiment are shown in
-% Figure 9A. Similar with 3-point bending test, the semicircular specimens with a radius of 47.5 mm and a thickness of
-% 20 mm are supported by two rollers at a span of 47.5 mm and loaded by another roller on its mid-span. Notches with a
-% length of 16.6 mm are created with different notch angles varying from 0 to 60 with respect to the vertical axis to
-% investigate the influences of the notch angles on the peak load (P) and the fracture toughness (KI,KII), which are calcu-
-% lated as follows:
-
-% where KI and KII are respectively mode I and mode II fracture toughness; r is the specimen radius; t is the specimen
-% thickness; a is the notch length; YI and YII are mode I and mode II normalised stress intensity factor. As the values of YI
-% and YII can be obtained from the data by Lim at al.6 KI and KII can be calculated based on the above equation once the
-% peak load (P) is known. The material properties of Johnstone are listed in Table 1. The friction angle and dilation angle
-% are respectively taken as 33 and 4  for average quality rock masses in Hoek and Brown96 for the following examples.
-% Figure 9 shows the corresponding SPH configuration of the semicircular bending test with a notch angle of 30 . In
-% the tests, a particle discretisation of 0.95 mm is used, resulting in a total number of 3995 SPH particles for generating
-% the specimen. To create accurate notch angles using reasonable particle numbers, the initial SPH arrangement in this
-% test is different from the traditional one such as the 3-point bending test in Section 5.1. The initial location of each SPH
-% particle in semicircular bending tests is related to the notch angle as shown in Figure 9B. Similar to the 3-point bending
-% tests, three layers of boundary particles are generated for simulating the point loading in the experiments. The velocities
-% of the top boundary particles are vx = 0,vy = − 2 mm/s, whereas the velocities of the bottom boundary particles are
-% as vy = 0. As Johnstone rocks are classified as soft rocks with a relatively small elastic Young's modulus, both artificial
-% viscosity and artificial stress are used in this test to stabilise the numerical solutions. The ramp loading is also applied
-% to alleviate the dynamic effect due to the sudden loading. The stresses of boundary particles are updated in the same
-% way as that in the 3-point bending test. The stresses of real particles near the loading particles are recorded during the
-% simulation process, from which the peak load and fracture toughness can be obtained for the comparison with the
-% experimental data.
-% Figure 10 illustrates the progressive development of fracture and the horizontal velocity profile at the failure stage
-% for the semicircular specimen with the rotational angle of 30 . As seen in Figure 10A, some particles near the tip of the
-% notch are first damaged, showing that the fracture is initiated at the location of the notch tip. Then, the fracture propa-
-% gates towards the loading point (Figure 10B–D), and eventually, a vertical curvilinear fracture pattern is formed in the
-% middle of the sample (Figure 10E). The horizontal velocity profile corresponding to Figure 10E is also plotted in
-% Figure 10F. It can be seen that the particles on the left side of the fracture move to the left whereas the particles on the
-% other side move to the right direction; thus, the sample is split into two halves at the end. In this approach, SPH particle
-% itself could not be cracked visually; however, each damaged SPH particle possesses a FPZ, and the material behaviour
-% within the FPZ will contribute to the decrease in the overall stress state of the SPH particle, thereby resulting in the sep-
-% aration between two damaged SPH particles. The same test without using the artificial stress is also plotted in
-% Figure 11. The result remains stable when the fracture is initiated (Figure 11A) but becomes unstable during the post-
-% failure process (Figure 11B,C). Unrealistic fracture and particles clustering are observed in Figure 11B,C, which indi-
-% cates the tensile instability problem is occurred in SPH. By comparing those two results, it can be concluded that the
-
-% tensile instability problem can be completely removed and good numerical stability can be achieved by just adopting
-% this artificial stress term.
-% Figure 12 depicts the comparison of mixed-mode fracture envelope between experiments and SPH simulations for
-% different notch inclination angles α = 0 , 15  , 30  , 45 , 50 and 60 . It shows that the simulation fracture patterns
-% marked as red lines match well with the experimental results shown as black lines. The final fracture pattern is a verti-
-% cal straight line when α = 0 (pure mode I). When α > 0 , the sample is subjected to mixed-mode or pure mode II load-
-% ing, resulting in a curvilinear fracture paths. For all simulation cases, the fractures initiate from the notch tip and then
-% propagate towards upper loading point, while the experiments show that a few fractures tend to initiate behind the
-% notch tip when the notch angle is beyond α =50 . Nevertheless, the simulation results still could successfully predict
-% the overall fracture envelope in experiments and demonstrate the
-% capability of the traditional SPH model for capturing
-
-% the fracture development under various complex loading conditions. In the meanwhile, the comparison of peak load
-% between experiments and simulations for the notch inclination angles varying from 0 to 60 with an internal incre-
-% ment of 5 is plotted in Figure 13A. It is noted here that a notch angle of 54 (instead of 55) is used in the current test
-% as the sample is subjected to pure mode II loading condition when α = 54 .95 The SPH simulation can well capture the
-% increasing trend of the peak load with the increasing notch angles in the experiment. Additionally, Figure 13B com-
-% pares the predictions of fracture toughness in SPH simulation against the experimental results and Lim's theory.95 The
-% simulation results perfectly fall within the experimental data ranges even though the fracture toughness data in the
-% experiments are quite scattered. Nevertheless, the numerical results agree closely with the empirical fracture toughness
-% envelope, which was proposed by Lim et al.95 and represented as a black line Figure 13B. It further confirms that our
-% model could accurately predict the mixed-mode fracture behaviour of rocks in semicircular bending test.
-
+The second application to be considered is two semicircular
+bending tests on Johnstone, which have been carried out by Lim et
+al.95. Wang {\it et al.}\cite{Wang_2020} proposed it with the aim of
+examine its predictive capability of the \arcshort{sph} model under a
+wide range of mixed-mode loading conditions. Nonetheless, here only
+both extreme cases 0$^º$ and 60$^º$ will be reproduced.
+
+The geometry and boundary conditions are sketched in Figure 
+\ref{fig:geometry-Semicircular-bending-test} . Similar with 3-point bending test,
+the semicircular specimens with a radius of 47.5 mm and a thickness of
+20 mm are supported by two rollers at a span of 47.5 mm and loaded by
+another roller on its mid-span. Notches with a length of 16.6 mm are
+created with different notch angles varying from 0 to 60 with
+respect to the vertical axis to investigate the influences of the
+notch angles on the peak load (P).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+  \centering
+  \includegraphics[width=0.6\textwidth]{./Figure-Semicircular-bending-test}
+  \caption{Geometry and boundary condition of the semicircular bending
+    test.}
+  \label{fig:geometry-Semicircular-bending-test}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+The material properties of Johnstone are listed in Table \ref{tab:Johnstone-properties} The friction angle and dilation angle
+are respectively taken as 33 and 4  for average quality rock
+masses in Hoek and Brown96 for the following examples.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
   \end{tabular}
-  \caption[Mechanical properties of thje concrete]{Material properties of Johnstone.}
+  \caption[Mechanical properties of Johnstone. ]{Material properties of Johnstone.}
   \label{tab:Johnstone-properties}
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-  \centering
-  \includegraphics[width=0.6\textwidth]{./Figure-Semicircular-bending-test}
-  \caption{Geometry and boundary condition of the semicircular bending
-    test.}
-  \label{fig:geometry-Semicircular-bending-test}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\cite{Wang_2020}
+Figure 9 shows the corresponding SPH configuration of the semicircular
+bending test with a notch angle of 30 . In the tests, a particle
+discretisation of 0.95 mm is used, resulting in a total number of 3995
+SPH particles for generating the specimen. To create accurate notch
+angles using reasonable particle numbers, the initial SPH arrangement
+in this test is different from the traditional one such as the 3-point
+bending test in Section 5.1. The initial location of each SPH particle in semicircular bending tests is related to the notch angle as shown in Figure 9B. Similar to the 3-point bending
+tests, three layers of boundary particles are generated for simulating
+the point loading in the experiments. The velocities of the top boundary particles are vx = 0,vy = − 2 mm/s, whereas the velocities of the bottom boundary particles are
+as vy = 0.
+
+As Johnstone rocks are classified as soft rocks with a relatively
+small elastic Young's modulus, both artificial viscosity and
+artificial stress are used in this test to stabilise the numerical
+solutions. The ramp loading is also applied to alleviate the dynamic
+effect due to the sudden loading.
+
+The stresses of boundary particles are updated in the same way as that
+in the 3-point bending test. The stresses of real particles near the
+loading particles are recorded during the simulation process, from
+which the peak load and fracture toughness can be obtained for the
+comparison with the experimental data.
+
+Figure 10 illustrates the progressive development of fracture and the
+horizontal velocity profile at the failure stage for the semicircular specimen with the rotational angle of 30 . As seen in Figure 10A, some particles near the tip of the
+notch are first damaged, showing that the fracture is initiated at the
+location of the notch tip. Then, the fracture propagates towards the
+loading point (Figure 10B–D), and eventually, a vertical curvilinear
+fracture pattern is formed in the middle of the sample (Figure
+10E). The horizontal velocity profile corresponding to Figure 10E is
+also plotted in Figure 10F. It can be seen that the particles on the
+left side of the fracture move to the left whereas the particles on
+the other side move to the right direction; thus, the sample is split
+into two halves at the end. In this approach, SPH particle itself could not be cracked visually; however, each damaged SPH particle possesses a FPZ, and the material behaviour
+within the FPZ will contribute to the decrease in the overall stress
+state of the SPH particle, thereby resulting in the separation between
+two damaged SPH particles. The same test without using the artificial
+stress is also plotted in Figure 11. The result remains stable when
+the fracture is initiated (Figure 11A) but becomes unstable during the
+post-failure process (Figure 11B,C). Unrealistic fracture and
+particles clustering are observed in Figure 11B,C, which indicates the
+tensile instability problem is occurred in SPH. By comparing those two
+results, it can be concluded that the tensile instability problem can
+be completely removed and good numerical stability can be achieved by
+just adopting this artificial stress term. Figure 12 depicts the
+comparison of mixed-mode fracture envelope between experiments and SPH
+simulations for different notch inclination angles α = 0 , 15  ,
+30  , 45 , 50 and 60 . It shows that the simulation fracture
+patterns marked as red lines match well with the experimental results
+shown as black lines. The final fracture pattern is a vertical
+straight line when α = 0 (pure mode I). When α > 0 , the sample is
+subjected to mixed-mode or pure mode II loading, resulting in a curvilinear fracture paths. For all simulation cases, the fractures initiate from the notch tip and then
+propagate towards upper loading point, while the experiments show that
+a few fractures tend to initiate behind the notch tip when the notch angle is beyond α =50 . Nevertheless, the simulation results still could successfully predict
+the overall fracture envelope in experiments and demonstrate the
+capability of the traditional SPH model for capturing the fracture development under various complex loading conditions. In the meanwhile, the comparison of peak load
+between experiments and simulations for the notch inclination angles
+varying from 0 to 60 with an internal increment of 5 is plotted
+in Figure 13A. It is noted here that a notch angle of 54 (instead of
+55) is used in the current test as the sample is subjected to pure
+mode II loading condition when α = 54 .95 The SPH simulation can
+well capture the increasing trend of the peak load with the increasing
+notch angles in the experiment. Additionally, Figure 13B compares the
+predictions of fracture toughness in SPH simulation against the
+experimental results and Lim's theory.95 The simulation results perfectly fall within the experimental data ranges even though the fracture toughness data in the
+experiments are quite scattered. Nevertheless, the numerical results
+agree closely with the empirical fracture toughness envelope, which
+was proposed by Lim et al.95 and represented as a black line Figure
+13B. It further confirms that our model could accurately predict the
+mixed-mode fracture behaviour of rocks in semicircular bending test.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 For the present research, a 2D setting of the experiment has been
@@
 \end{document}
-\message{ !name(2020_EFM_MPM_Eigensoftening.tex) !offset(-1244) }
+
+\message{ !name(2020_EFM_MPM_Eigensoftening.tex) !offset(-1283) }

### 2020-06-04 2020_EFM_MPM_Eigensoftening.tex
Mejora en  Edge-cracked square panel in mode I

@@
 linear-elastic Hookean material, whose Young's modulus \MMP{\gls{E} = 1.06
-$[M] / ([L] \cdot [T]^2)$, the Poisson's ratio \gls{nu} = 0.333, and
-critical energy-release rate \gls{Gf} = 0.0001 $[M] / \cdot
-[T]^2$. The absence of units is due to the current simulation will not be validated against experimental results, where
+$[M] [L]^{-1} [T]^{-2}$, the Poisson's ratio \gls{nu} = 0.333, and
+critical energy-release rate \gls{Gf} = 0.0001 $[L]^{2} [T]^{-2}$. The absence of units is due to the current simulation will not be validated against experimental results, where
 scale factor is relevant, but will be against an analytical
 solution provided by Pandolfi \& Ortiz \cite{Pandolfi_2012}.} In
-\acrshort{mpm}, two different discretization are required. On the one hand, a cartesian grid of
-nodes is considered with a nodal spacing value of 0.025. On the other
-hand, the plate will be modeled with a initial layout of four
-particles per element and occupying the Gauss quadrature positions.\\
-
-\PNA{NOMBRAR ALGO A LOS CASOS ANALITICOS O DE MICHAEL ORTIZ}
-
-Figure \ref{fig:Reactions-cracked-panel-mode-I} clearly shows the
-presence of wiggles in the reaction-displacements curve, in both
-loading and post-failure stages, when linear interpolation technique
-is used. In contrast, \acrshort{lme} simulation does not exhibit these
-spurious oscillations and remains linear until the failure. About the
-strength, linear interpolation produces stiffer results than
+\acrshort{mpm}, two different discretization are required. On one
+hand, a cartesian grid of nodes is considered with a nodal spacing
+value of 0.025. On the other hand, the plate will be modeled with a
+initial layout of four particles per element and occupying the Gauss
+quadrature positions.\\
+
+\MMP{Figure \ref{fig:Reactions-cracked-panel-mode-I} clearly shows the
+\acrshort{lme}$_{\gamma = 3.5}$ solution has a reaction peak value of 0.03 $[M] [L]
+[T]^{-2}$ for a imposed displacement 0.015 $[L]$ which agrees with the
+analytical solution \cite{Pandolfi_2012}}. It also shows the presence
+of wiggles in the reaction-displacements curve, in both loading and
+post-failure stages, when linear interpolation technique is used. In
+contrast, \acrshort{lme} simulation does not exhibit these spurious
+oscillations and remains linear until the failure. About the strength,
+linear interpolation produces stiffer results than
 \acrshort{lme}. This can be attributed to imprecision in the stress

### 2020-06-05 2020_EFM_MPM_Eigensoftening.tex
Cambios 5-5-2020
Casos I y II terminados. Sólo falta completar la simulación del caso III.

@@
 to the vertical axis to investigate the influences of the
-notch angles on the peak load.
+notch angles on the peak load \ref{fig:plot-Angle-Forces-test}.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 In the tests, particles were uniformly distributed with an almost
@@
 regular cartesian background grid of 1917 nodes with 1.5 mm of nodal distance
- was generated.
-
-% The velocities of the top boundary particles are vx =
-% 0,vy = − 2 mm/s, whereas the velocities of the bottom boundary
-% particles are as vy = 0.
-
-%     \gls{heps}
-%     \gls{Ceps}
-
-% As Johnstone rocks are classified as soft rocks with a relatively
-% small elastic Young's modulus. Ramp loading is applied to alleviate the dynamic
-% effect due to the sudden loading.
+was generated. The velocities of the top boundary particles are $v_x$ = 0, $v_y$ = −
+2 mm/s, whereas the velocities of the bottom boundary particles are
+$v_y$ = 0 mm/s. To reduce dynamic effects due to a sudden loading, it
+was preformed within a soft loading ramp. Finally, the model was
+calibrated with a regularization parameter \gls{Ceps} = 1.7 and a
+bandwidth value \gls{heps} = 15.
+
+Figure \ref{fig:Figure-Angle-Forces-test-damage-pattern} shows the
+comparison of mixed-mode fracture envelope between experiments and
+\acrshort{mpm} simulations for different notch inclination angles
+$\alpha$ = 0$^{\circ}$, 30$^{\circ}$ and 60$^{\circ}$. The final
+fracture pattern is a vertical straight line when $\alpha$ =
+0$^{\circ}$  (pure mode I). When $\alpha$ > 0$^{\circ}$, the sample is
+subjected to mixed-mode. For simulation cases 0$^{\circ}$ and 30$^{\circ}$, the fractures
+initiate from the notch tip and then propagate towards upper loading
+point. Experiments show that a few fractures tend to initiate behind
+notch tip when the notch angle is beyond 50$^{\circ}$, figure
+\ref{fig:Figure-Angle-Forces-test-damage-pattern} demonstrate that
+eigensoftening combined with \acrshort{mpm} is able to reproduce this
+behavior. Therefore, the simulation results predict successfully the
+fracture envelope in experiments and demonstrate the capability of
+the eigensoftening-\acrshort{mpm} model for capturing the fracture
+development under various complex loading conditions. 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering
+\subfigure[$\alpha$ = 0]{\includegraphics[width=0.49\textwidth]{./Figure-Angle-Forces-test-0-damage-pattern.png}}
+\subfigure[$\alpha$ = 30]{\includegraphics[width=0.49\textwidth]{./Figure-Angle-Forces-test-30-damage-pattern.png}}
+\subfigure[$\alpha$ = 60]{\includegraphics[width=0.49\textwidth]{./Figure-Angle-Forces-test-60-damage-pattern.png}}
+\caption{Crack pattern for different notch inclination angle, and
+  comparison with the experimental results  \cite{LIM_1993}.}
+\label{fig:Figure-Angle-Forces-test-damage-pattern}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Additionally, \ref{fig:plot-Angle-Forces-test} compare the peak load
+between experiments and simulations for the notch inclination angles
+0$^{\circ}$, 30$^{\circ}$ and 60$^{\circ}$. This figure proofs how the
+eigensoftening-\acrshort{mpm} simulation can well capture the
+increasing trend of the peak load with the increasing notch angles in
+the experiment.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+  \centering
+  \includegraphics[width=0.7\textwidth]{./Figure-Angle-Forces-test}
+  \caption{Numerical results compared with the experimental results \cite{LIM_1993}.}
+  \label{fig:plot-Angle-Forces-test}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2020-06-05 _region_.tex
Cambios 5-5-2020
Casos I y II terminados. Sólo falta completar la simulación del caso III.

@@
 The second application to be considered is two semicircular
-bending tests on Johnstone, which have been carried out by Lim et
-al.95. Wang {\it et al.}\cite{Wang_2020} proposed it with the aim of
-examine its predictive capability of the \arcshort{sph} model under a
-wide range of mixed-mode loading conditions. Nonetheless, here only
-both extreme cases 0$^º$ and 60$^º$ will be reproduced.
+bending tests on Johnstone, which have been carried out by Lim {\it et
+  al.} \cite{LIM_1993} and numerically reproduced by Wang {\it et
+  al.}\cite{Wang_2020} under \acrshort{sph} framework within an
+implicit algorithm. The aim of the test is to examine the predictive
+capability of the eigensoftening algorithm under different kind of
+mixed-mode loading conditions. This capability was previously within a
+\acrshort{otm} implementation \cite{Navas_2018_ES}.
 
 The geometry and boundary conditions are sketched in Figure 
-\ref{fig:geometry-Semicircular-bending-test} . Similar with 3-point bending test,
-the semicircular specimens with a radius of 47.5 mm and a thickness of
+\ref{fig:geometry-Semicircular-bending-test}. The experiment consist in two
+semicircular specimens with a radius of 47.5 mm and a thickness of
 20 mm are supported by two rollers at a span of 47.5 mm and loaded by
 another roller on its mid-span. Notches with a length of 16.6 mm are
-created with different notch angles varying from 0 to 60 with
-respect to the vertical axis to investigate the influences of the
-notch angles on the peak load (P).
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+created with different notch angles of 0$^º$ and 60$^º$ with respect
+to the vertical axis to investigate the influences of the
+notch angles on the peak load \ref{fig:plot-Angle-Forces-test}.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}
@@
 \end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-The material properties of Johnstone are listed in Table \ref{tab:Johnstone-properties} The friction angle and dilation angle
-are respectively taken as 33 and 4  for average quality rock
-masses in Hoek and Brown96 for the following examples.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The material properties of Johnstone are listed in Table \ref{tab:Johnstone-properties}.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \begin{table}
   \centering
-  \begin{tabular}[]{c c c c c c c}
+  \begin{tabular}[]{l l}
     \hline
-      &   $\rho$   & $\text{f}_c$ & $\text{f}_t$ & $G_F$ &   E   & $\text{d}_{max}$ \\
-      & (kg/m$^3$) &     (MPa)    &     (MPa)    & (N/m) & (GPa) & (mm) \\
-    \hline
-Value &    1540    &     102.7    &      5.4     &  141  &   31  &  12 \\
+    Young's modulus (\gls{E})   & 0.4\ $GPa$       \\
+    Poisson ratio (\gls{nu})    & 0.25           \\
+    Density (\gls{rho})         & 1.54\ $g/cm^3$ \\
+    Tensile strength (\gls{ft}) & 0.6\ $MPa$       \\
+    Critical opening displacement (\gls{Wc}) & 0.015\ $mm$ \\
     \hline
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-Figure 9 shows the corresponding SPH configuration of the semicircular
-bending test with a notch angle of 30 . In the tests, a particle
-discretisation of 0.95 mm is used, resulting in a total number of 3995
-SPH particles for generating the specimen. To create accurate notch
-angles using reasonable particle numbers, the initial SPH arrangement
-in this test is different from the traditional one such as the 3-point
-bending test in Section 5.1. The initial location of each SPH particle in semicircular bending tests is related to the notch angle as shown in Figure 9B. Similar to the 3-point bending
-tests, three layers of boundary particles are generated for simulating
-the point loading in the experiments. The velocities of the top boundary particles are vx = 0,vy = − 2 mm/s, whereas the velocities of the bottom boundary particles are
-as vy = 0.
-
-As Johnstone rocks are classified as soft rocks with a relatively
-small elastic Young's modulus, both artificial viscosity and
-artificial stress are used in this test to stabilise the numerical
-solutions. The ramp loading is also applied to alleviate the dynamic
-effect due to the sudden loading.
-
-The stresses of boundary particles are updated in the same way as that
-in the 3-point bending test. The stresses of real particles near the
-loading particles are recorded during the simulation process, from
-which the peak load and fracture toughness can be obtained for the
-comparison with the experimental data.
-
-Figure 10 illustrates the progressive development of fracture and the
-horizontal velocity profile at the failure stage for the semicircular specimen with the rotational angle of 30 . As seen in Figure 10A, some particles near the tip of the
-notch are first damaged, showing that the fracture is initiated at the
-location of the notch tip. Then, the fracture propagates towards the
-loading point (Figure 10B–D), and eventually, a vertical curvilinear
-fracture pattern is formed in the middle of the sample (Figure
-10E). The horizontal velocity profile corresponding to Figure 10E is
-also plotted in Figure 10F. It can be seen that the particles on the
-left side of the fracture move to the left whereas the particles on
-the other side move to the right direction; thus, the sample is split
-into two halves at the end. In this approach, SPH particle itself could not be cracked visually; however, each damaged SPH particle possesses a FPZ, and the material behaviour
-within the FPZ will contribute to the decrease in the overall stress
-state of the SPH particle, thereby resulting in the separation between
-two damaged SPH particles. The same test without using the artificial
-stress is also plotted in Figure 11. The result remains stable when
-the fracture is initiated (Figure 11A) but becomes unstable during the
-post-failure process (Figure 11B,C). Unrealistic fracture and
-particles clustering are observed in Figure 11B,C, which indicates the
-tensile instability problem is occurred in SPH. By comparing those two
-results, it can be concluded that the tensile instability problem can
-be completely removed and good numerical stability can be achieved by
-just adopting this artificial stress term. Figure 12 depicts the
-comparison of mixed-mode fracture envelope between experiments and SPH
-simulations for different notch inclination angles α = 0 , 15  ,
-30  , 45 , 50 and 60 . It shows that the simulation fracture
-patterns marked as red lines match well with the experimental results
-shown as black lines. The final fracture pattern is a vertical
-straight line when α = 0 (pure mode I). When α > 0 , the sample is
-subjected to mixed-mode or pure mode II loading, resulting in a curvilinear fracture paths. For all simulation cases, the fractures initiate from the notch tip and then
-propagate towards upper loading point, while the experiments show that
-a few fractures tend to initiate behind the notch tip when the notch angle is beyond α =50 . Nevertheless, the simulation results still could successfully predict
-the overall fracture envelope in experiments and demonstrate the
-capability of the traditional SPH model for capturing the fracture development under various complex loading conditions. In the meanwhile, the comparison of peak load
+In the tests, particles were uniformly distributed with an almost
+constant separation of 1 mm between them, resulting in a total number of 4672
+\acrshort{mpm} particles for generating the specimen. Additionally a
+regular cartesian background grid of 1917 nodes with 1.5 mm of nodal distance
+was generated. The velocities of the top boundary particles are $v_x$ = 0, $v_y$ = −
+2 mm/s, whereas the velocities of the bottom boundary particles are
+$v_y$ = 0 mm/s. To reduce dynamic effects due to a sudden loading, it
+was preformed within a soft loading ramp. Finally, the model was
+calibrated with a regularization parameter \gls{Ceps} = 1.7 and a
+bandwidth value \gls{heps} = 15.
+
+Figure \ref{fig:Figure-Angle-Forces-test-damage-pattern} shows the
+comparison of mixed-mode fracture envelope between experiments and
+\acrshort{mpm} simulations for different notch inclination angles
+$\alpha$ = 0$^{\circ}$, 30$^{\circ}$ and 60$^{\circ}$. The final
+fracture pattern is a vertical straight line when $\alpha$ =
+0$^{\circ}$  (pure mode I). When $\alpha$ > 0$^{\circ}$, the sample is
+subjected to mixed-mode. For simulation cases 0$^{\circ}$ and 30$^{\circ}$, the fractures
+initiate from the notch tip and then propagate towards upper loading
+point. Experiments show that a few fractures tend to initiate behind
+notch tip when the notch angle is beyond 50$^{\circ}$, figure
+\ref{fig:Figure-Angle-Forces-test-damage-pattern} demonstrate that
+eigensoftening combined with \acrshort{mpm} is able to reproduce this
+behavior. Therefore, the simulation results predict successfully the
+fracture envelope in experiments and demonstrate the capability of
+the eigensoftening-\acrshort{mpm} model for capturing the fracture
+development under various complex loading conditions. 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centering
+\subfigure[$\alpha$ = 0]{\includegraphics[width=0.49\textwidth]{./Figure-Angle-Forces-test-0-damage-pattern.png}}
+\subfigure[$\alpha$ = 30]{\includegraphics[width=0.49\textwidth]{./Figure-Angle-Forces-test-30-damage-pattern.png}}
+\subfigure[$\alpha$ = 60]{\includegraphics[width=0.49\textwidth]{./Figure-Angle-Forces-test-60-damage-pattern.png}}
+\caption{Crack pattern for different notch inclination angle, and
+  comparison with the experimental results  \cite{LIM_1993}.}
+\label{fig:Figure-Angle-Forces-test-damage-pattern}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+Additionally, \ref{fig:plot-Angle-Forces-test} compare the peak load
 between experiments and simulations for the notch inclination angles
-varying from 0 to 60 with an internal increment of 5 is plotted
-in Figure 13A. It is noted here that a notch angle of 54 (instead of
-55) is used in the current test as the sample is subjected to pure
-mode II loading condition when α = 54 .95 The SPH simulation can
-well capture the increasing trend of the peak load with the increasing
-notch angles in the experiment. Additionally, Figure 13B compares the
-predictions of fracture toughness in SPH simulation against the
-experimental results and Lim's theory.95 The simulation results perfectly fall within the experimental data ranges even though the fracture toughness data in the
-experiments are quite scattered. Nevertheless, the numerical results
-agree closely with the empirical fracture toughness envelope, which
-was proposed by Lim et al.95 and represented as a black line Figure
-13B. It further confirms that our model could accurately predict the
-mixed-mode fracture behaviour of rocks in semicircular bending test.
+0$^{\circ}$, 30$^{\circ}$ and 60$^{\circ}$. This figure proofs how the
+eigensoftening-\acrshort{mpm} simulation can well capture the
+increasing trend of the peak load with the increasing notch angles in
+the experiment.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+  \centering
+  \includegraphics[width=0.7\textwidth]{./Figure-Angle-Forces-test}
+  \caption{Numerical results compared with the experimental results \cite{LIM_1993}.}
+  \label{fig:plot-Angle-Forces-test}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 adopted. Both the hammer and the concrete beam are explicitly
-represented in order to properly capture the impact. Several levels of discretization were required to assess
-the objectiveness of the obtained results. The results here exposed
-are from a discretization of 30616 material points and 6297 nodes. To
-achieve better results, an unestructured grid layout has been adopted
-focusing the minimum nodal spacing, 0.47 mm, in the middle of the beam and in
-the impact surface of the hammer. For this simulation, \gls{gamma-lme} was
-fixed to 6. Once the accuracy of the \acrshort{lme} approximants have been proven
-in Section \ref{sec:3.1}, this discretization has been adopted.
+represented in order to properly capture the impact. Several levels of
+discretization were required to assess the objectiveness of the
+obtained results. The results here exposed are from a discretization
+of 30616 material points and 6297 nodes. To achieve better results, an
+unestructured grid layout has been adopted focusing the minimum nodal
+spacing, 0.47 mm, in the middle of the beam and in the impact surface
+of the hammer. For this simulation, \gls{gamma-lme} was fixed to
+6. Once the accuracy of the \acrshort{lme} approximants have been
+proven in Section \ref{sec:3.1}, this discretization has been adopted.
 %without comparing
@@
 
-\message{ !name(2020_EFM_MPM_Eigensoftening.tex) !offset(-1283) }
+\message{ !name(2020_EFM_MPM_Eigensoftening.tex) !offset(-1280) }

### 2020-06-05 Semicircular-bendinf-Peak-load-angle.py

@@ -1,0 +1,40 @@
+import pandas as pd
+import numpy as np
+import matplotlib as mpl
+import matplotlib.pyplot as plt
+plt.rc('text', usetex=True)
+plt.rc('font', family='serif')
+fig, ax = plt.subplots()
+
+# Total plot
+# # ax.set_xlim(0.00, 0.0002)
+# ax.set_xticks([0, 0.01, 0.02])
+# ax.set_yticks([-0.01, 0.0, 0.01, 0.02, 0.03, 0.04, 0.05])
+# ax.xaxis.set_minor_locator(AutoMinorLocator())
+# ax.yaxis.set_minor_locator(AutoMinorLocator())
+
+Experimental_data = pd.read_csv("Semicircular-bending-Experimental-results.txt",header=0,names=['angle','load'])
+# Experimental_data.boxplot(ax=ax,by='angle')
+ExpDat_angles = Experimental_data['angle'].to_numpy()
+ExpDat_P = Experimental_data['load'].to_numpy()
+
+Simulation_data   = pd.read_csv("Semicircular-bending-Simulation-results.txt", header=None)
+SimDat_angles = Simulation_data[0].to_numpy()
+SimDat_P = Simulation_data[1].to_numpy()
+
+plt.scatter(ExpDat_angles,ExpDat_P,marker='D',label=r'Experiment Lim \textit{et al.}')
+
+ax.plot(SimDat_angles,SimDat_P,':',marker='s',fillstyle='none',color='k',label=r'Simulation')
+
+# ED_1 = np.array([234,187,193,183,235])
+# ED_2 = np.array([268,220,236,211,212])
+# ED_3 = np.array([312,334,280,326,310,332])
+
+# ax.boxplot([ED_1,ED_2,ED_3],positions=[0,30,60])
+
+
+ax.set_xlabel(r'Notch inclination angle ($^{\circ}$)', fontsize=16)
+ax.set_ylabel(r'Force ($N$)', fontsize=16)
+plt.legend()
+plt.show()
+

### 2020-06-13 2020_EFM_MPM_Eigensoftening.tex

@@
 \label{sec:1}
-The presence of cracks is a violation of the continuity requirement of the
-\acrfull{fem}. To overcome this issue, numerous numerical
+\DM{The failure mechanisms of quasi-brittle materials and the  crack propagation have been studied from different fields such as materials science, structural engineering, earth science and petroleum engineering .
+The prediction of crack propagation has been approached with different numerical techniques.
+The \acrfull{fem} is widely used in industrial application.
+However,} the presence of cracks is a violation of the continuity requirement of the \acrfull{fem}.
+To overcome this issue, numerous numerical
 artifacts have been proposed with the aim of reproducing such a
@@
 
+ \DM{ Miguel...esto artículos se pueden citar pra enteder la evolución de la progración de la fractura. Hay estados del arte muy buenos entre ellos.  X-FEM with Level set
+T. Nagashima, M. Sawada Development of a damage propagation analysis system based on level set XFEM using the cohesive zone model Comput Struct, 174 (2016), pp. 42-53
+J. Huang An efficient morphology generation and level set representation of cementitious microstructures with arbitrarily shaped aggregates and cracks via extended finite elements
+Comput Struct, 206 (2018), pp. 122-144
+Y. Abdelaziz, A. Hamouine A survey of the extended finite element Comput Struct, 86 (11) (2008), pp. 1141-1151}
 Regarding \acrshort{mpm}, fracture \PNA{has been treated numerically through two different ways}.
@@
 warranties the \textit{least width} shape function support. To reach
-\DM{delete to} a compromise between two competing objectives, a Pareto set is
+a compromise between two competing objectives, a Pareto set is
 defined as,
@@
 $\alpha$ = 0$^{\circ}$, 30$^{\circ}$ and 60$^{\circ}$. The final
-fracture pattern is a vertical straight line when $\alpha$ =
-0$^{\circ}$  (pure mode I). When $\alpha$ > 0$^{\circ}$, the sample is
+fracture pattern is a vertical straight line when $\alpha$ = 0$^{\circ}$  (pure mode I). 
+When $\alpha$ > 0$^{\circ}$, the sample is
 subjected to mixed-mode. For simulation cases 0$^{\circ}$ and 30$^{\circ}$, the fractures
@@
 \label{sec:4}
+
+\DM{Cometario general: Pienso que hay que estructurar un poco la conclusión.
+No agregar tantas citas.
+Acá estás concluyendo tu trabajo.
+Iría de lo general a lo particular.
+Pondría claramente en cada parrafo cual es el aporte.
+Con tantas citas no queda claro que hiciste vos y que los otros.
+Las citas estarán puestas cuando vos comenzaste a hablar de lo que hiciete en el cuerpo del documento.
+Acá las citas minimas y tus aportes.
+Imagino un primer parrafo asi diciendo cuales son las limitaciones ...propuesta modificable...:}
+
+\DM{The paper proposes the eigensoftening algorithm in a \acrshort{MPM} framework for quasi-brittle materials to overcome the limitations observed in the EigenMPM \cite{Zhang_EE_2020}.
+The overestimation of tensile
+stress and strain peaks in the fracture mechanism of quasi-brittle materials and the stress oscillations observed with conventional \acrshort{mpm}/\acrshort{gimp} are faced.  }
+
 \PNA{Based on the EigenMPM approach to fracture proposed by Zhang {\it et al.} 
 \cite{Zhang_EE_2020}, two additional improvements have been proposed in the present research in order to 
-solve the shortcomings of the original concept that Zhang {\it et al.} pointed out in the aforementioned paper \cite{Zhang_EE_2020}.
+solve the shortcomings of the original concept that Zhang {\it et al.} pointed out in the aforementioned paper \cite{Zhang_EE_2020}. }
 
@@
 \acrshort{mpm} methodology are available in the literature
-\cite{Bardenhagen_Contact_2001,XZhang_Contact_2011}}
+\cite{Bardenhagen_Contact_2001,XZhang_Contact_2011}
 

### 2020-06-13 2020_EFM_MPM_Eigensoftening.tex
Cambios MMP propuestos por DM

--- 2020-06-05 2020_EFM_MPM_Eigensoftening.tex
@@
 \newacronym{fem}{FEM}{Finite Element Method}
+\newacronym{xfem}{XFEM}{Extended Finite Element Method}
 \newacronym{efgm}{EFGM}{Element-Free Galerkin Method}
@@
 \label{sec:1}
-The presence of cracks is a violation of the continuity requirement of the
-\acrfull{fem}. To overcome this issue, numerous numerical
+\DM{The failure mechanisms of quasi-brittle materials and the  crack propagation have been studied from different fields such as materials science, structural engineering, earth science and petroleum engineering .
+The prediction of crack propagation has been approached with different numerical techniques.
+The \acrfull{fem} is widely used in industrial application.
+However,} the presence of cracks is a violation of the continuity requirement of the \acrshort{fem}.
+To overcome this issue, numerous numerical
 artifacts have been proposed with the aim of reproducing such a
 complex behaviour. These techniques vary from the employment of cohesive
-approaches~\cite{Barenblatt,Hilleborg_1976}, \PNA{to the gradual insertion of}
+approaches~\cite{Barenblatt,Hilleborg_1976}, or \PNA{to the gradual insertion of}
 cohesive elements \cite{Ortiz_1999,Pandolfi_2002,Ruiz_2000} at solid
-elements boundaries, or handling arbitrary crack paths by level set
-representation of the fracture surface~\cite{Belytschko_03}. The
-simulation of fracture propagation in a more accurate and effective
+elements boundaries. To alleviate these shortcomings of the
+\acrshort{fem}, the \acrfull{xfem} in conjunction with level set
+technique was introduced by Belytschko {\it et al.}
+\cite{Belytschko_03} to handle arbitrary crack paths level
+set. \MMP{Some relevant contributions to the \acrshort{xfem} are the
+modeling micro-scale crack propagation \cite{HUANG_2018}, the
+introduction of a cohesive zone model \cite{NAGASHIMA_2016}, and more
+recently improving it capability to predict the crack path in 3D cases
+\cite{YUN_2019}.}
+
+The simulation of fracture propagation in a more accurate and effective
 way can be considered as one of the \PNA{ongoing goals} of the development of novel spatial discretization methods like meshfree techniques. Some
@@
 
-Regarding \acrshort{mpm}, fracture \PNA{has been treated numerically through two different ways}.
+\MMP{Concerning} \acrshort{mpm}, fracture \PNA{has been treated numerically through two different ways}.
 On the one hand, the ``CRAcks with Material Points (CRAMP)'' is proposed~\cite{Nairn_2003,Nairn_2006}.
@@
 \PNA{Although the traditional \acrshort{mpm} implementation allows collision of two bodies, inaccurate energy conservation is obtained without the implementation of a conservative contact algorithm to reproduce the hammer impact in the beam.
-%In the
-%%\acrshort{mpm}, the implementation of this feature can be bypassed to obtain preliminary results. Nevertheless, this kind of algorithm could
-%be implemented to get ever more accurate solutions. 
-Despite the observed discrepancies, this is
-out of the scope of this document, although future research of authors will overcome this
-limitation. Similarly, results of support forces will be more realistic when modelled by a suitable contact algorithm instead of avoiding any vertical displacement}.\\
+Despite the observed discrepancies, this is out of the scope of this
+document, although future research of authors will overcome this
+limitation. Similarly, results of support forces will be more
+realistic when modelled by a suitable contact algorithm instead of
+avoiding any vertical displacement}.\MMP{Navas {\it et al.}
+(2017)\cite{Navas_2017_ES} demonstrate the importance of the stiffness
+of the support in order to obtain accurate results of the reaction
+forces. Interesting contact algorithms within the \acrshort{mpm}
+methodology are available in the literature
+\cite{Bardenhagen_Contact_2001,XZhang_Contact_2011}.}
 
@@
 \label{sec:4}
-\PNA{Based on the EigenMPM approach to fracture proposed by Zhang {\it et al.}
-\cite{Zhang_EE_2020}, two additional improvements have been proposed in the present research in order to 
-solve the shortcomings of the original concept that Zhang {\it et al.} pointed out in the aforementioned paper \cite{Zhang_EE_2020}.
-
-Firstly, by
-introducing the concept of eigensoftening to the \acrshort{mpm} framework,
+
+\DM{The paper proposes the eigensoftening algorithm in a \acrshort{MPM} framework for quasi-brittle materials to overcome the limitations observed in the EigenMPM \cite{Zhang_EE_2020}.
+The overestimation of tensile
+stress and strain peaks in the fracture mechanism of quasi-brittle
+materials and the stress oscillations observed with conventional
+\acrshort{mpm}/\acrshort{gimp} are faced.} \PNA{Based on the
+EigenMPM approach to fracture, two additional improvements have been proposed in the present research in order to solve the shortcomings of the original concept pointed out in the aforementioned paper \cite{Zhang_EE_2020}.}
+
+Firstly, by introducing the concept of eigensoftening to the \acrshort{mpm} framework,
 which allows to consider gradual failure process of each material point. This concept is analogous the softening law which is traditionally employed in the context
-of cohesive fracture in \acrfull{fem}.
-Furthermore, this failure criterion admits the design of more elaborated damage curves, which can be employed in order to describe the failure process in more sophisticated
-materials. In this direction, an interesting future improvement of the
-algorithm would be the ability to simulate of crack patterns in
-composite material such as steel or carbon fiber reinforced concretes\cite{Ruiz2019}.
-Interesting researches have been done on this field~\cite{Navas_2018_ES}.
-In addition, the eigensoftening approach can be extrapolated to rock fracture in the same manner the eigenerosion was~\cite{Wang2017}, taking into account that the volumetric stiffness remains in order to support bulk loads.
-
-Secondly, \acrshort{lme} is employed to remove from
-the solution those wiggles provoked by inaccuracies in the stress integration.
-This spatial discretization was previously employed within the \acrshort{mpm} framework with excellent results under the elastic regime~\cite{Wobbes2020,Molinos2020}.
-The traditional time scheme of the \acrshort{mpm} has been improved with a Newmark Predictor Corrector scheme as well.
-In this research, the aforementioned techniques have helped to improve the
-results in fracture propagation through the eigensoftening and eigenerosion algorithms. Further improvement may be reached by adapting \acrshort{lme} through the
-deformation gradient \cite{Kochmann2019}. \textit{A priori} this would enhance the localisation properties of the proposed algorithms in more sophisticated domains.
-
-Finally, for better capturing the measurement of forces made in the
-laboratory, more realistic contact tools have to be
-developed. Navas~\textif{et al.} demonstrate the importance of the
-stiffness of the support in order to obtain accurate results of the
-reaction forces. Interesting contact algorithms within the
-\acrshort{mpm} methodology are available in the literature
-\cite{Bardenhagen_Contact_2001,XZhang_Contact_2011}}
+of cohesive fracture in \acrshort{fem}. Furthermore, this failure
+criterion admits the design of more elaborated damage curves, which
+can be employed in order to describe the failure process in more
+sophisticated materials. Secondly to achieve better results, three new
+numerical algorithms has been implemented. The \acrshort{lme}
+approximants are employed to remove from
+the solution those wiggles provoked by inaccuracies in the stress
+integration. The traditional time scheme of the
+\acrshort{mpm} has been improved with a Newmark Predictor Corrector
+scheme as well. And the traditional concept of element connectivity
+has been removed to allow a more flexible and efficient implementation of search
+algorithm. In this research, the aforementioned techniques have helped
+to improve the results in fracture propagation through the
+eigensoftening and eigenerosion algorithms.
+
+Finally, further improvements of the present research are exposed. The
+algorithm would have the ability to simulate of crack patterns in
+composite material such as steel or carbon fiber reinforced
+concretes\cite{Navas_2018_ES,Ruiz2019}. In addition, the eigensoftening
+approach can be extrapolated to rock fracture in the same manner the
+eigenerosion was~\cite{Wang2017}, taking into account that the
+volumetric stiffness remains in order to support bulk loads. Also the
+benefits of \acrshort{lme} can be exploited by adapting it through the
+deformation gradient \cite{Kochmann2019}. \textit{A priori} this would
+enhance the localisation properties of the proposed algorithms in more
+sophisticated domains.
 

### 2020-06-13 _region_.tex
Cambios MMP propuestos por DM

@@
 which allows to consider gradual failure process of each material point. This concept is analogous the softening law which is traditionally employed in the context
-of cohesive fracture in \acrfull{fem}.
+of cohesive fracture in \acrshort{fem}.
 Furthermore, this failure criterion admits the design of more elaborated damage curves, which can be employed in order to describe the failure process in more sophisticated
@@
 
-\message{ !name(2020_EFM_MPM_Eigensoftening.tex) !offset(-1280) }
+\message{ !name(2020_EFM_MPM_Eigensoftening.tex) !offset(-1295) }

### 2020-06-22 2020_EFM_MPM_Eigensoftening.tex
Cambios MMP Conclusiones
Cambios MMP

@@
 an impact hammer of 120.6 kg has been employed in the proposed simulations to drop it at an impact
-speed of 881 mm/s. The beam dimensions were 100 mm x 100 mm (B x D)
+speed of 2640 mm/s. The beam dimensions were 100 mm x 100 mm (B x D)
 in cross section, and 420 mm in total lenght (L). The initial
@@
 obtained results. The results here exposed are from a discretization
-of 30616 material points and 6297 nodes. To achieve better results, an
+of 21576 material points and 3943 nodes. To achieve better results, an
 unestructured grid layout has been adopted focusing the minimum nodal
-spacing, 0.47 mm, in the middle of the beam and in the impact surface
+spacing, 1.2 mm, in the middle of the beam and in the impact surface
 of the hammer. For this simulation, \gls{gamma-lme} was fixed to
-6. Once the accuracy of the \acrshort{lme} approximants have been
-proven in Section \ref{sec:3.1}, this discretization has been adopted.
-%without comparing
-%with linear interpolation. Therefore \\
+1.8, this low value of the regularization parameter smooth high stress
+overshots after the impact. Here the stabilization properties of the \acrshort{lme}
+described in \cite{Molinos2020} becomes crucial to achieve
+non-spurious results. In fact, standard linear element were tested
+with unsatisfactory results since grid-crossing occurs in the hammer
+head producing non realistic forces.\\
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Note that the general trend of both forces are correctly
+Note that the general trend of the impact forces was correctly
 captured. Observe that in experimental solution the delay between
 impact peak and reactions peak does not agree with the numerical
-ones. On the other hand, if the delay is computed analytically through
-concrete wave speed is much closer to the numerical results. A
-feasible explanation to this unexpected result can due the composite
-nature of the concrete. Another discrepancy is in the much higher
-values of maximum impact and reaction forces in numerical than in
-experimental. In this case, this is a consequence of over-rigidity
-in the supports.
+ones. A feasible explanation to this unexpected result can due to a
+over-rigidity in the supports.
 \PNA{Although the traditional \acrshort{mpm} implementation allows collision of two bodies, inaccurate energy conservation is obtained without the implementation of a conservative contact algorithm to reproduce the hammer impact in the beam.
@@
 \centering
-\subfigure[t = 0.27 ms]{\includegraphics[width=0.83\textwidth]{./Figure-impact-test-Damage-vs-Stress-0060}}
-\subfigure[t = 0.36 ms]{\includegraphics[width=0.83\textwidth]{./Figure-impact-test-Damage-vs-Stress-0080}}
-\subfigure[t = 0.45 ms]{\includegraphics[width=0.83\textwidth]{./Figure-impact-test-Damage-vs-Stress-0100}}
+\subfigure[t = 0.27 ms]{\includegraphics[width=0.83\textwidth]{./Figure-impact-test-Damage-vs-Stress-0005}}
+\subfigure[t = 0.36 ms]{\includegraphics[width=0.83\textwidth]{./Figure-impact-test-Damage-vs-Stress-0015}}
+\subfigure[t = 0.45 ms]{\includegraphics[width=0.83\textwidth]{./Figure-impact-test-Damage-vs-Stress-0030}}
 \caption{Evolution of the stress tensor magnitude for linear
@@
 enhance the localisation properties of the proposed algorithms in more
-sophisticated domains.
+sophisticated domains. And the implementation of a contact algorithm to model other impact cases such as bullets collisions.
 

### 2020-06-22 _region_.tex
Cambios MMP

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-Note that the general trend of both forces are correctly
+Note that the general trend of the impact forces was correctly
 captured. Observe that in experimental solution the delay between
 impact peak and reactions peak does not agree with the numerical
-ones. On the other hand, if the delay is computed analytically through
-concrete wave speed is much closer to the numerical results. A
-feasible explanation to this unexpected result can due the composite
-nature of the concrete. Another discrepancy is in the much higher
-values of maximum impact and reaction forces in numerical than in
-experimental. In this case, this is a consequence of over-rigidity
-in the supports.
+ones. A feasible explanation to this unexpected result can due to a
+over-rigidity in the supports.
 \PNA{Although the traditional \acrshort{mpm} implementation allows collision of two bodies, inaccurate energy conservation is obtained without the implementation of a conservative contact algorithm to reproduce the hammer impact in the beam.
-%In the
-%%\acrshort{mpm}, the implementation of this feature can be bypassed to obtain preliminary results. Nevertheless, this kind of algorithm could
-%be implemented to get ever more accurate solutions. 
-Despite the observed discrepancies, this is
-out of the scope of this document, although future research of authors will overcome this
-limitation. Similarly, results of support forces will be more realistic when modelled by a suitable contact algorithm instead of avoiding any vertical displacement}.\\
+Despite the observed discrepancies, this is out of the scope of this
+document, although future research of authors will overcome this
+limitation. Similarly, results of support forces will be more
+realistic when modelled by a suitable contact algorithm instead of
+avoiding any vertical displacement}.\MMP{Navas {\it et al.}
+(2017)\cite{Navas_2017_ES} demonstrate the importance of the stiffness
+of the support in order to obtain accurate results of the reaction
+forces. Interesting contact algorithms within the \acrshort{mpm}
+methodology are available in the literature
+\cite{Bardenhagen_Contact_2001,XZhang_Contact_2011}.}
 
@@
 
-\DM{Cometario general: Pienso que hay que estructurar un poco la conclusión.
-No agregar tantas citas.
-Acá estás concluyendo tu trabajo.
-Iría de lo general a lo particular.
-Pondría claramente en cada parrafo cual es el aporte.
-Con tantas citas no queda claro que hiciste vos y que los otros.
-Las citas estarán puestas cuando vos comenzaste a hablar de lo que hiciete en el cuerpo del documento.
-Acá las citas minimas y tus aportes.
-Imagino un primer parrafo asi diciendo cuales son las limitaciones ...propuesta modificable...:}
-
 \DM{The paper proposes the eigensoftening algorithm in a \acrshort{MPM} framework for quasi-brittle materials to overcome the limitations observed in the EigenMPM \cite{Zhang_EE_2020}.
 The overestimation of tensile
-stress and strain peaks in the fracture mechanism of quasi-brittle materials and the stress oscillations observed with conventional \acrshort{mpm}/\acrshort{gimp} are faced.  }
-
-\PNA{Based on the EigenMPM approach to fracture proposed by Zhang {\it et al.} 
-\cite{Zhang_EE_2020}, two additional improvements have been proposed in the present research in order to 
-solve the shortcomings of the original concept that Zhang {\it et al.} pointed out in the aforementioned paper \cite{Zhang_EE_2020}. }
-
-Firstly, by
-introducing the concept of eigensoftening to the \acrshort{mpm} framework,
+stress and strain peaks in the fracture mechanism of quasi-brittle
+materials and the stress oscillations observed with conventional
+\acrshort{mpm}/\acrshort{gimp} are faced.} \PNA{Based on the
+EigenMPM approach to fracture, two additional improvements have been proposed in the present research in order to solve the shortcomings of the original concept pointed out in the aforementioned paper \cite{Zhang_EE_2020}.}
+
+Firstly, by introducing the concept of eigensoftening to the \acrshort{mpm} framework,
 which allows to consider gradual failure process of each material point. This concept is analogous the softening law which is traditionally employed in the context
-of cohesive fracture in \acrshort{fem}.
-Furthermore, this failure criterion admits the design of more elaborated damage curves, which can be employed in order to describe the failure process in more sophisticated
-materials. In this direction, an interesting future improvement of the
-algorithm would be the ability to simulate of crack patterns in
-composite material such as steel or carbon fiber reinforced concretes\cite{Ruiz2019}.
-Interesting researches have been done on this field~\cite{Navas_2018_ES}.
-In addition, the eigensoftening approach can be extrapolated to rock fracture in the same manner the eigenerosion was~\cite{Wang2017}, taking into account that the volumetric stiffness remains in order to support bulk loads.
-
-Secondly, \acrshort{lme} is employed to remove from
-the solution those wiggles provoked by inaccuracies in the stress integration.
-This spatial discretization was previously employed within the \acrshort{mpm} framework with excellent results under the elastic regime~\cite{Wobbes2020,Molinos2020}.
-The traditional time scheme of the \acrshort{mpm} has been improved with a Newmark Predictor Corrector scheme as well.
-In this research, the aforementioned techniques have helped to improve the
-results in fracture propagation through the eigensoftening and eigenerosion algorithms. Further improvement may be reached by adapting \acrshort{lme} through the
-deformation gradient \cite{Kochmann2019}. \textit{A priori} this would enhance the localisation properties of the proposed algorithms in more sophisticated domains.
-
-Finally, for better capturing the measurement of forces made in the
-laboratory, more realistic contact tools have to be
-developed. Navas~\textif{et al.} demonstrate the importance of the
-stiffness of the support in order to obtain accurate results of the
-reaction forces. Interesting contact algorithms within the
-\acrshort{mpm} methodology are available in the literature
-\cite{Bardenhagen_Contact_2001,XZhang_Contact_2011}
+of cohesive fracture in \acrshort{fem}. Furthermore, this failure
+criterion admits the design of more elaborated damage curves, which
+can be employed in order to describe the failure process in more
+sophisticated materials. Secondly to achieve better results, three new
+numerical algorithms has been implemented. The \acrshort{lme}
+approximants are employed to remove from
+the solution those wiggles provoked by inaccuracies in the stress
+integration. The traditional time scheme of the
+\acrshort{mpm} has been improved with a Newmark Predictor Corrector
+scheme as well. And the traditional concept of element connectivity
+has been removed to allow a more flexible and efficient implementation of search
+algorithm. In this research, the aforementioned techniques have helped
+to improve the results in fracture propagation through the
+eigensoftening and eigenerosion algorithms.
+
+Finally, further improvements of the present research are exposed. The
+algorithm would have the ability to simulate of crack patterns in
+composite material such as steel or carbon fiber reinforced
+concretes\cite{Navas_2018_ES,Ruiz2019}. In addition, the eigensoftening
+approach can be extrapolated to rock fracture in the same manner the
+eigenerosion was~\cite{Wang2017}, taking into account that the
+volumetric stiffness remains in order to support bulk loads. Also the
+benefits of \acrshort{lme} can be exploited by adapting it through the
+deformation gradient \cite{Kochmann2019}. \textit{A priori} this would
+enhance the localisation properties of the proposed algorithms in more
+sophisticated domains. And the implementation of a contact algorithm to model other impact cases such as bullets collisions.
 
@@
 
-\message{ !name(2020_EFM_MPM_Eigensoftening.tex) !offset(-1295) }
+\message{ !name(2020_EFM_MPM_Eigensoftening.tex) !offset(-1300) }

### 2020-06-23 2020_EFM_MPM_Eigensoftening.tex
Cambios PNA

@@
 \usepackage{lineno}
-\usepackage{hyperref}
+% \usepackage{hyperref}
 \usepackage{float}
@@
 The simulation of fracture propagation in a more accurate and effective
-way can be considered as one of the \PNA{ongoing goals} of the development of novel spatial discretization methods like meshfree techniques. Some
+way can be considered as one of the \PNA{ongoing goals} of the development of novel spatial discretisation methods like meshfree techniques. Some
 examples of it are the \acrfull{mpm}
@@
 propagation is based on such parameters as energy release rate
-analyzed by Tan \& Nairn (2002)\cite{Nairn_2002}, and the stress
+analysed by Tan \& Nairn (2002)\cite{Nairn_2002}, and the stress
 intensity factor or the J-integral discussed by Guo \& Nairn
@@
 enable the material to develop displacement jumps at no cost of local
-elastic energy. Later, the eigenerosion approach to brittle facture
+elastic energy. Later, the eigenerosion approach to brittle fracture
 was carried out by Pandolfi {\it et al.}
@@
 The traditional \acrshort{mpm} technique is enhanced through the \acrfull{lme} approximation technique
-\cite{Arroyo2006} for the spatial discretization as well as a explicitly \acrshort{mpm} \acrfull{npc} scheme is derived for the time discretization.}\\
+\cite{Arroyo2006} for the spatial discretisation as well as a explicitly \acrshort{mpm} \acrfull{npc} scheme is derived for the time discretisation.}\\
 
@@
 \sum_I N_I |\vec{x}_p - \vec{x}_I |^2$, and $\beta$ is a
-regularization o \textit{thermalization} parameter such that for
+regularisation o \textit{thermalization} parameter such that for
 Pareto optimal solutions $\beta \in
@@
 (2009)\cite{Schmidt_2009}, who proved that $G_F$ converges to the Griffith
-fracture when the discretization size tends to zero. It is necessary to
+fracture when the discretisation size tends to zero. It is necessary to
 point out that, when a material point overpass the critical energy, its
@@
 strain of each material point at every time step is constant in the
-neighborhood of $\vec{x}_p^{k+1}$, the equation 
+neighbourhood of $\vec{x}_p^{k+1}$, the equation 
 \eqref{eq:variation-averaged-strain-energy-density} can be simplified
@@
 The first one deals with the presence of stress
-instabilities provoked by the spatial discretization, appearing even when the \acrshort{gimp} shape functions are employed. To overcome it, \acrshort{lme}
+instabilities provoked by the spatial discretisation, appearing even when the \acrshort{gimp} shape functions are employed. To overcome it, \acrshort{lme}
 approximants are introduced as an alternative to the existing interpolation techniques. Its
@@
 solution provided by Pandolfi \& Ortiz \cite{Pandolfi_2012}.} In
-\acrshort{mpm}, two different discretization are required. On one
+\acrshort{mpm}, two different discretisation are required. On one
 hand, a cartesian grid of nodes is considered with a nodal spacing
@@
 represented in order to properly capture the impact. Several levels of
-discretization were required to assess the objectiveness of the
-obtained results. The results here exposed are from a discretization
+discretisation were required to assess the objectiveness of the
+obtained results. The results here exposed are from a discretisation
 of 21576 material points and 3943 nodes. To achieve better results, an
-unestructured grid layout has been adopted focusing the minimum nodal
+unstructured grid layout has been adopted focusing the minimum nodal
 spacing, 1.2 mm, in the middle of the beam and in the impact surface
@@
   \centering
-  \includegraphics[width=0.8\textwidth]{Figure-impact-test-Forces-Time}
-  \caption{Evolution of the reaction forces plotted \textit{versus}
-    the imposed displacement for linear interpolation technique and
-    the \acrshort{lme} approximants.}
+  \subfigure[Hammer forces]{\includegraphics[width=0.8\textwidth]{Figure-impact-test-Forces-Time}}
+  \subfigure[Reactions]{\includegraphics[width=0.8\textwidth]{Figure-impact-test-Reactions-Time}}
+  \caption{Comparison of eigensoftening \textit{versus} experimental results.}
   \label{fig:Reactions-Forces-impact-test}
@@
 Note that the general trend of the impact forces was correctly
-captured. Observe that in experimental solution the delay between
-impact peak and reactions peak does not agree with the numerical
-ones. A feasible explanation to this unexpected result can due to a
-over-rigidity in the supports.
+captured.
 \PNA{Although the traditional \acrshort{mpm} implementation allows collision of two bodies, inaccurate energy conservation is obtained without the implementation of a conservative contact algorithm to reproduce the hammer impact in the beam.
@@
 \subfigure[t = 0.45 ms]{\includegraphics[width=0.83\textwidth]{./Figure-impact-test-Damage-vs-Stress-0030}}
-\caption{Evolution of the stress tensor magnitude for linear
+\caption{Evolution of the stress tensor magnitude [MPa] for linear
   interpolation (pictures in the left side), and \acrshort{lme}
@@
 \end{document}
+
+%%% Local Variables:
+%%% ispell-local-dictionary: "en_GB"
+%%% End:

### 2020-06-23 2020_EFM_MPM_Eigensoftening.tex
Updates from Overleaf

--- 2020-06-22 2020_EFM_MPM_Eigensoftening.tex
@@
   to the \acrshort{mpm} with the aim of presenting a suitable alternative
-  to the existing fracture algorithms developed for the
-  \acrshort{mpm}. The good fitting in the predictions made by the
+  to the existing fracture algorithms developed for \PNA{such a methodology}.
+  %\acrshort{mpm}. 
+  The good fitting in the predictions made by the
   eigensoftening algorithm against both analytical and experimental
-  results proofs the well performance of the method when challenging
+  results proofs the \PNA{excellent} performance of the method when challenging
   applications are to modeled.
@@
    f^{int}_I = \sum_p (1 - \chi_p)\ \tens{\sigma}_{p}^{k+1} \cdot
-   \Grad{N_{Ip}}\ \Omega_p
+   \Grad{N_{Ip}}\ \Omega_p,
  \end{equation}
@@
 time. Also, each particle has to be associated with the
-closest node instead with the belonging element as heretofore has been
+closest node instead of with the belonging element as heretofore has been
 done.
@@
 list of nodes close to it among which the information transfers
-occurs. Once the closest node are defined, the particle
-posses automatically a list of \textit{tributary nodes}. This has two
-immediate benefits, the first is that shape functions with global
-support as \acrshort{lme} are easier to implement,
-and the second is the increase of the efficiency of the $\epsilon$-neighbourhood
+occurs. Once the closest nodes are defined, the particle
+possesses automatically a list of \textit{tributary nodes}. This has two
+immediate benefits: the first one is that shape functions with global
+support as \acrshort{lme} are easier to be implemented,
+and the second one is the increase of the efficiency of the $\epsilon$-neighbourhood
 reconstruction. Regarding this last benefit, since the current
@@
   particles close to each node is unique for each node and is updated
-  in each time step.} close to it, is possible to define efficiently a
+  in each time step.} close to it, it is possible to define efficiently a
 search list with those particles close to the current particle.
@@
 eigensoftening algorithm described in Section \ref{sec:2.3}.\MMP{A proof
-of it is exposed in Sections \ref{sec:3.2} \ref{sec:3.3}, where experimental results
-are compared with experimental ones as well as eigensoftening
-computations. In the first case comparing with a semicircular bending
+of it is exposed in Sections \ref{sec:3.2} and \ref{sec:3.3}, where experimental results
+are compared \PNA{with numerical ones, being the eigensoftening technique the one employed in this research for the
+computations.} In the first case comparing with a semicircular bending
 test and in the second case with a drop-weight impact test.}
@@
 $[M] [L]^{-1} [T]^{-2}$, the Poisson's ratio \gls{nu} = 0.333, and
-critical energy-release rate \gls{Gf} = 0.0001 $[L]^{2} [T]^{-2}$. The absence of units is due to the current simulation will not be validated against experimental results, where
-scale factor is relevant, but will be against an analytical
+critical energy-release rate \gls{Gf} = 0.0001 $[L]^{2} [T]^{-2}$. The absence of units is due to the current simulation will not be tested against experimental results, where
+scale factor is relevant, but will be validated against an analytical
 solution provided by Pandolfi \& Ortiz \cite{Pandolfi_2012}.} In
-\acrshort{mpm}, two different discretization are required. On one
+\acrshort{mpm}, two different discretizations are required. On the one
 hand, a cartesian grid of nodes is considered with a nodal spacing
-value of 0.025. On the other hand, the plate will be modeled with a
+value of 0.025 $[L]$. On the other hand, the plate will be modeled with a
 initial layout of four particles per element and occupying the Gauss
@@
 
-\MMP{Figure \ref{fig:Reactions-cracked-panel-mode-I} clearly shows the
+\MMP{Figure \ref{fig:Reactions-cracked-panel-mode-I} clearly shows that the
 \acrshort{lme}$_{\gamma = 3.5}$ solution has a reaction peak value of 0.03 $[M] [L]
@@
 over. They are due to the dynamic nature of the solver: \PNA{once the
-  energy is release dinamically by the crack, the waves propagate
+  energy is released dinamically by the crack, the waves propagate
   along the domain.}
@@
 
-The second application to be considered is two semicircular
-bending tests on Johnstone, which have been carried out by Lim {\it et
+The second application to be considered \PNA{analyzes the bending behavior of semicircular specimens of Johnstone rocks, text which were experimentally} carried out by Lim {\it et
   al.} \cite{LIM_1993} and numerically reproduced by Wang {\it et
@@
 capability of the eigensoftening algorithm under different kind of
-mixed-mode loading conditions. This capability was previously within a
+mixed-mode loading conditions. This capability was assessed previously within a
 \acrshort{otm} implementation \cite{Navas_2018_ES}.
@@
 The geometry and boundary conditions are sketched in Figure 
-\ref{fig:geometry-Semicircular-bending-test}. The experiment consist in two
+\ref{fig:geometry-Semicircular-bending-test}. The experiment \PNA{consist of loading
 semicircular specimens with a radius of 47.5 mm and a thickness of
-20 mm are supported by two rollers at a span of 47.5 mm and loaded by
-another roller on its mid-span. Notches with a length of 16.6 mm are
-created with different notch angles of 0$^º$ and 60$^º$ with respect
-to the vertical axis to investigate the influences of the
-notch angles on the peak load \ref{fig:plot-Angle-Forces-test}.
+20 mm, supported by two rollers at a span of 47.5 mm, by
+another roller on its top mid-span. Notches with a length of 16.6 mm are
+created with the different notch angles of 0$^º$, 30$^º$ and 60$^º$ with respect
+to the vertical axis in order to investigate the influence of the
+notch angle on the peak load \ref{fig:plot-Angle-Forces-test}.}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-The material properties of Johnstone are listed in Table \ref{tab:Johnstone-properties}.
+The material properties of Johnstone rock are listed in Table \ref{tab:Johnstone-properties}.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 constant separation of 1 mm between them, resulting in a total number of 4672
-\acrshort{mpm} particles for generating the specimen. Additionally a
+\acrshort{mpm} particles for generating the specimen. Additionally, a
 regular cartesian background grid of 1917 nodes with 1.5 mm of nodal distance
@@
 2 mm/s, whereas the velocities of the bottom boundary particles are
-$v_y$ = 0 mm/s. To reduce dynamic effects due to a sudden loading, it
-was preformed within a soft loading ramp. Finally, the model was
+$v_y$ = 0 mm/s. To reduce dynamic effects due to a sudden loading, \PNA{a soft loading ramp has been employed as a loading curve.} Finally, the model was
 calibrated with a regularization parameter \gls{Ceps} = 1.7 and a
@@
 fracture pattern is a vertical straight line when $\alpha$ = 0$^{\circ}$  (pure mode I). 
-When $\alpha$ > 0$^{\circ}$, the sample is
-subjected to mixed-mode. For simulation cases 0$^{\circ}$ and 30$^{\circ}$, the fractures
+When $\alpha > 0^{\circ}$, the sample is
+subjected to a mixed-mode pattern. For the cases of 0$^{\circ}$ and 30$^{\circ}$, cracks
 initiate from the notch tip and then propagate towards upper loading
-point. Experiments show that a few fractures tend to initiate behind
-notch tip when the notch angle is beyond 50$^{\circ}$, figure
-\ref{fig:Figure-Angle-Forces-test-damage-pattern} demonstrate that
-eigensoftening combined with \acrshort{mpm} is able to reproduce this
+point. Experiments show that a few cracks tend to initiate behind
+notch tip when the notch angle is beyond 50$^{\circ}$. Figure
+\ref{fig:Figure-Angle-Forces-test-damage-pattern} demonstrates that
+eigensoftening, combined with \acrshort{mpm}, is able to reproduce this
 behavior. Therefore, the simulation results predict successfully the
@@
 0$^{\circ}$, 30$^{\circ}$ and 60$^{\circ}$. This figure proofs how the
-eigensoftening-\acrshort{mpm} simulation can well capture the
+eigensoftening-\acrshort{mpm} simulation can appropriately capture the
 increasing trend of the peak load with the increasing notch angles in

### 2020-06-30 2020_EFM_MPM_Eigensoftening.tex

@@
 solution provided by Pandolfi \& Ortiz \cite{Pandolfi_2012}.} In
-\acrshort{mpm}, two different discretizations are required. On the one
+\acrshort{mpm}, two different discretisation are required. On one
 hand, a cartesian grid of nodes is considered with a nodal spacing

### 2020-06-30 2020_EFM_MPM_Eigensoftening.tex
uGIMP

@@
 capability of the \acrshort{lme} approximants to improve the result
-\textit{versus} the standard linear interpolation. The application
+\textit{versus} the standard linear interpolation and \acrshort{ugimp}. The application
 consists of a square plate of size\MMP{$H = 1\ [L] $} containing an initial edge
@@
 $[M] [L]^{-1} [T]^{-2}$, the Poisson's ratio \gls{nu} = 0.333, and
-critical energy-release rate \gls{Gf} = 0.0001 $[L]^{2} [T]^{-2}$. The absence of units is due to the current simulation will not be tested against experimental results, where
+critical energy-release rate \gls{Gf} = 0.0001 $[L]^{2} [T]^{-2}$. The absence of units is due to the current
+simulation will not be tested against experimental results, where
 scale factor is relevant, but will be validated against an analytical
@@
 oscillations and remains linear until the failure. About the strength,
-linear interpolation produces stiffer results than
-\acrshort{lme}. This can be attributed to imprecision in the stress
-field due to grid-crossing phenomena.\\
+linear interpolation produces stiffer results than \acrshort{lme}. This can be attributed to imprecision in the
+stress field due to grid-crossing phenomena. \MMP{Alternative to
+  \acrshort{lme}, \acrshort{ugimp} shape
+functions can be employed to mitigate grid-crossing instabilities.
+Figure \ref{fig:Reactions-cracked-panel-mode-I} support this since it
+does not exhibits it when particles cross element borders as occur
+with linear interpolation. Unfortunately the extended support of this
+kind of shape function interfere with nodes in both sides of the notch,
+producing an undesired ``tie-effect''. This involves in a violation of
+the free border boundary condition in the notch. Possible solutions to this effect
+are the suppression of the elements in the notch, within a CRAMP-like
+method where two pairs of nodes are employed, or reducing the mesh size. With \acrshort{lme}
+approximants these artefacts are not required since it is possible to control the support
+of the shape function reducing the grid-crossing and avoiding the
+``tie-effect'' in the notch at the same time.}\\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Additionally, Figure \ref{fig:Stress-cracked-panel-mode-I}
-exhibits more clearly the difference between linear interpolation and
+remark clearly the difference between linear interpolation and
 \acrshort{lme}, since numerical instability becomes rather significant
@@
 materials and the stress oscillations observed with conventional
-\acrshort{mpm}/\acrshort{gimp} are faced.} \PNA{Based on the
+\acrshort{mpm} are faced.} \PNA{Based on the
 EigenMPM approach to fracture, two additional improvements have been proposed in the present research in order to solve the shortcomings of the original concept pointed out in the aforementioned paper \cite{Zhang_EE_2020}.}
@@
 the solution those wiggles provoked by inaccuracies in the stress
-integration. The traditional time scheme of the
-\acrshort{mpm} has been improved with a Newmark Predictor Corrector
-scheme as well. And the traditional concept of element connectivity
-has been removed to allow a more flexible and efficient implementation of search
-algorithm. In this research, the aforementioned techniques have helped
+integration and \MMP{to avoid the ``tie-effect'' observed in the
+\acrshort{ugimp}}. The traditional time scheme of the \acrshort{mpm}
+has been improved with a Newmark Predictor Corrector scheme as
+well. And the traditional concept of element connectivity has been
+removed to allow a more flexible and efficient implementation of
+search algorithm. In this research, the aforementioned techniques have helped
 to improve the results in fracture propagation through the

### 2020-06-30 2020_EFM_MPM_Eigensoftening.tex
Version final

--- 2020-06-30 2020_EFM_MPM_Eigensoftening.tex
@@
   to the \acrshort{mpm} with the aim of presenting a suitable alternative
-  to the existing fracture algorithms developed for \PNA{such a methodology}.
+  to the existing fracture algorithms developed for such a methodology.
   %\acrshort{mpm}. 
@@
   eigensoftening algorithm against both analytical and experimental
-  results proofs the \PNA{excellent} performance of the method when challenging
+  results proofs the excellent performance of the method when challenging
   applications are to modeled.
@@
 \label{sec:1}
-\DM{The failure mechanisms of quasi-brittle materials and the  crack propagation have been studied from different fields such as materials science, structural engineering, earth science and petroleum engineering .
+The failure mechanisms of quasi-brittle materials and the  crack propagation have been studied from different fields such as materials science, structural engineering, earth science and petroleum engineering .
 The prediction of crack propagation has been approached with different numerical techniques.
 The \acrfull{fem} is widely used in industrial application.
-However,} the presence of cracks is a violation of the continuity requirement of the \acrshort{fem}.
+However, the presence of cracks is a violation of the continuity requirement of the \acrshort{fem}.
 To overcome this issue, numerous numerical
@@
 complex behaviour. These techniques vary from the employment of cohesive
-approaches~\cite{Barenblatt,Hilleborg_1976}, or \PNA{to the gradual insertion of}
+approaches~\cite{Barenblatt,Hilleborg_1976}, or to the gradual insertion of
 cohesive elements \cite{Ortiz_1999,Pandolfi_2002,Ruiz_2000} at solid
@@
 \cite{Belytschko_03} to handle arbitrary crack paths level
-set. \MMP{Some relevant contributions to the \acrshort{xfem} are the
+set. Some relevant contributions to the \acrshort{xfem} are the
 modeling micro-scale crack propagation \cite{HUANG_2018}, the
@@
 recently improving it capability to predict the crack path in 3D cases
-\cite{YUN_2019}.}
+\cite{YUN_2019}.
 
 The simulation of fracture propagation in a more accurate and effective
-way can be considered as one of the \PNA{ongoing goals} of the development of novel spatial discretisation methods like meshfree techniques. Some
+way can be considered as one of the ongoing goals of the development of novel spatial discretisation methods like meshfree techniques. Some
 examples of it are the \acrfull{mpm}
@@
 
-\MMP{Concerning} \acrshort{mpm}, fracture \PNA{has been treated numerically through two different ways}.
+Concerning \acrshort{mpm}, fracture has been treated numerically through two different ways.
 On the one hand, the ``CRAcks with Material Points (CRAMP)'' is proposed~\cite{Nairn_2003,Nairn_2006}.
-\PNA{The basis of this methodology consist of the removal of} the restriction
+The basis of this methodology consist of the removal of the restriction
 of the single-valued velocity field close to the crack through, at least, two sets of nodes. In this method, different labels are assigned to the material points
@@
 (2004)\cite{Nairn_2004}. 
-On the other hand, the \PNA{foundation} of the second approach is the introduction of failed
+On the other hand, the foundation of the second approach is the introduction of failed
 material points to describe the crack evolution. In these methods, the
@@
 was carried out by Pandolfi {\it et al.}
-\cite{Pandolfi_2012,Pandolfi_2013}. \PNA{In this technique, the concept of ``erosion'' of
+\cite{Pandolfi_2012,Pandolfi_2013}. In this technique, the concept of ``erosion'' of
 the material point is depicted, being the material point able to remain intact or become completely failed or eroded, when no loading
-capacity is bore}. This method has been successfully applied to simulate high
+capacity is bore. This method has been successfully applied to simulate high
 complex phenomena such as dynamic fragmentation of metals
@@
 crack band model \cite{Bazant83}, since energy dissipation is performed through the softened (or failed) volume, this methodology is able to capture the gradual rather than abrupt
-dissipation of the fracture energy. \PNA{Moreover, in order to mitigate stress
+dissipation of the fracture energy. Moreover, in order to mitigate stress
 oscillations as well as to deal with tensile instabilities, such those that
@@
 The traditional \acrshort{mpm} technique is enhanced through the \acrfull{lme} approximation technique
-\cite{Arroyo2006} for the spatial discretisation as well as a explicitly \acrshort{mpm} \acrfull{npc} scheme is derived for the time discretisation.}\\
+\cite{Arroyo2006} for the spatial discretisation as well as a explicitly \acrshort{mpm} \acrfull{npc} scheme is derived for the time discretisation.\\
 
@@
 of the eigenerosion proposed by Pandolfi \& Ortiz
-(2012)\cite{Pandolfi_2012} for fracture of brittle materials.\DM{The
-  evaluation of both approaches \cite{Navas_2017_ES}}\MMP{against
-  experimental measures}\DM{show that the eigenerosion algorithm significantly overestimates the tensile stress and the strain peaks, meanwhile eigensoftening captures the forces and crack
-patterns accurately}. Furthermore,
+(2012)\cite{Pandolfi_2012} for fracture of brittle materials. The
+  evaluation of both approaches \cite{Navas_2017_ES} against
+  experimental measures show that the eigenerosion algorithm significantly overestimates the tensile stress and the strain peaks, meanwhile eigensoftening captures the forces and crack
+patterns accurately. Furthermore,
 the accuracy of this algorithm has been proven for complex fracture
@@
 current free-energy density per unit mass  $W_q^{k+1}$ and the
-normalizing constant $C_{\epsilon}$, \PNA{which also defines the
-  $\epsilon$-neighborhood size, being $\epsilon = C_\epsilon h$}, \MMP{ and
-  $h$ is a measure of the distance between nodes.}
+normalizing constant $C_{\epsilon}$, which also defines the
+  $\epsilon$-neighborhood size, being $\epsilon = C_\epsilon h$, and
+  $h$ is a measure of the distance between nodes.
 
@@
 For the eigensoftening algorithm, a strength criterion for crack
-initialization was adopted. \MMP{Particularly the maximum principal stress
+initialization was adopted. Particularly the maximum principal stress
 theory for brittle fracture was considered in \cite{Navas_2017_ES},
 this allows to quantify the variation of the averaged strain energy density in the
-$\epsilon$-neighborhood of the material point $\vec{x}_p^{k+1}$ as}
+$\epsilon$-neighborhood of the material point $\vec{x}_p^{k+1}$ as
 \begin{equation}
@@
 where $m_p$ is the total mass of the
-$\epsilon$-neighborhood,\DM{defined similarly to the eigenerosion
+$\epsilon$-neighborhood, defined similarly to the eigenerosion
   method (Eq.~\eqref{eq:mass-EE}). The equivalent critical stress
-  leads to a definition of the   averaged strain energy} in terms of the averaged
+  leads to a definition of the   averaged strain energy in terms of the averaged
 strain as $\delta W_{\epsilon,p} =
@@
 where $\chi_p$ and $\Omega_p$ are respectively the damage or softening
-variable and the volume for each material point $p$. \PNA{$\chi_p$ is any function, taking
+variable and the volume for each material point $p$. $\chi_p$ is any function, taking
 values between zero (an intact material) and one (completely failed
 material points), that relates the crack opening and the residual strength.
-To calculate it, typical shapes of cohesive laws such as linear, bilinear or exponential, may be employed.} For the case of a linear softening such the sketched one in the Figure \ref{fig:Damage-ft-wc}, $\chi_p$ is computed as,
+To calculate it, typical shapes of cohesive laws such as linear, bilinear or exponential, may be employed.
+For the case of a linear softening such the sketched one in the Figure \ref{fig:Damage-ft-wc}, $\chi_p$ is computed as,
  \begin{equation}
@@
 \label{sec:epsil-neighb-reconst}
-\PNA{The construction of the $\epsilon$-neighbourhood is a major issue of the proposed methodology.} Since this operation could be extremely demanding, optimal
+The construction of the $\epsilon$-neighbourhood is a major issue of the proposed methodology. Since this operation could be extremely demanding, optimal
 numerical implementation should be employed. In opposite with the Cell-linked
@@
 algorithms like Crossing Number \cite{Shimrat_1962} or Correct
-Even-Odd \cite{Galetzka_et_al_2017}, \PNA{the proposed methodology adopted herein is linked to the shape function neighbourhood. In order to avoid the aforementioned error} prone
+Even-Odd \cite{Galetzka_et_al_2017}, the proposed methodology adopted herein is linked to the shape function neighbourhood. In order to avoid the aforementioned error prone
 techniques, we endeavour to exploit the meshfree benefits of
@@
 done.
-\MMP{Now lets define the concept of a particle \textit{tributary nodes} as the
+Now lets define the concept of a particle \textit{tributary nodes} as the
 list of nodes close to it among which the information transfers
@@
 coding effort. A detailed explanation of the proposed algorithm can be
-found in \ref{sec:node-linked-method-1}.}
+found in \ref{sec:node-linked-method-1}.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-\DM{The proposed approach to overcome the two main shortcomings of
+The proposed approach to overcome the two main shortcomings of
 EighenMPM \cite{Zhang_EE_2020} has been evaluated with ``three
-  benchmark tests''}.
+benchmark tests''.
 The first one deals with the presence of stress
@@
 fracture \cite{Navas_2018_ES}. It can be solved through the
-eigensoftening algorithm described in Section \ref{sec:2.3}.\MMP{A proof
+eigensoftening algorithm described in Section \ref{sec:2.3}. A proof
 of it is exposed in Sections \ref{sec:3.2} and \ref{sec:3.3}, where experimental results
-are compared \PNA{with numerical ones, being the eigensoftening technique the one employed in this research for the
-computations.} In the first case comparing with a semicircular bending
-test and in the second case with a drop-weight impact test.}
+are compared with numerical ones, being the eigensoftening technique the one employed in this research for the
+computations. In the first case comparing with a semicircular bending
+test and in the second case with a drop-weight impact test.
 
@@
 capability of the \acrshort{lme} approximants to improve the result
-\textit{versus} the standard linear interpolation. The application
-consists of a square plate of size\MMP{$H = 1\ [L] $} containing an initial edge
+\textit{versus} the standard linear interpolation and \acrshort{ugimp}
+\cite{Bardenhagen2004}. The application
+consists of a square plate of size $H = 1\ [L] $ containing an initial edge
 crack of length $0.25 \cdot H$ loaded in a pure mode I by displacement
@@
 The constitutive model considered in the numerical experiment is a
-linear-elastic Hookean material, whose Young's modulus \MMP{\gls{E} = 1.06
+linear-elastic Hookean material, whose Young's modulus \gls{E} = 1.06
 $[M] [L]^{-1} [T]^{-2}$, the Poisson's ratio \gls{nu} = 0.333, and
-critical energy-release rate \gls{Gf} = 0.0001 $[L]^{2} [T]^{-2}$. The absence of units is due to the current simulation will not be tested against experimental results, where
+critical energy-release rate \gls{Gf} = 0.0001 $[L]^{2} [T]^{-2}$. The absence of units is due to the current
+simulation will not be tested against experimental results, where
 scale factor is relevant, but will be validated against an analytical
-solution provided by Pandolfi \& Ortiz \cite{Pandolfi_2012}.} In
+solution provided by Pandolfi \& Ortiz \cite{Pandolfi_2012}. In
 \acrshort{mpm}, two different discretisation are required. On one
@@
 
-\MMP{Figure \ref{fig:Reactions-cracked-panel-mode-I} clearly shows that the
+Figure \ref{fig:Reactions-cracked-panel-mode-I} clearly shows that the
 \acrshort{lme}$_{\gamma = 3.5}$ solution has a reaction peak value of 0.03 $[M] [L]
 [T]^{-2}$ for a imposed displacement 0.015 $[L]$ which agrees with the
-analytical solution \cite{Pandolfi_2012}}. It also shows the presence
+analytical solution \cite{Pandolfi_2012}. It also shows the presence
 of wiggles in the reaction-displacements curve, in both loading and
@@
 oscillations and remains linear until the failure. About the strength,
-linear interpolation produces stiffer results than
-\acrshort{lme}. This can be attributed to imprecision in the stress
-field due to grid-crossing phenomena.\\
+linear interpolation produces stiffer results than \acrshort{lme}. This can be attributed to imprecision in the
+stress field due to grid-crossing phenomena. Alternative to
+  \acrshort{lme}, \acrshort{ugimp} shape
+functions can be employed to mitigate grid-crossing instabilities.
+Figure \ref{fig:Reactions-cracked-panel-mode-I} support this since it
+does not exhibits it when particles cross element borders as occur
+with linear interpolation. Unfortunately the extended support of this
+kind of shape function interfere with nodes in both sides of the notch,
+producing an undesired ``tie-effect''. This involves in a violation of
+the free border boundary condition in the notch. Possible solutions to this effect
+are the suppression of the elements in the notch, within a CRAMP-like
+method where two pairs of nodes are employed, or reducing the mesh size. With \acrshort{lme}
+approximants these artefacts are not required since it is possible to control the support
+of the shape function reducing the grid-crossing and avoiding the
+``tie-effect'' in the notch at the same time.\\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Additionally, Figure \ref{fig:Stress-cracked-panel-mode-I}
-exhibits more clearly the difference between linear interpolation and
+remark clearly the difference between linear interpolation and
 \acrshort{lme}, since numerical instability becomes rather significant
 when particles crosses the boundary of the element in the linear
-case, which is observed at 60 seconds. \PNA{Although, apparently, the
+case, which is observed at 60 seconds. Although, apparently, the
 differences in the obtained peaks are not extremely significant, it
@@
 \acrshort{lme} produces soft stress field evolution even after
-  breaking.} 
+breaking. 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 attributed to the eigenerosion algorithm since the fracture process is
-over. They are due to the dynamic nature of the solver: \PNA{once the
+over. They are due to the dynamic nature of the solver: once the
 energy is released dinamically by the crack, the waves propagate
-  along the domain.}
+along the domain.
 
@@
 
-The second application to be considered \PNA{analyzes the bending behavior of semicircular specimens of Johnstone rocks, text which were experimentally} carried out by Lim {\it et
+The second application to be considered analyses the bending behavior of semicircular specimens of Johnstone rocks, text which were experimentally carried out by Lim {\it et
   al.} \cite{LIM_1993} and numerically reproduced by Wang {\it et
@@
 The geometry and boundary conditions are sketched in Figure 
-\ref{fig:geometry-Semicircular-bending-test}. The experiment \PNA{consist of loading
+\ref{fig:geometry-Semicircular-bending-test}. The experiment consist of loading
 semicircular specimens with a radius of 47.5 mm and a thickness of
@@
 to the vertical axis in order to investigate the influence of the
-notch angle on the peak load \ref{fig:plot-Angle-Forces-test}.}
+notch angle on the peak load \ref{fig:plot-Angle-Forces-test}.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 2 mm/s, whereas the velocities of the bottom boundary particles are
-$v_y$ = 0 mm/s. To reduce dynamic effects due to a sudden loading, \PNA{a soft loading ramp has been employed as a loading curve.} Finally, the model was
+$v_y$ = 0 mm/s. To reduce dynamic effects due to a sudden loading, a soft loading ramp has been employed as a loading curve. Finally, the model was
 calibrated with a regularization parameter \gls{Ceps} = 1.7 and a
@@
 \label{sec:3.3}
-\PNA{This section is devoted to proof
+This section is devoted to proof
 the accuracy of the eigensoftening algorithm within the \acrshort{mpm} framework when the behavior
@@
 fracture occurs in a period of milliseconds and waves propagate fast along the high strength
-materials involved in the aforementioned test.} Accordingly, small time steps are
+materials involved in the aforementioned test. Accordingly, small time steps are
 required to achieve a numerically stable simulation.\\
@@
 captured.
-\PNA{Although the traditional \acrshort{mpm} implementation allows collision of two bodies, inaccurate energy conservation is obtained without the implementation of a conservative contact algorithm to reproduce the hammer impact in the beam.
+Although the traditional \acrshort{mpm} implementation allows collision of two bodies, inaccurate energy conservation is obtained without the implementation of a conservative contact algorithm to reproduce the hammer impact in the beam.
 Despite the observed discrepancies, this is out of the scope of this
@@
 realistic when modelled by a suitable contact algorithm instead of
-avoiding any vertical displacement}.\MMP{Navas {\it et al.}
+avoiding any vertical displacement. Navas {\it et al.}
 (2017)\cite{Navas_2017_ES} demonstrate the importance of the stiffness
@@
 methodology are available in the literature
-\cite{Bardenhagen_Contact_2001,XZhang_Contact_2011}.}
+\cite{Bardenhagen_Contact_2001,XZhang_Contact_2011}.
 
@@
 
-\DM{The paper proposes the eigensoftening algorithm in a \acrshort{MPM} framework for quasi-brittle materials to overcome the limitations observed in the EigenMPM \cite{Zhang_EE_2020}.
+The paper proposes the eigensoftening algorithm in a \acrshort{MPM} framework for quasi-brittle materials to overcome the limitations observed in the EigenMPM \cite{Zhang_EE_2020}.
 The overestimation of tensile
@@
 materials and the stress oscillations observed with conventional
-\acrshort{mpm}/\acrshort{gimp} are faced.} \PNA{Based on the
-EigenMPM approach to fracture, two additional improvements have been proposed in the present research in order to solve the shortcomings of the original concept pointed out in the aforementioned paper \cite{Zhang_EE_2020}.}
+\acrshort{mpm} are faced. Based on the
+EigenMPM approach to fracture, two additional improvements have been proposed in the present research in order to solve the shortcomings of the original concept pointed out in the aforementioned paper \cite{Zhang_EE_2020}.
 
@@
 the solution those wiggles provoked by inaccuracies in the stress
-integration. The traditional time scheme of the
-\acrshort{mpm} has been improved with a Newmark Predictor Corrector
-scheme as well. And the traditional concept of element connectivity
-has been removed to allow a more flexible and efficient implementation of search
-algorithm. In this research, the aforementioned techniques have helped
+integration and to avoid the ``tie-effect'' observed in the
+\acrshort{ugimp}. The traditional time scheme of the \acrshort{mpm}
+has been improved with a Newmark Predictor Corrector scheme as
+well. And the traditional concept of element connectivity has been
+removed to allow a more flexible and efficient implementation of
+search algorithm. In this research, the aforementioned techniques have helped
 to improve the results in fracture propagation through the

### 2020-06-30 2020_EFM_MPM_Eigensoftening.tex
Updates from Overleaf

--- 2020-06-30 2020_EFM_MPM_Eigensoftening.tex
@@
 functions can be employed to mitigate grid-crossing instabilities.
-Figure \ref{fig:Reactions-cracked-panel-mode-I} support this since it
-does not exhibits it when particles cross element borders as occur
-with linear interpolation. Unfortunately the extended support of this
+Figure \ref{fig:Reactions-cracked-panel-mode-I} supports this fact since it
+does not exhibit instabilities when particles cross element borders meanwhile these instabilities are found with linear interpolation. Unfortunately, the extended support of this
 kind of shape function interfere with nodes in both sides of the notch,

### 2020-06-30 Author-Novelty.tex
Versión final

\documentclass[12pt,a4paper]{article}
\usepackage{mathptm}

\pagenumbering{gobble}

\title{LME-MPM applied to quasi-brittle fracture}
\author{Miguel Molinos, Pedro Navas, Diego Manzanal and Manuel Pastor}
%\date{}                                           % Activate to display a given date or no date
\begin{document}
\maketitle

\centering
\section*{Highlights}
\setlength{\parskip}{1cm plus 5mm minus 4mm}
\begin{itemize}
\item Fracture mechanics within the Material Point Method is a challenging research fields that is being improved day-to-day.

\item Eigenerosion is one of the fracture models that has been validated within dynamic problems with excellent results. The Eigensoftening algorithm is an interesting improvement of Eigenerosion for quasi-brittle materials.

\item The Local Maximum Entropy shape functions together with a Predictor-Corrector time integration scheme enhance the traditional MPM scheme.

\item Several results of the enhanced MPM with eigenerosion and eigensoftening models are provided in order to compare the performance of the proposed methodology against analytical and experimental solutions with excellent results.

\end{itemize}

\end{document}

### 2020-06-30 Cover-letter.tex
Versión final

\batchmode
\documentclass[10pt]{letter}

\usepackage{mathptm}
\usepackage{fullpage}

\pagestyle{empty}
\begin{document}

Mr. Miguel Molinos\\
ETSI Caminos, Canales y Puertos\\
Technical University of Madrid\\
C/ Prof. Aranguren 3\\
28040 Madrid, Spain\\
Tel. N.:+34 910674396\\
email address: m.molinos@alumnos.upm.es\\

\vspace{.2in}

30 June 2020

\vspace{.3in}

Editor\\
Computers and Structures\\

Dear Sir:

\vspace{.2in}

Please find enclosed the electronic submission of the
\textbf{research article} entitled \textit{``LME-MPM applied to quasi-brittle fracture''} by Miguel Molinos, Pedro Navas, Diego Manzanal and Manuel Pastor. We would like to have this manuscript reviewed by \textbf{Computers and Structures}.

The authors of this paper warrant that this manuscript represents
original work that is not being considered for publication, in
whole or in part, in another journal, book, conference proceedings
or other publications. No already published work can be found in
this document, and all used sources have been cited in the
\textit{References} section. In addition, this manuscript is one
of a kind. All the authors have contributed substantially to the
manuscript and approved the final submission.

Should you need to contact us, please, use the details given above.

\vspace{.1in}

Sincerely,

\vspace{.3in}

Miguel Molinos

\end{document}

### 2020-07-30 2020_EFM_MPM_Eigensoftening.tex
Cambio de revista

@@
 
-% \journal{Engineering Fracture Mechanics}
-\journal{Computers and Structures}
+\journal{Engineering Fracture Mechanics}
+% \journal{Computers and Structures}
 
@@
 behind this concept is inspired in the cohesive fracture. This gradual
-failure criterion is plotted in figure \label{fig:Damage-ft-wc}, where
+failure criterion is plotted in Figure \ref{fig:Damage-ft-wc}, where
 a linear decreasing cohesive law is presented to illustrate the
@@
 another roller on its top mid-span. Notches with a length of 16.6 mm are
-created with the different notch angles of 0$^º$, 30$^º$ and 60$^º$ with respect
+created with the different notch angles of 0$^{\circ}$, 30$^{\circ}$ and 60$^{\circ}$ with respect
 to the vertical axis in order to investigate the influence of the
@@
 regular cartesian background grid of 1917 nodes with 1.5 mm of nodal distance
-was generated. The velocities of the top boundary particles are $v_x$ = 0, $v_y$ = −
-2 mm/s, whereas the velocities of the bottom boundary particles are
+was generated. The velocity of the top boundary particles is 
+$v_y$ = − 2 mm/s, whereas the velocity of the bottom boundary particles is
 $v_y$ = 0 mm/s. To reduce dynamic effects due to a sudden loading, a soft loading ramp has been employed as a loading curve. Finally, the model was
@@
 
-The paper proposes the eigensoftening algorithm in a \acrshort{MPM} framework for quasi-brittle materials to overcome the limitations observed in the EigenMPM \cite{Zhang_EE_2020}.
+The paper proposes the eigensoftening algorithm in a \acrshort{mpm} framework for quasi-brittle materials to overcome the limitations observed in the EigenMPM \cite{Zhang_EE_2020}.
 The overestimation of tensile
@@
 (FJCI-2017–31544) respectively.
+
+\printglossaries
 
@@
   \KwInput{For each $p$, $\epsilon$-neighbourhood, $f_{t,p}$, $h_{\epsilon,p}$, $w_c$}
-  \KwOutput{Return damage parameter $\chi := \{\chi_p\}$}
+  \KwOutput{Return damage parameter $\chi = \{\chi_p\}$}
   % \KwData{Testing set $x$}
@@
   {
-    \If{$\chi_p = 0$ \AND $\epsilon_{f,p} = 0$}
+    \If{$\chi_p = 0$ \And $\epsilon_{f,p} = 0$}
     {
@@
       {
-        $\sigma_{q,I} \leftarrow \text{getEigenvaluesOf}(\sigma_{q})$ \;
+        $\sigma_{q,I} \leftarrow \text{getEigenvaluesOf} (\sigma_{q}) $ \;
         \If{$\chi_q < 1$}
         {
-          $\sum m_p\sigma_{p,I} \leftarrow \sum m_p\sigma_{p,I} + m_q\sigma_{q,I}$ \;
-        }
-        $m_p \leftarrow m_p + m_q$ \;
+          $ \sum m_p\sigma_{p,I} \leftarrow \sum m_p\sigma_{p,I} + m_q\sigma_{q,I}$ \;
+        }
+        $ m_p \leftarrow m_p + m_q$ \;
       }
@@
       }
-      \ElseIf{$\chi_p \neq 1$ \AND $\epsilon_{f,p} > 0$}
+      \ElseIf{$\chi_p \neq 1$ \And $\epsilon_{f,p} > 0$}
       {
@@
   }
-  \caption{Compute damage parameter $\chi_p^{k+1}$}
     \label{alg-eigens}
+  \caption{Compute damage parameter $\chi$}
 \end{algorithm}

### 2020-07-30 Author-Novelty.tex
Cambio de revista

@@
 \begin{itemize}
-\item Fracture mechanics within the Material Point Method is a challenging research fields that is being improved day-to-day.
+\item Fracture mechanics within the MPM is a challenging research field
 
-\item Eigenerosion is one of the fracture models that has been validated within dynamic problems with excellent results.
-The Eigensoftening algorithm is an interesting improvement of Eigenerosion for quasi-brittle materials.
+\item The Eigensoftening algorithm is an improvement to simulate quasi-brittle materials
 
-\item The Local Maximum Entropy shape functions together with a Predictor-Corrector time integration scheme enhance the traditional MPM scheme.
+\item The LME shape functions together with a NPC time integration enhance the standard MPM
 
-\item Several results of the enhanced MPM with eigenerosion and eigensoftening models are provided in order to compare the performance of the proposed methodology against analytical and experimental solutions with excellent results.
+\item The Eigensoftening-MPM has been validated against analytical and experimental results
 

### 2020-10-06 Revisiones/MMP_Responses to the reviewers.tex
Correcciones y hojas de respuestas

\documentclass[12pt]{article}
\usepackage{geometry} % see geometry.pdf on how to lay out the page. There's lots.
\geometry{a4paper} % or letter or a5paper or ... etc
\usepackage{graphicx}
\usepackage{cite}
\usepackage{color}
\usepackage{bm}
\usepackage{amsmath}

% \geometry{landscape} % rotated page geometry

\title{Response to the reviewers of the manuscript ``LME-MPM applied to quasi-brittle fracture."}
\author{Miguel Molinos, Pedro Navas, Diego Manzanal and Manuel Pastor\\}
\date{}

%\date{} % delete this line to display the current date

%%% BEGIN DOCUMENT
\begin{document}

\maketitle
%\tableofcontents

We are grateful to the reviewers for taking their time  to review our work. Their comments have helped us to improve the paper. Changes to the original manuscript are given in  color \textcolor{red}{red} for corrections and  \textcolor{blue}{blue} for modified text in the revised version.  A detailed response to both reviewers is given below.

\section*{Response to Editor}

 \begin{enumerate}

\item \textit{Please include a nomenclature in alphabetic order: Latin, Greek, Acronyms.}\\

Done.

\item \textit{Reduce the list of references to the essential papers only..}\\

Done.

\item \textit{Please avoid acronyms as LME-MPM in the tittle and expand the abbreviations.}\\

Done.

 \end{enumerate}

\section*{Response to Reviewer \#1}
{\it
I am aware of several approaches to modeling fracture in MPM from explicit methods (CRAMP) to methods based on material softening. This paper provides yet another option. I am not convinced of its benefits, but it can still be published with revisions (and with cleaning up of some of the English wording).
}
\\
\\
The reviewer's positive commentaries are greatly appreciated.
\\

\textit{The authors rely on a variant of MPM called LME-MPM. I was not familiar with this option before. This paper might need more explanation, but maybe the references are enough.}\\

The LME-MPM is explained in more detail in an earlier article by the authors.
\\

\textit{Here are some specific comments:}

 \begin{enumerate}

 \item \textit{"proofs" should be "proves".}\\

 Fixed.

 \item \textit{"numerical artifacts have been proposed" People don't intentionally create artifacts. I think authors meant something different. This paper needs some English editing, but I will not comment on them all.}\\

The correct word is artifices in stead of artifacts. As suggested by the reviewer, a proofreading will be done to improve the English of the manuscript.

 \item \textit{Page 4: Equation (1) (from standard MPM) must sum over particles, but that is not stated. Perhaps they are using "repeated indices" summed, but that is not stated either. Also, MPM codes typically do not track particle acceleration. How is that terms tracked here? (actually I see in Eq, (3), but that is not common in MPM, instead, that extrapolation is used to update particle position and then discarded).}\\

As reviewer noticed, the Einstein summation convention for repeated indices has been adopted. This will be clarified in the revised version of the manuscript. Concerning the use of the particle acceleration in the algorithm, this a key part of the Newmark predictor-corrector (NPC) proposed by the authors in Molinos {\it et al.}  \cite{Molinos_2020} (not yet published), this algorithm detailed in the Appendix A. Additionally,  since the algorithm proposed in the aforementioned publication was adapted for the MPM from the proposed by Navas {\it et al.} \cite{Navas_2018a} (2018), the reviewer can visit it to get more details about the good performance of the NPC in the dynamic regime. In the aforementioned publication, the overall performance of the algorithm in demanding dynamic cases is demonstrated. To clarify this issue, an additional reference to this work will be incorporated to the revised version of the manuscript.

\item \textit{Page 7: "reinforces" should be "reinforced" (in FRC)}\\

Fixed.

\item \textit{Section 2.3: Fracture modelling approach. The core of this paper appears to be "isotropic softening" where particles degrade the same in all directions. Although this is common approach in numerical modeling, I am skeptical it can really extend fracture mechanics. For example, how does this modeling handle mode I (failure by tensile stress) from mode II (failure by shear stress). An alternative is to use anisotropic softening and that approach has been implemented in MPM: J. A. Nairn, "Direct Comparison of Anisotropic Damage Mechanics to Fracture Mechanics of Explicit Cracks," Eng. Fract. Mech., 203, 197-207 (2018) and papers cited therein (citing such papers would also help promote impact factor of Engineering Fracture Mechanics).}\\

Authors really appreciate the suggestion of the reviewer to including a cite to the work of J.A. Nairn. The state of art of the manuscript will be revised to include this research and remove the non necessary references. Answering reviewer\textquotesingle s question, the eigensoftening technique is able to handle with both modes I and II. Observe equation (14) is formulated in terms of $\sigma_{I}$. This is the first component of the stress tensor in the maximum principal stress. Therefore, fracture will appear following the $\sigma_I$ trajectories. For instance, it it is well known that a pure shear stress state ($\tau$) can be expressed as a composition of two stress states, one traction ($\sigma_{I} = \tau$) and other compression ($\sigma_{II} = -  \tau$) with principal axes rotated 45$^o$. Additionally, as  Navas {\it et al.}  \cite{Navas_2018b} probed by means of qualitative and quantitative comparisons, the eigensofteing is able to deal with mixed modes even with non isotropic materials as the FRC.

However, as the reviewer argues, in order to capture complex behaviours such as delamination, the damage model for concrete must consider the anisotropy of the material in the formulation. Therefore, the authors agree with the reviewer that the use of an anisotropic damage model would be an important step forward for the proposed model. This pitfall will be clarified and the proposal of an anisotropic damage model will be included in the conclusions as a future research line of the authors.

\item \textit{General: What shape functions are used or what are the $N_I$? It was not clear to me. The nomenclatture "N" is common used in MPM and finite element literature to refer to cell shape functions. MPM integrates these of particle volume to get GIMP shape functions.}\\

$N_I$ is used to define the value of the shape function for a given node $I$ in any position of the space $x$. The shape functions here described (LME) has global support, consequently in this case it does not refer to \textit{cell} shape functions. This concept will be better explained int the  manuscript to avoid misunderstood.

\item \textit{Page 12: "four particles per element and occupying the Gauss quadrature positions" MPM does not numerically integrate particles and they move while the grid does not. Why start at Gaussian quadrature positions? I have never seen that in MPM. The usual discretization is to use equally spaced material points (or at quarter points of the cells).}\\

In MPM, the user is able to choose the initial position of the particles. Therefore, we choose the Gaussian quadrature positions to ensure good integration properties at least in the first time steps. Of course, in a general scenario, the user has not control over the position of the material points in the following the next time steps.

\item \textit{Page 16: "Figure 7 shows the comparison of mixed-mode fracture"
Isotropic failure methods can be used on mixed-mode failure and might even give results that look reasonable. But mixed mode results should depend on separate stresses to initiation tensile failure or shear failure and different amounts critical energy for mode I and Mode II. For example, if this work uses a single toughness, all failure will result in the same energy regardless of ratio of mode I to mode II. That response does not agree well with experimental results (e.g., mixed-mode delamination or adhesive failure).}\\

As the reviewer argues, to simulate complex fracture patterns as delamination, the model should consider an anisotropic behaviour. Although, contrary to the reviewer\textquotesingle s opinion, the eigensofening is capable to capture mixed-mode failure. In previous research, Navas {\it et al.}  \cite{Navas_2018b} demonstrate against experimental results that the eigensoftening approach is able to capture properly the crack pattern and other experimental measurements.

\item \textit{Page 19: "Although the traditional MPM implementation allows collision of two bodies, inaccurate energy conservation is obtained without the implementation of a conservative contact algorithm to reproduce the hammer impact in the beam." Well known and many papers are available that do contact in MPM (including many improvements over the two cited in Refs 51 and 52). It is one of the common reasons for using MPM instead of finite element modeling.}\\

As the reviewer remarks, better results would be obtained if a better contact algorithm is implemented. In addition, the implementation of a proper contact algorithm would help to modelise the supports of the concrete beam in a realistic fashion (Section 3.3).

\item \textit{Page 19: "opposite to the uGIMP shape function, LME allows unstructured grids" Actually, uGIMP has no problem handling a rectilinear grid with arbitrarily sized elements. It could even handle unstructured grids with extra work, but I have never seen it done.}\\

It is true that uGIMP has no problem to handle a rectilinear grid with arbitrarily sized elements since the construction of this shape functions is based on generating 2D or 3D shape functions by multiplicative construction of a closed 1D expression. Unfortunately, in the absence of a regular grid, construction of the weighting functions is only achieved at considerable effort and computational cost as Bardenhagen and Kober \cite{Bardenhagen_2004} (2004) states. This thought will be included in the revised manuscript.

\item \textit{General: I did not find any mention of handling crack contact either during fracture (such as pure mode II fracture) on when a crack forms and then comes back into contact when forces later change direction. Is it possible in this methods or is it a limitation of the approach (such limitations should be listed). The mentioned CRAMP algorithm fully handles contact using results similar to MPM contact methods. I recall the anisotropic softening methods handle crack contact as well. The challenge is that when a crack in progress comes into contact, it should respond with a stiffness similar to the initial material and not some isotropically reduced stiffness. Can this approach distinguish tension and compression? Real materials have very different failure mode.}\\

The authors appreciate the constructive discussion of the reviewer. Extending the eigensoftening algorithm to anisotropic softening seems to be a interesting research line in future. It will be added to the conclusions. Handling crack contact is a current pitfall of the algorithm and will be properly listed in the corrected version of the manuscript. Furthermore, in Pandolfi and Ortiz (2012) \cite{Ortiz_Pandolfi_2012} (Section 3.2) two alternatives to overcome this limitation where briefly discussed. Since the examples proposed in the present research does not involves contact constrain, those improvements were not the focus of our research. This pitfall will be included in the description of the algorithm.

\item \textit{uGIMP: uGIMP can be based on linear or spline grid shape functions. The later can eliminate all oscillations seen in linear uGIMP. The improvements are most dramatic in bending problems such as example 2 and 3 here. Did authors try them?}\\

The authors really appreciate the interesting proposal of the reviewer. We were aware of the work proposed by Steffen {\it et al.} \cite{Steffen_2008} with the B-splines. But we were not aware of the possibility of using spline grid shape functions in the uGIMP. However, since the aim of this manuscript is  discussing the capabilities of a new fracture algorithm for the MPM, we only considered the linear uGIMP shape functions and the LME approximants to stablish a comparison. Nevertheles, the discussion proposed by the reviewer seems to be interesting for a work focused on the computational aspect of the MPM.

 \end{enumerate}

\hspace{5mm}

\section*{Response to Reviewer \#2}

\textit {The manuscript describes an approach to tackle fracture process in brittle materials. Using the material point method as discretization and the eigendeformation concept (in the version devised by one of the authors in his previous contributions), authors propose an efficient algorithm that is illustrated by a few examples of application. The paper is well written, the literature adequately acknowledged. }\\

\textit{A few comments.}
 \begin{enumerate}

\item \textit{If you can reduce the references to the necessary ones, it would be great.}\\

Done.

\item \textit{The introduction to the case of study in section 3 is not necessary, you can shorten it.}\\

You are right, unnecessary references  and explanations will be removed.

\item \textit{Images look as pixels. Is this an artefact of the approach or figures can be obtained in a smoother shade of colors ?}\\

We are printing the evolution of stress and other magnitudes in the material points. Therefore, each "pixel" represents a material point. We will add an explanatory note in the legend of the figures to avoid misunderstandings.

\item \textit{Units of measure are not mathematical symbols, they MUST not be written in italic (they are wrong in Table 1 and in the text and correct in Table 2).}\\

Done.

\item \textit{What is the rationale behind the choice of the material parameters in Example 3.1? The units seem to be dimensionless, so please remove the dimensions, they are unnatural.}\\

The material parameters are the same as those used by Pandolfi and Ortiz (2012) \cite{Ortiz_Pandolfi_2012} for the eigenerosion approach. Dimensions will be removed.

\item \textit{Can you explain why there is a wrong time history in the simulation of the drop-weight test?
}\\

The reason is we are not simulating the real hammer used in the experiments. In instead of it, we simulated a hammer with two different materials. The "head" of the numerical hammer has the same properties like the used in the experiments, the "body" of the numerical hammer has different density and elastic modulus. This approach makes it possible to considerably reduce the length of the numerical hammer and, therefore, the computational cost of the simulation. The elastic modulus and density of the second material were calibrated to reproduce accurately the impact, unfortunately after it, the numerical hammer does not behave exactly as the used in the experiments.

\end{enumerate}

\bibliographystyle{unsrt}
\begin{thebibliography}{10}

\bibitem{Bardenhagen_2004}
Bardenhagen, S. and Kober, E. M.
\newblock {The generalized interpolation material point method}.
\newblock {Computer Modeling in Engineering and Sciences},  2004

\bibitem{Steffen_2008}
Steffen, M. and Wallstedt, Philip and Guilkey, James and Kirby, Robert and Berzins, Martin.
\newblock {Examination and analysis of implementation choices within the Material Point Method (MPM)}.
\newblock {CMES - Computer Modeling in Engineering and Sciences}, 2008

\bibitem{Molinos_2020}
Molinos, M. and Navas, P. and Pastor, M. and Mart\'in Stickle, M.
\newblock {On the dynamic assessment of the Local-Maximum Entropy Material Point Method through an Explicit Predictor-Corrector Scheme}.
\newblock {Computer Methods in Applied Mechanics and Engineering},  Under review,

\bibitem{Navas_2018a}
Navas, P. and L{\'{o}}pez-Querol, S and Yu, R. C. and Pastor, M.
\newblock {Optimal transportation meshfree method in geotechnical engineering problems under large deformation regime}.
\newblock {International Journal for Numerical Methods in Engineering},  2018.

\bibitem{Navas_2018b}
Navas, P. and Yu, R. and Ruiz, G.
\newblock {Meshfree modeling of the dynamic mixed-mode fracture in FRC through an eigensoftening approach}.
\newblock {Engineering Structures},  2018.

\bibitem{Ortiz_Pandolfi_2012}
Pandolfi, A. and Ortiz, M.
\newblock {An eigenerosion approach to brittle fracture}.
\newblock {International Journal for Numerical Methods in Engineering},  2012.

\end{thebibliography}

\end{document}

### 2020-10-06 2020_EFM_MPM_Eigensoftening.tex
Updates from Overleaf
Submitted
Correcciones y hojas de respuestas

@@
 \usepackage[acronym]{glossaries}
-
 \makeglossaries
@@
 
-\title{LME-MPM applied to quasi-brittle fracture.}
+%\title{About the modelling of fracture in quasi-brittle materials thorough the local maximum entropy material point method : the eigensoftening algorithm as proposed approach.}
+
+\title{\textcolor{blue}{Local maximum entropy material point method applied to quasi-brittle fracture.} }
 
@@
   to the \acrshort{mpm} with the aim of presenting a suitable alternative
-  to the existing fracture algorithms developed for such a methodology.
-  %\acrshort{mpm}. 
-  The good fitting in the predictions made by the
-  eigensoftening algorithm against both analytical and experimental
-  results proofs the excellent performance of the method when challenging
+  to the existing fracture algorithms developed for such a methodology.  The good fitting in the predictions made by
+   the eigensoftening algorithm against both analytical and experimental
+  results \textcolor{red}{proves} the excellent performance of the method when challenging
   applications are to modeled.
@@
 \linenumbers
+
+\printglossary[type=\acronymtype]
 
@@
 To overcome this issue, numerous numerical
-artifacts have been proposed with the aim of reproducing such a
+\textcolor{red}{artifices}  have been proposed with the aim of reproducing such a
 complex behaviour. These techniques vary from the employment of cohesive
@@
 \label{sec:2.1}
-The \acrshort{mpm}~\cite{Sulsky1994} is a meshfree Lagrangian-Eulerian
-method where moving material points, henceforth in this research,
-particles ($\square_p$) will carry on all the physical information of the local state ($\sigma_p,
-\varepsilon_p$) and a set of fixed background nodes ($\square_I$) will
-be introduced to compute the balance of momentum equation. Since the
-\acrshort{mpm} possesses the advantages of both Lagrangian and
-Eulerian descriptions, no element distortion takes place in the
-\acrshort{mpm}. Therefore, it is an appropriate and efficient method
+
+\textcolor{blue}{The \acrshort{mpm}~\cite{Sulsky1994} is a meshfree Lagrangian-Eulerian method where the continuum \gls{domain} is discretised with a finite set of material points (also known as particles in this research) $\hat{\Omega} = \{ \vec{x}_p, p \in \mathcal{C} \} \subset \Omega$, where $\mathcal{C} = 1, \ldots, n_p$.
+Any particle field such as position, velocity, mass, volume and stress denoted by $\vec{x}_p$, $\vec{v}_p$, $m_p$, $V_p$ and $\tens{\sigma}_p$, respectively, are assigned to each material point.
+In addition to this set of material points, a set of fixed background nodes is introduced to compute the balance of momentum equation.
+This set of nodes is defined as  $\textbf{X} = \{ \vec{x}_I, I \in \mathcal{B} \} \subset \mathbb{R}^{2}$, where $\mathcal{B} = 1, \ldots, n_I$.
+In the present research, any nodal quantity is denoted by ($\square_I$).}
+
+Since the \acrshort{mpm} possesses the advantages of both Lagrangian and Eulerian descriptions, no  element distortion takes place in the \acrshort{mpm}.
+Therefore, it is an appropriate and efficient method
 to solve problems with moving discontinuities such as fracture evolution.\\
@@
 (iii) a Lagrangian advection of the particles. In the present research,
-an explicit predictor-corrector time integration scheme is adopted. The
+\textcolor{blue}{the explicit predictor-corrector time integration scheme proposed by Molinos~\etal~\cite{Molinos2020} is adopted}. The
 purpose of this choice is motivated due to its proved robustness and
 stability for dynamic computations. In the first stage, the nodal
-velocity predictor $ \vec{\tilde{v}}_I^{k+1}$ is computed through
-nodal velocities $\vec{v}_I$ and accelerations $\vec{a}_I$ and evaluated
+velocity predictor \textcolor{red}{$ \vec{v}_{I}^{pred}$} is computed through
+\textcolor{red}{particles} velocities \textcolor{red}{$\vec{v}_p$} and accelerations \textcolor{red}{$\vec{a}_p$} and evaluated
 in the $k$ time step,
+%%%%%%%%%%%%%%%%%%%%%%%
 \begin{equation}
  \label{eq:Predictor-velocity}
-  \vec{\tilde{v}}_I^{k+1} = \frac{N_{Ip}^{k} m_p (\vec{v}_p^k + (1 - \gamma)\ \Delta t\ \vec{a}_p^k)}{\tens{m}_I^{k+1}}\ .
+    \vec{v}_{I}^{pred} =  \textcolor{blue}{\sum_{p\ \in\ \mathcal{C}}} \frac{ N_{I}(\vec{x}_p^k )\ m_p\ (\vec{v}_p^k + (1 - \gamma)\ \Delta t\ \vec{a}_p^k)}{m_I}.
 \end{equation}
+%%%%%%%%%%%%%%%%%%%%%%%
 Where \gls{gamma-npc} is an user-defined parameter (typically adopted as
-0.5), $\tens{m}_I$ represents the lumped mass matrix, and $N_{Ip}^{k}$ is
-the nodal contribution of the shape function evaluated in the particle
+0.5), $\tens{m}_I$ represents the lumped mass matrix, and \textcolor{red}{$N_{I}(\vec{x}_p^k) $} is the nodal contribution of the shape function evaluated in the particle
 coordinates $\vec{x}_p^k$. This way of computing the nodal predictor is numerically stable
@@
   \label{eq:Update-lagrangian-pce}
-        &\vec{a}_p^{k+1} =
-          \frac{N_{Ip}^k\vec{f}_{I}^{k}}{\tens{m}_I^k}\ ,\\
-      &\vec{v}_p^{k+1} = \vec{v}_p^n + \Delta t\
-        \frac{N_{Ip}^k\
+        &\vec{a}_p^{k+1} = \textcolor{blue}{\sum_{I\ \in\ \mathcal{B}_p}}
+          \frac{N_{I}(\vec{x}_p^k)\ \vec{f}_{I}^{k}}{\tens{m}_I^k}\ ,\\
+      &\vec{v}_p^{k+1} = \vec{v}_p^n + \textcolor{blue}{\sum_{I\ \in\ \mathcal{B}_p}} \Delta t\
+        \frac{N_{I}(\vec{x}_p^k)\
         \vec{f}_{I}^{k}}{\tens{m}_I^k}\ ,\\
-      &\vec{x}_p^{k+1} = \vec{x}_p^n + \Delta t\
-         N_{Ip}^k\ \vec{v}_{I}^{k} +
-        \frac{1}{2}\Delta t^2\ \frac{N_{Ip}^k\
+      &\vec{x}_p^{k+1} = \vec{x}_p^n +  \textcolor{blue}{\sum_{I\ \in\ \mathcal{B}_p}} \Delta t\
+         N_{I}(\vec{x}_p^k)\ \vec{v}_{I}^{k} +
+        \frac{1}{2}\Delta t^2\ \frac{N_{I}(\vec{x}_p^k)\
         \vec{f}_{I}^{k}}{\tens{m}_I^k}\ .
@@
 the accuracy of this algorithm has been proven for complex fracture
-patterns such as the ones obtained with fiber reinforces concrete (FRC),
+patterns such as the ones obtained with fiber \textcolor{red}{reinforced} concrete (FRC),
 \cite{Navas_2018_ES}.\\
@@
 
-The proposed approach to overcome the two main shortcomings of
-EighenMPM \cite{Zhang_EE_2020} has been evaluated with ``three
-benchmark tests''.
-The first one deals with the presence of stress
-instabilities provoked by the spatial discretisation, appearing even when the \acrshort{gimp} shape functions are employed. To overcome it, \acrshort{lme}
-approximants are introduced as an alternative to the existing interpolation techniques. Its
-performance in mitigating spurious stress oscillations under the \acrshort{mpm}~\cite{Wobbes2020,Molinos2020} framework helps to enhance
-notoriously the quality of the results as it is observed in Section
-\ref{sec:3.1}, where both interpolation techniques
-are compared by carrying out an eigenerosion simulation. The second
-limitation is concerned to its inability to simulate properly quasi-brittle
-fracture \cite{Navas_2018_ES}. It can be solved through the
-eigensoftening algorithm described in Section \ref{sec:2.3}. A proof
-of it is exposed in Sections \ref{sec:3.2} and \ref{sec:3.3}, where experimental results
-are compared with numerical ones, being the eigensoftening technique the one employed in this research for the
-computations. In the first case comparing with a semicircular bending
-test and in the second case with a drop-weight impact test.
+\textcolor{blue}{The proposed approach to overcome the two main shortcomings of
+EighenMPM  has been evaluated with three benchmark tests.
+On the one hand, the benchmark proposed in section \ref{sec:3.1} discuss the presence of stress instabilities provoked by the spatial discretisation.
+For that purpose, two different interpolation techniques, \acrshort{gimp} and \acrshort{lme}, as been compared by carrying out an eigenerosion simulation.
+And on the other hand the inability of the eigenerosion to simulate properly quasi-brittle fracture is discussed in sections \ref{sec:3.2} and \ref{sec:3.3}, where experimental results are compared with numerical ones.
+In the first case comparing with a semicircular bending test and in the second case with a drop-weight impact test.}
 
@@
 \cite{Bardenhagen2004}. The application
-consists of a square plate of size $H = 1\ [L] $ containing an initial edge
+consists of a square plate of size $H = 1$ containing an initial edge
 crack of length $0.25 \cdot H$ loaded in a pure mode I by displacement
@@
 The constitutive model considered in the numerical experiment is a
-linear-elastic Hookean material, whose Young's modulus \gls{E} = 1.06
-$[M] [L]^{-1} [T]^{-2}$, the Poisson's ratio \gls{nu} = 0.333, and
-critical energy-release rate \gls{Gf} = 0.0001 $[L]^{2} [T]^{-2}$. The absence of units is due to the current
+linear-elastic Hookean material, whose Young's modulus \gls{E} = 1.06, the Poisson's ratio \gls{nu} = 0.333, and
+critical energy-release rate \gls{Gf} = 0.0001. The absence of units is due to the current
 simulation will not be tested against experimental results, where
@@
 hand, a cartesian grid of nodes is considered with a nodal spacing
-value of 0.025 $[L]$. On the other hand, the plate will be modeled with a
+value of 0.025. On the other hand, the plate will be modeled with a
 initial layout of four particles per element and occupying the Gauss
@@
 Figure \ref{fig:Reactions-cracked-panel-mode-I} clearly shows that the
-\acrshort{lme}$_{\gamma = 3.5}$ solution has a reaction peak value of 0.03 $[M] [L]
-[T]^{-2}$ for a imposed displacement 0.015 $[L]$ which agrees with the
+\acrshort{lme}$_{\gamma = 3.5}$ solution has a reaction peak value of 0.03 for a imposed displacement 0.015 which agrees with the
 analytical solution \cite{Pandolfi_2012}. It also shows the presence
@@
   interpolation (pictures in the left side), and \acrshort{lme}
-  (pictures in the right side). Both simulations performed with an
-  eigenerosion algorithm.}
+  (pictures in the right side).  \textcolor{blue}{The results are printed directly on the material points.}}
 \label{fig:Stress-cracked-panel-mode-I}
@@
     \hline
-    Young's modulus (\gls{E})   & 0.4\ $GPa$       \\
+    Young's modulus (\gls{E})   & 0.4\  \textcolor{red}{GPa}       \\
     Poisson ratio (\gls{nu})    & 0.25           \\
-    Density (\gls{rho})         & 1.54\ $g/cm^3$ \\
-    Tensile strength (\gls{ft}) & 0.6\ $MPa$       \\
-    Critical opening displacement (\gls{Wc}) & 0.015\ $mm$ \\
+    Density (\gls{rho})         & 1.54\ \textcolor{red}{$\text{g/cm}^3$} \\
+    Tensile strength (\gls{ft}) & 0.6\ \textcolor{red}{MPa}       \\
+    Critical opening displacement (\gls{Wc}) & 0.015\ \textcolor{red}{mm} \\
     \hline
@@
 regular cartesian background grid of 1917 nodes with 1.5 mm of nodal distance
-was generated. The velocity of the top boundary particles is 
-$v_y$ = − 2 mm/s, whereas the velocity of the bottom boundary particles is
-$v_y$ = 0 mm/s. To reduce dynamic effects due to a sudden loading, a soft loading ramp has been employed as a loading curve. Finally, the model was
-calibrated with a regularization parameter \gls{Ceps} = 1.7 and a
+was generated. The velocity of the top boundary particles is $v_y = 2 mm/s$, 
+whereas the velocity of the bottom boundary particles is $v_y = 0 mm/s$.
+To reduce dynamic effects due to a sudden loading, a soft loading ramp has been employed as a loading curve. 
+Finally, the model was calibrated with a regularization parameter \gls{Ceps} = 1.7 and a
 bandwidth value \gls{heps} = 15.
@@
 \caption{Crack pattern for different notch inclination angle, and
-  comparison with the experimental results  \cite{LIM_1993}.}
+  comparison with the experimental results  \cite{LIM_1993}. \textcolor{blue}{The results are printed directly on the material points.}}
 \label{fig:Figure-Angle-Forces-test-damage-pattern}
@@
   interpolation (pictures in the left side), and \acrshort{lme}
-  (pictures in the right side). Both simulations performed with an
-  eigenerosion algorithm.}
+  (pictures in the right side). \textcolor{blue}{The results are printed directly on the material points.}}
 \label{fig:Stress-vs-damage-impact-test}
@@
     \begin{equation*}
-      \vec{v}_I^{pred} = \frac{ N_{Ip}^{k} m_p (\vec{v}_p^k + (1 - \gamma)\ \Delta t\ \vec{a}_p^k)}{m_I}
+      \vec{v}_I^{pred} = \textcolor{blue}{\sum_{p\ \in\ \mathcal{C}}} \frac{ N_{I}(\vec{x}_p^k)\  m_p\ (\vec{v}_p^k + (1 - \gamma)\ \Delta t\ \vec{a}_p^k)}{m_I}
     \end{equation*}\;
+    \vspace{-0.5cm}
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
@@
       \Delta \tens{\varepsilon}_{p}^{k+1} = \Delta t\
-        \dot{\tens{\varepsilon}_{p}}^{k+1} = \Delta t\ \left[ \vec{v}_{I}^{pred} \otimes
-        \Grad{N_{Ip}^{k+1}} \right]^s
-    \end{equation*} \;
+        \dot{\tens{\varepsilon}_{p}}^{k+1} =  \textcolor{blue}{\sum_{I\ \in\ \mathcal{B}_p}} \Delta t\ \left[ \vec{v}_{I}^{pred} \otimes
+        \Grad{N_{I}(\vec{x}_p^k)} \right]^s
+    \end{equation*}\;
+    \vspace{-0.5cm}
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
@@
     \end{equation*}\;
+    \vspace{-0.5cm}
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
     \begin{align*}
-      &\vec{a}_p^{k+1} = \frac{N_{Ip}^k\vec{f}_{I}^{k}}{\tens{m}_I^k}\\
-      &\vec{v}_p^{k+1} = \vec{v}_p^n + \Delta t\
-        \frac{N_{Ip}^k\
+      &\vec{a}_p^{k+1} = \textcolor{blue}{\sum_{I\ \in\ \mathcal{B}_p}} \frac{N_{I}(\vec{x}_p^k)\ \vec{f}_{I}^{k}}{\tens{m}_I^k}\\
+      &\vec{v}_p^{k+1} = \vec{v}_p^n + \textcolor{blue}{\sum_{I\ \in\ \mathcal{B}_p}} \Delta t\
+        \frac{N_{I}(\vec{x}_p^k) \
         \vec{f}_{I}^{k}}{\tens{m}_I^k}\\
-      &\vec{x}_p^{k+1} = \vec{x}_p^n + \Delta t\
-         N_{Ip}^k\ \vec{v}_{I}^{k} +
-        \frac{1}{2}\Delta t^2\ \frac{N_{Ip}^k\
+      &\vec{x}_p^{k+1} = \vec{x}_p^n + \textcolor{blue}{\sum_{I\ \in\ \mathcal{B}_p}} \Delta t\
+         N_{I}(\vec{x}_p^k) \ \vec{v}_{I}^{k} + 
+        \frac{1}{2}\Delta t^2\ \frac{N_{I}(\vec{x}_p^k)\
         \vec{f}_{I}^{k}}{\tens{m}_I^k}
     \end{align*}\;
+    \vspace{-0.5cm}
     %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
@@
   \KwOutput{Return damage parameter $\chi = \{\chi_p\}$}
-  % \KwData{Testing set $x$}
+  \KwData{Testing set $x$}
   $\chi_p \leftarrow \chi_p^{k}$ \;
@@
   {
-    \If{$\chi_p = 0$ \And $\epsilon_{f,p} = 0$}
+    \If{$\chi_p = 0$ \textbf{and} $\epsilon_{f,p} = 0$}
     {
@@
       }
-      \ElseIf{$\chi_p \neq 1$ \And $\epsilon_{f,p} > 0$}
+      \ElseIf{$\chi_p \neq 1$  \textbf{and} $\epsilon_{f,p} > 0$}
       {

### 2020-10-06 2020_EFM_MPM_Eigensoftening.tex
Revisión MMP

@@
 \usepackage{cancel}
+\usepackage{textcomp}
 
@@
 However, the presence of cracks is a violation of the continuity requirement of the \acrshort{fem}.
-To overcome this issue, numerous numerical
-\textcolor{red}{artifices}  have been proposed with the aim of reproducing such a
-complex behaviour. These techniques vary from the employment of cohesive
-approaches~\cite{Barenblatt,Hilleborg_1976}, or to the gradual insertion of
-cohesive elements \cite{Ortiz_1999,Pandolfi_2002,Ruiz_2000} at solid
-elements boundaries. To alleviate these shortcomings of the
-\acrshort{fem}, the \acrfull{xfem} in conjunction with level set
+To overcome this issue, numerous numerical \textcolor{red}{artifices} have been proposed with the aim of reproducing such a
+complex behaviour. \textcolor{blue}{An example of this}, is the gradual insertion of
+cohesive elements \cite{Ortiz_1999} at solid elements boundaries. To alleviate these shortcomings of the \acrshort{fem}, the \acrfull{xfem} in conjunction with level set
 technique was introduced by Belytschko {\it et al.}
@@
 set. Some relevant contributions to the \acrshort{xfem} are the
-modeling micro-scale crack propagation \cite{HUANG_2018}, the
-introduction of a cohesive zone model \cite{NAGASHIMA_2016}, and more
-recently improving it capability to predict the crack path in 3D cases
-\cite{YUN_2019}.
-
+modeling micro-scale crack propagation \cite{HUANG_2018} \textcolor{blue}{or} the
+introduction of a cohesive zone model \cite{NAGASHIMA_2016}.\\
 The simulation of fracture propagation in a more accurate and effective
@@
 examples of it are the \acrfull{mpm}
-\cite{Schreyer_2002,Chen_2002,Nairn_2003,Zhenmao_2005}, the
-\acrfull{efgm} \cite{BELYTSCHKO_1995,BELYTSCHKO_2000,Zhuang_2012,Muthu_2013}, the
-\acrfull{sph} \cite{Wang_2020,Wang_2019}, the \acrfull{otm} \cite{Li2010,Li_2012,Pandolfi_2013,Li_2015} or Peridynamics
-\cite{HA_2011,RABCZUK_2017} among others. \\
-
+\cite{Schreyer_2002,Nairn_2003,NAIRN_2018}, the
+\acrfull{efgm}~\cite{BELYTSCHKO_1995b,BELYTSCHKO_2000}, the
+\acrfull{sph}~\cite{Wang_2020,Wang_2019}, the \acrfull{otm}~\cite{Pandolfi_2013,Li_2015} or Peridynamics~\cite{HA_2011,RABCZUK_2017} among others.\\
 Concerning \acrshort{mpm}, fracture has been treated numerically through two different ways.
-On the one hand, the ``CRAcks with Material Points (CRAMP)'' is proposed~\cite{Nairn_2003,Nairn_2006}.
+On the one hand, the ``CRAcks with Material Points (CRAMP)'' is proposed~\cite{Nairn_2003}.
 The basis of this methodology consist of the removal of the restriction
@@
 propagation is based on such parameters as energy release rate
-analysed by Tan \& Nairn (2002)\cite{Nairn_2002}, and the stress
-intensity factor or the J-integral discussed by Guo \& Nairn
-(2004)\cite{Nairn_2004}. 
-On the other hand, the foundation of the second approach is the introduction of failed
-material points to describe the crack evolution. In these methods, the
-formation of failed points describes the nucleation of cracks, and
+analysed by Tan \& Nairn (2002)\cite{Nairn_2002}.
+On the other hand, the foundation of the second approach is the introduction of failed material points to describe the crack evolution.
+In these methods, the formation of failed points describes the nucleation of cracks, and
 thereafter its propagation and branching. Consequently, the position
@@
 prediction of failure evolution is computed with a decohesion model,
-which has been discussed by Chen {\it et al.}\cite{Zhenmao_2005} and
-Schreyer {\it et al.}\cite{Schreyer_2002}. Successful simulations are provided within the framework of the fracture of brittle materials by Chen {\it et
-  al.} \cite{Chen_2002,Chen_2003} and Sulsky \& Schreyer
-\cite{Sulsky_2004}.\\
+which has been discussed by Schreyer {\it et al.}\cite{Schreyer_2002}.
+Successful simulations are provided within the framework of the fracture of brittle materials by Chen {\it et al.} \cite{Chen_2002}.\\
 
@@
 though this approach, the results exhibit an overestimation of tensile
-stress and strain peaks. Furthermore, since the work of Zhang {\it et al.}
-\cite{Zhang_EE_2020} is made with conventional \acrshort{mpm}/\acrshort{gimp}, stress oscillations are to be faced.\\
-
-To overcome the limitations observed in the EigenMPM
-\cite{Zhang_EE_2020}, the present research proposes the eigensoftening
-algorithm developed by Navas {\it et al.}
+stress and strain peaks. Furthermore, since the \textcolor{red}{aforementioned} work is made with conventional \acrshort{mpm}/\acrshort{gimp}, stress oscillations are to be faced.\\
+
+To overcome the limitations observed in the EigenMPM, the present research proposes the eigensoftening algorithm developed by Navas {\it et al.}
 \cite{Navas_2017_ES,Navas2018a} for the \acrshort{otm} framework and
@@
 occurs when particles crosses an element boundary, the work of Molinos~\etal~\cite{Molinos2020} is followed.
-The traditional \acrshort{mpm} technique is enhanced through the \acrfull{lme} approximation technique
-\cite{Arroyo2006} for the spatial discretisation as well as a explicitly \acrshort{mpm} \acrfull{npc} scheme is derived for the time discretisation.\\
+The traditional \acrshort{mpm} technique is enhanced through the \acrfull{lme} approximation technique \cite{Arroyo2006} for the spatial discretisation as well as a explicitly \acrshort{mpm} \acrfull{npc} scheme is derived for the time discretisation.\\
 
@@
 (iii) a Lagrangian advection of the particles. In the present research,
-\textcolor{blue}{the explicit predictor-corrector time integration scheme proposed by Molinos~\etal~\cite{Molinos2020} is adopted}. The
-purpose of this choice is motivated due to its proved robustness and
-stability for dynamic computations. In the first stage, the nodal
-velocity predictor \textcolor{red}{$ \vec{v}_{I}^{pred}$} is computed through
+\textcolor{blue}{the explicit predictor-corrector time integration scheme proposed by Molinos {\it et al.} \cite{Molinos2020} has been adopted.
+The purpose of this choice is motivated due to its proved robustness and stability for dynamic computations, Navas {\it et al.} \cite{Navas2018a}}.
+In the first stage, the nodal velocity predictor \textcolor{red}{$ \vec{v}_{I}^{pred}$} is computed through
 \textcolor{red}{particles} velocities \textcolor{red}{$\vec{v}_p$} and accelerations \textcolor{red}{$\vec{a}_p$} and evaluated
@@
 (2006)\cite{Arroyo2006} as a bridge between finite elements and
-meshfree methods. The key idea under this interpolation technique is
-the interpretation of each nodal value $N_I$ as a
-probability. Related with this definition, two important limits are
-introduced. First the maximum-entropy (\textit{max-ent}) limit, which
-ensures a \textit{unbiased statistical inference} based on the nodal
-data as states the Jayne's\cite{Jaynes1957} principle of
-\textit{maximum entropy}. And second the Delaunay triangulation that
-warranties the \textit{least width} shape function support. To reach
-a compromise between two competing objectives, a Pareto set is
+meshfree methods.
+\textcolor{blue}{The basic idea of the shape functions based on such an estimate is to interpret the shape function $N_I(\vec{x})$ as a probability.
+This allows us to introduce two important limits: the principle of maximum-entropy (\textit{max-ent}) statistical
+inference stated by Jaynes \cite{Jaynes1957}, and the Delaunay triangulation
+which ensures the minimal width of the shape function.}
+
+\textcolor{blue}{This approximation scheme represents an optimal compromise, in the sense of
+Pareto, between the \textit{unbiased statistical inference} based on
+the nodal data which leads to the principle of \textit{Maximum-Entropy}
+stated by Jaynes \cite{Jaynes1957}, and the definition of local shape
+functions of \textit{least width} the least biased shape functions.
+Following \cite{Arroyo2006}, entropy of a discrete random variable can be defined as the uncertainty of the random variable.
+A measure of this uncertainty can be obtained by means of Shannon\textquotesingle s entropy:}
+\begin{equation}
+  \label{eq:Shannon-entropy}
+  \textcolor{blue}{H(p_1,\ldots,p_n) = -\sum^{N_n}_{I=1}{p_I\ \log p_I }}
+\end{equation}
+\textcolor{blue}{where $p_I$ stands for probability of the random variable outcomes.
+By interpreting these probabilities as the shape functions $N_I(\vec{x})$ of an approximation scheme, equation \eqref{eq:Shannon-entropy} can be regarded as a measure of the uncertainty of the approximation.} To reach a compromise between two competing objectives, a Pareto set is
 defined as,
@@
 \acrshort{mpm} framework as an alternative approach to the decohesion
-model \cite{Zhenmao_2005,Schreyer_2002}. The eigensoftening concept
+model \cite{Schreyer_2002}. The eigensoftening concept
 was originally developed by Navas {\it et al.}
@@
   experimental measures show that the eigenerosion algorithm significantly overestimates the tensile stress and the strain peaks, meanwhile eigensoftening captures the forces and crack
-patterns accurately. Furthermore,
-the accuracy of this algorithm has been proven for complex fracture
-patterns such as the ones obtained with fiber \textcolor{red}{reinforced} concrete (FRC),
+patterns accurately.
+Furthermore, the accuracy of this algorithm has been proven for \textcolor{blue}{mixed-mode} fracture patterns such as the ones obtained with fiber \textcolor{red}{reinforced} concrete (FRC),
 \cite{Navas_2018_ES}.\\
@@
 Implementation details can be consulted in \ref{sec:eigens-algor-1}.
+\textcolor{blue}{Unfortunately, this method is not free of pitfalls.
+The first one involves the isotropic model of failure assumption of the eigensofteing, therefore, complex fracture patterns such as delamination can not be simulated.
+A possible solution for this incovenience is the use of anisotropic damage model.
+Regarding this, the current work can be extended following the approach proposed by Nairn~\cite{NAIRN_2018}.
+The second one is handling crack contact.
+After particle fails, the stress tensor of it is enforced to be zero in all the directions, of course, this is a direct consequence of the isotropic model of failure assumption.
+Consequently, a spurious slip condition is enforced in the tangent direction of the crack, also the material loose its toughness to compression in the fracture interface.
+This limitation was noticed earlier by in Pandolfy and Ortiz \cite{Pandolfi_2012} two alternatives to overcome this limitation where briefly discussed.
+Again, the use of an anisotropic damage model~\cite{NAIRN_2018} would overcome this limitation.}
 
@@
 the definition of a numerical tolerance is required for auxiliar
-algorithms like Crossing Number \cite{Shimrat_1962} or Correct
-Even-Odd \cite{Galetzka_et_al_2017}, the proposed methodology adopted herein is linked to the shape function neighbourhood. In order to avoid the aforementioned error prone
+algorithms, the proposed methodology adopted herein is linked to the shape function neighbourhood. In order to avoid the aforementioned error prone
 techniques, we endeavour to exploit the meshfree benefits of
@@
 capability of the eigensoftening algorithm under different kind of
-mixed-mode loading conditions. This capability was assessed previously within a
-\acrshort{otm} implementation \cite{Navas_2018_ES}.
+mixed-mode loading conditions.
 
@@
 
-An interesting case of this experimental test was reported by Zhang {\it et al.} \cite{Zhang_2009,Zhang_2010a}. As in the aforementioned study,
+An interesting case of this experimental test was reported by Zhang {\it et al.} \cite{Zhang_2010a}. As in the aforementioned study,
 an impact hammer of 120.6 kg has been employed in the proposed simulations to drop it at an impact
@@
 in the opposite to the \acrshort{ugimp} shape function, \acrshort{lme}
-allows unstructured grids. This is a remarkable benefit for this kind
+allows unstructured grids \textcolor{blue}{without a considerable effort and computational cost or any additional accommodation}. This is a remarkable benefit for this kind
 of simulations since the majority of the computational effort is
@@
 
-Finally, further improvements of the present research are exposed. The
-algorithm would have the ability to simulate of crack patterns in
-composite material such as steel or carbon fiber reinforced
-concretes\cite{Navas_2018_ES,Ruiz2019}. In addition, the eigensoftening
-approach can be extrapolated to rock fracture in the same manner the
-eigenerosion was~\cite{Wang2017}, taking into account that the
-volumetric stiffness remains in order to support bulk loads. Also the
-benefits of \acrshort{lme} can be exploited by adapting it through the
-deformation gradient \cite{Kochmann2019}. \textit{A priori} this would
-enhance the localisation properties of the proposed algorithms in more
-sophisticated domains. And the implementation of a contact algorithm to model other impact cases such as bullets collisions.
+\textcolor{blue}{Next, further improvements of the present research are exposed.
+Firstly, the eigensoftening approach can be extrapolated to rock fracture in the same manner the eigenerosion was~\cite{Wang2017}, taking into account that the volumetric stiffness remains in order to support bulk loads.
+Secondly, the algorithm would have the ability to simulate of crack patterns in
+composite material such as steel or carbon fiber reinforced concretes by means of empirical definitions of $\chi$ curve~\cite{Navas_2018_ES}.
+However, capturing fracture patters in anisotropic media such as carbon fibre plates requires the redefinition of the approximation towards an anisotropic softening damage model.
+In addition, this improvement also would allows the model to handle crack contact.
+Finally, the implementation of a contact algorithm to model other impact cases such as bullets collisions.}
 

### 2020-10-06 _region_-MacBook Pro de Pedro.tex
Revisión MMP

--- 2020-06-22 _region_.tex
@@
   \centering
-  \includegraphics[width=0.8\textwidth]{Figure-impact-test-Forces-Time}
+  \subfigure[Hammer forces]{\includegraphics[width=0.8\textwidth]{Figure-impact-test-Forces-Time}}
+  \subfigure[Reactions]{\includegraphics[width=0.8\textwidth]{Figure-impact-test-Reactions-Time}}
   \caption{Evolution of the reaction forces plotted \textit{versus}
@@
 
-\message{ !name(2020_EFM_MPM_Eigensoftening.tex) !offset(-1300) }
+%%% Local Variables:
+%%% ispell-local-dictionary: "en_GB"
+%%% End:
+
+\message{ !name(2020_EFM_MPM_Eigensoftening.tex) !offset(-1304) }

### 2020-10-09 Revisiones/MMP_Responses to the reviewers.tex
Cambios PNA

@@
 \usepackage{amsmath}
+\usepackage{textcomp}
 
@@
 The LME-MPM is explained in more detail in an earlier article by the authors.
+In this paper, only several notions are provided.
+This notions have been extended in order to improve the understanding of it
 \\
@@
 
-The correct word is artifices in stead of artifacts. As suggested by the reviewer, a proofreading will be done to improve the English of the manuscript.
+The correct word is "artifices" instead of artifacts. As suggested by the reviewer, a proofreading will be done to improve the English of the manuscript.
 
@@
 
-As reviewer noticed, the Einstein summation convention for repeated indices has been adopted.
+As the reviewer noticed, the Einstein summation convention for repeated indices has been adopted.
 This will be clarified in the revised version of the manuscript.
-Concerning the use of the particle acceleration in the algorithm, this a key part of the Newmark predictor-corrector (NPC) proposed by the authors in Molinos {\it et al.}  \cite{Molinos_2020} (not yet published), this algorithm detailed in the Appendix A.
-Additionally,  since the algorithm proposed in the aforementioned publication was adapted for the MPM from the proposed by Navas {\it et al.} \cite{Navas_2018a} (2018), the reviewer can visit it to get more details about the good performance of the NPC in the dynamic regime.
-In the aforementioned publication, the overall performance of the algorithm in demanding dynamic cases is demonstrated.
+Concerning the use of the particle acceleration in the algorithm, this a key part of the Newmark predictor-corrector (NPC) proposed by the authors in Molinos {\it et al.}  \cite{Molinos_2020} (not yet published).
+This algorithm detailed in the Appendix A.
+Additionally,  since the algorithm proposed in the aforementioned publication was adapted for the MPM from the proposed by Navas {\it et al.} \cite{Navas_2018a} (2018).
+More details of the good performance of the NPC algorithm in the dynamic region can be found in the aforementioned paper.
 To clarify this issue, an additional reference to this work will be incorporated to the revised version of the manuscript.
@@
 
-Authors really appreciate the suggestion of the reviewer to including a cite to the work of J.A.
-Nairn.
+Authors appreciate the suggestion of the reviewer to mention interesting affine works.
 The state of art of the manuscript will be revised to include this research and remove the non necessary references.
 Answering reviewer\textquotesingle s question, the eigensoftening technique is able to handle with both modes I and II.
-Observe equation (14) is formulated in terms of $\sigma_{I}$.
+Observe that equation (14) is formulated in terms of $\sigma_{I}$.
 This is the first component of the stress tensor in the maximum principal stress.
@@
 For instance, it it is well known that a pure shear stress state ($\tau$) can be expressed as a composition of two stress states, one traction ($\sigma_{I} = \tau$) and other compression ($\sigma_{II} = -  \tau$) with principal axes rotated 45$^o$.
-Additionally, as  Navas {\it et al.}  \cite{Navas_2018b} probed by means of qualitative and quantitative comparisons, the eigensofteing is able to deal with mixed modes even with non isotropic materials as the FRC.
-
-However, as the reviewer argues, in order to capture complex behaviours such as delamination, the damage model for concrete must consider the anisotropy of the material in the formulation.
-Therefore, the authors agree with the reviewer that the use of an anisotropic damage model would be an important step forward for the proposed model.
-This pitfall will be clarified and the proposal of an anisotropic damage model will be included in the conclusions as a future research line of the authors.
+Additionally, as  Navas {\it et al.}  \cite{Navas_2018b} proved by means of qualitative and quantitative comparisons, the eigensofteing technique is able to deal with mixed modes even with non isotropic materials as the FRC.
 
@@
 Therefore, we choose the Gaussian quadrature positions to ensure good integration properties at least in the first time steps.
-Of course, in a general scenario, the user has not control over the position of the material points in the following the next time steps.
+Of course, in a general scenario, the user has not control over the position of the material points in the following time steps.
 
@@
 
+However, we agree with the reviewer that in order to capture complex behaviours such as delamination, the damage model for concrete must consider the anisotropy of the material in the formulation.
+Therefore, the authors agree with the reviewer that the use of an anisotropic damage model would be an important step forward for the proposed model.
+This pitfall will be clarified and the proposal of an anisotropic damage model will be included in the conclusions as a future research line of the authors.
+
 \item \textit{Page 19: "Although the traditional MPM implementation allows collision of two bodies, inaccurate energy conservation is obtained without the implementation of a conservative contact algorithm to reproduce the hammer impact in the beam." Well known and many papers are available that do contact in MPM (including many improvements over the two cited in Refs 51 and 52).
@@
 As the reviewer remarks, better results would be obtained if a better contact algorithm is implemented.
-In addition, the implementation of a proper contact algorithm would help to modelise the supports of the concrete beam in a realistic fashion (Section 3.3).
+In addition, the implementation of a proper contact algorithm would help to model the supports of the concrete beam in a more realistic manner (Section 3.3).
 
@@
 The authors appreciate the constructive discussion of the reviewer.
-Extending the eigensoftening algorithm to anisotropic softening seems to be a interesting research line in future.
+Extending the eigensoftening algorithm to anisotropic softening seems to be an interesting research line in the future.
 It will be added to the conclusions.
 Handling crack contact is a current pitfall of the algorithm and will be properly listed in the corrected version of the manuscript.
-Furthermore, in Pandolfi and Ortiz (2012) \cite{Ortiz_Pandolfi_2012} (Section 3.2) two alternatives to overcome this limitation where briefly discussed.
+Furthermore, in Pandolfi and Ortiz (2012) \cite{Ortiz_Pandolfi_2012} (Section 3.2) two alternatives to overcome this limitation were briefly discussed.
 Since the examples proposed in the present research does not involves contact constrain, those improvements were not the focus of our research.
@@
 
-The authors really appreciate the interesting proposal of the reviewer.
+The authors appreciate the interesting proposal of the reviewer.
 We were aware of the work proposed by Steffen {\it et al.} \cite{Steffen_2008} with the B-splines.
 But we were not aware of the possibility of using spline grid shape functions in the uGIMP.
-However, since the aim of this manuscript is  discussing the capabilities of a new fracture algorithm for the MPM, we only considered the linear uGIMP shape functions and the LME approximants to stablish a comparison.
-Nevertheles, the discussion proposed by the reviewer seems to be interesting for a work focused on the computational aspect of the MPM.
+However, since the aim of this manuscript is the discussion of the capabilities of a new fracture algorithm for the MPM, we only considered the linear uGIMP shape functions and the LME approximants to establish a comparison.
+Nevertheless, the discussion proposed by the reviewer seems to be interesting for a work focused on the computational aspect of the MPM.
 
@@
 \textit {The manuscript describes an approach to tackle fracture process in brittle materials.
-Using the material point method as discretization and the eigendeformation concept (in the version devised by one of the authors in his previous contributions), authors propose an efficient algorithm that is illustrated by a few examples of application.
+Using the material point method as discretisation and the eigendeformation concept (in the version devised by one of the authors in his previous contributions), authors propose an efficient algorithm that is illustrated by a few examples of application.
 The paper is well written, the literature adequately acknowledged.
@@
 
-You are right, unnecessary references  and explanations will be removed.
+We agree with the reviewer\textquotesingle s opinion, unnecessary references  and explanations will be removed.
 
@@
 
-The reason is we are not simulating the real hammer used in the experiments.
+The reason lies on the fact that the real hammer, used in the experimental tests, is not reproduced exactly on the simulations in order to avoid to reproduce an enormous hammer compared to the beam.
 In instead of it, we simulated a hammer with two different materials.
-The "head" of the numerical hammer has the same properties like the used in the experiments, the "body" of the numerical hammer has different density and elastic modulus.
+The "head" of the numerical hammer has the same properties as the one used in the experiments, the "body" of the numerical hammer has different density and elastic modulus.
 This approach makes it possible to considerably reduce the length of the numerical hammer and, therefore, the computational cost of the simulation.
-The elastic modulus and density of the second material were calibrated to reproduce accurately the impact, unfortunately after it, the numerical hammer does not behave exactly as the used in the experiments.
+The elastic modulus and density of the second material were calibrated to reproduce accurately the impact, unfortunately after it, the numerical hammer does not behave exactly as the one used in the experiments.
 

### 2020-10-09 2020_EFM_MPM_Eigensoftening.tex
Cambios PNA

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\usepackage{siunitx}
+\usepackage[record,% using bib2gls
+ symbols, % create list of symbols
+ acronym
+]{glossaries-extra}
+
+\GlsXtrLoadResources[
+  src={symbols}, % data in symbols.bib
+  sort-field={name}, % sort by name field
+  sort={letter-nocase}, % case-insensitive letter sort
+  type=symbols, % put these terms in the symbols list
+  field-aliases={unit=symbol}% convert unit key to symbol
+]
+
 % Init glossaries
-\usepackage[acronym]{glossaries}
-\makeglossaries
+%\usepackage[acronym]{glossaries}
+%\makeglossaries
 
@@
 \newacronym{fe}{FE}{Forward Euler}
+\newacronym{cramp}{CRAMP}{CRAcks with Material Points}
 
@@
 
-\title{\textcolor{blue}{Local maximum entropy material point method applied to quasi-brittle fracture.} }
+\title{\textcolor{blue}{Local Maximum Entropy Material Point Method applied to quasi-brittle fracture.} }
 
@@
 \begin{abstract}
-  The objective of this work is to introduce an alternative
+  \textcolor{blue}{This work aims} to introduce an alternative
   technique to address the fracture process of brittle and
@@
   originally for the \acrfull{otm} approximation scheme, is extended
-  to the \acrshort{mpm} with the aim of presenting a suitable alternative
-  to the existing fracture algorithms developed for such a methodology.  The good fitting in the predictions made by
-   the eigensoftening algorithm against both analytical and experimental
-  results \textcolor{red}{proves} the excellent performance of the method when challenging
-  applications are to modeled.
+  to the \acrshort{mpm} \textcolor{blue}{to present} a suitable alternative
+  to the existing fracture algorithms developed for such a methodology. 
+  The good fitting in the predictions made by the eigensoftening algorithm against both analytical and experimental results \textcolor{red}{proves} the excellent performance of the method when challenging applications are to model.
 \end{abstract}
@@
 \linenumbers
-
-\printglossary[type=\acronymtype]
 
@@
 To overcome this issue, numerous numerical \textcolor{red}{artifices} have been proposed with the aim of reproducing such a
-complex behaviour. \textcolor{blue}{An example of this}, is the gradual insertion of
-cohesive elements \cite{Ortiz_1999} at solid elements boundaries. To alleviate these shortcomings of the \acrshort{fem}, the \acrfull{xfem} in conjunction with level set
-technique was introduced by Belytschko {\it et al.}
+complex behaviour.
+\textcolor{blue}{An example of this}, is the gradual insertion of cohesive elements \cite{Ortiz_1999} at solid elements boundaries.
+To alleviate these shortcomings of the \acrshort{fem}, the \acrfull{xfem} in conjunction with level set technique was introduced by Belytschko {\it et al.}
 \cite{Belytschko_03} to handle arbitrary crack paths level
 set. Some relevant contributions to the \acrshort{xfem} are the
-modeling micro-scale crack propagation \cite{HUANG_2018} \textcolor{blue}{or} the
-introduction of a cohesive zone model \cite{NAGASHIMA_2016}.\\
-The simulation of fracture propagation in a more accurate and effective
-way can be considered as one of the ongoing goals of the development of novel spatial discretisation methods like meshfree techniques. Some
-examples of it are the \acrfull{mpm}
-\cite{Schreyer_2002,Nairn_2003,NAIRN_2018}, the
+modeling micro-scale crack propagation \cite{HUANG_2018} \textcolor{red}{or introducing} a cohesive zone model \cite{NAGASHIMA_2016}.\\
+
+\textcolor{blue}{The accurate and effective simulation of fracture propagation can be considered as one of the ongoing goals of the development of novel spatial discretisation methods like meshfree techniques.} Some examples of it are the \acrfull{mpm} \cite{Schreyer_2002,Nairn_2003,NAIRN_2018}, the
 \acrfull{efgm}~\cite{BELYTSCHKO_1995b,BELYTSCHKO_2000}, the
@@
 Concerning \acrshort{mpm}, fracture has been treated numerically through two different ways.
-On the one hand, the ``CRAcks with Material Points (CRAMP)'' is proposed~\cite{Nairn_2003}.
-The basis of this methodology consist of the removal of the restriction
-of the single-valued velocity field close to the crack through, at least, two sets of nodes. In this method, different labels are assigned to the material points
-and nodes to distinguish if they are in the same side of the crack or
-not. Under this approach, crack surface is described with line segments
-in 2D and triangle patches in 3D cases. The chosen criteria for crack
-propagation is based on such parameters as energy release rate
-analysed by Tan \& Nairn (2002)\cite{Nairn_2002}.
-On the other hand, the foundation of the second approach is the introduction of failed material points to describe the crack evolution.
-In these methods, the formation of failed points describes the nucleation of cracks, and
-thereafter its propagation and branching. Consequently, the position
-of the crack does not need to be explicitly stated. This fact represents
-significant advantages over the ``CRAMP''. Under this approach, the
-prediction of failure evolution is computed with a decohesion model,
-which has been discussed by Schreyer {\it et al.}\cite{Schreyer_2002}.
+\textcolor{blue}{One of these approaches is the \acrshort{cramp} technique proposed by Nairn {\it et al.}~\cite{Nairn_2003}.
+The methodology removes the restriction of single-valued for the velocity field close to the crack.
+This is achieved through, at least, two sets of nodes}.
+In this method, different labels are assigned to the material points and nodes to distinguish if they are in the same side of the crack or not.
+Under this approach, crack surface is described with line segments in 2D and triangle patches in 3D cases.
+\textcolor{red}{In \acrshort{cramp}, the} chosen criteria for crack propagation \textcolor{red}{relies on} the energy release rate analysed by Tan \& Nairn~\cite{Nairn_2002}.
+\textcolor{blue}{The second approach is to introduce failure material points to describe the evolution of the crack.} In these methods, the formation of failed points describes the nucleation of cracks and its propagation and branching.
+\textcolor{blue}{Consequently, it is not necessary to state explicitly the position of the crack}.
+This fact represents significant advantages over the \acrshort{cramp}.
+Under this approach, the prediction of failure evolution is computed with a decohesion model.
+\textcolor{blue}{Further discussion about it can be found in Schreyer {\it et al.}\cite{Schreyer_2002}} .
 Successful simulations are provided within the framework of the fracture of brittle materials by Chen {\it et al.} \cite{Chen_2002}.\\
 
-Similar to this approach, Schmidt {\it et al.}
-\cite{Schmidt_2009} introduced the concept of eigenfracture, where
-crack sets are approximated by means of eigen-deformations, which
+Similar to this approach, Schmidt {\it et al.}~\cite{Schmidt_2009} introduced the concept of eigenfracture, where crack sets are approximated by means of eigen-deformations, which
 enable the material to develop displacement jumps at no cost of local
-elastic energy. Later, the eigenerosion approach to brittle fracture
-was carried out by Pandolfi {\it et al.}
-\cite{Pandolfi_2012,Pandolfi_2013}. In this technique, the concept of ``erosion'' of
-the material point is depicted, being the material point able to remain intact or become completely failed or eroded, when no loading
-capacity is bore. This method has been successfully applied to simulate high
+elastic energy.
+\textcolor{blue}{Later, Pandolfi {\it et al.}~\cite{Pandolfi_2012,Pandolfi_2013} proposed the eigenerosion approach to brittle fracture}.
+In this technique, the concept of ``erosion'' of
+the material point is depicted, being the material point able to remain intact or become completely failed or eroded, when no loading capacity is bore. This method has been applied to simulate high
 complex phenomena such as dynamic fragmentation of metals
-\cite{Li_2015}. Recently, Zhang {\it et al.}
+\cite{Li_2015} \textcolor{red}{with good results}. Recently, Zhang {\it et al.}
 \cite{Zhang_EE_2020} adopted the eigenerosion to resolve the dynamic
 fracture of brittle materials in the \acrshort{mpm}
-framework. Nonetheless, when quasi-brittle materials are simulated
-though this approach, the results exhibit an overestimation of tensile
-stress and strain peaks. Furthermore, since the \textcolor{red}{aforementioned} work is made with conventional \acrshort{mpm}/\acrshort{gimp}, stress oscillations are to be faced.\\
+framework.
+\textcolor{blue}{Nonetheless, the results exhibit an overestimation of tensile stress and strain peaks for quasi-brittle materials.
+Furthermore, this approach based on conventional \acrshort{mpm}/\acrshort{gimp} has stress oscillations to solve}.\\
 
@@
 engineered for quasi-brittle materials. Inspired in the concept of the
-crack band model \cite{Bazant83}, since energy dissipation is performed through the softened (or failed) volume, this methodology is able to capture the gradual rather than abrupt
-dissipation of the fracture energy. Moreover, in order to mitigate stress
-oscillations as well as to deal with tensile instabilities, such those that
-occurs when particles crosses an element boundary, the work of Molinos~\etal~\cite{Molinos2020} is followed.
+crack band model \cite{Bazant83}, since energy dissipation \textcolor{red}{occurs} through the softened (or failed) volume, this methodology \textcolor{red}{can} capture the gradual rather than abrupt
+dissipation of the fracture energy.
+Moreover,  \textcolor{blue}{Molinos~\etal~\cite{Molinos2020} proposed a methodology to mitigate stress oscillations and deal with tensile instabilities}.
 The traditional \acrshort{mpm} technique is enhanced through the \acrfull{lme} approximation technique \cite{Arroyo2006} for the spatial discretisation as well as a explicitly \acrshort{mpm} \acrfull{npc} scheme is derived for the time discretisation.\\
@@
 eigenerosion and eigensoftening algorithms are presented in Section
-\ref{sec:2}. Then, both approaches are compared and verified by means of
-comparisons with analytical and experimental results in Section
-\ref{sec:3}. Finally, relevant conclusions are exposed in Section \ref{sec:4}.
+\ref{sec:2}. Then, both approaches are compared and verified \textcolor{red}{through}
+comparisons with analytical and experimental results in Section \ref{sec:3}. Finally, relevant conclusions
+are exposed in Section \ref{sec:4}.
 
@@
 
-The aim of this section is to describe and introduce some special
+\textcolor{red}{This section aims to} describe and introduce some \textcolor{red}{non-standard}
 techniques required to face the fracture problem under the \acrshort{mpm}
@@
 process, where particle data is projected to the grid nodes, (ii) an
-Eulerian step, where balance of momentum equation is expressed as a
-nodal equilibrium equation in a FEM-like procedure, and finally
+Eulerian step, where \textcolor{red}{the} balance of momentum equation is \textcolor{blue}{computed in the set of background nodes}, finally
 (iii) a Lagrangian advection of the particles. In the present research,
-\textcolor{blue}{the explicit predictor-corrector time integration scheme proposed by Molinos {\it et al.} \cite{Molinos2020} has been adopted.
-The purpose of this choice is motivated due to its proved robustness and stability for dynamic computations, Navas {\it et al.} \cite{Navas2018a}}.
+\textcolor{blue}{we adopted the explicit predictor-corrector time integration scheme proposed by Molinos {\it et al.} \cite{Molinos2020}.
+The purpose of this choice is motivated due to its proven robustness and stability for dynamic computations, Navas {\it et al.} \cite{Navas2018a}}.
 In the first stage, the nodal velocity predictor \textcolor{red}{$ \vec{v}_{I}^{pred}$} is computed through
@@
 \end{align}
-The complete pseudo-algorithm it is summarised in \ref{sec:expl-pred-corr}.
+
+\textcolor{blue}{\ref{sec:expl-pred-corr} summarises the complete pseudo-algorithm.}
 
@@
 (0,\infty)$. Notice that $\beta$ has units of $[L]^{-2}$,
-therefore it can be controlled by adjusting a dimensionless
+\textcolor{red}{and} can be controlled by adjusting a dimensionless
 parameter\footnote{To avoid confusion with the \gls{gamma-npc} parameter of
@@
 \end{eqnarray}
-An additional remark concerning the support of the interpolation
-function is that, in practice, the value of $N_I$ decay exponentially following $\exp(-\beta \vec{r}
-)$. In this sense,
+An additional remark concerning the support of the interpolation function is that, in practice, the value of $N_I$ decay exponentially following $\exp(-\beta \vec{r})$. In this sense,
 a good practice is to truncate it under a tolerance  (typically around 10$^{-6}$) that would ensure a reasonable
@@
 \label{sec:2.3}
-Within the context of \acrshort{mpm} formulation, fracture can be
+Within the \textcolor{red}{\acrshort{mpm} formulation context}, fracture can be
 modelled by failing particles according to a suitable failure
@@
 model \cite{Schreyer_2002}. The eigensoftening concept
-was originally developed by Navas {\it et al.}
+was \textcolor{red}{developed initially} by Navas {\it et al.}
 (2017)\cite{Navas_2017_ES} as an extension for quasi-brittle materials
@@
   evaluation of both approaches \cite{Navas_2017_ES} against
-  experimental measures show that the eigenerosion algorithm significantly overestimates the tensile stress and the strain peaks, meanwhile eigensoftening captures the forces and crack
+  experimental measures show that the eigenerosion algorithm significantly overestimates the tensile stress and the strain peaks, Meanwhile eigensoftening captures the forces and crack
 patterns accurately.
-Furthermore, the accuracy of this algorithm has been proven for \textcolor{blue}{mixed-mode} fracture patterns such as the ones obtained with fiber \textcolor{red}{reinforced} concrete (FRC),
+Furthermore, the accuracy of this algorithm has been proven for \textcolor{red}{mixed-mode} fracture patterns such as the ones obtained with fiber \textcolor{red}{reinforced} concrete (FRC),
 \cite{Navas_2018_ES}.\\
@@
 
-The failure criterion consist of considering that a material point is failed
+The failure criterion \textcolor{blue}{considers that a material point fails}
 when $G_p^{k+1}$ surpasses the critical energy release rate that
@@
 point out that, when a material point overpass the critical energy, its
-contribution to the internal forces vector is set to zero, but its
+contribution to the internal forces vector is set to zero. \textcolor{red}{However,} its
 contribution to the mass matrix is preserved.\\
@@
 concentration (higher than tensile strength) appears in quasi-brittle
-materials \cite{Navas_2017_ES}. To overcome this limitation, the
-aforementioned authors proposed the concept of eigensoftening to take
-into account the gradual failure in quasi-brittle materials. The idea
-behind this concept is inspired in the cohesive fracture. This gradual
+materials \cite{Navas_2017_ES}.
+To overcome this limitation, the authors \cite{Navas_2017_ES} proposed the eigensoftening \textcolor{red}{approach} to \textcolor{red}{consider} the gradual failure in quasi-brittle materials.
+\textcolor{blue}{The cohesive fracture inspires the idea behind this concept}.
+This gradual
 failure criterion is plotted in Figure \ref{fig:Damage-ft-wc}, where
@@
   \includegraphics[width=0.5\textwidth]{Figure-Damage}
-  \caption{Scheme of a linear cohesive law, where the shaded area is
+  \caption{Scheme of a cohesive linear law, where the shaded area is
     $G_f$, $f_t$ is the tensile strength, and $w_c$ is the critical
@@
 material points), that relates the crack opening and the residual strength.
-To calculate it, typical shapes of cohesive laws such as linear, bilinear or exponential, may be employed.
+\textcolor{blue}{Typical shapes of cohesive laws such as linear, bilinear or exponential may be employed to calculate it}.
 For the case of a linear softening such the sketched one in the Figure \ref{fig:Damage-ft-wc}, $\chi_p$ is computed as,
@@
 The first one involves the isotropic model of failure assumption of the eigensofteing, therefore, complex fracture patterns such as delamination can not be simulated.
-A possible solution for this incovenience is the use of anisotropic damage model.
+A possible solution for this inconvenience is the use of anisotropic damage model.
 Regarding this, the current work can be extended following the approach proposed by Nairn~\cite{NAIRN_2018}.
 The second one is handling crack contact.
-After particle fails, the stress tensor of it is enforced to be zero in all the directions, of course, this is a direct consequence of the isotropic model of failure assumption.
+After the particle fails, the stress tensor of it is enforced to be zero in all the directions.
+Of course, this is a direct consequence of the isotropic model of failure assumption.
 Consequently, a spurious slip condition is enforced in the tangent direction of the crack, also the material loose its toughness to compression in the fracture interface.
-This limitation was noticed earlier by in Pandolfy and Ortiz \cite{Pandolfi_2012} two alternatives to overcome this limitation where briefly discussed.
+This limitation was noticed earlier by in Pandolfy and Ortiz \cite{Pandolfi_2012} where alternatives to overcome this limitation were briefly discussed.
 Again, the use of an anisotropic damage model~\cite{NAIRN_2018} would overcome this limitation.}
@@
 the definition of a numerical tolerance is required for auxiliar
-algorithms, the proposed methodology adopted herein is linked to the shape function neighbourhood. In order to avoid the aforementioned error prone
-techniques, we endeavour to exploit the meshfree benefits of
-the \acrshort{lme} approximants to introduce a node-linked method. Due
-to the global support of this interpolation technique, the classical
-interpretation of the \acrshort{fem} element typically adopted in
-\acrshort{mpm} simulations is not required anymore. Instead, a linked
-list with the surrounding nodes for each node is defined at the initial
-time. Also, each particle has to be associated with the
-closest node instead of with the belonging element as heretofore has been
-done.
-Now lets define the concept of a particle \textit{tributary nodes} as the
-list of nodes close to it among which the information transfers
-occurs. Once the closest nodes are defined, the particle
-possesses automatically a list of \textit{tributary nodes}. This has two
-immediate benefits: the first one is that shape functions with global
-support as \acrshort{lme} are easier to be implemented,
-and the second one is the increase of the efficiency of the $\epsilon$-neighbourhood
-reconstruction. Regarding this last benefit, since the current
-particle has a \textit{tributary nodes} list assigned to it, and
-consequently each node has a linked list with a set of
-\textit{tributary particles}\footnote{Notice that the list of the
-  particles close to each node is unique for each node and is updated
-  in each time step.} close to it, it is possible to define efficiently a
+algorithms, the proposed methodology adopted herein is linked to the shape function neighbourhood.
+In order to avoid error prone techniques \textcolor{blue}{such those mentioned before}, we endeavour to exploit the meshfree benefits of the \acrshort{lme} approximants to introduce a node-linked method.
+
+\textcolor{blue}{The standard version of the \acrshort{mpm} has a well defined nodal connectivity since the elements in the background mesh are defined locally.
+So far, most implementations of the \acrshort{mpm} relies on this.
+Nevertheless, due to the global support of the \acrshort{lme} approximants, the rigid concept of element connectivity vanish in favour of a more flexible and mesh-free interpretation of the connectivity.
+First, let us define the concept of a particle \textit{tributary nodes}  as the list of nodes close to it among which the information transfers occur.
+To improve computational efficiency, a linked list with the surrounding nodes for each node is defined at the initial time.
+Also, each particle is related with the closest node instead of belonging to an element.
+This is radical change in the way of search algorithm has been implemented heretofore.} Once the closest nodes are defined, the particle possesses automatically a list of \textit{tributary nodes}.
+This has two immediate benefits: the first one is that shape functions with global
+support as \acrshort{lme} are easier to be implemented, and the second one is the increase of the efficiency of the $\epsilon$-neighbourhood
+reconstruction.
+Regarding this last benefit, since the current particle has a \textit{tributary nodes} list assigned to it, and consequently each node has a linked list with a set of \textit{tributary particles}\footnote{Notice that the list of the
+  particles close to each node is unique for each node and is updated in each time step.} close to it, it is possible to define efficiently a
 search list with those particles close to the current particle.
@@
 EighenMPM  has been evaluated with three benchmark tests.
-On the one hand, the benchmark proposed in section \ref{sec:3.1} discuss the presence of stress instabilities provoked by the spatial discretisation.
-For that purpose, two different interpolation techniques, \acrshort{gimp} and \acrshort{lme}, as been compared by carrying out an eigenerosion simulation.
-And on the other hand the inability of the eigenerosion to simulate properly quasi-brittle fracture is discussed in sections \ref{sec:3.2} and \ref{sec:3.3}, where experimental results are compared with numerical ones.
-In the first case comparing with a semicircular bending test and in the second case with a drop-weight impact test.}
+On the one hand, the benchmark proposed in section \ref{sec:3.1} discusses the presence of stress instabilities provoked by the spatial discretisation.
+For that purpose, two different interpolation techniques, \acrshort{gimp} and \acrshort{lme}, has been compared by carrying out an eigenerosion simulation.
+On the other hand the inability of the eigenerosion to simulate quasi-brittle fracture properly is discussed in sections \ref{sec:3.2} and \ref{sec:3.3}, where experimental results are compared with numerical ones.
+The case proposed in section \ref{sec:3.2} is a semicircular bending test, and in section \ref{sec:3.3}, a drop-weight impact test.}
 
@@
 \label{sec:3.1}
-The aim of the problem presented hereinafter is to assess the
-capability of the \acrshort{lme} approximants to improve the result
-\textit{versus} the standard linear interpolation and \acrshort{ugimp}
+The aim of the problem presented \textcolor{red}{in this section} is to assess the
+capability of the \acrshort{lme} approximants to improve the result \textit{versus} the standard linear interpolation and \acrshort{ugimp}
 \cite{Bardenhagen2004}. The application
@@
 critical energy-release rate \gls{Gf} = 0.0001. The absence of units is due to the current
-simulation will not be tested against experimental results, where
-scale factor is relevant, but will be validated against an analytical
-solution provided by Pandolfi \& Ortiz \cite{Pandolfi_2012}. In
-\acrshort{mpm}, two different discretisation are required. On one
-hand, a cartesian grid of nodes is considered with a nodal spacing
-value of 0.025. On the other hand, the plate will be modeled with a
+simulation will not be tested against experimental results, where scale factor is relevant, but will be validated against an analytical
+solution provided by Pandolfi \& Ortiz \cite{Pandolfi_2012}. In \acrshort{mpm}, two different discretisation are required. On one
+hand, a cartesian grid of nodes is considered with a nodal spacing value of 0.025. On the other hand, the plate will be modeled with a
 initial layout of four particles per element and occupying the Gauss
@@
 contrast, \acrshort{lme} simulation does not exhibit these spurious
-oscillations and remains linear until the failure. About the strength,
-linear interpolation produces stiffer results than \acrshort{lme}. This can be attributed to imprecision in the
-stress field due to grid-crossing phenomena. Alternative to
+oscillations and remains linear until the failure.
+About the strength, linear interpolation produces stiffer results than \acrshort{lme}.
+This \textcolor{red}{over stiffening} can be attributed to imprecision in the stress field due to grid-crossing phenomena.
+Alternative to
   \acrshort{lme}, \acrshort{ugimp} shape
@@
 Figure \ref{fig:Reactions-cracked-panel-mode-I} supports this fact since it
-does not exhibit instabilities when particles cross element borders meanwhile these instabilities are found with linear interpolation. Unfortunately, the extended support of this
-kind of shape function interfere with nodes in both sides of the notch,
-producing an undesired ``tie-effect''. This involves in a violation of
-the free border boundary condition in the notch. Possible solutions to this effect
-are the suppression of the elements in the notch, within a CRAMP-like
-method where two pairs of nodes are employed, or reducing the mesh size. With \acrshort{lme}
-approximants these artefacts are not required since it is possible to control the support
-of the shape function reducing the grid-crossing and avoiding the
-``tie-effect'' in the notch at the same time.\\
+does not exhibit instabilities when particles cross element borders meanwhile these instabilities are found with linear interpolation.
+Unfortunately, the extended support of this kind of shape function interfere with nodes in both sides of the notch, producing an undesired ``tie-effect''.
+This involves in a violation of the free border boundary condition in the notch.
+Possible solutions to this effect are the suppression of the elements in the notch, within a CRAMP-like method where two pairs of nodes are employed, or reducing the mesh size.
+With \acrshort{lme} approximants these \textcolor{red}{artifices} are not required since it is possible to control the support of the shape function reducing the grid-crossing and to avoid the``tie-effect'' at the same time.\\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 when particles crosses the boundary of the element in the linear
-case, which is observed at 60 seconds. Although, apparently, the
-differences in the obtained peaks are not extremely significant, it
+case, which is observed at 60 seconds. Although, the differences in the obtained peaks are not extremely significant, it
 can be owing to the aforementioned hookean material
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-An important consideration regarding the presence of oscillations once
-both parts of the panel are separated is observed in Figure
-\ref{fig:Reactions-cracked-panel-mode-I}. These phenomena should not be
-attributed to the eigenerosion algorithm since the fracture process is
-over. They are due to the dynamic nature of the solver: once the
-energy is released dinamically by the crack, the waves propagate
+An important consideration regarding the presence of oscillations once both parts of the panel are separated is observed in Figure \ref{fig:Reactions-cracked-panel-mode-I}.
+These phenomena should not be attributed to the eigenerosion algorithm since the fracture process is over.
+\textcolor{blue}{These oscillations} are due to the dynamic nature of the solver: once the energy is released dinamically by the crack, the waves propagate
 along the domain.
@@
   al.}\cite{Wang_2020} under \acrshort{sph} framework within an
-implicit algorithm. The aim of the test is to examine the predictive
-capability of the eigensoftening algorithm under different kind of
-mixed-mode loading conditions.
+implicit algorithm. \textcolor{red}{The test aims} to examine the predictive capability of the eigensoftening algorithm under different kind of mixed-mode loading conditions.
 
@@
 semicircular specimens with a radius of 47.5 mm and a thickness of
-20 mm, supported by two rollers at a span of 47.5 mm, by
+20 mm, \textcolor{red}{and} supported by two rollers at a span of 47.5 mm, by
 another roller on its top mid-span. Notches with a length of 16.6 mm are
@@
 regular cartesian background grid of 1917 nodes with 1.5 mm of nodal distance
-was generated. The velocity of the top boundary particles is $v_y = 2 mm/s$, 
+was generated. The velocity \textcolor{blue}{of the particles in the top boundary} is $v_y = 2 mm/s$, 
 whereas the velocity of the bottom boundary particles is $v_y = 0 mm/s$.
-To reduce dynamic effects due to a sudden loading, a soft loading ramp has been employed as a loading curve. 
+\textcolor{blue}{This boundary condition has been imposed via a soft loading ramp to ovoid dynamic effects due to a sudden loading}.
 Finally, the model was calibrated with a regularization parameter \gls{Ceps} = 1.7 and a
@@
 
-Figure \ref{fig:Figure-Angle-Forces-test-damage-pattern} shows the
+Figure \ref{fig:Figure-Angle-Forces-test-damage-pattern} \textcolor{red}{compares} the
 comparison of mixed-mode fracture envelope between experiments and
@@
 \ref{fig:Figure-Angle-Forces-test-damage-pattern} demonstrates that
-eigensoftening, combined with \acrshort{mpm}, is able to reproduce this
+eigensoftening, combined with \acrshort{mpm}, \textcolor{red}{can} to reproduce this
 behavior. Therefore, the simulation results predict successfully the
-fracture envelope in experiments and demonstrate the capability of
-the eigensoftening-\acrshort{mpm} model for capturing the fracture
-development under various complex loading conditions. 
+fracture envelope in experiments and \textcolor{red}{highlight} the capability of
+the eigensoftening-\acrshort{mpm} for capturing the fracture development under various complex loading conditions. 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 This section is devoted to proof
-the accuracy of the eigensoftening algorithm within the \acrshort{mpm} framework when the behavior
-of quasi-brittle materials under dynamic loading is simulated. One of the most interesting examples of this
-loading case is the three-point bending test on a concrete notched beam when it is conducted under impact loading.
-Indeed, this experimental test is appropriate to be reproduced numerically with the explicit solver proposed in this paper since
-fracture occurs in a period of milliseconds and waves propagate fast along the high strength
-materials involved in the aforementioned test. Accordingly, small time steps are
-required to achieve a numerically stable simulation.\\
-
-An interesting case of this experimental test was reported by Zhang {\it et al.} \cite{Zhang_2010a}. As in the aforementioned study,
-an impact hammer of 120.6 kg has been employed in the proposed simulations to drop it at an impact
+the accuracy of the eigensoftening algorithm within the \acrshort{mpm} framework when the behavior of quasi-brittle materials under dynamic loading is simulated.
+One of the most interesting examples of this loading case is the three-point bending test on a concrete notched beam when conducted under impact loading.
+Indeed, this experimental test is appropriate to be reproduced numerically with the explicit solver proposed in this paper since fracture occurs in a period of milliseconds and waves propagate fast along the high strength materials involved in the test.
+Accordingly, small time steps are required to achieve a numerically stable simulation.\\
+
+An interesting case of this experimental test was reported by Zhang {\it et al.} \cite{Zhang_2010a}.
+As in \textcolor{red}{this} study, an impact hammer of 120.6 kg has been employed in the proposed simulations to drop it at an impact
 speed of 2640 mm/s. The beam dimensions were 100 mm x 100 mm (B x D)
@@
 described in \cite{Molinos2020} becomes crucial to achieve
-non-spurious results. In fact, standard linear element were tested
+non-spurious results. Standard linear element were tested
 with unsatisfactory results since grid-crossing occurs in the hammer
@@
 captured.
-Although the traditional \acrshort{mpm} implementation allows collision of two bodies, inaccurate energy conservation is obtained without the implementation of a conservative contact algorithm to reproduce the hammer impact in the beam.
+Although the traditional \acrshort{mpm} implementation allows collision of two bodies, inaccurate energy conservation is obtained without \textcolor{red}{implementing} of a conservative contact algorithm to reproduce the hammer impact in the beam.
 Despite the observed discrepancies, this is out of the scope of this
-document, although future research of authors will overcome this
+\textcolor{red}{paper}, although future research of authors will overcome this
 limitation. Similarly, results of support forces will be more
@@
 under the \acrshort{otm} framework. Two additional considerations about
-this results are concerning the interpolation technique. On the one hand,
-in the opposite to the \acrshort{ugimp} shape function, \acrshort{lme}
-allows unstructured grids \textcolor{blue}{without a considerable effort and computational cost or any additional accommodation}. This is a remarkable benefit for this kind
-of simulations since the majority of the computational effort is
-clearly localised in a tiny region of the domain. On the other
-hand, there is the possibility to reduce the shape function support to avoid
-a material point in one side of the crack is affected by those in the
-other side of the crack.
+this results are concerning the interpolation technique.
+
+On the one hand, in the opposite to the \acrshort{ugimp} shape function, \acrshort{lme}
+allows unstructured grids \textcolor{blue}{without a considerable computational cost or any additional accommodation in the formulation.
+This is suitable for those simulations where \textcolor{red}{the majority} of the computation efforts are located in a small region of the domain.}
+On the other hand, there is the possibility of reducing the shape function support to avoid \textcolor{blue}{the ''tie-effect" due to a non-convex domain}.
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-The paper proposes the eigensoftening algorithm in a \acrshort{mpm} framework for quasi-brittle materials to overcome the limitations observed in the EigenMPM \cite{Zhang_EE_2020}.
-The overestimation of tensile
+The paper proposes the eigensoftening algorithm in a \acrshort{mpm} framework for quasi-brittle materials to overcome the EigenMPM \cite{Zhang_EE_2020} limitations. The overestimation of tensile 
 stress and strain peaks in the fracture mechanism of quasi-brittle
@@
 \acrshort{mpm} are faced. Based on the
-EigenMPM approach to fracture, two additional improvements have been proposed in the present research in order to solve the shortcomings of the original concept pointed out in the aforementioned paper \cite{Zhang_EE_2020}.
-
-Firstly, by introducing the concept of eigensoftening to the \acrshort{mpm} framework,
-which allows to consider gradual failure process of each material point. This concept is analogous the softening law which is traditionally employed in the context
+EigenMPM approach to fracture, two additional improvements have been proposed in the present research to solve the shortcomings of the original concept pointed out in  \cite{Zhang_EE_2020}.
+
+Firstly, by introducing the concept of eigensoftening to the \acrshort{mpm} framework \textcolor{blue}{allows capture} the failure process of each material point.
+This concept is analogous the softening law which is traditionally employed in the context
 of cohesive fracture in \acrshort{fem}. Furthermore, this failure
@@
 \textcolor{blue}{Next, further improvements of the present research are exposed.
-Firstly, the eigensoftening approach can be extrapolated to rock fracture in the same manner the eigenerosion was~\cite{Wang2017}, taking into account that the volumetric stiffness remains in order to support bulk loads.
+First, the eigensoftening approach can be extrapolated to rock fracture in the same manner the eigenerosion was~\cite{Wang2017}, taking into account that the volumetric stiffness remains in order to support bulk loads.
 Secondly, the algorithm would have the ability to simulate of crack patterns in
 composite material such as steel or carbon fiber reinforced concretes by means of empirical definitions of $\chi$ curve~\cite{Navas_2018_ES}.
-However, capturing fracture patters in anisotropic media such as carbon fibre plates requires the redefinition of the approximation towards an anisotropic softening damage model.
-In addition, this improvement also would allows the model to handle crack contact.
-Finally, the implementation of a contact algorithm to model other impact cases such as bullets collisions.}
+However, capturing fracture patterns in anisotropic media such as carbon fibre plates requires the redefinition of the approximation towards an anisotropic softening damage model.
+In addition, this improvement would also allow the model to handle crack contact.
+Finally, the implementation of a contact algorithm to model other impact cases such as bullets collisions would improve the accuracy of such problems.}
 

### 2020-10-09 2020_EFM_MPM_Eigensoftening.tex
symbols

@@
 
-\usepackage{siunitx}
-\usepackage[record,% using bib2gls
- symbols, % create list of symbols
- acronym
+\usepackage[symbols,
+  stylemods={tree},% loads glossaries-extra-stylemods to patch styles
+  record % using 'bib2gls'
 ]{glossaries-extra}
 
+% assign titles to group labels:
+\glsxtrsetgrouptitle{latin}{Latin}
+\glsxtrsetgrouptitle{greek}{Greek}
+
 \GlsXtrLoadResources[
-  src={symbols}, % data in symbols.bib
-  sort-field={name}, % sort by name field
-  sort={letter-nocase}, % case-insensitive letter sort
-  type=symbols, % put these terms in the symbols list
-  field-aliases={unit=symbol}% convert unit key to symbol
+ src={symbols-latin},
+ type=symbols,
+ group={latin},% assign group label
+ set-widest,% needed for 'alttree' styles
+ save-locations=false
 ]
+
+\GlsXtrLoadResources[
+ src={symbols-greek},
+ type=symbols,
+ group={greek},% assign group label
+ set-widest,% needed for 'alttree' styles
+ save-locations=false
+]
+
+%\usepackage{siunitx}
+%\usepackage[record,% using bib2gls
+% acronym
+%]{glossaries-extra}
+
+%\GlsXtrLoadResources[
+%  src={symbols}, % data in symbols.bib
+%  sort-field={name}, % sort by name field
+%  sort={letter-nocase}, % case-insensitive letter sort
+%  type=symbols, % put these terms in the symbols list
+%  field-aliases={unit=symbol}% convert unit key to symbol
+%]
 
@@
 
-\newglossaryentry{domain}
-{
-  name=$\varOmega$,
-  description={Continuum domain}
-}
-
-\newglossaryentry{contour}
-{
-  name=$\partial\varOmega$,
-  description={Boundary of the continuum domain $\varOmega$. Also
-    defined as $\Gamma$}
-}
-
-\newglossaryentry{dirichlet-boundary}
-{
-  name=$ \Gamma_d$,
-  description={Essential or Dirichlet boundary conditions over $\partial\varOmega$}
-}
-
-\newglossaryentry{neumann-boundary}
-{
-  name=$ \Gamma_n$,
-  description={Natural or Nemann boundary conditions over $\partial\varOmega$}
-}
-
-\newglossaryentry{a}
-{
-  name=$\vect{a}$,
-  description={First order tensor which describes the acceleration field}
-}
-
-\newglossaryentry{v}
-{
-  name=$\vect{v}$,
-  description={First order tensor which describes the velocity field}
-}
-
-\newglossaryentry{u}
-{
-  name=$\vect{u}$,
-  description={First order tensor which describes the displacement field}
-}
-
-\newglossaryentry{x}
-{
-  name=$\vect{x}$,
-  description={First order tensor which describes the global coordinates field}
-}
-
-\newglossaryentry{xi}
-{
-  name=$\vect{\xi}$,
-  description={First order tensor which describes the local coordinates field}
-}
-
-\newglossaryentry{stress}
-{
-  name=$\tens{\sigma}$,
-  description={Second order tensor which means the Cauchy stress tensor}
-}
-
-\newglossaryentry{strain}
-{
-  name=$\tens{\varepsilon}$,
-  description={Second order tensor which means the Cauchy strain tensor}
-}
-
-\newglossaryentry{Constitutive}
-{
-  name=$\tens{D}$,
-  description={Four order tensor which means the constitutive response
-    of the material}
-}
-
-\newglossaryentry{LME-beta}
-{
-  name=$\beta$,
-  description={Regularization or thermalization parameter of the
-    LME$_{\beta}$ Pareto set}
-}
-
-\newglossaryentry{rho}
-{
-  name=$\rho$,
-  description={Describes the scalar density field}
-}
-
-\newglossaryentry{fc}
-{
-  name=f$_c$,
-  description={Compressive strenght}
-}
-
-\newglossaryentry{ft}
-{
-  name=f$_t$,
-  description={Tensile strenght}
-}
-
-\newglossaryentry{Gf}
-{
-  name=G$_F$,
-  description={Specific fracture energy}
-}
-
-\newglossaryentry{E}
-{
-  name=E,
-  description={Elastic modulus}
-}
-
-\newglossaryentry{nu}
-{
-  name=$\nu$,
-  description={Poisson ratio}
-}
-
-\newglossaryentry{Ceps}
-{
-  name=$C_{\epsilon}$,
-  description={Normalizing constant}
-}
-
-\newglossaryentry{heps}
-{
-  name=$h_{\epsilon}$,
-  description={Band width}
-}
-
-\newglossaryentry{Wc}
-{
-  name=$w_{c}$,
-  description={Critical opening displacement}
-}
-
-\newglossaryentry{gamma-npc}
-{
-  name=$\gamma$,
-  description={Time integration parameter for the \acrshort{npc} algorithm}
-}
-
-\newglossaryentry{gamma-lme}
-{
-  name=$\widehat{\gamma}$,
-  description={Dimensionless parameter to control the value of the
-    thermalization parameter $\beta$ of the \acrshort{lme} shape functions.}
-}
+%\newglossaryentry{domain}
+%{
+%  name=$\varOmega$,
+%  description={Continuum domain}
+%}
+
+%\newglossaryentry{contour}
+%{
+%  name=$\partial\varOmega$,
+%  description={Boundary of the continuum domain $\varOmega$. Also
+%defined as $\Gamma$}
+%}
+
+%\newglossaryentry{dirichlet-boundary}
+%{
+%  name=$ \Gamma_d$,
+%  description={Essential or Dirichlet boundary conditions over $\partial\varOmega$}
+%}
+
+%\newglossaryentry{neumann-boundary}
+%{
+%  name=$ \Gamma_n$,
+%  description={Natural or Nemann boundary conditions over $\partial\varOmega$}
+%}
+
+%\newglossaryentry{a}
+%{
+%  name=$\vect{a}$,
+%  description={First order tensor which describes the acceleration field}
+%}
+
+%\newglossaryentry{v}
+%{
+%  name=$\vect{v}$,
+%  description={First order tensor which describes the velocity field}
+%}
+
+%\newglossaryentry{u}
+%{
+%  name=$\vect{u}$,
+%  description={First order tensor which describes the displacement field}
+%}
+
+%\newglossaryentry{x}
+%{
+%  name=$\vect{x}$,
+%  description={First order tensor which describes the global coordinates field}
+%}
+
+%\newglossaryentry{xi}
+%{
+%  name=$\vect{\xi}$,
+%  description={First order tensor which describes the local coordinates field}
+%}
+
+%\newglossaryentry{stress}
+%{
+%  name=$\tens{\sigma}$,
+%  description={Second order tensor which means the Cauchy stress tensor}
+%}
+
+%\newglossaryentry{strain}
+%{
+%  name=$\tens{\varepsilon}$,
+%  description={Second order tensor which means the Cauchy strain tensor}
+%}
+
+%\newglossaryentry{Constitutive}
+%{
+%  name=$\tens{D}$,
+%  description={Four order tensor which means the constitutive response
+%    of the material}
+%}
+
+%\newglossaryentry{LME-beta}
+%{
+%  name=$\beta$,
+%  description={Regularization or thermalization parameter of the
+%    LME$_{\beta}$ Pareto set}
+%}
+
+%\newglossaryentry{rho}
+%{
+%  name=$\rho$,
+%  description={Describes the scalar density field}
+%}
+
+%\newglossaryentry{fc}
+%{
+%  name=f$_c$,
+%  description={Compressive strenght}
+%}
+
+%\newglossaryentry{ft}
+%{
+%  name=f$_t$,
+%  description={Tensile strenght}
+%}
+
+%\newglossaryentry{Gf}
+%{
+%  name=G$_F$,
+%  description={Specific fracture energy}
+%}
+
+%\newglossaryentry{E}
+%{
+%  name=E,
+%  description={Elastic modulus}
+%}
+
+%\newglossaryentry{nu}
+%{
+%  name=$\nu$,
+%  description={Poisson ratio}
+%}
+
+%\newglossaryentry{Ceps}
+%{
+%  name=$C_{\epsilon}$,
+%  description={Normalizing constant}
+%}
+
+%\newglossaryentry{heps}
+%{
+%  name=$h_{\epsilon}$,
+%  description={Band width}
+%}
+
+%\newglossaryentry{Wc}
+%{
+%  name=$w_{c}$,
+%  description={Critical opening displacement}
+%}
+
+%\newglossaryentry{gamma-npc}
+%{
+%  name=$\gamma$,
+%  description={Time integration parameter for the \acrshort{npc} algorithm}
+%}
+
+%\newglossaryentry{gamma-lme}
+%{
+%  name=$\widehat{\gamma}$,
+%  description={Dimensionless parameter to control the value of the
+%    thermalization parameter $\beta$ of the \acrshort{lme} shape functions.}
+%}
 
@@
 
-\textcolor{blue}{The \acrshort{mpm}~\cite{Sulsky1994} is a meshfree Lagrangian-Eulerian method where the continuum \gls{domain} is discretised with a finite set of material points (also known as particles in this research) $\hat{\Omega} = \{ \vec{x}_p, p \in \mathcal{C} \} \subset \Omega$, where $\mathcal{C} = 1, \ldots, n_p$.
+\textcolor{blue}{The \acrshort{mpm}~\cite{Sulsky1994} is a meshfree Lagrangian-Eulerian method where the continuum $\gls{domain}$ is discretised with a finite set of material points (also known as particles in this research) $\hat{\Omega} = \{ \vec{x}_p, p \in \mathcal{C} \} \subset \Omega$, where $\mathcal{C} = 1, \ldots, n_p$.
 Any particle field such as position, velocity, mass, volume and stress denoted by $\vec{x}_p$, $\vec{v}_p$, $m_p$, $V_p$ and $\tens{\sigma}_p$, respectively, are assigned to each material point.
@@
 %%%%%%%%%%%%%%%%%%%%%%%
-Where \gls{gamma-npc} is an user-defined parameter (typically adopted as
+Where $\gls{gamma-npc}$ is an user-defined parameter (typically adopted as
 0.5), $\tens{m}_I$ represents the lumped mass matrix, and \textcolor{red}{$N_{I}(\vec{x}_p^k) $} is the nodal contribution of the shape function evaluated in the particle
@@
 \textcolor{red}{and} can be controlled by adjusting a dimensionless
-parameter\footnote{To avoid confusion with the \gls{gamma-npc} parameter of
+parameter\footnote{To avoid confusion with the $\gls{gamma-npc}$ parameter of
   the \acrshort{npc}, the dimensionless parameter defined in Arroyo \&
   Ortiz \cite{Arroyo2006} as $\gamma$ will be represent by
-  \gls{gamma-lme} to preserve as much as possible the original notation.},
+  $\gls{gamma-lme}$ to preserve as much as possible the original notation.},
 $\widehat{\gamma}=\beta h^2$, where $h$ is defined as a
@@
 The constitutive model considered in the numerical experiment is a
-linear-elastic Hookean material, whose Young's modulus \gls{E} = 1.06, the Poisson's ratio \gls{nu} = 0.333, and
-critical energy-release rate \gls{Gf} = 0.0001. The absence of units is due to the current
+linear-elastic Hookean material, whose Young's modulus $\gls{E}$ = 1.06, the Poisson's ratio $\gls{nu}$ = 0.333, and
+critical energy-release rate $\gls{Gf}$ = 0.0001. The absence of units is due to the current
 simulation will not be tested against experimental results, where scale factor is relevant, but will be validated against an analytical
@@
     \hline
-    Young's modulus (\gls{E})   & 0.4\  \textcolor{red}{GPa}       \\
-    Poisson ratio (\gls{nu})    & 0.25           \\
-    Density (\gls{rho})         & 1.54\ \textcolor{red}{$\text{g/cm}^3$} \\
-    Tensile strength (\gls{ft}) & 0.6\ \textcolor{red}{MPa}       \\
-    Critical opening displacement (\gls{Wc}) & 0.015\ \textcolor{red}{mm} \\
+    Young's modulus ($\gls{E}$)   & 0.4\  \textcolor{red}{GPa}       \\
+    Poisson ratio ($\gls{nu}$)    & 0.25           \\
+    Density ($\gls{rho}$)         & 1.54\ \textcolor{red}{$\text{g/cm}^3$} \\
+    Tensile strength ($\gls{ft}$) & 0.6\ \textcolor{red}{MPa}       \\
+    Critical opening displacement ($\gls{Wc}$) & 0.015\ \textcolor{red}{mm} \\
     \hline
@@
 \textcolor{blue}{This boundary condition has been imposed via a soft loading ramp to ovoid dynamic effects due to a sudden loading}.
-Finally, the model was calibrated with a regularization parameter \gls{Ceps} = 1.7 and a
-bandwidth value \gls{heps} = 15.
+Finally, the model was calibrated with a regularization parameter $\gls{Ceps}$ = 1.7 and a
+bandwidth value $\gls{heps}$ = 15.
 
@@
 {\it et al.}~\cite{Navas_2017_ES}, being the material properties, such
-as the material density, \gls{rho}, the compressive strenght, \gls{fc},
-the tensile strenght \gls{ft}, the specific fracture energy, \gls{Gf},
-and the elastic modulus \gls{E}, provided in table \ref{tab:concrete-properties}.\\
+as the material density, $\gls{rho}$, the compressive strenght, $\gls{fc}$,
+the tensile strenght $\gls{ft}$, the specific fracture energy, $\gls{Gf}$,
+and the elastic modulus $\gls{E}$, provided in table \ref{tab:concrete-properties}.\\
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 spacing, 1.2 mm, in the middle of the beam and in the impact surface
-of the hammer. For this simulation, \gls{gamma-lme} was fixed to
+of the hammer. For this simulation, $\gls{gamma-lme}$ was fixed to
 1.8, this low value of the regularization parameter smooth high stress
@@
 
-\printglossaries
+%\printglossaries
+\printunsrtglossary[type=symbols,style=alttreegroup,title={List of Symbols}]
 

### 2020-10-09 2020_EFM_MPM_Eigensoftening.tex
symbols

--- 2020-10-09 2020_EFM_MPM_Eigensoftening.tex
@@
 \usepackage{siunitx}
-\usepackage[record,% using bib2gls
- symbols, % create list of symbols
- acronym
-]{glossaries-extra}
-
-\GlsXtrLoadResources[
-  src={symbols}, % data in symbols.bib
-  sort-field={name}, % sort by name field
-  sort={letter-nocase}, % case-insensitive letter sort
-  type=symbols, % put these terms in the symbols list
-  field-aliases={unit=symbol}% convert unit key to symbol
-]
+%\usepackage[record,% using bib2gls
+% acronym
+%]{glossaries-extra}
+
+%\GlsXtrLoadResources[
+%  src={symbols}, % data in symbols.bib
+%  sort-field={name}, % sort by name field
+%  sort={letter-nocase}, % case-insensitive letter sort
+%  type=symbols, % put these terms in the symbols list
+%  field-aliases={unit=symbol}% convert unit key to symbol
+%]
 
 % Init glossaries
-%\usepackage[acronym]{glossaries}
-%\makeglossaries
+\usepackage[acronym]{glossaries}
+\makeglossaries
 
@@
 \printglossaries
+%\printunsrtglossary[type=symbols,style=alttreegroup,title={List of Symbols}]
 

### 2020-11-04 2020_EFM_MPM_Eigensoftening.tex
Updates from Overleaf

@@
 \newacronym{cramp}{CRAMP}{CRAcks with Material Points}
+\newacronym{frc}{FRC}{Fiber Reinforced Concrete}
 
@@
 {
-  name=$ \Gamma_d$,
+  name=$\Gamma_d$,
   description={Essential or Dirichlet boundary conditions over $\partial\varOmega$}
@@
 {
-  name=$ \Gamma_n$,
+  name=$\Gamma_n$,
   description={Natural or Nemann boundary conditions over $\partial\varOmega$}
+}
+
+\newglossaryentry{rho}
+{
+  name=$\rho$,
+  description={Describes the scalar density field}
+}
+
+\newglossaryentry{m}
+{
+  name=$m$,
+  description={Describes the scalar mass field}
 }
@@
   description={Second order tensor which means the Cauchy strain tensor}
+}
+
+\newglossaryentry{strain_q}
+{
+  name=$\delta\epsilon$,
+  description={Effective strain}
 }
@@
 
-\newglossaryentry{rho}
-{
-  name=$\rho$,
-  description={Describes the scalar density field}
-}
-
 \newglossaryentry{fc}
@@
 {
-  name=$C_{\epsilon}$,
+  name=C$_{\epsilon}$,
   description={Normalizing constant}
@@
 
+\newglossaryentry{eps-neighborhood}
+{
+ name=$\epsilon$,
+  description={Neighbourhood size}
+}
+
 \newglossaryentry{heps}
 {
-  name=$h_{\epsilon}$,
+  name=h$_{\epsilon}$,
   description={Band width}
@@
 
+\newglossaryentry{Wn}
+{
+  name=$w_{n}$,
+  description={Current crack opening}
+}
+
 \newglossaryentry{gamma-npc}
@@
   description={Dimensionless parameter to control the value of the
-    thermalization parameter $\beta$ of the \acrshort{lme} shape functions.}
+    thermalization parameter \gls{LME-beta} of the \acrshort{lme} shape functions.}
 }
@@
 \journal{Engineering Fracture Mechanics}
-% \journal{Computers and Structures}
 
@@
 \textcolor{blue}{The \acrshort{mpm}~\cite{Sulsky1994} is a meshfree Lagrangian-Eulerian method where the continuum \gls{domain} is discretised with a finite set of material points (also known as particles in this research) $\hat{\Omega} = \{ \vec{x}_p, p \in \mathcal{C} \} \subset \Omega$, where $\mathcal{C} = 1, \ldots, n_p$.
-Any particle field such as position, velocity, mass, volume and stress denoted by $\vec{x}_p$, $\vec{v}_p$, $m_p$, $V_p$ and $\tens{\sigma}_p$, respectively, are assigned to each material point.
+Any particle field such as position, velocity, mass, stain and stress denoted by \gls{x}, \gls{v}, \gls{m}, \gls{strain} and \gls{stress}, respectively, are assigned to each material point.
+In the present research, any particle quantity is denoted by ($\square_p$).
 In addition to this set of material points, a set of fixed background nodes is introduced to compute the balance of momentum equation.
@@
 definition given by Shannon (1948) \cite{Shannon1948}, the shape
-function width is defined as $U(\vec{x}_p,N_I) \coloneqq
-\sum_I N_I |\vec{x}_p - \vec{x}_I |^2$, and $\beta$ is a
-regularisation o \textit{thermalization} parameter such that for
+function width is defined as $U(\vec{x}_p,N_I) \coloneqq \sum_I N_I |\vec{x}_p - \vec{x}_I |^2$, and \gls{LME-beta} is a regularisation o \textit{thermalization} parameter such that for
 Pareto optimal solutions $\beta \in
-(0,\infty)$. Notice that $\beta$ has units of $[L]^{-2}$,
+(0,\infty)$. Notice that \gls{LME-beta} has units of $[L]^{-2}$,
 \textcolor{red}{and} can be controlled by adjusting a dimensionless
@@
 strains are not involved in the present research, Newton-Raphson is an
-enough efficient method. For an uniform nodal spacing, $\beta$ can be
+enough efficient method. For an uniform nodal spacing, \gls{LME-beta} can be
 considered constant, thus first derivatives of the interpolation technique $\nabla
@@
 patterns accurately.
-Furthermore, the accuracy of this algorithm has been proven for \textcolor{red}{mixed-mode} fracture patterns such as the ones obtained with fiber \textcolor{red}{reinforced} concrete (FRC),
-\cite{Navas_2018_ES}.\\
+Furthermore, the accuracy of this algorithm has been proven for \textcolor{red}{mixed-mode} fracture patterns such as the ones obtained with \textcolor{red}{\acrfull{frc}}, \cite{Navas_2018_ES}.\\
 
@@
 \end{align}
-where $B_{\epsilon}(x_p^{k+1})$ is a $^n$dimensional sphere of radius $\epsilon$
+where $B_{\epsilon}(x_p^{k+1})$ is a $^n$dimensional sphere of radius \gls{eps-neighborhood}
 centered at $x_p^{k+1}$. The particles which lie under this sphere are
-known as the $\epsilon$-neighborhood of the material point (see
+known as the \gls{eps-neighborhood}-neighborhood of the material point (see
 \cite{Pandolfi_2012}). This concept is conveniently sketched in
@@
   \caption{Scheme of a linear cohesive law, where the shaded area is
-    $G_f$, $f_t$ is the tensile strength, and $w_c$ is the critical
+    \gls{Gf}, \gls{ft} is the tensile strength, and \gls{Wc} is the critical
     opening displacement.}
@@
 current free-energy density per unit mass  $W_q^{k+1}$ and the
-normalizing constant $C_{\epsilon}$, which also defines the
-  $\epsilon$-neighborhood size, being $\epsilon = C_\epsilon h$, and
-  $h$ is a measure of the distance between nodes.
+normalizing constant \gls{Ceps}, which also defines the \gls{eps-neighborhood}-neighborhood size, being $\epsilon = C_\epsilon h$, and $h$ is a measure of the distance between nodes.
 
@@
 when $G_p^{k+1}$ surpasses the critical energy release rate that
-measures the material-specific energy, $G_F$. The convergence of this
+measures the material-specific energy, \gls{Gf}. The convergence of this
 approach has been analyzed by Schmidt {\it et al.}
-(2009)\cite{Schmidt_2009}, who proved that $G_F$ converges to the Griffith
+(2009)\cite{Schmidt_2009}, who proved that \gls{Gf} converges to the Griffith
 fracture when the discretisation size tends to zero. It is necessary to
@@
 concept earlier described. In the picture, the shaded region represents
-the static fracture energy per unit of area, $G_F$. Notice how a
-cohesive crack appears when the maximum tensile strength, $f_t$, is
-reached. Once the crack, $w_n$, reaches the value of the critical
-crack opening, $w_c$, a stress-free crack is attained.
+the static fracture energy per unit of area, \gls{Gf}. Notice how a
+cohesive crack appears when the maximum tensile strength, \gls{ft}, is
+reached. Once the crack, \gls{Wn}, reaches the value of the critical
+crack opening, \gls{Wc}, a stress-free crack is attained.
 %%%%%%%%%%%
@@
   \caption{Scheme of a cohesive linear law, where the shaded area is
-    $G_f$, $f_t$ is the tensile strength, and $w_c$ is the critical
+    \gls{Gf}, \gls{ft} is the tensile strength, and \gls{Wc} is the critical
     opening displacement.}
@@
 this allows to quantify the variation of the averaged strain energy density in the
-$\epsilon$-neighborhood of the material point $\vec{x}_p^{k+1}$ as
+\gls{eps-neighborhood}-neighborhood of the material point $\vec{x}_p^{k+1}$ as
 \begin{equation}
@@
 where $\tens{\sigma}_{q,I}$ is the maximum principal stress of each
-material point in the $\epsilon$-neighborhood. At this point, an \textit{effective} strain $\varepsilon_q$ is introduced in order to obtain the variation of
+material point in the \gls{eps-neighborhood}-neighborhood. At this point, an \textit{effective} strain \gls{strain_q} is introduced in order to obtain the variation of
 the local strain energy as $\delta W_q = \sigma_{q,1}
-\delta\varepsilon_q$. Now, with the assumption that the effective
+\delta\epsilon_q$. Now, with the assumption that the effective
 strain of each material point at every time step is constant in the
@@
   \delta W_{\epsilon,p} =
-  \frac{\delta \tens{\epsilon}_p}{m_p} \sum_{x_q^{k+1} \in
+  \frac{\delta\tens{\epsilon}_p}{m_p} \sum_{x_q^{k+1} \in
   B_{\epsilon}(x_p^{k+1})} m_q \tens{\sigma}_{q,I}. 
@@
 strain as $\delta W_{\epsilon,p} =
- \tens{\sigma}_{\epsilon,p}\ \delta\varepsilon_p$. The softening behaviour is
+ \tens{\sigma}_{\epsilon,p}\ \delta\epsilon_p$. The softening behaviour is
 activated once $\tens{\sigma}_{\epsilon,p}^{k+1}$ surpasses the
-tensile strength, $f_t$. This consists of a reduction of the internal
+tensile strength, \gls{ft}. This consists of a reduction of the internal
 forces as, 
@@
 Bazant~\cite{Bazant83}, Navas {\it et al.} \cite{Navas_2018_ES}
-\cite{Navas_2017_ES} introduced a band width parameter $h_{\epsilon}$ in order to relate the crack opening with the strain.
+\cite{Navas_2017_ES} introduced a band width parameter \gls{heps} in order to relate the crack opening with the strain.
 Concerning this parameter, a typical value between two and
@@
 $\varepsilon_{\epsilon,f}$ can be represented as the current crack
-opening $w_n$ within the band width $h_{\epsilon}$. Therefore, 
+opening \gls{Wn} within the band width \gls{heps}. Therefore, 
 \begin{equation}
@@
     \hline
-      &   $\rho$   & $\text{f}_c$ & $\text{f}_t$ & $G_F$ &   E   & $\text{d}_{max}$ \\
+      &   $\rho$   & $\text{f}_c$ & $\text{f}_t$ & \gls{Gf} &   E   & $\text{d}_{max}$ \\
       & (kg/m$^3$) &     (MPa)    &     (MPa)    & (N/m) & (GPa) & (mm) \\
@@
   \DontPrintSemicolon
-  \KwInput{For each $p$, $\epsilon$-neighbourhood, $f_{t,p}$, $h_{\epsilon,p}$, $w_c$}
+  \KwInput{For each $p$, $\epsilon$-neighbourhood, $f_{t,p}$, $h_{\epsilon,p}$, \gls{Wc}}
   \KwOutput{Return damage parameter $\chi = \{\chi_p\}$}
